### 2022-05-11 paper/paper.Rmd
Initial commit

---
title: Automatically drawing vegetation maps using digital time-lapse cameras in alpine ecosystems
authors:
  - name: Ryotaro Okamoto
    thanks: https://github.com/0kam
    department: Doctoral Program in Biology
    affiliation: University of Tsukuba
    location: 1-1-1 Tennodai, Tsukuba, Ibaraki 305-8577 Japan. 
    email: okamoto.ryotaro.su@alumni.tsukuba.ac.jp
  - name: Hiroyuki Oguma
    department: Biodiversity Division
    affiliation: National Institute for Environmental Studies
    location: 16-2 Onogawa, Tsukuba, Ibaraki 305-8506 JAPAN
    email: oguma@nies.go.jp
  - name: Reiko Ide
    department: Earth System Division
    affiliation: National Institute for Environmental Studies
    location: 16-2 Onogawa, Tsukuba, Ibaraki 305-8506 JAPAN
    email: ide.reiko@nies.go.jp
abstract: |
  Enter the text of your abstract here.
keywords:
  - alpine ecology
  - deep learning
  - ecosystem monitoring
bibliography: references.bib
biblio-style: unsrt
output: rticles::arxiv_article

header-includes:
  - \usepackage{amsmath}
  - \setlength{\parindent}{10.5pt}
---

```{r setup, include=FALSE}
library(tidyverse)
library(gtsummary)
translate_classes <- function(names) {
  res = c()
  for (i in 1:length(names)) {
    res[i] <- 
      switch (names[i],
              "コケモモ-ハイマツ群集" = "Dwarf Pine",
              "ササ群落" = "Dwarf Bamboo",
              "その他植生" = "Other Vegetations",
              "裸地等" = "Non Vegetation",
              "空" = "Sky",
              "macro avg" = "Macro Average",
              "weighted avg" = "Weighted Average"
      )
  }
  return(res)
}

vegetation_levels = c(
  "Macro Average",
  "Weighted Average",
  "Dwarf Pine",
  "Dwarf Bamboo",
  "Other Vegetations",
  "Non Vegetation",
  "Sky"
)
```

# Introduction
  The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (IPCC 2007). Alpine vegetation depends on severe climatic conditions such as low temperatures and long snow-covered periods. Thus alpine areas have rare and unique species adapted to the extreme environments. Several studies have reported that recent global climatic changes, e.g., increasing temperatures and reducing snow-covered periods, have accelerated the invasion of non-native species into alpine areas (see Alexander et al., 2016). In Japan, dwarf bamboo (*Sasa kurilensis*) has invaded alpine snow meadows, probably driven by the extension of the snow-free period (Kudo et al., 2011). Also, climate change has affected the growth and phenologies of native species. For example, the growth of dwarf pine (*Pinus pumila*), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (Amagai et al., 2015). Monitoring and predicting such changes are essential for effective conservation planning. Since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (Kudo et al., 2010), spatially high-resolution monitoring with a wide range is required.

Previous studies have mainly depended on field observations, yet it is hard to cover broad areas in alpine regions due to poor accessibility and severe weather. Satellite, airborne, and Unmanned Aerial Vehicle (UAV) remote sensing methods seem to be alternatives. However, satellite imageries of alpine areas are rarely available due to cloud cover, and the spatial resolution is not enough to observe vegetation changes at the plant community scale. Airborne imageries can obtain high-resolution data, but its cost becomes a bottleneck for frequent monitoring. Although UAV methods have become popular as a cost-effective tool for ecological monitoring (citation), operating UAVs in alpine regions is challenging due to the strong wind and harsh topology.

On the other hand, researchers have also utilized automated digital time-lapse cameras mounted on the ground for monitoring green-leaf phenologies in forests (Richardson et al., 2018), grasslands (Browning et al., 2017) and alpine meadows (Ide and Oguma, 2013). Unlike satellite imageries, such cameras provide images free of clouds and atmospheric effects. Also, they can obtain high-resolution (i.e., sub-meter scale) and frequent (i.e., daily or hourly) images at a meager cost. These studies set some regions of interest (ROI) in the images and calculate the phenology index (e.g., excess greenness, Woebbecke et al., 1995) for each ROI. While we can visually interpret the vegetation distribution and its changes from a set of such time-lapse images, few studies have tackled this. This lack seems to be because applying such time-lapse imageries in monitoring vegetation distribution has two technical challenges.

First, unlike multispectral sensors satellites equip, digital cameras can only obtain three bands (Red, Green, and Blue), making it harder to classify the vegetation. Second, since digital time-lapse cameras are mounted on the ground, applying geo-spatial analysis to these images is challenging. In other words, even if we find a vegetation change, we cannot identify its geographic location and analyze it with topological data. Treating ground-based time-lapse images as geographic data is essential for utilizing these in conservation planning.

This study proposes an automated method for drawing vegetation maps and locating vegetation changes with a digital time-lapse camera by solving these two challenges. We aim to use cheap but powerful digital time-lapse cameras in alpine ecosystem conservation.

# Materials and methods  
## Digital time-lapse camera imagery   
We used repeat photography data owned by National Institute for Environmental Studies, Japan (NIES). All the images are publically available on NIES' webpage (https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2). In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt. Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps. The camera takes one photograph per hour, from 6 a.m. to 7 p.m. . The camera's field of view (FOV) includes Mt. Tateyama, which ranges from about 2350 m a.s.l. to 3015 m a.s.l. in elevation. The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines. From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen, deciduous dwarf trees (e.g., Pinus pumila, Sorbus sp), dwarf bamboos (e.g., Sasa kurilensis), and alpine herbaceous plants (e.g., Geum pentapetalum, Nephrophyllidium crista-galli). We pulled the images from late summer to late fall of 2010 and 2020.

## Preprocessing  
### Selecting images   
First, we selected images that are suitable for vegetation classification. We choose four days with good weather from late summer to late fall each year (9/19, 10/1, 10/11, 10/23 in 2010. 9/19, 10/2, 10/11, 10/23 in 2020). We used the images of this season because we can separate vegetation from the patterns of autumn foliage coloration. Then we pull four images from 11 a.m. to 2 p.m. each day to avoid the effect of temporal noise such as shadows. Finally, we got 16 images for each year.

### Automatic image-to-image alignment  
Since images are slightly misaligned with each other due to wind, we aligned them before processing. We implemented the program with Python3 language and OpenCV4 image processing library. First, we set one image of 2010 as the alignment target. Next, we automatically found matching keypoints between the target and other images using AKAZE local feature extractor and K-nearest neighbor matcher. Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points.

## Automatic vegetation classification  
Next, we classified the pixel time series of repeat photography imageries into vegetations. Because deciduous plants have great differences in autumn phenology among species, researchers have used that information for vegetation classification with satellite imageries (e.g., Tigges et al., 2013, Son et al., 2014, Heupel et al., 2018). In our target area, we can recognize the vegetation type with the pixel time series of autumn (Fig. 2). However, no research has applied this technique to ground-based repeat photography imageries. We developed a deep-learning method to take advantage of high-resolution and frequent repeat photography data. Fig.3 shows the classification process.

### Model Architecture  
Since ground-based photographs can provide high spatial resolution (about ~ 0.5m in our dataset), we can use leaf texture as additional information for classification. For example, we can see a glossy surface on dwarf bamboos and a mat surface on dwarf pines. Thus, we used a small patch (9x9 pixels square) rather than a single pixel as an input of the model. Therefore, a model input is a time series of image patches. Our model has two components to deal with this data structure (see Fig. 3). First, we extracted each patch's features (e.g., texture) using Convolutional Neural Network (CNN) layers (Fig. 4a). CNN is a neural network specialized in recognizing spatial structures of data, such as images. The CNN part outputs a time series of extracted features. Second, we used Recurrent Neural Net (RNN) layers (Fig. 4b) to classify the temporal patterns of the features extracted by the CNN part. RNN is a neural network specialized in recognizing temporal or sequential data dynamics, such as text and speech. Amongst many variants of RNN, we used Long Short Time Memory (LSTM). Combining CNN and RNN, our model can classify the input image-patch time series considering the colors and textures of each patch and their temporal patterns. This CNN-RNN architecture has also been used for audio classification. Using a Deep Learning method has another positive side effect; mini-batch training. Since we used high-resolution images (16 x 21M pix), the training dataset became so immense that we could not feed them to the model at once: that consumes the computer's RAM too much. However, using Deep Learning methods enables us to provide them in small portions (called mini-batches) to save RAM consumption.

### Implementation and model training  
We implemented the classifier with Python3 language and PyTorch deep neural network library. All source codes are publically available via GitHub (https://github.com/0kam/xxxx).

### Dataset preparation  
We set 5 classes: dwarf pine, dwarf bamboo, other vegetation, no vegetation, and sky. Using free image annotation software (Semantic Segmentation Editor), an expert prepared teacher data (Fig. x) for classification.

# Automatic georectification  
Then, we developed a novel method to convert ground-based landscape imagery into GIS-ready geographical data. This process is called georectification. Georectification of ground-based images has been a difficult task, and this causes the underuse of potentially rich information in ground-based imageries. In plain words, georectification means aligning images into Digital Surface Models (DSMs) so that every pixel of an image gets a geographical coordinate. We can consider a camera as a function that transforms 3D geographical coordinates (latitude, longitude, height) into 2D image coordinates (locations of each pixel). So estimating the parameters of this function (such as the camera location, pose, and the field of view), we can align an image to a DSM. Usually, georectification has three steps:
1. Finding Ground Control Points (GCPs) in the image.
2. Estimating camera parameters such as camera poses and field of view using GCPs.
3. Mapping the image onto the DSM using camera parameters.

Recently, researchers have developed some georectification methods to use ground-based photographs in glaciology (Messerli and Grinsted 2015) and snow cover studies (Portnier et al. 2020). Especially, Portnier et al. 2020 is worth mentioning for its semi-automatic method using mountain silhouettes as GCPs. However, this silhouette-based method has a drawback in the projection accuracy. It only uses limited areas (silhouettes) of images in the image-to-DSM alignment, and also it ignores lens distortion. Because our target site has a complex vegetation distribution and our camera has considerable lens distortion, we needed a more accurate method.

## Local-feature-based matching of images and DSMs  
To get matching points between images and DSMs on a broader area, we used an airborne image already georectified. Combining an airborne image and a DSM, we rendered simulated landscape images (Fig. x). Then we got matching points (GCPs) by applying AKAZE local feature matcher to a target image and this simulated image (Fig. x). GCPs have geographical coordinates (from the DSM) and image coordinates (from the image). Our procedure requires the camera's exact location and initial camera parameters to render the simulated image.

## Modeling and estimating lens distortions  
We modeled the lens distortion based on Weng et al. 1992 and OpenCV's implementation (Eq. 1). Our model includes radial (k1~k6), tangental (p1, p2), thin prism (s1~s4) distortion, and unequal pixel aspect ratio (a1, a2). See Weng et al. 1992 for lens distortion modeling. Also, we recommend readers to Portnier et al. 2020 for camera models without lens distortions. Thus, now we can project GCPs' geographical coordinates into image coordinates using lens distortion parameters and other camera parameters (the camera location, pose, and the field of view). We optimized these (except camera location) by minimizing the square projection error of the GCPs using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES). We could not estimate the camera location because it makes the problem too complicated (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).

$$
\begin{bmatrix}
{x}'' \\ 
{y}'' 
\end{bmatrix} 
= 
\begin{bmatrix} 
x’ \frac{1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + k_4 r^2 + k_5 r^4 + k_6 r^6} + 2 p_1 x’ y’ + p_2(r^2 + 2 x’^2) + s_1 r^2 + s_2 r^4 \\ 
y’ \frac{1 + a_1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + a_2 + k_4 r^2 + k_5 r^4 + k_6 r^6} + p_1 (r^2 + 2 y’^2) + 2 p_2 x’ y’ + s_3 r^2 + s_4 r^4 \ \end{bmatrix}
$$

## Implementation and data set  
We implemented the algorithm with Python3 language and published it as an open-source package via GitHub (https://github.com/0kam/alproj). You can try it with your data. We used an airborne photograph taken in the November of 201X with a spatial resolution of 1.0 m. Also, we used the 5m resolution Digital Elevation Model provided by the Geospatial Information Authority of Japan (GSI) as a DSM.

# Results

## Vegetation classification accuracy

```{r plot_vegetation_acc, echo=FALSE, message=FALSE, fig.width=4, fig.height=3}
df <- read_csv("../runs/cnn_lstm9x9_cv_5_ep_200/staritfied_cv.csv",
               col_select = c(metrics, vegetation, value, fold))
theme_gtsummary_mean_sd()
df %>%
  filter(metrics != "support") %>%
  mutate(vegetation = translate_classes(vegetation)) %>%
  mutate(vegetation = factor(vegetation, levels = vegetation_levels)) %>%
  pivot_wider(names_from = metrics, values_from = value) %>%
  select(-fold) %>%
  tbl_summary(
    by = c(vegetation),
    label = list(
      precision ~ "Precision",
      recall ~ "Recall",
      `f1-score` ~ "F1 Score")
  ) %>%
  modify_header(label = "")

```

## Georectification accuracy

## Vegetation maps

## Detection and localization of vegetation changes

# Discussion   
We suggested a fully automated procedure to transform time-lapse imagery into georeferenced vegetation maps at a meager cost. This task is challenging because of 1. the difficulty of classifying vegetations with ordinal digital camera imagery and 2. the difficulty of georectification. We solved these issues by 1. using the temporal information of autumn leaf colors for vegetation classification and 2. developing a novel method for accurate image georectification. Our vegetation classification performance (with an accuracy of 0.87) and georectification methods (with an RMSE of $rmse$ m) are practical.

## The benefit of using time-series imagery for vegetation classification  
One of the shortcomings of ordinal digital cameras is that they only have three bands (Red, Blue, and Green). We made up for this lack of information by using the rich temporal information that time-lapse cameras can obtain. Many plant species have characteristic phenologies, such as flowering and autumn foliages. Observing this requires long-term (such as year-round) monitoring with a high frequency, and digital time-lapse cameras are suitable. This study only focused on the two species (dwarf bamboo and stone pine) that are easy to classify, even with a single image. However, like the previous studies (Tigges et al., 2013, Son et al., 2014, Heupel et al., 2018), we expect our method to classify more vegetations (e.g., dwarf deciduous trees and alpine herbaceous plants) using the temporal information of leaf colors. 
We also used hourly images for each day. Fig. x shows that this additional information made our model robust against transient noises, such as shadows. Since alpine ecosystems have rough topologies, shadows are a considerable problem. Time-lapse cameras are also beneficial for this reason.

## The performance of our georectification method and its limitation.

## Future application and conclusion

### 2022-05-11 paper/paper.tex
Initial commit

--- 2022-05-11 paper/paper.Rmd
@@
----
-title: Automatically drawing vegetation maps using digital time-lapse cameras in alpine ecosystems
-authors:
-  - name: Ryotaro Okamoto
-    thanks: https://github.com/0kam
-    department: Doctoral Program in Biology
-    affiliation: University of Tsukuba
-    location: 1-1-1 Tennodai, Tsukuba, Ibaraki 305-8577 Japan. 
-    email: okamoto.ryotaro.su@alumni.tsukuba.ac.jp
-  - name: Hiroyuki Oguma
-    department: Biodiversity Division
-    affiliation: National Institute for Environmental Studies
-    location: 16-2 Onogawa, Tsukuba, Ibaraki 305-8506 JAPAN
-    email: oguma@nies.go.jp
-  - name: Reiko Ide
-    department: Earth System Division
-    affiliation: National Institute for Environmental Studies
-    location: 16-2 Onogawa, Tsukuba, Ibaraki 305-8506 JAPAN
-    email: ide.reiko@nies.go.jp
-abstract: |
-  Enter the text of your abstract here.
-keywords:
-  - alpine ecology
-  - deep learning
-  - ecosystem monitoring
-bibliography: references.bib
-biblio-style: unsrt
-output: rticles::arxiv_article
+\documentclass{article}
 
-header-includes:
-  - \usepackage{amsmath}
-  - \setlength{\parindent}{10.5pt}
----
+\usepackage{arxiv}
 
-```{r setup, include=FALSE}
-library(tidyverse)
-library(gtsummary)
-translate_classes <- function(names) {
-  res = c()
-  for (i in 1:length(names)) {
-    res[i] <- 
-      switch (names[i],
-              "コケモモ-ハイマツ群集" = "Dwarf Pine",
-              "ササ群落" = "Dwarf Bamboo",
-              "その他植生" = "Other Vegetations",
-              "裸地等" = "Non Vegetation",
-              "空" = "Sky",
-              "macro avg" = "Macro Average",
-              "weighted avg" = "Weighted Average"
-      )
-  }
-  return(res)
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
+\usepackage{graphicx}
+
+\title{Automatically drawing vegetation maps using digital time-lapse
+cameras in alpine ecosystems}
+
+\author{
+    Ryotaro Okamoto
+    \thanks{\url{https://github.com/0kam}}
+   \\
+    Doctoral Program in Biology \\
+    University of Tsukuba \\
+  1-1-1 Tennodai, Tsukuba, Ibaraki 305-8577 Japan. \\
+  \texttt{\href{mailto:okamoto.ryotaro.su@alumni.tsukuba.ac.jp}{\nolinkurl{okamoto.ryotaro.su@alumni.tsukuba.ac.jp}}} \\
+   \And
+    Hiroyuki Oguma
+   \\
+    Biodiversity Division \\
+    National Institute for Environmental Studies \\
+  16-2 Onogawa, Tsukuba, Ibaraki 305-8506 JAPAN \\
+  \texttt{\href{mailto:oguma@nies.go.jp}{\nolinkurl{oguma@nies.go.jp}}} \\
+   \And
+    Reiko Ide
+   \\
+    Earth System Division \\
+    National Institute for Environmental Studies \\
+  16-2 Onogawa, Tsukuba, Ibaraki 305-8506 JAPAN \\
+  \texttt{\href{mailto:ide.reiko@nies.go.jp}{\nolinkurl{ide.reiko@nies.go.jp}}} \\
   }
 
-vegetation_levels = c(
-  "Macro Average",
-  "Weighted Average",
-  "Dwarf Pine",
-  "Dwarf Bamboo",
-  "Other Vegetations",
-  "Non Vegetation",
-  "Sky"
-)
-```
+% tightlist command for lists without linebreak
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
-# Introduction
-  The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (IPCC 2007).
-Alpine vegetation depends on severe climatic conditions such as low temperatures and long snow-covered periods.
-Thus alpine areas have rare and unique species adapted to the extreme environments.
-Several studies have reported that recent global climatic changes, e.g., increasing temperatures and reducing snow-covered periods, have accelerated the invasion of non-native species into alpine areas (see Alexander et al., 2016).
-In Japan, dwarf bamboo (*Sasa kurilensis*) has invaded alpine snow meadows, probably driven by the extension of the snow-free period (Kudo et al., 2011).
-Also, climate change has affected the growth and phenologies of native species.
-For example, the growth of dwarf pine (*Pinus pumila*), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (Amagai et al., 2015).
-Monitoring and predicting such changes are essential for effective conservation planning.
-Since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (Kudo et al., 2010), spatially high-resolution monitoring with a wide range is required.
+% From pandoc table feature
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 
-Previous studies have mainly depended on field observations, yet it is hard to cover broad areas in alpine regions due to poor accessibility and severe weather.
-Satellite, airborne, and Unmanned Aerial Vehicle (UAV) remote sensing methods seem to be alternatives.
-However, satellite imageries of alpine areas are rarely available due to cloud cover, and the spatial resolution is not enough to observe vegetation changes at the plant community scale.
-Airborne imageries can obtain high-resolution data, but its cost becomes a bottleneck for frequent monitoring.
-Although UAV methods have become popular as a cost-effective tool for ecological monitoring (citation), operating UAVs in alpine regions is challenging due to the strong wind and harsh topology.
+\usepackage{amsmath}
+\setlength{\parindent}{10.5pt}
+\begin{document}
+\maketitle
 
-On the other hand, researchers have also utilized automated digital time-lapse cameras mounted on the ground for monitoring green-leaf phenologies in forests (Richardson et al., 2018), grasslands (Browning et al., 2017) and alpine meadows (Ide and Oguma, 2013).
-Unlike satellite imageries, such cameras provide images free of clouds and atmospheric effects.
-Also, they can obtain high-resolution (i.e., sub-meter scale) and frequent (i.e., daily or hourly) images at a meager cost.
-These studies set some regions of interest (ROI) in the images and calculate the phenology index (e.g., excess greenness, Woebbecke et al., 1995) for each ROI.
-While we can visually interpret the vegetation distribution and its changes from a set of such time-lapse images, few studies have tackled this.
-This lack seems to be because applying such time-lapse imageries in monitoring vegetation distribution has two technical challenges.
+\begin{abstract}
+Enter the text of your abstract here.
+\end{abstract}
 
-First, unlike multispectral sensors satellites equip, digital cameras can only obtain three bands (Red, Green, and Blue), making it harder to classify the vegetation.
-Second, since digital time-lapse cameras are mounted on the ground, applying geo-spatial analysis to these images is challenging.
-In other words, even if we find a vegetation change, we cannot identify its geographic location and analyze it with topological data.
-Treating ground-based time-lapse images as geographic data is essential for utilizing these in conservation planning.
+\keywords{
+    alpine ecology
+   \and
+    deep learning
+   \and
+    ecosystem monitoring
+  }
 
-This study proposes an automated method for drawing vegetation maps and locating vegetation changes with a digital time-lapse camera by solving these two challenges.
-We aim to use cheap but powerful digital time-lapse cameras in alpine ecosystem conservation.
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-# Materials and methods  
-## Digital time-lapse camera imagery   
-We used repeat photography data owned by National Institute for Environmental Studies, Japan (NIES).
-All the images are publically available on NIES' webpage (https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2).
-In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt.
-Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps.
-The camera takes one photograph per hour, from 6 a.m.
-to 7 p.m.
-.
-The camera's field of view (FOV) includes Mt.
-Tateyama, which ranges from about 2350 m a.s.l.
-to 3015 m a.s.l.
-in elevation.
-The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines.
-From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen, deciduous dwarf trees (e.g., Pinus pumila, Sorbus sp), dwarf bamboos (e.g., Sasa kurilensis), and alpine herbaceous plants (e.g., Geum pentapetalum, Nephrophyllidium crista-galli).
-We pulled the images from late summer to late fall of 2010 and 2020.
+The effects of climate change on terrestrial ecosystems are particularly
+significant in alpine regions (IPCC 2007). Alpine vegetation depends on
+severe climatic conditions such as low temperatures and long
+snow-covered periods. Thus alpine areas have rare and unique species
+adapted to the extreme environments. Several studies have reported that
+recent global climatic changes, e.g., increasing temperatures and
+reducing snow-covered periods, have accelerated the invasion of
+non-native species into alpine areas (see Alexander et al., 2016). In
+Japan, dwarf bamboo (\emph{Sasa kurilensis}) has invaded alpine snow
+meadows, probably driven by the extension of the snow-free period (Kudo
+et al., 2011). Also, climate change has affected the growth and
+phenologies of native species. For example, the growth of dwarf pine
+(\emph{Pinus pumila}), a dominant species in Japanese alpine regions,
+has been affected by climatic conditions such as temperature and
+snowmelt (Amagai et al., 2015). Monitoring and predicting such changes
+are essential for effective conservation planning. Since the impact of
+climate change on alpine vegetation varies depending on species and the
+microhabitats (Kudo et al., 2010), spatially high-resolution monitoring
+with a wide range is required.
 
-## Preprocessing  
-### Selecting images   
-First, we selected images that are suitable for vegetation classification.
-We choose four days with good weather from late summer to late fall each year (9/19, 10/1, 10/11, 10/23 in 2010.
-9/19, 10/2, 10/11, 10/23 in 2020).
-We used the images of this season because we can separate vegetation from the patterns of autumn foliage coloration.
-Then we pull four images from 11 a.m.
-to 2 p.m.
-each day to avoid the effect of temporal noise such as shadows.
-Finally, we got 16 images for each year.
+Previous studies have mainly depended on field observations, yet it is
+hard to cover broad areas in alpine regions due to poor accessibility
+and severe weather. Satellite, airborne, and Unmanned Aerial Vehicle
+(UAV) remote sensing methods seem to be alternatives. However, satellite
+imageries of alpine areas are rarely available due to cloud cover, and
+the spatial resolution is not enough to observe vegetation changes at
+the plant community scale. Airborne imageries can obtain high-resolution
+data, but its cost becomes a bottleneck for frequent monitoring.
+Although UAV methods have become popular as a cost-effective tool for
+ecological monitoring (citation), operating UAVs in alpine regions is
+challenging due to the strong wind and harsh topology.
 
-### Automatic image-to-image alignment  
-Since images are slightly misaligned with each other due to wind, we aligned them before processing.
-We implemented the program with Python3 language and OpenCV4 image processing library.
-First, we set one image of 2010 as the alignment target.
-Next, we automatically found matching keypoints between the target and other images using AKAZE local feature extractor and K-nearest neighbor matcher.
-Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points.
+On the other hand, researchers have also utilized automated digital
+time-lapse cameras mounted on the ground for monitoring green-leaf
+phenologies in forests (Richardson et al., 2018), grasslands (Browning
+et al., 2017) and alpine meadows (Ide and Oguma, 2013). Unlike satellite
+imageries, such cameras provide images free of clouds and atmospheric
+effects. Also, they can obtain high-resolution (i.e., sub-meter scale)
+and frequent (i.e., daily or hourly) images at a meager cost. These
+studies set some regions of interest (ROI) in the images and calculate
+the phenology index (e.g., excess greenness, Woebbecke et al., 1995) for
+each ROI. While we can visually interpret the vegetation distribution
+and its changes from a set of such time-lapse images, few studies have
+tackled this. This lack seems to be because applying such time-lapse
+imageries in monitoring vegetation distribution has two technical
+challenges.
 
-## Automatic vegetation classification  
-Next, we classified the pixel time series of repeat photography imageries into vegetations.
-Because deciduous plants have great differences in autumn phenology among species, researchers have used that information for vegetation classification with satellite imageries (e.g., Tigges et al., 2013, Son et al., 2014, Heupel et al., 2018).
-In our target area, we can recognize the vegetation type with the pixel time series of autumn (Fig.
-2).
-However, no research has applied this technique to ground-based repeat photography imageries.
-We developed a deep-learning method to take advantage of high-resolution and frequent repeat photography data.
-Fig.3 shows the classification process.
+First, unlike multispectral sensors satellites equip, digital cameras
+can only obtain three bands (Red, Green, and Blue), making it harder to
+classify the vegetation. Second, since digital time-lapse cameras are
+mounted on the ground, applying geo-spatial analysis to these images is
+challenging. In other words, even if we find a vegetation change, we
+cannot identify its geographic location and analyze it with topological
+data. Treating ground-based time-lapse images as geographic data is
+essential for utilizing these in conservation planning.
 
-### Model Architecture  
-Since ground-based photographs can provide high spatial resolution (about ~ 0.5m in our dataset), we can use leaf texture as additional information for classification.
-For example, we can see a glossy surface on dwarf bamboos and a mat surface on dwarf pines.
-Thus, we used a small patch (9x9 pixels square) rather than a single pixel as an input of the model.
-Therefore, a model input is a time series of image patches.
-Our model has two components to deal with this data structure (see Fig.
-3).
-First, we extracted each patch's features (e.g., texture) using Convolutional Neural Network (CNN) layers (Fig.
-4a).
-CNN is a neural network specialized in recognizing spatial structures of data, such as images.
-The CNN part outputs a time series of extracted features.
-Second, we used Recurrent Neural Net (RNN) layers (Fig.
-4b) to classify the temporal patterns of the features extracted by the CNN part.
-RNN is a neural network specialized in recognizing temporal or sequential data dynamics, such as text and speech.
-Amongst many variants of RNN, we used Long Short Time Memory (LSTM).
-Combining CNN and RNN, our model can classify the input image-patch time series considering the colors and textures of each patch and their temporal patterns.
-This CNN-RNN architecture has also been used for audio classification.
-Using a Deep Learning method has another positive side effect; mini-batch training.
-Since we used high-resolution images (16 x 21M pix), the training dataset became so immense that we could not feed them to the model at once: that consumes the computer's RAM too much.
-However, using Deep Learning methods enables us to provide them in small portions (called mini-batches) to save RAM consumption.
+This study proposes an automated method for drawing vegetation maps and
+locating vegetation changes with a digital time-lapse camera by solving
+these two challenges. We aim to use cheap but powerful digital
+time-lapse cameras in alpine ecosystem conservation.
 
-### Implementation and model training  
-We implemented the classifier with Python3 language and PyTorch deep neural network library. All source codes are publically available via GitHub (https://github.com/0kam/xxxx).
+\hypertarget{materials-and-methods}{%
+\section{Materials and methods}\label{materials-and-methods}}
 
-### Dataset preparation  
-We set 5 classes: dwarf pine, dwarf bamboo, other vegetation, no vegetation, and sky.
-Using free image annotation software (Semantic Segmentation Editor), an expert prepared teacher data (Fig.
-x) for classification.
+\hypertarget{digital-time-lapse-camera-imagery}{%
+\subsection{Digital time-lapse camera
+imagery}\label{digital-time-lapse-camera-imagery}}
 
-# Automatic georectification  
-Then, we developed a novel method to convert ground-based landscape imagery into GIS-ready geographical data.
-This process is called georectification.
-Georectification of ground-based images has been a difficult task, and this causes the underuse of potentially rich information in ground-based imageries.
-In plain words, georectification means aligning images into Digital Surface Models (DSMs) so that every pixel of an image gets a geographical coordinate.
-We can consider a camera as a function that transforms 3D geographical coordinates (latitude, longitude, height) into 2D image coordinates (locations of each pixel).
-So estimating the parameters of this function (such as the camera location, pose, and the field of view), we can align an image to a DSM.
-Usually, georectification has three steps:
-1. Finding Ground Control Points (GCPs) in the image.
-2. Estimating camera parameters such as camera poses and field of view using GCPs.
-3. Mapping the image onto the DSM using camera parameters.
+We used repeat photography data owned by National Institute for
+Environmental Studies, Japan (NIES). All the images are publically
+available on NIES' webpage
+(\url{https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2}). In
+2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon
+Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m
+a.s.l., above the forest limit), located at the foot of Mt. Tateyama
+(3015 m a.s.l.), in the Nothern Japanese Alps. The camera takes one
+photograph per hour, from 6 a.m. to 7 p.m. . The camera's field of view
+(FOV) includes Mt. Tateyama, which ranges from about 2350 m a.s.l. to
+3015 m a.s.l. in elevation. The area has a complex mosaic-like
+vegetation structure because of its topography, including rocks, cliffs,
+curls, and moraines. From April to November, the camera has observed the
+snowmelt and seasonal phenology of evergreen, deciduous dwarf trees
+(e.g., Pinus pumila, Sorbus sp), dwarf bamboos (e.g., Sasa kurilensis),
+and alpine herbaceous plants (e.g., Geum pentapetalum, Nephrophyllidium
+crista-galli). We pulled the images from late summer to late fall of
+2010 and 2020.
 
-Recently, researchers have developed some georectification methods to use ground-based photographs in glaciology (Messerli and Grinsted 2015) and snow cover studies (Portnier et al.
-2020).
-Especially, Portnier et al.
-2020 is worth mentioning for its semi-automatic method using mountain silhouettes as GCPs.
-However, this silhouette-based method has a drawback in the projection accuracy.
-It only uses limited areas (silhouettes) of images in the image-to-DSM alignment, and also it ignores lens distortion.
-Because our target site has a complex vegetation distribution and our camera has considerable lens distortion, we needed a more accurate method.
+\hypertarget{preprocessing}{%
+\subsection{Preprocessing}\label{preprocessing}}
 
-## Local-feature-based matching of images and DSMs  
-To get matching points between images and DSMs on a broader area, we used an airborne image already georectified.
-Combining an airborne image and a DSM, we rendered simulated landscape images (Fig.
-x).
-Then we got matching points (GCPs) by applying AKAZE local feature matcher to a target image and this simulated image (Fig.
-x).
-GCPs have geographical coordinates (from the DSM) and image coordinates (from the image).
-Our procedure requires the camera's exact location and initial camera parameters to render the simulated image.
+\hypertarget{selecting-images}{%
+\subsubsection{Selecting images}\label{selecting-images}}
 
-## Modeling and estimating lens distortions  
-We modeled the lens distortion based on Weng et al.
-1992 and OpenCV's implementation (Eq.
-1).
-Our model includes radial (k1~k6), tangental (p1, p2), thin prism (s1~s4) distortion, and unequal pixel aspect ratio (a1, a2).
-See Weng et al.
-1992 for lens distortion modeling.
-Also, we recommend readers to Portnier et al.
-2020 for camera models without lens distortions.
-Thus, now we can project GCPs' geographical coordinates into image coordinates using lens distortion parameters and other camera parameters (the camera location, pose, and the field of view).
-We optimized these (except camera location) by minimizing the square projection error of the GCPs using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES).
-We could not estimate the camera location because it makes the problem too complicated (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).
+First, we selected images that are suitable for vegetation
+classification. We choose four days with good weather from late summer
+to late fall each year (9/19, 10/1, 10/11, 10/23 in 2010. 9/19, 10/2,
+10/11, 10/23 in 2020). We used the images of this season because we can
+separate vegetation from the patterns of autumn foliage coloration. Then
+we pull four images from 11 a.m. to 2 p.m. each day to avoid the effect
+of temporal noise such as shadows. Finally, we got 16 images for each
+year.
 
-$$
+\hypertarget{automatic-image-to-image-alignment}{%
+\subsubsection{Automatic image-to-image
+alignment}\label{automatic-image-to-image-alignment}}
+
+Since images are slightly misaligned with each other due to wind, we
+aligned them before processing. We implemented the program with Python3
+language and OpenCV4 image processing library. First, we set one image
+of 2010 as the alignment target. Next, we automatically found matching
+keypoints between the target and other images using AKAZE local feature
+extractor and K-nearest neighbor matcher. Then, we searched and applied
+the homography matrix that minimizes the distance between each pair of
+the matching points.
+
+\hypertarget{automatic-vegetation-classification}{%
+\subsection{Automatic vegetation
+classification}\label{automatic-vegetation-classification}}
+
+Next, we classified the pixel time series of repeat photography
+imageries into vegetations. Because deciduous plants have great
+differences in autumn phenology among species, researchers have used
+that information for vegetation classification with satellite imageries
+(e.g., Tigges et al., 2013, Son et al., 2014, Heupel et al., 2018). In
+our target area, we can recognize the vegetation type with the pixel
+time series of autumn (Fig. 2). However, no research has applied this
+technique to ground-based repeat photography imageries. We developed a
+deep-learning method to take advantage of high-resolution and frequent
+repeat photography data. Fig.3 shows the classification process.
+
+\hypertarget{model-architecture}{%
+\subsubsection{Model Architecture}\label{model-architecture}}
+
+Since ground-based photographs can provide high spatial resolution
+(about \textasciitilde{} 0.5m in our dataset), we can use leaf texture
+as additional information for classification. For example, we can see a
+glossy surface on dwarf bamboos and a mat surface on dwarf pines. Thus,
+we used a small patch (9x9 pixels square) rather than a single pixel as
+an input of the model. Therefore, a model input is a time series of
+image patches. Our model has two components to deal with this data
+structure (see Fig. 3). First, we extracted each patch's features (e.g.,
+texture) using Convolutional Neural Network (CNN) layers (Fig. 4a). CNN
+is a neural network specialized in recognizing spatial structures of
+data, such as images. The CNN part outputs a time series of extracted
+features. Second, we used Recurrent Neural Net (RNN) layers (Fig. 4b) to
+classify the temporal patterns of the features extracted by the CNN
+part. RNN is a neural network specialized in recognizing temporal or
+sequential data dynamics, such as text and speech. Amongst many variants
+of RNN, we used Long Short Time Memory (LSTM). Combining CNN and RNN,
+our model can classify the input image-patch time series considering the
+colors and textures of each patch and their temporal patterns. This
+CNN-RNN architecture has also been used for audio classification. Using
+a Deep Learning method has another positive side effect; mini-batch
+training. Since we used high-resolution images (16 x 21M pix), the
+training dataset became so immense that we could not feed them to the
+model at once: that consumes the computer's RAM too much. However, using
+Deep Learning methods enables us to provide them in small portions
+(called mini-batches) to save RAM consumption.
+
+\hypertarget{implementation-and-model-training}{%
+\subsubsection{Implementation and model
+training}\label{implementation-and-model-training}}
+
+We implemented the classifier with Python3 language and PyTorch deep
+neural network library. All source codes are publically available via
+GitHub (\url{https://github.com/0kam/xxxx}).
+
+\hypertarget{dataset-preparation}{%
+\subsubsection{Dataset preparation}\label{dataset-preparation}}
+
+We set 5 classes: dwarf pine, dwarf bamboo, other vegetation, no
+vegetation, and sky. Using free image annotation software (Semantic
+Segmentation Editor), an expert prepared teacher data (Fig. x) for
+classification.
+
+\hypertarget{automatic-georectification}{%
+\section{Automatic georectification}\label{automatic-georectification}}
+
+Then, we developed a novel method to convert ground-based landscape
+imagery into GIS-ready geographical data. This process is called
+georectification. Georectification of ground-based images has been a
+difficult task, and this causes the underuse of potentially rich
+information in ground-based imageries. In plain words, georectification
+means aligning images into Digital Surface Models (DSMs) so that every
+pixel of an image gets a geographical coordinate. We can consider a
+camera as a function that transforms 3D geographical coordinates
+(latitude, longitude, height) into 2D image coordinates (locations of
+each pixel). So estimating the parameters of this function (such as the
+camera location, pose, and the field of view), we can align an image to
+a DSM. Usually, georectification has three steps: 1. Finding Ground
+Control Points (GCPs) in the image. 2. Estimating camera parameters such
+as camera poses and field of view using GCPs. 3. Mapping the image onto
+the DSM using camera parameters.
+
+Recently, researchers have developed some georectification methods to
+use ground-based photographs in glaciology (Messerli and Grinsted 2015)
+and snow cover studies (Portnier et al.~2020). Especially, Portnier et
+al.~2020 is worth mentioning for its semi-automatic method using
+mountain silhouettes as GCPs. However, this silhouette-based method has
+a drawback in the projection accuracy. It only uses limited areas
+(silhouettes) of images in the image-to-DSM alignment, and also it
+ignores lens distortion. Because our target site has a complex
+vegetation distribution and our camera has considerable lens distortion,
+we needed a more accurate method.
+
+\hypertarget{local-feature-based-matching-of-images-and-dsms}{%
+\subsection{Local-feature-based matching of images and
+DSMs}\label{local-feature-based-matching-of-images-and-dsms}}
+
+To get matching points between images and DSMs on a broader area, we
+used an airborne image already georectified. Combining an airborne image
+and a DSM, we rendered simulated landscape images (Fig. x). Then we got
+matching points (GCPs) by applying AKAZE local feature matcher to a
+target image and this simulated image (Fig. x). GCPs have geographical
+coordinates (from the DSM) and image coordinates (from the image). Our
+procedure requires the camera's exact location and initial camera
+parameters to render the simulated image.
+
+\hypertarget{modeling-and-estimating-lens-distortions}{%
+\subsection{Modeling and estimating lens
+distortions}\label{modeling-and-estimating-lens-distortions}}
+
+We modeled the lens distortion based on Weng et al.~1992 and OpenCV's
+implementation (Eq. 1). Our model includes radial
+(k1\textasciitilde k6), tangental (p1, p2), thin prism
+(s1\textasciitilde s4) distortion, and unequal pixel aspect ratio (a1,
+a2). See Weng et al.~1992 for lens distortion modeling. Also, we
+recommend readers to Portnier et al.~2020 for camera models without lens
+distortions. Thus, now we can project GCPs' geographical coordinates
+into image coordinates using lens distortion parameters and other camera
+parameters (the camera location, pose, and the field of view). We
+optimized these (except camera location) by minimizing the square
+projection error of the GCPs using the Covariance Matrix Adaptation
+Evolution Strategy (CMA-ES). We could not estimate the camera location
+because it makes the problem too complicated (e.g., a telephoto taken
+from a distance and a wide-angle taken from a close look similar).
+
+\[
 \begin{bmatrix}
@@
 y’ \frac{1 + a_1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + a_2 + k_4 r^2 + k_5 r^4 + k_6 r^6} + p_1 (r^2 + 2 y’^2) + 2 p_2 x’ y’ + s_3 r^2 + s_4 r^4 \ \end{bmatrix}
-$$
+\]
 
-## Implementation and data set  
-We implemented the algorithm with Python3 language and published it as an open-source package via GitHub (https://github.com/0kam/alproj).
-You can try it with your data.
-We used an airborne photograph taken in the November of 201X with a spatial resolution of 1.0 m.
-Also, we used the 5m resolution Digital Elevation Model provided by the Geospatial Information Authority of Japan (GSI) as a DSM.
+\hypertarget{implementation-and-data-set}{%
+\subsection{Implementation and data
+set}\label{implementation-and-data-set}}
 
-# Results
+We implemented the algorithm with Python3 language and published it as
+an open-source package via GitHub
+(\url{https://github.com/0kam/alproj}). You can try it with your data.
+We used an airborne photograph taken in the November of 201X with a
+spatial resolution of 1.0 m. Also, we used the 5m resolution Digital
+Elevation Model provided by the Geospatial Information Authority of
+Japan (GSI) as a DSM.
 
-## Vegetation classification accuracy
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
-```{r plot_vegetation_acc, echo=FALSE, message=FALSE, fig.width=4, fig.height=3}
-df <- read_csv("../runs/cnn_lstm9x9_cv_5_ep_200/staritfied_cv.csv",
-               col_select = c(metrics, vegetation, value, fold))
-theme_gtsummary_mean_sd()
-df %>%
-  filter(metrics != "support") %>%
-  mutate(vegetation = translate_classes(vegetation)) %>%
-  mutate(vegetation = factor(vegetation, levels = vegetation_levels)) %>%
-  pivot_wider(names_from = metrics, values_from = value) %>%
-  select(-fold) %>%
-  tbl_summary(
-    by = c(vegetation),
-    label = list(
-      precision ~ "Precision",
-      recall ~ "Recall",
-      `f1-score` ~ "F1 Score")
-  ) %>%
-  modify_header(label = "")
+\hypertarget{vegetation-classification-accuracy}{%
+\subsection{Vegetation classification
+accuracy}\label{vegetation-classification-accuracy}}
 
-```
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.05}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.14}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.16}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.12}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.13}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.16}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.15}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.09}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\textbf{Macro Average}, N = 5
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\textbf{Weighted Average}, N = 5
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\textbf{Dwarf Pine}, N = 5
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\textbf{Dwarf Bamboo}, N = 5
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\textbf{Other Vegetations}, N = 5
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\textbf{Non Vegetation}, N = 5
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\textbf{Sky}, N = 5
+\end{minipage} \\
+\midrule
+\endhead
+Precision & 0.977 (0.008) & 0.997 (0.001) & 0.977 (0.012) & 0.951
+(0.013) & 0.999 (0.000) & 0.959 (0.066) & 1.000 (0.000) \\
+Recall & 0.987 (0.001) & 0.997 (0.001) & 0.995 (0.003) & 0.960 (0.006) &
+0.996 (0.002) & 0.984 (0.004) & 1.000 (0.000) \\
+F1 Score & 0.982 (0.005) & 0.997 (0.001) & 0.986 (0.005) & 0.955 (0.004)
+& 0.997 (0.001) & 0.970 (0.034) & 1.000 (0.000) \\
+\bottomrule
+\end{longtable}
 
-## Georectification accuracy
+\hypertarget{georectification-accuracy}{%
+\subsection{Georectification accuracy}\label{georectification-accuracy}}
 
-## Vegetation maps
+\hypertarget{vegetation-maps}{%
+\subsection{Vegetation maps}\label{vegetation-maps}}
 
-## Detection and localization of vegetation changes
+\hypertarget{detection-and-localization-of-vegetation-changes}{%
+\subsection{Detection and localization of vegetation
+changes}\label{detection-and-localization-of-vegetation-changes}}
 
-# Discussion   
-We suggested a fully automated procedure to transform time-lapse imagery into georeferenced vegetation maps at a meager cost.
-This task is challenging because of 1.
-the difficulty of classifying vegetations with ordinal digital camera imagery and 2.
-the difficulty of georectification.
-We solved these issues by 1.
-using the temporal information of autumn leaf colors for vegetation classification and 2.
-developing a novel method for accurate image georectification.
-Our vegetation classification performance (with an accuracy of 0.87) and georectification methods (with an RMSE of $rmse$ m) are practical.
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
-## The benefit of using time-series imagery for vegetation classification  
-One of the shortcomings of ordinal digital cameras is that they only have three bands (Red, Blue, and Green).
-We made up for this lack of information by using the rich temporal information that time-lapse cameras can obtain.
-Many plant species have characteristic phenologies, such as flowering and autumn foliages.
-Observing this requires long-term (such as year-round) monitoring with a high frequency, and digital time-lapse cameras are suitable.
-This study only focused on the two species (dwarf bamboo and stone pine) that are easy to classify, even with a single image.
-However, like the previous studies (Tigges et al., 2013, Son et al., 2014, Heupel et al., 2018), we expect our method to classify more vegetations (e.g., dwarf deciduous trees and alpine herbaceous plants) using the temporal information of leaf colors.
-We also used hourly images for each day.
-Fig.
-x shows that this additional information made our model robust against transient noises, such as shadows.
-Since alpine ecosystems have rough topologies, shadows are a considerable problem.
-Time-lapse cameras are also beneficial for this reason.
+We suggested a fully automated procedure to transform time-lapse imagery
+into georeferenced vegetation maps at a meager cost. This task is
+challenging because of 1. the difficulty of classifying vegetations with
+ordinal digital camera imagery and 2. the difficulty of
+georectification. We solved these issues by 1. using the temporal
+information of autumn leaf colors for vegetation classification and 2.
+developing a novel method for accurate image georectification. Our
+vegetation classification performance (with an accuracy of 0.87) and
+georectification methods (with an RMSE of \(rmse\) m) are practical.
 
-## The performance of our georectification method and its limitation.
+\hypertarget{the-benefit-of-using-time-series-imagery-for-vegetation-classification}{%
+\subsection{The benefit of using time-series imagery for vegetation
+classification}\label{the-benefit-of-using-time-series-imagery-for-vegetation-classification}}
 
-## Future application and conclusion
+One of the shortcomings of ordinal digital cameras is that they only
+have three bands (Red, Blue, and Green). We made up for this lack of
+information by using the rich temporal information that time-lapse
+cameras can obtain. Many plant species have characteristic phenologies,
+such as flowering and autumn foliages. Observing this requires long-term
+(such as year-round) monitoring with a high frequency, and digital
+time-lapse cameras are suitable. This study only focused on the two
+species (dwarf bamboo and stone pine) that are easy to classify, even
+with a single image. However, like the previous studies (Tigges et al.,
+2013, Son et al., 2014, Heupel et al., 2018), we expect our method to
+classify more vegetations (e.g., dwarf deciduous trees and alpine
+herbaceous plants) using the temporal information of leaf colors. We
+also used hourly images for each day. Fig. x shows that this additional
+information made our model robust against transient noises, such as
+shadows. Since alpine ecosystems have rough topologies, shadows are a
+considerable problem. Time-lapse cameras are also beneficial for this
+reason.
+
+\hypertarget{the-performance-of-our-georectification-method-and-its-limitation.}{%
+\subsection{The performance of our georectification method and its
+limitation.}\label{the-performance-of-our-georectification-method-and-its-limitation.}}
+
+\hypertarget{future-application-and-conclusion}{%
+\subsection{Future application and
+conclusion}\label{future-application-and-conclusion}}
+
+\bibliographystyle{unsrt}
+\bibliography{references.bib}
+
+\end{document}

### 2022-05-11 scripts/cnn_lstm.py

@@ -1,0 +1,221 @@
+import torch
+from torch import nn
+from torch.nn import functional as F
+import torch_optimizer as optim 
+from scripts.utils import read_sses, DrawDS, LabelledDS, cf_labelled, draw_legend, draw_teacher
+from torchvision import transforms
+from torch.utils.data import DataLoader
+from sklearn.model_selection import train_test_split, StratifiedKFold
+from sklearn.metrics import classification_report
+from tqdm import tqdm
+from pathlib import Path
+from glob import glob
+from tensorboardX import SummaryWriter
+from matplotlib import pyplot as plt
+from PIL import Image
+import pandas as pd
+
+class AsImage(object):
+    def __init__(self, kernel_size):
+        self.kernel_size = kernel_size
+    def __call__(self, x):
+        return x.view((-1,) + self.kernel_size)
+
+class CRNNClassifier(nn.Module):
+    def __init__(self, x_shape, y_dim):
+        super(CRNNClassifier, self).__init__()
+        self.x_shape = x_shape
+        self.conv1 = nn.Conv2d(3, 8, (3,3), 1)
+        self.bn2d_1 = nn.BatchNorm2d(8)
+        self.prelu1 = nn.PReLU()
+        self.maxpool1 = nn.MaxPool2d((3,3), 1)       
+        conv_out_shape = (x_shape[2]-4) * (x_shape[3]-4) * 8
+        self.h_dim = int((conv_out_shape + y_dim) / 2)
+        self.lstm = nn.LSTM(conv_out_shape, self.h_dim, batch_first=True)
+        self.bn1 = nn.BatchNorm1d(self.h_dim)
+        self.do1 = nn.Dropout(0.0)
+        self.fc1 = nn.Linear(self.h_dim, self.h_dim)
+        self.prelu2 = nn.PReLU()
+        self.bn2 = nn.BatchNorm1d(self.h_dim)
+        self.do2 = nn.Dropout(0.0)
+        self.fc2 = nn.Linear(self.h_dim, y_dim)
+
+    def forward(self, x):
+        h = self.conv1(x)
+        h = self.prelu1(h)
+        h = self.bn2d_1(h)
+        h = self.maxpool1(h)
+        h = h.view((-1, self.x_shape[0], h.shape[1]*h.shape[2]*h.shape[3]))
+        _, h = self.lstm(h)
+        h = h[0].view(-1, self.h_dim)
+        h = self.bn1(h)
[…]

### 2022-05-11 scripts/figures.py

@@ -1,0 +1,49 @@
+import numpy as np
+from PIL import Image
+from glob import glob
+# Animation of images 
+
+images = [Image.open(i).convert("P", palette=Image.ADAPTIVE, colors=256) for i in sorted(glob("data/train2/2010/images_2010/*"))]
+images = [i.resize((800,600), Image.BICUBIC) for i in images]
+images[0].save("results/animation_2010.gif", save_all=True, append_images=images[1:],  duration=300, loop=0)
+
+
+images = [Image.open(i).convert("P", palette=Image.ADAPTIVE, colors=256) for i in sorted(glob("data/train2/2020/images_2020/*"))]
+images = [i.resize((800,600), Image.BICUBIC) for i in images]
+images[0].save("results/animation_2020.gif", save_all=True, append_images=images[1:],  duration=300, loop=0)
+
+# Animation of patches
+def animate_patches(in_path, out_path):
+    patch = np.load(in_path).reshape(-1, 16, 3, 9, 9)[25,:,:,:,:].transpose(0,2,3,1)
+    patch = [patch[i,:,:,:] for i in range(patch.shape[0])]
+    patch = [Image.fromarray(i).convert("P", palette=Image.ADAPTIVE, colors=256) for i in patch]
+    patch = [i.resize((200,200), Image.NEAREST) for i in patch]
+    patch[0].save(out_path, save_all=True, append_images=patch[1:],  duration=300, loop=0)
+animate_patches("data/train2/patches9x9/labelled/1/images_2010_31238.npy", "results/animation_sasa.gif")
+animate_patches("data/train2/patches9x9/labelled/2/images_2010_21185.npy", "results/animation_rachi.gif")
+animate_patches("data/train2/patches9x9/labelled/3/images_2010_22678.npy", "results/animation_sonota.gif")
+animate_patches("data/train2/patches9x9/labelled/4/images_2010_10215.npy", "results/animation_sora.gif")
+animate_patches("data/train2/patches9x9/labelled/5/images_2010_14997.npy", "results/animation_haimatsu.gif")
+
+# Count changed numbers
+## haimatsu
+diff_h = np.asarray(Image.open("results/diff_haimatsu_cnn_9x9.png"))[1488:,:,:]
[…]

### 2022-05-11 scripts/georectify.py

@@ -1,0 +1,15 @@
+# Loading requirements
+from alproj.surface import create_db, crop
+from alproj.project import sim_image, reverse_proj
+from alproj.gcp import akaze_match, set_gcp
+from alproj.optimize import CMAOptimizer
+import sqlite3
+import numpy as np
+import rasterio
+
+res = 1.0 # Resolution in m
+aerial = rasterio.open("airborne.tif")
+dsm = rasterio.open("dsm.tif")
+out_path = "pointcloud.db" # Output database
+
+create_db(aerial, dsm, out_path) # This takes some minutes

### 2022-05-11 scripts/run_cnnlstm.py

@@ -1,0 +1,56 @@
+from scripts.utils import set_patches
+from scripts.cnn_lstm import CNNLSTM
+import numpy as np
+import tensorboardX
+hmat = np.loadtxt("data_source/hmat_label.txt")
+mask = np.load("data_source/mask.npy")
+shrink = 10
+log_dir = "cnn_lstm9x9"
+
+#set_patches("data_source/labels", "data_source/aligned/2012", "data/train/patches9x9/", (9,9), batch_size=50, unlabelled=False, shrink=shrink, hmat=hmat, mask=mask)
+#set_patches("data_source/labels", "data_source/aligned/2020", "data/train/patches9x9/", (9,9), batch_size=50, unlabelled=False, shrink=shrink, hmat=hmat, mask=mask)
+
+lstm = CNNLSTM("data/train/patches9x9", "data_source/labels", (9,9), 200, device="cuda")
+lstm.draw_legend("results/legend.png")
+lstm.draw_teacher("results/teacher.png", (5616,3744), shrink=shrink, hmat=hmat, mask=mask)
+
+lstm.kfold(10, "cnn_lstm9x9_cv_5_ep_200", 5)
+
+lstm.train(200, log_dir)
+lstm.load("./runs/"+log_dir+"/best.pth")
+
+res2012, _ = lstm.draw("data_source/aligned/2012", "results/cnn_9x9_2012.png", (9,9), 50000)
+res2020, _ = lstm.draw("data_source/aligned/2020", "results/cnn_9x9_2020.png", (9,9), 50000)
+
+import numpy as np
+from matplotlib import pyplot as plt
+import pylab as pl
+import cv2
+np.save("results/res2012_cnn_9x9.npy", res2012)
+np.save("results/res2020_cnn_9x9.npy", res2020)
+
+lstm.labels
+lstm.class_to_idx
+
+diff = np.zeros(res2012.shape)
+diff[np.logical_and(res2012!=4, res2020==4)] = 1 # ハイマツ以外 -> ハイマツ
+diff[np.logical_and(res2012==4, res2020!=4)] = 2 # ハイマツ -> ハイマツ以外
+cmap = plt.get_cmap("tab20", 3)
+plt.imsave("results/diff_haimatsu_cnn_9x9.png", diff, cmap = cmap)
+
+diff_labels = [
+    "出現",
+    "消滅"
+]
+pl.cla()
[…]

### 2022-05-11 scripts/utils.py

@@ -1,0 +1,298 @@
+from glob import glob
+from PIL import Image
+import torch
+from torch.nn import functional as F
+from torch.utils.data import Dataset, DataLoader, IterableDataset
+from torchvision.datasets import DatasetFolder
+from torchvision.transforms.functional import to_tensor
+import pandas as pd
+import json
+import cv2
+import numpy as np
+from tqdm import tqdm
+import os
+from pathlib import Path
+import shutil
+import pylab as pl
+from matplotlib import pyplot as plt
+from shapely import geometry
+
+from matplotlib.font_manager import FontProperties
+font_path = "/usr/share/fonts/truetype/migmix/migmix-1p-regular.ttf"
+font_prop = FontProperties(fname=font_path)
+plt.rcParams["font.family"] = font_prop.get_name()
+
+# Set up patches
+def read_sses(label_dir, image_size, label="all", shrink=0, hmat = None, mask = None):
+    """
+    Read multiple json files created with Semantic Segmentation Editor
+    Parameters
+    ----------
+    label_dir : str
+        A path for a directory which stores json files.
+    image_size : tuple of int
+        (width, height) of the specified image
+    label : str or list of str
+        list of labels to use. If "all" (default), use all labels
+    shrink : int
+        shrink size in pixels  
+    hmat : np.array
+        homography matrix to apply
+    mask : np.array
+        mask to apply
+    Returns
+    -------
+    image : np.array
+        A masked image.
+    labels : pd.DataFrame
+        
+    """
+    objects = []
+    for p in glob(label_dir + "/*"):
+        with open(p) as js:
+            obj = json.load(js)["objects"]
+            obj = pd.json_normalize(obj)
+            objects.append(obj)
+    objects = pd.concat(objects)
+    max_class_idx = max(objects["classIndex"])
+    class_idx = objects["classIndex"].copy()
+    class_idx[class_idx == 0] = max_class_idx + 1
+    objects["classIndex"] = class_idx
+    if label != "all":
+        l = objects.label.copy()
+        i = objects.classIndex.copy()
+        l[objects.label.isin(label) == False] = "その他"
+        i[objects.label.isin(label) == False] = 9999 # 9999 = その他
+        objects.label = l
+        objects.classIndex = i
+
+    polygons = list(objects["polygon"])
+    labels = objects["classIndex"]
[…]

### 2022-05-13 paper/paper.Rmd
added citations

@@
   - ecosystem monitoring
-bibliography: references.bib
+bibliography: export.bib
 biblio-style: unsrt
@@
 library(tidyverse)
+library(magrittr)
 library(gtsummary)
@@
               "ササ群落" = "Dwarf Bamboo",
-              "その他植生" = "Other Vegetations",
+              "その他植生" = "Other vegetation",
               "裸地等" = "Non Vegetation",
@@
   "Dwarf Bamboo",
-  "Other Vegetations",
+  "Other vegetation",
   "Non Vegetation",
@@
 # Introduction
-  The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (IPCC 2007).
-Alpine vegetation depends on severe climatic conditions such as low temperatures and long snow-covered periods.
+  The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (\cite{IPCC2007}).
+Alpine vegetation depends on severe conditions such as low temperatures and long snow-covered periods.
 Thus alpine areas have rare and unique species adapted to the extreme environments.
-Several studies have reported that recent global climatic changes, e.g., increasing temperatures and reducing snow-covered periods, have accelerated the invasion of non-native species into alpine areas (see Alexander et al., 2016).
-In Japan, dwarf bamboo (*Sasa kurilensis*) has invaded alpine snow meadows, probably driven by the extension of the snow-free period (Kudo et al., 2011).
+Several studies have reported that recent global climatic changes, e.g., increasing temperatures and reducing snow-covered periods, have accelerated the invasion of non-native species into alpine areas (see \cite{Alexander2016AlpBotany}).
+In Japan, dwarf bamboo (*Sasa kurilensis*) has invaded alpine snow meadows, probably driven by the extension of the snow-free period (\cite{Kudo2011EcoEvo}).
 Also, climate change has affected the growth and phenologies of native species.
-For example, the growth of dwarf pine (*Pinus pumila*), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (Amagai et al., 2015).
+For example, the growth of dwarf pine (*Pinus pumila*), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}).
 Monitoring and predicting such changes are essential for effective conservation planning.
-Since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (Kudo et al., 2010), spatially high-resolution monitoring with a wide range is required.
+Since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.
 
@@
 Satellite, airborne, and Unmanned Aerial Vehicle (UAV) remote sensing methods seem to be alternatives.
-However, satellite imageries of alpine areas are rarely available due to cloud cover, and the spatial resolution is not enough to observe vegetation changes at the plant community scale.
-Airborne imageries can obtain high-resolution data, but its cost becomes a bottleneck for frequent monitoring.
-Although UAV methods have become popular as a cost-effective tool for ecological monitoring (citation), operating UAVs in alpine regions is challenging due to the strong wind and harsh topology.
+However, satellite imagery of alpine areas are rarely available due to cloud cover, and the spatial resolution is not enough to observe vegetation changes at the plant community scale.
+Airborne imagery can obtain high-resolution data, but its cost becomes a bottleneck for frequent monitoring.
+Although UAV methods have become a cost-effective tool for ecological monitoring (\cite{Baena2017PLOSONE}), operating UAVs in alpine regions is challenging due to the strong wind and harsh topology.
 
-On the other hand, researchers have also utilized automated digital time-lapse cameras mounted on the ground for monitoring green-leaf phenologies in forests (Richardson et al., 2018), grasslands (Browning et al., 2017) and alpine meadows (Ide and Oguma, 2013).
-Unlike satellite imageries, such cameras provide images free of clouds and atmospheric effects.
+On the other hand, researchers have also utilized automated digital time-lapse cameras mounted on the ground for monitoring green-leaf phenologies in forests (\cite{Richardson2009EcolAppl}), grasslands (\cite{Browning2017RemSen}), and alpine meadows (\cite{IdeOguma2013EcolInfom}).
+Unlike satellite imagery, such cameras provide images free of clouds and atmospheric effects.
 Also, they can obtain high-resolution (i.e., sub-meter scale) and frequent (i.e., daily or hourly) images at a meager cost.
-These studies set some regions of interest (ROI) in the images and calculate the phenology index (e.g., excess greenness, Woebbecke et al., 1995) for each ROI.
-While we can visually interpret the vegetation distribution and its changes from a set of such time-lapse images, few studies have tackled this.
-This lack seems to be because applying such time-lapse imageries in monitoring vegetation distribution has two technical challenges.
+These studies set some regions of interest (ROI) in the images and calculate the phenology index (e.g., excess greenness, \cite{Woebbecke1995ASAE}).
+Also, we can visually interpret the vegetation distribution and its changes from such time-lapse images.
+However, few studies have tackled this.
+This lack seems to be because applying such time-lapse imagery in monitoring vegetation distribution has two technical challenges.
 
-First, unlike multispectral sensors satellites equip, digital cameras can only obtain three bands (Red, Green, and Blue), making it harder to classify the vegetation.
+First, unlike satellites' multispectral sensors, ordinal digital cameras can only obtain three bands (Red, Green, and Blue), making it harder to classify the vegetation.
 Second, since digital time-lapse cameras are mounted on the ground, applying geo-spatial analysis to these images is challenging.
 In other words, even if we find a vegetation change, we cannot identify its geographic location and analyze it with topological data.
-Treating ground-based time-lapse images as geographic data is essential for utilizing these in conservation planning.
+Treating ground-based time-lapse images as geographic data is essential to utilize them in conservation planning.
 
 This study proposes an automated method for drawing vegetation maps and locating vegetation changes with a digital time-lapse camera by solving these two challenges.
+We solved the first challenge by utilizing temporal changes in leaf colors in vegetation classification.
+We also developed an accurate method for transforming a ground-based photograph into geographic data to tackle the second challenge.
 We aim to use cheap but powerful digital time-lapse cameras in alpine ecosystem conservation.
@@
 The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines.
-From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen, deciduous dwarf trees (e.g., Pinus pumila, Sorbus sp), dwarf bamboos (e.g., Sasa kurilensis), and alpine herbaceous plants (e.g., Geum pentapetalum, Nephrophyllidium crista-galli).
-We pulled the images from late summer to late fall of 2010 and 2020.
+From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen, deciduous dwarf trees (e.g., *Pinus pumila*, *Sorbus* sp.), dwarf bamboos (e.g., *Sasa kurilensis*), and alpine herbaceous plants (e.g., *Geum pentapetalum*, *Nephrophyllidium crista-galli*).
+We used the images from late summer to late fall of 2012 and 2020.
 
@@
 We used the images of this season because we can separate vegetation from the patterns of autumn foliage coloration.
-Then we pull four images from 11 a.m.
+Also, we chose four images from 11 a.m.
 to 2 p.m.
@@
 Since images are slightly misaligned with each other due to wind, we aligned them before processing.
-We implemented the program with Python3 language and OpenCV4 image processing library.
+We implemented the program with Python3 programming language and OpenCV4 (https://opencv.org/) image processing library.
 First, we set one image of 2010 as the alignment target.
-Next, we automatically found matching keypoints between the target and other images using AKAZE local feature extractor and K-nearest neighbor matcher.
-Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points.
+Next, we automatically found matching keypoints between the target and other images using AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
+Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's "findHomography" function.
 
 ## Automatic vegetation classification  
-Next, we classified the pixel time series of repeat photography imageries into vegetations.
-Because deciduous plants have great differences in autumn phenology among species, researchers have used that information for vegetation classification with satellite imageries (e.g., Tigges et al., 2013, Son et al., 2014, Heupel et al., 2018).
+Next, we classified the pixel time series of repeat photography imagery into vegetation.
+Because deciduous plants have great differences in autumn phenology among species, researchers have used that information for vegetation classification with satellite imagery (e.g., \cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}).
 In our target area, we can recognize the vegetation type with the pixel time series of autumn (Fig.
 2).
-However, no research has applied this technique to ground-based repeat photography imageries.
+However, no research has applied this technique to ground-based repeat photography imagery.
 We developed a deep-learning method to take advantage of high-resolution and frequent repeat photography data.
@@
 ### Model Architecture  
-Since ground-based photographs can provide high spatial resolution (about ~ 0.5m in our dataset), we can use leaf texture as additional information for classification.
+Since ground-based photographs can provide high spatial resolution (sub-meter scale in our dataset), we can use leaf texture as additional information for classification.
 For example, we can see a glossy surface on dwarf bamboos and a mat surface on dwarf pines.
@@
 RNN is a neural network specialized in recognizing temporal or sequential data dynamics, such as text and speech.
-Amongst many variants of RNN, we used Long Short Time Memory (LSTM).
+Amongst many variants of RNN, we used Long Short Time Memory (LSTM, \cite{Hochreiter1997LSTM}).
 Combining CNN and RNN, our model can classify the input image-patch time series considering the colors and textures of each patch and their temporal patterns.
-This CNN-RNN architecture has also been used for audio classification.
+This CNN-RNN architecture has also been used for audio classification(\cite{Shi2015CRNNtext}) and scene text recognition(\cite{Shi2015CRNNtext}).
 Using a Deep Learning method has another positive side effect; mini-batch training.
@@
 ### Implementation and model training  
-We implemented the classifier with Python3 language and PyTorch deep neural network library. All source codes are publically available via GitHub (https://github.com/0kam/xxxx).
+We implemented the classifier with Python3 language and PyTorch deep neural network library (https://pytorch.org/). All source codes are publically available via GitHub (https://github.com/0kam/xxxx).
 
@@
 This process is called georectification.
-Georectification of ground-based images has been a difficult task, and this causes the underuse of potentially rich information in ground-based imageries.
+Georectification of ground-based images has been a difficult task, and this causes the underuse of potentially rich information in ground-based imagery.
 In plain words, georectification means aligning images into Digital Surface Models (DSMs) so that every pixel of an image gets a geographical coordinate.
@@
 
-Recently, researchers have developed some georectification methods to use ground-based photographs in glaciology (Messerli and Grinsted 2015) and snow cover studies (Portnier et al.
-2020).
-Especially, Portnier et al.
-2020 is worth mentioning for its semi-automatic method using mountain silhouettes as GCPs.
+Recently, researchers have developed some georectification methods to use ground-based photographs in glaciology (\cite{Messerli2015GeoInst}) and snow cover studies (\cite{Portenier2020Cryosphere}).
+Especially, \cite{Portenier2020Cryosphere} is worth mentioning for its semi-automatic method using mountain silhouettes as GCPs.
 However, this silhouette-based method has a drawback in the projection accuracy.
@@
 ## Modeling and estimating lens distortions  
-We modeled the lens distortion based on Weng et al.
-1992 and OpenCV's implementation (Eq.
+We modeled the lens distortion based on \cite{Weng1992CameraCalib} and OpenCV's implementation (Eq.
 1).
@@
 1992 for lens distortion modeling.
-Also, we recommend readers to Portnier et al.
-2020 for camera models without lens distortions.
+Also, we recommend readers to \cite{Portenier2020Cryosphere} for camera models without lens distortions.
 Thus, now we can project GCPs' geographical coordinates into image coordinates using lens distortion parameters and other camera parameters (the camera location, pose, and the field of view).
-We optimized these (except camera location) by minimizing the square projection error of the GCPs using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES).
+We optimized these (except camera location) by minimizing the square projection error of the GCPs using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}).
 We could not estimate the camera location because it makes the problem too complicated (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).
@@
   mutate(vegetation = translate_classes(vegetation)) %>%
-  mutate(vegetation = factor(vegetation, levels = vegetation_levels)) %>%
+  mutate(vegetation = factor(vegetation, levels = vegetation_levels)) %T>%
+  {
+    group_by(., vegetation, metrics) %>%
+      summarise(
+        mean = mean(value),
+        sd = sd(value)
+      ) %>%
+      write_csv("table1.csv")
+  } %>%
   pivot_wider(names_from = metrics, values_from = value) %>%
@@
 This task is challenging because of 1.
-the difficulty of classifying vegetations with ordinal digital camera imagery and 2.
+the difficulty of classifying vegetation with ordinal digital camera imagery and 2.
 the difficulty of georectification.
@@
 This study only focused on the two species (dwarf bamboo and stone pine) that are easy to classify, even with a single image.
-However, like the previous studies (Tigges et al., 2013, Son et al., 2014, Heupel et al., 2018), we expect our method to classify more vegetations (e.g., dwarf deciduous trees and alpine herbaceous plants) using the temporal information of leaf colors.
+However, like the previous studies (\cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}), we expect our method to classify more vegetation (e.g., dwarf deciduous trees and alpine herbaceous plants) using the temporal information of leaf colors.
 We also used hourly images for each day.

### 2022-05-13 paper/paper.tex
added citations

@@
 The effects of climate change on terrestrial ecosystems are particularly
-significant in alpine regions (IPCC 2007). Alpine vegetation depends on
-severe climatic conditions such as low temperatures and long
+significant in alpine regions (\cite{IPCC2007}). Alpine vegetation
+depends on severe conditions such as low temperatures and long
 snow-covered periods. Thus alpine areas have rare and unique species
@@
 reducing snow-covered periods, have accelerated the invasion of
-non-native species into alpine areas (see Alexander et al., 2016). In
-Japan, dwarf bamboo (\emph{Sasa kurilensis}) has invaded alpine snow
-meadows, probably driven by the extension of the snow-free period (Kudo
-et al., 2011). Also, climate change has affected the growth and
-phenologies of native species. For example, the growth of dwarf pine
-(\emph{Pinus pumila}), a dominant species in Japanese alpine regions,
-has been affected by climatic conditions such as temperature and
-snowmelt (Amagai et al., 2015). Monitoring and predicting such changes
-are essential for effective conservation planning. Since the impact of
-climate change on alpine vegetation varies depending on species and the
-microhabitats (Kudo et al., 2010), spatially high-resolution monitoring
-with a wide range is required.
+non-native species into alpine areas (see
+\cite{Alexander2016AlpBotany}). In Japan, dwarf bamboo (\emph{Sasa
+kurilensis}) has invaded alpine snow meadows, probably driven by the
+extension of the snow-free period (\cite{Kudo2011EcoEvo}). Also, climate
+change has affected the growth and phenologies of native species. For
+example, the growth of dwarf pine (\emph{Pinus pumila}), a dominant
+species in Japanese alpine regions, has been affected by climatic
+conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}).
+Monitoring and predicting such changes are essential for effective
+conservation planning. Since the impact of climate change on alpine
+vegetation varies depending on species and the microhabitats
+(\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide
+range is required.
 
@@
 (UAV) remote sensing methods seem to be alternatives. However, satellite
-imageries of alpine areas are rarely available due to cloud cover, and
-the spatial resolution is not enough to observe vegetation changes at
-the plant community scale. Airborne imageries can obtain high-resolution
-data, but its cost becomes a bottleneck for frequent monitoring.
-Although UAV methods have become popular as a cost-effective tool for
-ecological monitoring (citation), operating UAVs in alpine regions is
+imagery of alpine areas are rarely available due to cloud cover, and the
+spatial resolution is not enough to observe vegetation changes at the
+plant community scale. Airborne imagery can obtain high-resolution data,
+but its cost becomes a bottleneck for frequent monitoring. Although UAV
+methods have become a cost-effective tool for ecological monitoring
+(\cite{Baena2017PLOSONE}), operating UAVs in alpine regions is
 challenging due to the strong wind and harsh topology.
@@
 time-lapse cameras mounted on the ground for monitoring green-leaf
-phenologies in forests (Richardson et al., 2018), grasslands (Browning
-et al., 2017) and alpine meadows (Ide and Oguma, 2013). Unlike satellite
-imageries, such cameras provide images free of clouds and atmospheric
-effects. Also, they can obtain high-resolution (i.e., sub-meter scale)
-and frequent (i.e., daily or hourly) images at a meager cost. These
-studies set some regions of interest (ROI) in the images and calculate
-the phenology index (e.g., excess greenness, Woebbecke et al., 1995) for
-each ROI. While we can visually interpret the vegetation distribution
-and its changes from a set of such time-lapse images, few studies have
-tackled this. This lack seems to be because applying such time-lapse
-imageries in monitoring vegetation distribution has two technical
-challenges.
+phenologies in forests (\cite{Richardson2009EcolAppl}), grasslands
+(\cite{Browning2017RemSen}), and alpine meadows
+(\cite{IdeOguma2013EcolInfom}). Unlike satellite imagery, such cameras
+provide images free of clouds and atmospheric effects. Also, they can
+obtain high-resolution (i.e., sub-meter scale) and frequent (i.e., daily
+or hourly) images at a meager cost. These studies set some regions of
+interest (ROI) in the images and calculate the phenology index (e.g.,
+excess greenness, \cite{Woebbecke1995ASAE}). Also, we can visually
+interpret the vegetation distribution and its changes from such
+time-lapse images. However, few studies have tackled this. This lack
+seems to be because applying such time-lapse imagery in monitoring
+vegetation distribution has two technical challenges.
 
-First, unlike multispectral sensors satellites equip, digital cameras
+First, unlike satellites' multispectral sensors, ordinal digital cameras
 can only obtain three bands (Red, Green, and Blue), making it harder to
@@
 data. Treating ground-based time-lapse images as geographic data is
-essential for utilizing these in conservation planning.
+essential to utilize them in conservation planning.
 
@@
 locating vegetation changes with a digital time-lapse camera by solving
-these two challenges. We aim to use cheap but powerful digital
-time-lapse cameras in alpine ecosystem conservation.
+these two challenges. We solved the first challenge by utilizing
+temporal changes in leaf colors in vegetation classification. We also
+developed an accurate method for transforming a ground-based photograph
+into geographic data to tackle the second challenge. We aim to use cheap
+but powerful digital time-lapse cameras in alpine ecosystem
+conservation.
 
@@
 snowmelt and seasonal phenology of evergreen, deciduous dwarf trees
-(e.g., Pinus pumila, Sorbus sp), dwarf bamboos (e.g., Sasa kurilensis),
-and alpine herbaceous plants (e.g., Geum pentapetalum, Nephrophyllidium
-crista-galli). We pulled the images from late summer to late fall of
-2010 and 2020.
+(e.g., \emph{Pinus pumila}, \emph{Sorbus} sp.), dwarf bamboos (e.g.,
+\emph{Sasa kurilensis}), and alpine herbaceous plants (e.g., \emph{Geum
+pentapetalum}, \emph{Nephrophyllidium crista-galli}). We used the images
+from late summer to late fall of 2012 and 2020.
 
@@
 10/11, 10/23 in 2020). We used the images of this season because we can
-separate vegetation from the patterns of autumn foliage coloration. Then
-we pull four images from 11 a.m. to 2 p.m. each day to avoid the effect
-of temporal noise such as shadows. Finally, we got 16 images for each
-year.
+separate vegetation from the patterns of autumn foliage coloration.
+Also, we chose four images from 11 a.m. to 2 p.m. each day to avoid the
+effect of temporal noise such as shadows. Finally, we got 16 images for
+each year.
 
@@
 aligned them before processing. We implemented the program with Python3
-language and OpenCV4 image processing library. First, we set one image
-of 2010 as the alignment target. Next, we automatically found matching
-keypoints between the target and other images using AKAZE local feature
-extractor and K-nearest neighbor matcher. Then, we searched and applied
-the homography matrix that minimizes the distance between each pair of
-the matching points.
+programming language and OpenCV4 (\url{https://opencv.org/}) image
+processing library. First, we set one image of 2010 as the alignment
+target. Next, we automatically found matching keypoints between the
+target and other images using AKAZE local feature extractor
+(\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher. Then, we
+searched and applied the homography matrix that minimizes the distance
+between each pair of the matching points, using OpenCV's
+``findHomography'' function.
 
@@
 
-Next, we classified the pixel time series of repeat photography
-imageries into vegetations. Because deciduous plants have great
-differences in autumn phenology among species, researchers have used
-that information for vegetation classification with satellite imageries
-(e.g., Tigges et al., 2013, Son et al., 2014, Heupel et al., 2018). In
-our target area, we can recognize the vegetation type with the pixel
+Next, we classified the pixel time series of repeat photography imagery
+into vegetation. Because deciduous plants have great differences in
+autumn phenology among species, researchers have used that information
+for vegetation classification with satellite imagery (e.g.,
+\cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}).
+In our target area, we can recognize the vegetation type with the pixel
 time series of autumn (Fig. 2). However, no research has applied this
-technique to ground-based repeat photography imageries. We developed a
+technique to ground-based repeat photography imagery. We developed a
 deep-learning method to take advantage of high-resolution and frequent
@@
 Since ground-based photographs can provide high spatial resolution
-(about \textasciitilde{} 0.5m in our dataset), we can use leaf texture
-as additional information for classification. For example, we can see a
-glossy surface on dwarf bamboos and a mat surface on dwarf pines. Thus,
-we used a small patch (9x9 pixels square) rather than a single pixel as
-an input of the model. Therefore, a model input is a time series of
-image patches. Our model has two components to deal with this data
-structure (see Fig. 3). First, we extracted each patch's features (e.g.,
-texture) using Convolutional Neural Network (CNN) layers (Fig. 4a). CNN
-is a neural network specialized in recognizing spatial structures of
-data, such as images. The CNN part outputs a time series of extracted
-features. Second, we used Recurrent Neural Net (RNN) layers (Fig. 4b) to
-classify the temporal patterns of the features extracted by the CNN
-part. RNN is a neural network specialized in recognizing temporal or
-sequential data dynamics, such as text and speech. Amongst many variants
-of RNN, we used Long Short Time Memory (LSTM). Combining CNN and RNN,
-our model can classify the input image-patch time series considering the
-colors and textures of each patch and their temporal patterns. This
-CNN-RNN architecture has also been used for audio classification. Using
-a Deep Learning method has another positive side effect; mini-batch
-training. Since we used high-resolution images (16 x 21M pix), the
-training dataset became so immense that we could not feed them to the
-model at once: that consumes the computer's RAM too much. However, using
-Deep Learning methods enables us to provide them in small portions
-(called mini-batches) to save RAM consumption.
+(sub-meter scale in our dataset), we can use leaf texture as additional
+information for classification. For example, we can see a glossy surface
+on dwarf bamboos and a mat surface on dwarf pines. Thus, we used a small
+patch (9x9 pixels square) rather than a single pixel as an input of the
+model. Therefore, a model input is a time series of image patches. Our
+model has two components to deal with this data structure (see Fig. 3).
+First, we extracted each patch's features (e.g., texture) using
+Convolutional Neural Network (CNN) layers (Fig. 4a). CNN is a neural
+network specialized in recognizing spatial structures of data, such as
+images. The CNN part outputs a time series of extracted features.
+Second, we used Recurrent Neural Net (RNN) layers (Fig. 4b) to classify
+the temporal patterns of the features extracted by the CNN part. RNN is
+a neural network specialized in recognizing temporal or sequential data
+dynamics, such as text and speech. Amongst many variants of RNN, we used
+Long Short Time Memory (LSTM, \cite{Hochreiter1997LSTM}). Combining CNN
+and RNN, our model can classify the input image-patch time series
+considering the colors and textures of each patch and their temporal
+patterns. This CNN-RNN architecture has also been used for audio
+classification(\cite{Shi2015CRNNtext}) and scene text
+recognition(\cite{Shi2015CRNNtext}). Using a Deep Learning method has
+another positive side effect; mini-batch training. Since we used
+high-resolution images (16 x 21M pix), the training dataset became so
+immense that we could not feed them to the model at once: that consumes
+the computer's RAM too much. However, using Deep Learning methods
+enables us to provide them in small portions (called mini-batches) to
+save RAM consumption.
 
@@
 We implemented the classifier with Python3 language and PyTorch deep
-neural network library. All source codes are publically available via
-GitHub (\url{https://github.com/0kam/xxxx}).
+neural network library (\url{https://pytorch.org/}). All source codes
+are publically available via GitHub
+(\url{https://github.com/0kam/xxxx}).
 
@@
 difficult task, and this causes the underuse of potentially rich
-information in ground-based imageries. In plain words, georectification
+information in ground-based imagery. In plain words, georectification
 means aligning images into Digital Surface Models (DSMs) so that every
@@
 Recently, researchers have developed some georectification methods to
-use ground-based photographs in glaciology (Messerli and Grinsted 2015)
-and snow cover studies (Portnier et al.~2020). Especially, Portnier et
-al.~2020 is worth mentioning for its semi-automatic method using
-mountain silhouettes as GCPs. However, this silhouette-based method has
-a drawback in the projection accuracy. It only uses limited areas
-(silhouettes) of images in the image-to-DSM alignment, and also it
-ignores lens distortion. Because our target site has a complex
-vegetation distribution and our camera has considerable lens distortion,
-we needed a more accurate method.
+use ground-based photographs in glaciology (\cite{Messerli2015GeoInst})
+and snow cover studies (\cite{Portenier2020Cryosphere}). Especially,
+\cite{Portenier2020Cryosphere} is worth mentioning for its
+semi-automatic method using mountain silhouettes as GCPs. However, this
+silhouette-based method has a drawback in the projection accuracy. It
+only uses limited areas (silhouettes) of images in the image-to-DSM
+alignment, and also it ignores lens distortion. Because our target site
+has a complex vegetation distribution and our camera has considerable
+lens distortion, we needed a more accurate method.
 
@@
 
-We modeled the lens distortion based on Weng et al.~1992 and OpenCV's
-implementation (Eq. 1). Our model includes radial
+We modeled the lens distortion based on \cite{Weng1992CameraCalib} and
+OpenCV's implementation (Eq. 1). Our model includes radial
 (k1\textasciitilde k6), tangental (p1, p2), thin prism
@@
 a2). See Weng et al.~1992 for lens distortion modeling. Also, we
-recommend readers to Portnier et al.~2020 for camera models without lens
-distortions. Thus, now we can project GCPs' geographical coordinates
-into image coordinates using lens distortion parameters and other camera
-parameters (the camera location, pose, and the field of view). We
-optimized these (except camera location) by minimizing the square
-projection error of the GCPs using the Covariance Matrix Adaptation
-Evolution Strategy (CMA-ES). We could not estimate the camera location
-because it makes the problem too complicated (e.g., a telephoto taken
-from a distance and a wide-angle taken from a close look similar).
+recommend readers to \cite{Portenier2020Cryosphere} for camera models
+without lens distortions. Thus, now we can project GCPs' geographical
+coordinates into image coordinates using lens distortion parameters and
+other camera parameters (the camera location, pose, and the field of
+view). We optimized these (except camera location) by minimizing the
+square projection error of the GCPs using the Covariance Matrix
+Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}). We could
+not estimate the camera location because it makes the problem too
+complicated (e.g., a telephoto taken from a distance and a wide-angle
+taken from a close look similar).
 
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.05}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.14}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.16}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.12}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.13}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.16}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.15}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.09}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0541}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1405}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1568}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1243}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1351}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1568}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1459}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0865}}@{}}
 \toprule
@@
 \end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\textbf{Other Vegetations}, N = 5
+\textbf{Other vegetation}, N = 5
 \end{minipage} & \begin{minipage}[b]{\linewidth}\centering
@@
 into georeferenced vegetation maps at a meager cost. This task is
-challenging because of 1. the difficulty of classifying vegetations with
+challenging because of 1. the difficulty of classifying vegetation with
 ordinal digital camera imagery and 2. the difficulty of
@@
 species (dwarf bamboo and stone pine) that are easy to classify, even
-with a single image. However, like the previous studies (Tigges et al.,
-2013, Son et al., 2014, Heupel et al., 2018), we expect our method to
-classify more vegetations (e.g., dwarf deciduous trees and alpine
-herbaceous plants) using the temporal information of leaf colors. We
-also used hourly images for each day. Fig. x shows that this additional
-information made our model robust against transient noises, such as
-shadows. Since alpine ecosystems have rough topologies, shadows are a
-considerable problem. Time-lapse cameras are also beneficial for this
-reason.
+with a single image. However, like the previous studies
+(\cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen},
+\cite{Heupel2018PFG}), we expect our method to classify more vegetation
+(e.g., dwarf deciduous trees and alpine herbaceous plants) using the
+temporal information of leaf colors. We also used hourly images for each
+day. Fig. x shows that this additional information made our model robust
+against transient noises, such as shadows. Since alpine ecosystems have
+rough topologies, shadows are a considerable problem. Time-lapse cameras
+are also beneficial for this reason.
 
@@
 \bibliographystyle{unsrt}
-\bibliography{references.bib}
+\bibliography{export.bib}
 

### 2022-05-13 scripts/run_cnnlstm.py
crossvalidation finished

@@ -14,7 +14,7 @@ lstm = CNNLSTM("data/train/patches9x9", "data_source/labels", (9,9), 200, device
 lstm.draw_legend("results/legend.png")
 lstm.draw_teacher("results/teacher.png", (5616,3744), shrink=shrink, hmat=hmat, mask=mask)
 
-lstm.kfold(10, "cnn_lstm9x9_cv_5_ep_200", 5)
+lstm.kfold(200, "cnn_lstm9x9_cv_5_ep_200", 5)
 
 lstm.train(200, log_dir)
 lstm.load("./runs/"+log_dir+"/best.pth")

### 2022-06-06 scripts/analyse.R
Added intepolation.R and analyse.R

@@ -1,0 +1,91 @@
+library(tidyverse)
+library(stars)
+library(sf)
+
+change_names <- function(nums) {
+    case_when(
+        nums == 1 ~ "Dwarf Bamboo",
+        nums == 2 ~ "No Vegetation",
+        nums == 3 ~ "Other Vegetation",
+        nums == 4 ~ "Sky",
+        nums == 5 ~ "Dwarf Pine"
+    )
+}
+
+vege2012 <- read_stars("data/res2012_cnn_9x9.tiff")
+vege2020 <- read_stars("data/res2020_cnn_9x9.tiff")
+dem <- read_stars("data/tateyamadem_small.tiff") %>%
+    st_warp(vege2012)
+
+# Get raster resolutions
+res <- st_dimensions(vege2012) %>%
+    as_tibble() %>%
+    pull(delta) %>%
+    as.numeric() %>%
+    abs()
+
+df <- c(vege2012, vege2020, dem) %>%
+    as_tibble() %>%
+    rename(
+        v2012 = res2012_cnn_9x9.tiff,
+        v2020 = res2020_cnn_9x9.tiff,
+        elevation = tateyamadem_small.tiff
+        ) %>%
+    pivot_longer(
+        cols = c("v2012", "v2020"),
+        names_to = "year",
+        values_to = "vegetation",
+        names_prefix = "v"
+        ) %>%
+    filter(is.na(vegetation) == FALSE) %>%
+    mutate(vegetation = change_names(vegetation)) %>%
+    filter(vegetation != "Sky")
+
+# Vegetation histogram along elevation
+breaks <- seq(2350, 3000, 50)
+
+df %>%
+    group_by(vegetation, year) %>%
+    ggplot(aes(x = elevation, fill = year)) +
+    geom_histogram(
+        aes(y = after_stat(count * res[1] * res[2])),
+        breaks = breaks,
+        alpha = 0.4,
+        position = "identity"
+        ) +
+    facet_wrap(~vegetation) +
+    ylab(expression(paste ("Area (", {mm^2}, ")", sep = ""))) +
+    xlab("Elevation") +
+    theme_minimal()
+
+# Elevation-axis movement of the vegetation
+df %>%
+    group_by(vegetation, year) %>%
+    summarise(
+        mean_elevation = mean(elevation)
+    )
+
+df %>%
+    group_by(vegetation, year) %>%
+    summarise(
+        elevation_2012 = mean(elevation[year == "2012"]),
[…]

### 2022-06-06 scripts/georectify.py

@@ -1,0 +1,87 @@
+# Loading requirements
+from alproj.surface import create_db, crop
+from alproj.project import sim_image, reverse_proj
+from alproj.gcp import akaze_match, set_gcp
+from alproj.optimize import CMAOptimizer
+import sqlite3
+import numpy as np
+import rasterio
+
+res = 1.0 # Resolution in m
+aerial = rasterio.open("data/tateyama2.tiff")
+dsm = rasterio.open("data/tateyamadem_small.tiff")
+out_path = "data/pointcloud.db" # Output database
+
+create_db(aerial, dsm, out_path) # This takes some minutes
+
+params = {"x":732731,"y":4051171, "z":2458, "fov":70, "pan":100, "tilt":0, "roll":0,\
+          "a1":1, "a2":1, "k1":0, "k2":0, "k3":0, "k4":0, "k5":0, "k6":0, \
+          "p1":0, "p2":0, "s1":0, "s2":0, "s3":0, "s4":0, \
+          "w":5616, "h":3744, "cx":5616/2, "cy":3744/2}
+
+conn = sqlite3.connect("data/pointcloud.db")
+
+distance = 3000 # The radius of the fan shape
+chunksize = 1000000
+
+vert, col, ind = crop(conn, params, distance, chunksize) # This takes some minutes.
+
+import cv2
+sim = sim_image(vert, col, ind, params)
+cv2.imwrite("data/initial.png", sim)
+
+df = reverse_proj(sim, vert, ind, params)
+
+path_org = "data_source/aligned/2012/mrd_085_eos_vis_20121021_1200.png"
+path_sim = "data/initial.png"
+
+match, plot = akaze_match(path_org, path_sim, ransac_th=200, plot_result=True)
+cv2.imwrite("data/matched.png", plot)
+gcps = set_gcp(match, df)
+gcps.to_csv("data/gcp.csv")
+
+obj_points = gcps[["x","y","z"]] # Object points in a geographic coordinate system
+img_points = gcps[["u","v"]] # Image points in an image coordinate system 
+params_init = params # Initial parameters
+target_params = ["fov", "pan", "tilt", "roll", "a1", "a2", "k1", "k2", "k3", "k4", "k5", "k6", "p1", "p2", "s1", "s2", "s3", "s4"] # Parameters to be optimized
+cma_optimizer = CMAOptimizer(obj_points, img_points, params_init) # Create an optimizer instance.
+cma_optimizer.set_target(target_params)
[…]

### 2022-06-06 scripts/run_cnnlstm.py

@@ -1,0 +1,103 @@
+from PIL import Image
+from scripts.utils import set_patches
+from scripts.cnn_lstm import CNNLSTM
+import numpy as np
+import tensorboardX
+
+hmat = np.loadtxt("data_source/hmat_label.txt")
+mask = np.load("data_source/mask.npy")
+shrink = 10
+log_dir = "cnn_lstm9x9"
+
+#set_patches("data_source/labels", "data_source/aligned/2012", "data/train/patches9x9/", (9,9), batch_size=50, unlabelled=False, shrink=shrink, hmat=hmat, mask=mask)
+#set_patches("data_source/labels", "data_source/aligned/2020", "data/train/patches9x9/", (9,9), batch_size=50, unlabelled=False, shrink=shrink, hmat=hmat, mask=mask)
+
+lstm = CNNLSTM("data/train/patches9x9", "data_source/labels", (9,9), 200, device="cuda")
+lstm.draw_legend("results/legend.png")
+lstm.draw_teacher("results/teacher.png", (5616,3744), shrink=shrink, hmat=hmat, mask=mask)
+
+lstm.kfold(10, "cnn_lstm9x9_cv_5_ep_200", 5)
+
+lstm.train(200, log_dir)
+lstm.load("./runs/"+log_dir+"/best.pth")
+
+res2012, _ = lstm.draw("data_source/aligned/2012", "results/cnn_9x9_2012.png", (9,9), 50000)
+res2020, _ = lstm.draw("data_source/aligned/2020", "results/cnn_9x9_2020.png", (9,9), 50000)
+
+
+# Plotting results
+import numpy as np
+from matplotlib import pyplot as plt
+import pylab as pl
+from matplotlib.colors import ListedColormap
+
+## Color maps
+
+cmap_veg = ListedColormap(
+    np.array(
+        [[0,0,0], # 0: No data
+        [154,205,50], # 1: Dwarf bamboo
+        [192,192,192], # 2: No vegetation
+        [139,69,19], # 3: Other vegetation
+        [255,255,255], # 4: Sky
+        [0,100,0]] # 5: Dwarf pine
+    ) / 255
+)
+
+cmap_diff = ListedColormap(
+    np.array(
+        [[0,0,0,0], # 0: No data
+        [192,192,192, 127], # 1: No Difference
[…]

### 2022-06-06 paper/paper.tex
Initial commit

@@
 
-\title{Automatically drawing vegetation maps using digital time-lapse
-cameras in alpine ecosystems}
+\title{Automatically drawing vegetation maps using digital time-lapse cameras in alpine ecosystems}
 
@@
 \setlength{\parindent}{10.5pt}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 \begin{document}
@@
 
-The effects of climate change on terrestrial ecosystems are particularly
-significant in alpine regions (\cite{IPCC2007}). Alpine vegetation
-depends on severe conditions such as low temperatures and long
-snow-covered periods. Thus alpine areas have rare and unique species
-adapted to the extreme environments. Several studies have reported that
-recent global climatic changes, e.g., increasing temperatures and
-reducing snow-covered periods, have accelerated the invasion of
-non-native species into alpine areas (see
-\cite{Alexander2016AlpBotany}). In Japan, dwarf bamboo (\emph{Sasa
-kurilensis}) has invaded alpine snow meadows, probably driven by the
-extension of the snow-free period (\cite{Kudo2011EcoEvo}). Also, climate
-change has affected the growth and phenologies of native species. For
-example, the growth of dwarf pine (\emph{Pinus pumila}), a dominant
-species in Japanese alpine regions, has been affected by climatic
-conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}).
-Monitoring and predicting such changes are essential for effective
-conservation planning. Since the impact of climate change on alpine
-vegetation varies depending on species and the microhabitats
-(\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide
-range is required.
+The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (\cite{IPCC2007}).
+Alpine vegetation depends on severe conditions such as low temperatures and long snow-covered periods.
+Thus alpine areas have rare and unique species adapted to the extreme environments.
+Several studies have reported that recent global climatic changes, e.g., increasing temperatures and reducing snow-covered periods, have accelerated the invasion of non-native species into alpine areas (see \cite{Alexander2016AlpBotany}).
+In Japan, dwarf bamboo (\emph{Sasa kurilensis}) has invaded alpine snow meadows, probably driven by the extension of the snow-free period (\cite{Kudo2011EcoEvo}).
+Also, climate change has affected the growth and phenologies of native species.
+For example, the growth of dwarf pine (\emph{Pinus pumila}), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}).
+Monitoring and predicting such changes are essential for effective conservation planning.
+Since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.
 
-Previous studies have mainly depended on field observations, yet it is
-hard to cover broad areas in alpine regions due to poor accessibility
-and severe weather. Satellite, airborne, and Unmanned Aerial Vehicle
-(UAV) remote sensing methods seem to be alternatives. However, satellite
-imagery of alpine areas are rarely available due to cloud cover, and the
-spatial resolution is not enough to observe vegetation changes at the
-plant community scale. Airborne imagery can obtain high-resolution data,
-but its cost becomes a bottleneck for frequent monitoring. Although UAV
-methods have become a cost-effective tool for ecological monitoring
-(\cite{Baena2017PLOSONE}), operating UAVs in alpine regions is
-challenging due to the strong wind and harsh topology.
+Previous studies have mainly depended on field observations, yet it is hard to cover broad areas in alpine regions due to poor accessibility and severe weather.
+Satellite, airborne, and Unmanned Aerial Vehicle (UAV) remote sensing methods seem to be alternatives.
+However, satellite imagery of alpine areas is rarely available due to cloud cover, and the spatial resolution is not enough to observe vegetation changes at the plant community scale.
+Airborne imagery can obtain high-resolution data, but its cost becomes a bottleneck for frequent monitoring.
+Although UAV methods have become a cost-effective tool for ecological monitoring (\cite{Baena2017PLOSONE}), operating UAVs in alpine regions is challenging due to the strong wind and harsh topology.
 
-On the other hand, researchers have also utilized automated digital
-time-lapse cameras mounted on the ground for monitoring green-leaf
-phenologies in forests (\cite{Richardson2009EcolAppl}), grasslands
-(\cite{Browning2017RemSen}), and alpine meadows
-(\cite{IdeOguma2013EcolInfom}). Unlike satellite imagery, such cameras
-provide images free of clouds and atmospheric effects. Also, they can
-obtain high-resolution (i.e., sub-meter scale) and frequent (i.e., daily
-or hourly) images at a meager cost. These studies set some regions of
-interest (ROI) in the images and calculate the phenology index (e.g.,
-excess greenness, \cite{Woebbecke1995ASAE}). Also, we can visually
-interpret the vegetation distribution and its changes from such
-time-lapse images. However, few studies have tackled this. This lack
-seems to be because applying such time-lapse imagery in monitoring
-vegetation distribution has two technical challenges.
+On the other hand, researchers have also utilized automated digital time-lapse cameras mounted on the ground for monitoring green-leaf phenologies in forests (\cite{Richardson2009EcolAppl}), grasslands (\cite{Browning2017RemSen}), and alpine meadows (\cite{IdeOguma2013EcolInfom}).
+Unlike satellite imagery, such cameras provide images free of clouds and atmospheric effects.
+Also, they can obtain high-resolution (i.e., sub-meter scale) and frequent (i.e., daily or hourly) images at a meager cost.
+These studies set some regions of interest (ROI) in the images and calculate the phenology index (e.g., excess greenness, \cite{Woebbecke1995ASAE}).
+Also, we can visually interpret the vegetation distribution and its changes from such time-lapse images.
+However, few studies have tackled this.
+This lack of studies seems to be because applying such time-lapse imagery in monitoring vegetation distribution has two technical challenges.
 
-First, unlike satellites' multispectral sensors, ordinal digital cameras
-can only obtain three bands (Red, Green, and Blue), making it harder to
-classify the vegetation. Second, since digital time-lapse cameras are
-mounted on the ground, applying geo-spatial analysis to these images is
-challenging. In other words, even if we find a vegetation change, we
-cannot identify its geographic location and analyze it with topological
-data. Treating ground-based time-lapse images as geographic data is
-essential to utilize them in conservation planning.
+First, unlike satellites' multispectral sensors, ordinal digital cameras can only obtain three bands (Red, Green, and Blue), making it harder to classify the vegetation.
+Second, since digital time-lapse cameras are mounted on the ground, transforming these images into geospatial data (e.g., orthoimage) is challenging.
+In other words, even if we find a vegetation change, we cannot identify its geographic location and analyze it with other geographic data (e.g., topography).
+Treating ground-based time-lapse images as geographic data is essential to utilize them in conservation planning.
 
-This study proposes an automated method for drawing vegetation maps and
-locating vegetation changes with a digital time-lapse camera by solving
-these two challenges. We solved the first challenge by utilizing
-temporal changes in leaf colors in vegetation classification. We also
-developed an accurate method for transforming a ground-based photograph
-into geographic data to tackle the second challenge. We aim to use cheap
-but powerful digital time-lapse cameras in alpine ecosystem
-conservation.
+This study proposes an automated method for drawing vegetation maps and locating vegetation changes with a digital time-lapse camera by solving these two challenges.
+We solved the first challenge by utilizing temporal changes in leaf colors in vegetation classification.
+We also developed an accurate method for transforming a ground-based photograph into geographic data to tackle the second challenge.
+Finally, we show an example application of our method by detecting and localizing vegetation changes with an 8-years digital time-lapse imagery of the Japanese alps.
+We aim to use cheap but powerful digital time-lapse cameras in alpine ecosystem conservation.
 
@@
 \hypertarget{digital-time-lapse-camera-imagery}{%
-\subsection{Digital time-lapse camera
-imagery}\label{digital-time-lapse-camera-imagery}}
+\subsection{Digital time-lapse camera imagery}\label{digital-time-lapse-camera-imagery}}
 
-We used repeat photography data owned by National Institute for
-Environmental Studies, Japan (NIES). All the images are publically
-available on NIES' webpage
-(\url{https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2}). In
-2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon
-Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m
-a.s.l., above the forest limit), located at the foot of Mt. Tateyama
-(3015 m a.s.l.), in the Nothern Japanese Alps. The camera takes one
-photograph per hour, from 6 a.m. to 7 p.m. . The camera's field of view
-(FOV) includes Mt. Tateyama, which ranges from about 2350 m a.s.l. to
-3015 m a.s.l. in elevation. The area has a complex mosaic-like
-vegetation structure because of its topography, including rocks, cliffs,
-curls, and moraines. From April to November, the camera has observed the
-snowmelt and seasonal phenology of evergreen, deciduous dwarf trees
-(e.g., \emph{Pinus pumila}, \emph{Sorbus} sp.), dwarf bamboos (e.g.,
-\emph{Sasa kurilensis}), and alpine herbaceous plants (e.g., \emph{Geum
-pentapetalum}, \emph{Nephrophyllidium crista-galli}). We used the images
-from late summer to late fall of 2012 and 2020.
+We used repeat photography data owned by National Institute for Environmental Studies, Japan (NIES).
+All the images are publically available on NIES' webpage (\url{https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2}).
+In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt.
+Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps.
+The camera takes one photograph per hour, from 6 a.m.
+to 7 p.m.
+.
+The camera's field of view (FOV) includes Mt.
+Tateyama, which ranges from about 2350 m a.s.l.
+to 3015 m a.s.l.
+in elevation.
+The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines.
+From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen, deciduous dwarf trees (e.g., \emph{Pinus pumila}, \emph{Sorbus} sp.), dwarf bamboos (e.g., \emph{Sasa kurilensis}), and alpine herbaceous plants (e.g., \emph{Geum pentapetalum}, \emph{Nephrophyllidium crista-galli}).
+We used the images from late summer to late fall of 2012 and 2020.
 
@@
 
-First, we selected images that are suitable for vegetation
-classification. We choose four days with good weather from late summer
-to late fall each year (9/19, 10/1, 10/11, 10/23 in 2010. 9/19, 10/2,
-10/11, 10/23 in 2020). We used the images of this season because we can
-separate vegetation from the patterns of autumn foliage coloration.
-Also, we chose four images from 11 a.m. to 2 p.m. each day to avoid the
-effect of temporal noise such as shadows. Finally, we got 16 images for
-each year.
+First, we selected images that are suitable for vegetation classification.
+We choose four days with good weather from late summer to late fall each year (9/19, 10/1, 10/11, 10/23 in 2010.
+9/19, 10/2, 10/11, 10/23 in 2020).
+We used the images of this season because we can separate vegetation from the patterns of autumn foliage coloration.
+Also, we chose four images from 11 a.m.
+to 2 p.m.
+each day to avoid the effect of temporal noise such as shadows.
+Finally, we got 16 images for each year.
 
 \hypertarget{automatic-image-to-image-alignment}{%
-\subsubsection{Automatic image-to-image
-alignment}\label{automatic-image-to-image-alignment}}
+\subsubsection{Automatic image-to-image alignment}\label{automatic-image-to-image-alignment}}
 
-Since images are slightly misaligned with each other due to wind, we
-aligned them before processing. We implemented the program with Python3
-programming language and OpenCV4 (\url{https://opencv.org/}) image
-processing library. First, we set one image of 2010 as the alignment
-target. Next, we automatically found matching keypoints between the
-target and other images using AKAZE local feature extractor
-(\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher. Then, we
-searched and applied the homography matrix that minimizes the distance
-between each pair of the matching points, using OpenCV's
-``findHomography'' function.
+Since images are slightly misaligned with each other due to wind, we aligned them before processing.
+We implemented the program with Python3 programming language and OpenCV4 (\url{https://opencv.org/}) image processing library.
+First, we set one image of 2010 as the alignment target.
+Next, we automatically found matching keypoints between the target and other images using AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
+Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's ``findHomography'' function.
 
 \hypertarget{automatic-vegetation-classification}{%
-\subsection{Automatic vegetation
-classification}\label{automatic-vegetation-classification}}
+\subsection{Automatic vegetation classification}\label{automatic-vegetation-classification}}
 
-Next, we classified the pixel time series of repeat photography imagery
-into vegetation. Because deciduous plants have great differences in
-autumn phenology among species, researchers have used that information
-for vegetation classification with satellite imagery (e.g.,
-\cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}).
-In our target area, we can recognize the vegetation type with the pixel
-time series of autumn (Fig. 2). However, no research has applied this
-technique to ground-based repeat photography imagery. We developed a
-deep-learning method to take advantage of high-resolution and frequent
-repeat photography data. Fig.3 shows the classification process.
+Next, we classified the pixel time series of repeat photography imagery into vegetation.
+Because deciduous plants have great differences in autumn phenology among species, researchers have used that information for vegetation classification with satellite imagery (e.g., \cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}).
+In our target area, we can recognize the vegetation type with the pixel time series of autumn (Fig.
+2).
+However, no research has applied this technique to ground-based repeat photography imagery.
+We developed a deep-learning method to take advantage of high-resolution and frequent repeat photography data.
+Fig.3 shows the classification process.
 
@@
 
-Since ground-based photographs can provide high spatial resolution
-(sub-meter scale in our dataset), we can use leaf texture as additional
-information for classification. For example, we can see a glossy surface
-on dwarf bamboos and a mat surface on dwarf pines. Thus, we used a small
-patch (9x9 pixels square) rather than a single pixel as an input of the
-model. Therefore, a model input is a time series of image patches. Our
-model has two components to deal with this data structure (see Fig. 3).
-First, we extracted each patch's features (e.g., texture) using
-Convolutional Neural Network (CNN) layers (Fig. 4a). CNN is a neural
-network specialized in recognizing spatial structures of data, such as
-images. The CNN part outputs a time series of extracted features.
-Second, we used Recurrent Neural Net (RNN) layers (Fig. 4b) to classify
-the temporal patterns of the features extracted by the CNN part. RNN is
-a neural network specialized in recognizing temporal or sequential data
-dynamics, such as text and speech. Amongst many variants of RNN, we used
-Long Short Time Memory (LSTM, \cite{Hochreiter1997LSTM}). Combining CNN
-and RNN, our model can classify the input image-patch time series
-considering the colors and textures of each patch and their temporal
-patterns. This CNN-RNN architecture has also been used for audio
-classification(\cite{Shi2015CRNNtext}) and scene text
-recognition(\cite{Shi2015CRNNtext}). Using a Deep Learning method has
-another positive side effect; mini-batch training. Since we used
-high-resolution images (16 x 21M pix), the training dataset became so
-immense that we could not feed them to the model at once: that consumes
-the computer's RAM too much. However, using Deep Learning methods
-enables us to provide them in small portions (called mini-batches) to
-save RAM consumption.
+Since ground-based photographs can provide high spatial resolution (sub-meter scale in our dataset), we can use leaf texture as additional information for classification.
+For example, we can see a glossy surface on dwarf bamboos and a mat surface on dwarf pines.
+Thus, we used a small patch (9x9 pixels square) rather than a single pixel as an input of the model.
+Therefore, a model input is a time series of image patches.
 
-\hypertarget{implementation-and-model-training}{%
-\subsubsection{Implementation and model
-training}\label{implementation-and-model-training}}
+Our model has two components to deal with this data structure (see Fig.
+3).
+First, we extracted each patch's features (e.g., texture) using Convolutional Neural Network (CNN) layers (Fig.
+4a).
+CNN is a neural network specialized in recognizing spatial structures of data, such as images.
+The CNN part outputs a time series of extracted features.
+Second, we used Recurrent Neural Net (RNN) layers (Fig.
+4b) to classify the temporal patterns of the features extracted by the CNN part.
+RNN is a neural network specialized in recognizing temporal or sequential data dynamics, such as text and speech.
+Amongst many variants of RNN, we used Long Short Time Memory (LSTM, \cite{Hochreiter1997LSTM}).
+Combining CNN and RNN, our model can classify the input image-patch time series considering the colors and textures of each patch and their temporal patterns.
+This CNN-RNN architecture has also been used for audio classification(\cite{Shi2015CRNNtext}) and scene text recognition(\cite{Shi2015CRNNtext}).
 
-We implemented the classifier with Python3 language and PyTorch deep
-neural network library (\url{https://pytorch.org/}). All source codes
-are publically available via GitHub
-(\url{https://github.com/0kam/xxxx}).
+Using a Deep Learning method has another positive side effect; mini-batch training.
+Since we used high-resolution images (16 x 21M pix), the training dataset became so immense that we could not feed them to the model at once: that consumes the computer's RAM too much.
+However, using Deep Learning methods enables us to provide them in small portions (called mini-batches) to save RAM consumption.
 
@@
 
-We set 5 classes: dwarf pine, dwarf bamboo, other vegetation, no
-vegetation, and sky. Using free image annotation software (Semantic
-Segmentation Editor), an expert prepared teacher data (Fig. x) for
-classification.
+We set 5 vegetation classes: dwarf pine, dwarf bamboo, other vegetation, no vegetation, and sky.
+Using a free image annotation software (Semantic Segmentation Editor, Hitachi, \url{https://github.com/Hitachi-Automotive-And-Industry-Lab/semantic-segmentation-editor}), an expert drew polygons on an image of 2015 for each class.
+Since vegetation might be different in 2012, 2015, and 2020, applying this teacher data to the image of 2012 and 2020 may cause misclassification.
+However, vegetation changes are expected to occur at the edge of the plant community.
+Thus we shrink each polygon with several pixels before applying it to the training.
+
+\hypertarget{implementation-and-model-training}{%
+\subsubsection{Implementation and model training}\label{implementation-and-model-training}}
+
+We implemented the classifier with Python3 language and PyTorch deep neural network library (\url{https://pytorch.org/}).
+All source codes are publically available via GitHub (\url{https://github.com/0kam/xxxx}).
 
@@
 
-Then, we developed a novel method to convert ground-based landscape
-imagery into GIS-ready geographical data. This process is called
-georectification. Georectification of ground-based images has been a
-difficult task, and this causes the underuse of potentially rich
-information in ground-based imagery. In plain words, georectification
-means aligning images into Digital Surface Models (DSMs) so that every
-pixel of an image gets a geographical coordinate. We can consider a
-camera as a function that transforms 3D geographical coordinates
-(latitude, longitude, height) into 2D image coordinates (locations of
-each pixel). So estimating the parameters of this function (such as the
-camera location, pose, and the field of view), we can align an image to
-a DSM. Usually, georectification has three steps: 1. Finding Ground
-Control Points (GCPs) in the image. 2. Estimating camera parameters such
-as camera poses and field of view using GCPs. 3. Mapping the image onto
-the DSM using camera parameters.
+Then, we developed a novel method to convert ground-based landscape imagery into GIS-ready geographical data.
+This process is called georectification.
+Georectification of ground-based images has been a difficult task, and this causes the underuse of potentially rich information in ground-based imagery.
+In plain words, georectification means aligning images into Digital Surface Models (DSMs) so that every pixel of an image gets a geographical coordinate.
+We can consider a camera as a function that transforms 3D geographical coordinates (latitude, longitude, height) into 2D image coordinates (locations of each pixel).
+So estimating the parameters of this function (such as the camera location, pose, and the field of view), we can map an image onto a DSM.
+We recommend readers to \cite{Portenier2020Cryosphere} for a plain mathmatical explanation of this process.
+Usually, georectification has three steps:
 
-Recently, researchers have developed some georectification methods to
-use ground-based photographs in glaciology (\cite{Messerli2015GeoInst})
-and snow cover studies (\cite{Portenier2020Cryosphere}). Especially,
-\cite{Portenier2020Cryosphere} is worth mentioning for its
-semi-automatic method using mountain silhouettes as GCPs. However, this
-silhouette-based method has a drawback in the projection accuracy. It
-only uses limited areas (silhouettes) of images in the image-to-DSM
-alignment, and also it ignores lens distortion. Because our target site
-has a complex vegetation distribution and our camera has considerable
-lens distortion, we needed a more accurate method.
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Finding Ground Control Points (GCPs) in the image.\\
+\item
+  Estimating camera parameters such as camera poses and field of view using GCPs.\\
+\item
+  Mapping the image onto the DSM using camera parameters.
+\end{enumerate}
+
+Recently, researchers have developed some georectification methods to use ground-based photographs in glaciology (\cite{Messerli2015GeoInst}) and snow cover studies (\cite{Portenier2020Cryosphere}).
+Especially, \cite{Portenier2020Cryosphere} is worth mentioning for its semi-automatic method using mountain silhouettes as GCPs.
+However, this silhouette-based method has a drawback in the projection accuracy.
+It only uses limited areas (silhouettes) of images in the image-to-DSM alignment, and also it ignores lens distortion.
+Because our target site has a complex vegetation distribution and our camera has considerable lens distortion, we needed a more accurate method.
 
 \hypertarget{local-feature-based-matching-of-images-and-dsms}{%
-\subsection{Local-feature-based matching of images and
-DSMs}\label{local-feature-based-matching-of-images-and-dsms}}
+\subsection{Local-feature-based matching of images and DSMs}\label{local-feature-based-matching-of-images-and-dsms}}
 
-To get matching points between images and DSMs on a broader area, we
-used an airborne image already georectified. Combining an airborne image
-and a DSM, we rendered simulated landscape images (Fig. x). Then we got
-matching points (GCPs) by applying AKAZE local feature matcher to a
-target image and this simulated image (Fig. x). GCPs have geographical
-coordinates (from the DSM) and image coordinates (from the image). Our
-procedure requires the camera's exact location and initial camera
-parameters to render the simulated image.
+To get matching points between images and DSMs on a broader area, we used an airborne image already georectified.
+Combining an airborne image and a DSM, we rendered simulated landscape images (Fig.
+x).
+Then we got matching points (GCPs) by applying AKAZE local feature matcher to a target image and this simulated image (Fig.
+x).
+GCPs have geographical coordinates (from the DSM) and image coordinates (from the image).
+Our procedure requires the camera's exact location and initial camera parameters to render the simulated image.
 
 \hypertarget{modeling-and-estimating-lens-distortions}{%
-\subsection{Modeling and estimating lens
-distortions}\label{modeling-and-estimating-lens-distortions}}
+\subsection{Modeling and estimating lens distortions}\label{modeling-and-estimating-lens-distortions}}
 
-We modeled the lens distortion based on \cite{Weng1992CameraCalib} and
-OpenCV's implementation (Eq. 1). Our model includes radial
-(k1\textasciitilde k6), tangental (p1, p2), thin prism
-(s1\textasciitilde s4) distortion, and unequal pixel aspect ratio (a1,
-a2). See Weng et al.~1992 for lens distortion modeling. Also, we
-recommend readers to \cite{Portenier2020Cryosphere} for camera models
-without lens distortions. Thus, now we can project GCPs' geographical
-coordinates into image coordinates using lens distortion parameters and
-other camera parameters (the camera location, pose, and the field of
-view). We optimized these (except camera location) by minimizing the
-square projection error of the GCPs using the Covariance Matrix
-Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}). We could
-not estimate the camera location because it makes the problem too
-complicated (e.g., a telephoto taken from a distance and a wide-angle
-taken from a close look similar).
+We modeled the lens distortion (\ref{camera_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation, where \({x}''\) and \({y}''\) are the coordinates of each pixels after distortion and \(x'\) and \(y'\) are the coordinates before distortion.
+Our model includes radial (\(k1~k6\)), tangental (\(p1, p2\)), thin prism (\(s1~s4\)) distortion, and unequal pixel aspect ratio (\(a1, a2\)).
+See Weng et al.~1992 for the details of lens distortion modeling.
+Thus, now we can project GCPs' geographical coordinates into image coordinates using lens distortion parameters and other camera parameters (the camera location, pose, and the field of view).
+We optimized these (except camera location) by minimizing the square projection error of the GCPs using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}).
+We could not estimate the camera location because it makes the problem too complicated (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).
 
-\[
+\begin{equation}
+\label{camera_model}
 \begin{bmatrix}
@@
 y’ \frac{1 + a_1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + a_2 + k_4 r^2 + k_5 r^4 + k_6 r^6} + p_1 (r^2 + 2 y’^2) + 2 p_2 x’ y’ + s_3 r^2 + s_4 r^4 \ \end{bmatrix}
-\]
+\end{equation}
 
 \hypertarget{implementation-and-data-set}{%
-\subsection{Implementation and data
-set}\label{implementation-and-data-set}}
+\subsection{Implementation and data set}\label{implementation-and-data-set}}
 
-We implemented the algorithm with Python3 language and published it as
-an open-source package via GitHub
-(\url{https://github.com/0kam/alproj}). You can try it with your data.
-We used an airborne photograph taken in the November of 201X with a
-spatial resolution of 1.0 m. Also, we used the 5m resolution Digital
-Elevation Model provided by the Geospatial Information Authority of
-Japan (GSI) as a DSM.
+We implemented the algorithm with Python3 language and published it as an open-source package via GitHub (\url{https://github.com/0kam/alproj}).
+You can try it with your data.
+We used an airborne photograph taken in the November of 201X with a spatial resolution of 1.0 m.
+Also, we used the 5m resolution Digital Elevation Model provided by the Geospatial Information Authority of Japan (GSI) as a DSM.
 
@@
 \hypertarget{vegetation-classification-accuracy}{%
-\subsection{Vegetation classification
-accuracy}\label{vegetation-classification-accuracy}}
+\subsection{Vegetation classification accuracy}\label{vegetation-classification-accuracy}}
 
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0541}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1405}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1568}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1243}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1351}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1568}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1459}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0865}}@{}}
+We evaluated the performance of the vegetation classifier using a 5-fold cross-validation design.
+Each fold was stratified with the vegetation categories.
+We used three standard metrics in machine learning evaluation: precision, recall, and F1-score (\ref{metrics}), where \(TP, FP, FN\) is true positives, false positives, and false negatives, respectively.
+
+\begin{align}
+\label{metrics}
+precision = \frac{TP}{TP + FP} \\
+recall = \frac{TP}{TP + FN} \\
+F_1 = \frac{2 \cdot precision \cdot recall}{precision + recall} \\
+\end{align}
+
+The vegetation classifier achieved a high recall and precision in all five categories \ref{tab:vegetation_cv}.
+Recall and precision were lowest in dwarf bamboo with the smallest training data.
+Even in dwarf bamboo, false positives occurred at low frequency (about 5\%), and only a tiny amount of true positives were missed by the pipeline (about 4\%).
+Since the weighted average of each metric was higher (more than 0.99), balancing the training dataset with vegetation categories may improve these results.
+
+\ref{fig:vegetation} shows the products of vegetation classification. We can observe the distribution of dwarf pine and dwarf bamboo at the plant-community scale.
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-1}Cross validation result \label{tab:vegetation_cv}}
+\centering
+\begin{tabular}[t]{llll}
 \toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\textbf{Macro Average}, N = 5
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\textbf{Weighted Average}, N = 5
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\textbf{Dwarf Pine}, N = 5
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\textbf{Dwarf Bamboo}, N = 5
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\textbf{Other vegetation}, N = 5
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\textbf{Non Vegetation}, N = 5
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\textbf{Sky}, N = 5
-\end{minipage} \\
+vegetation & f1-score & precision & recall\\
 \midrule
-\endhead
-Precision & 0.977 (0.008) & 0.997 (0.001) & 0.977 (0.012) & 0.951
-(0.013) & 0.999 (0.000) & 0.959 (0.066) & 1.000 (0.000) \\
-Recall & 0.987 (0.001) & 0.997 (0.001) & 0.995 (0.003) & 0.960 (0.006) &
-0.996 (0.002) & 0.984 (0.004) & 1.000 (0.000) \\
-F1 Score & 0.982 (0.005) & 0.997 (0.001) & 0.986 (0.005) & 0.955 (0.004)
-& 0.997 (0.001) & 0.970 (0.034) & 1.000 (0.000) \\
+ & 0.982 & 0.977 & 0.987\\
+\cmidrule{2-4}
+\multirow{-2}{*}{\raggedright\arraybackslash Macro Average} & (0.005) & (0.008) & (0.001)\\
+\cmidrule{1-4}
+ & 0.997 & 0.997 & 0.997\\
+\cmidrule{2-4}
+\multirow{-2}{*}{\raggedright\arraybackslash Weighted Average} & (0.001) & (0.001) & (0.001)\\
+\cmidrule{1-4}
+ & 0.986 & 0.977 & 0.995\\
+\cmidrule{2-4}
+\multirow{-2}{*}{\raggedright\arraybackslash Dwarf Pine} & (0.005) & (0.012) & (0.003)\\
+\cmidrule{1-4}
+ & 0.955 & 0.951 & 0.960\\
+\cmidrule{2-4}
+\multirow{-2}{*}{\raggedright\arraybackslash Dwarf Bamboo} & (0.004) & (0.013) & (0.006)\\
+\cmidrule{1-4}
+ & 0.997 & 0.999 & 0.996\\
+\cmidrule{2-4}
+\multirow{-2}{*}{\raggedright\arraybackslash Other vegetation} & (0.001) & (0.000) & (0.002)\\
+\cmidrule{1-4}
+ & 0.970 & 0.959 & 0.984\\
+\cmidrule{2-4}
+\multirow{-2}{*}{\raggedright\arraybackslash Non Vegetation} & (0.034) & (0.066) & (0.004)\\
+\cmidrule{1-4}
+ & 1.000 & 1.000 & 1.000\\
+\cmidrule{2-4}
+\multirow{-2}{*}{\raggedright\arraybackslash Sky} & (0.000) & (0.000) & (0.000)\\
 \bottomrule
-\end{longtable}
+\multicolumn{4}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}Mean (SD) of 5-Fold Cross-Varidation}\\
+\end{tabular}
+\end{table}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{vegetation} \caption{Vegetation classification results}\label{fig:vegetation}
+\end{figure}
 
@@
 \hypertarget{detection-and-localization-of-vegetation-changes}{%
-\subsection{Detection and localization of vegetation
-changes}\label{detection-and-localization-of-vegetation-changes}}
+\subsection{Detection and localization of vegetation changes}\label{detection-and-localization-of-vegetation-changes}}
 
@@
 
-We suggested a fully automated procedure to transform time-lapse imagery
-into georeferenced vegetation maps at a meager cost. This task is
-challenging because of 1. the difficulty of classifying vegetation with
-ordinal digital camera imagery and 2. the difficulty of
-georectification. We solved these issues by 1. using the temporal
-information of autumn leaf colors for vegetation classification and 2.
-developing a novel method for accurate image georectification. Our
-vegetation classification performance (with an accuracy of 0.87) and
-georectification methods (with an RMSE of \(rmse\) m) are practical.
+We suggested a fully automated procedure to transform time-lapse imagery into georeferenced vegetation maps at a meager cost.
+This task is challenging because of 1.
+the difficulty of classifying vegetation with ordinal digital camera imagery and 2.
+the difficulty of georectification.
+We solved these issues by 1.
+using the temporal information of autumn leaf colors for vegetation classification and 2.
+developing a novel method for accurate image georectification.
+Our vegetation classification performance (with an accuracy of 0.87) and georectification methods (with an RMSE of \(rmse\) m) are practical.
 
 \hypertarget{the-benefit-of-using-time-series-imagery-for-vegetation-classification}{%
-\subsection{The benefit of using time-series imagery for vegetation
-classification}\label{the-benefit-of-using-time-series-imagery-for-vegetation-classification}}
+\subsection{The benefit of using time-series imagery for vegetation classification}\label{the-benefit-of-using-time-series-imagery-for-vegetation-classification}}
 
-One of the shortcomings of ordinal digital cameras is that they only
-have three bands (Red, Blue, and Green). We made up for this lack of
-information by using the rich temporal information that time-lapse
-cameras can obtain. Many plant species have characteristic phenologies,
-such as flowering and autumn foliages. Observing this requires long-term
-(such as year-round) monitoring with a high frequency, and digital
-time-lapse cameras are suitable. This study only focused on the two
-species (dwarf bamboo and stone pine) that are easy to classify, even
-with a single image. However, like the previous studies
-(\cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen},
-\cite{Heupel2018PFG}), we expect our method to classify more vegetation
-(e.g., dwarf deciduous trees and alpine herbaceous plants) using the
-temporal information of leaf colors. We also used hourly images for each
-day. Fig. x shows that this additional information made our model robust
-against transient noises, such as shadows. Since alpine ecosystems have
-rough topologies, shadows are a considerable problem. Time-lapse cameras
-are also beneficial for this reason.
+One of the shortcomings of ordinal digital cameras is that they only have three bands (Red, Blue, and Green).
+We made up for this lack of information by using the rich temporal information that time-lapse cameras can obtain.
+Many plant species have characteristic phenologies, such as flowering and autumn foliages.
+Observing this requires long-term (such as year-round) monitoring with a high frequency, and digital time-lapse cameras are suitable.
+This study only focused on the two species (dwarf bamboo and stone pine) that are easy to classify, even with a single image.
+However, like the previous studies (\cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}), we expect our method to classify more vegetation (e.g., dwarf deciduous trees and alpine herbaceous plants) using the temporal information of leaf colors.
+We also used hourly images for each day.
+Fig.
+x shows that this additional information made our model robust against transient noises, such as shadows.
+Since alpine ecosystems have rough topologies, shadows are a considerable problem.
+Time-lapse cameras are also beneficial for this reason.
 
-\hypertarget{the-performance-of-our-georectification-method-and-its-limitation.}{%
-\subsection{The performance of our georectification method and its
-limitation.}\label{the-performance-of-our-georectification-method-and-its-limitation.}}
+\hypertarget{the-performance-of-the-georectification-method-and-its-limitation.}{%
+\subsection{The performance of the georectification method and its limitation.}\label{the-performance-of-the-georectification-method-and-its-limitation.}}
 
 \hypertarget{future-application-and-conclusion}{%
-\subsection{Future application and
-conclusion}\label{future-application-and-conclusion}}
+\subsection{Future application and conclusion}\label{future-application-and-conclusion}}
 

### 2022-06-06 paper/paper.tex
Updated paper

@@
 
-Previous studies have mainly depended on field observations, yet it is hard to cover broad areas in alpine regions due to poor accessibility and severe weather.
+Previous studies have mainly depended on field observations, yet it is hard to cover broad areas in alpine regions due to the poor accessibility and severe weather.
 Satellite, airborne, and Unmanned Aerial Vehicle (UAV) remote sensing methods seem to be alternatives.
@@
 However, few studies have tackled this.
-This lack of studies seems to be because applying such time-lapse imagery in monitoring vegetation distribution has two technical challenges.
+This lack of studies seems to be because applying such repeat photography in monitoring vegetation distribution has two technical challenges.
 
@@
 Second, since digital time-lapse cameras are mounted on the ground, transforming these images into geospatial data (e.g., orthoimage) is challenging.
-In other words, even if we find a vegetation change, we cannot identify its geographic location and analyze it with other geographic data (e.g., topography).
-Treating ground-based time-lapse images as geographic data is essential to utilize them in conservation planning.
+In other words, even if we find a vegetation change, we cannot quantitatively measure and analyze it as geographic data.
+It is essential to treat ground-based images as geographic data to utilize them in conservation planning.
 
-This study proposes an automated method for drawing vegetation maps and locating vegetation changes with a digital time-lapse camera by solving these two challenges.
+This study proposes an automated method for drawing vegetation maps and locating and measuring vegetation changes with a digital time-lapse camera by solving these two challenges.
 We solved the first challenge by utilizing temporal changes in leaf colors in vegetation classification.
@@
 From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen, deciduous dwarf trees (e.g., \emph{Pinus pumila}, \emph{Sorbus} sp.), dwarf bamboos (e.g., \emph{Sasa kurilensis}), and alpine herbaceous plants (e.g., \emph{Geum pentapetalum}, \emph{Nephrophyllidium crista-galli}).
-We used the images from late summer to late fall of 2012 and 2020.
+We used the images from late summer to late fall of 2012 and 2020 to observe the distribution changes of the dwarf pine (\emph{Pinus pumila}): the dominant species in Japanese alps, and the invasive dwarf bamboo (\emph{Sasa kurilensis}).
 
@@
 9/19, 10/2, 10/11, 10/23 in 2020).
-We used the images of this season because we can separate vegetation from the patterns of autumn foliage coloration.
+We used the images of this season because we can classify vegetation with the patterns of autumn foliage coloration.
 Also, we chose four images from 11 a.m.

### 2022-06-08 scripts/analyse.R
modified analysis.R

@@ -89,3 +89,4 @@ df %>%
     select(-c(year, n, area)) %>%
     distinct() %>%
     mutate(diff = area_2020 - area_2012)
+# 

### 2022-06-08 paper/paper.Rmd

@@
 biblio-style: unsrt
-output: rticles::arxiv_article
+output:
+  bookdown::pdf_book:
+    fig_caption: yes
+    base_format: rticles::arxiv_article
 
@@
 library(gtsummary)
+library(kableExtra)
 translate_classes <- function(names) {
@@
 # Introduction
+
 The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (\cite{IPCC2007}).
@@
 
-Previous studies have mainly depended on field observations, yet it is hard to cover broad areas in alpine regions due to poor accessibility and severe weather.
+Previous studies have mainly depended on field observations, yet it is hard to cover broad areas in alpine regions due to the poor accessibility and severe weather.
 Satellite, airborne, and Unmanned Aerial Vehicle (UAV) remote sensing methods seem to be alternatives.
-However, satellite imagery of alpine areas are rarely available due to cloud cover, and the spatial resolution is not enough to observe vegetation changes at the plant community scale.
+However, satellite imagery of alpine areas is rarely available due to cloud cover, and the spatial resolution is not enough to observe vegetation changes at the plant community scale.
 Airborne imagery can obtain high-resolution data, but its cost becomes a bottleneck for frequent monitoring.
@@
 However, few studies have tackled this.
-This lack seems to be because applying such time-lapse imagery in monitoring vegetation distribution has two technical challenges.
+This lack of studies seems to be because applying such repeat photography in monitoring vegetation distribution has two technical challenges.
 
 First, unlike satellites' multispectral sensors, ordinal digital cameras can only obtain three bands (Red, Green, and Blue), making it harder to classify the vegetation.
-Second, since digital time-lapse cameras are mounted on the ground, applying geo-spatial analysis to these images is challenging.
-In other words, even if we find a vegetation change, we cannot identify its geographic location and analyze it with topological data.
-Treating ground-based time-lapse images as geographic data is essential to utilize them in conservation planning.
+Second, since digital time-lapse cameras are mounted on the ground, transforming these images into geospatial data (e.g., orthoimage) is challenging.
+In other words, even if we find a vegetation change, we cannot quantitatively measure and analyze it as geographic data.
+It is essential to treat ground-based images as geographic data to utilize them in conservation planning.
 
-This study proposes an automated method for drawing vegetation maps and locating vegetation changes with a digital time-lapse camera by solving these two challenges.
+This study proposes an automated method for drawing vegetation maps and locating and measuring vegetation changes with a digital time-lapse camera by solving these two challenges.
 We solved the first challenge by utilizing temporal changes in leaf colors in vegetation classification.
 We also developed an accurate method for transforming a ground-based photograph into geographic data to tackle the second challenge.
+Finally, we show an example application of our method by detecting and localizing vegetation changes with an 8-years digital time-lapse imagery of the Japanese alps.
 We aim to use cheap but powerful digital time-lapse cameras in alpine ecosystem conservation.
@@
 # Materials and methods
+
 ## Digital time-lapse camera imagery
+
 We used repeat photography data owned by National Institute for Environmental Studies, Japan (NIES).
-All the images are publically available on NIES' webpage (https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2).
+All the images are publically available on NIES' webpage (<https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2>).
 In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt.
@@
 From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen, deciduous dwarf trees (e.g., *Pinus pumila*, *Sorbus* sp.), dwarf bamboos (e.g., *Sasa kurilensis*), and alpine herbaceous plants (e.g., *Geum pentapetalum*, *Nephrophyllidium crista-galli*).
-We used the images from late summer to late fall of 2012 and 2020.
+We used the images from late summer to late fall of 2012 and 2020 to observe the distribution changes of the dwarf pine (*Pinus pumila*): the dominant species in Japanese alps, and the invasive dwarf bamboo (*Sasa kurilensis*).
 
 ## Preprocessing
+
 ### Selecting images
+
 First, we selected images that are suitable for vegetation classification.
@@
 ### Automatic image-to-image alignment
+
 Since images are slightly misaligned with each other due to wind, we aligned them before processing.
-We implemented the program with Python3 programming language and OpenCV4 (https://opencv.org/) image processing library.
+We implemented the program with Python3 programming language and OpenCV4 (<https://opencv.org/>) image processing library.
 First, we set one image of 2010 as the alignment target.
@@
 ## Automatic vegetation classification
+
 Next, we classified the pixel time series of repeat photography imagery into vegetation.
@@
 ### Model Architecture
+
 Since ground-based photographs can provide high spatial resolution (sub-meter scale in our dataset), we can use leaf texture as additional information for classification.
@@
 Therefore, a model input is a time series of image patches.
+
 Our model has two components to deal with this data structure (see Fig.
@@
 This CNN-RNN architecture has also been used for audio classification(\cite{Shi2015CRNNtext}) and scene text recognition(\cite{Shi2015CRNNtext}).
+
 Using a Deep Learning method has another positive side effect; mini-batch training.
@@
 
+### Dataset preparation
+
+We set 5 vegetation classes: dwarf pine, dwarf bamboo, other vegetation, no vegetation, and sky.
+Using a free image annotation software (Semantic Segmentation Editor, Hitachi, <https://github.com/Hitachi-Automotive-And-Industry-Lab/semantic-segmentation-editor>), an expert drew polygons on an image of 2015 for each class.
+Since vegetation might be different in 2012, 2015, and 2020, applying this teacher data to the image of 2012 and 2020 may cause misclassification.
+However, vegetation changes are expected to occur at the edge of the plant community.
+Thus we shrink each polygon with several pixels before applying it to the training.
+
 ### Implementation and model training
-We implemented the classifier with Python3 language and PyTorch deep neural network library (https://pytorch.org/). All source codes are publically available via GitHub (https://github.com/0kam/xxxx).
 
-### Dataset preparation  
-We set 5 classes: dwarf pine, dwarf bamboo, other vegetation, no vegetation, and sky.
-Using free image annotation software (Semantic Segmentation Editor), an expert prepared teacher data (Fig.
-x) for classification.
+We implemented the classifier with Python3 language and PyTorch deep neural network library (<https://pytorch.org/>).
+All source codes are publically available via GitHub (<https://github.com/0kam/xxxx>).
 
 # Automatic georectification
+
 Then, we developed a novel method to convert ground-based landscape imagery into GIS-ready geographical data.
@@
 We can consider a camera as a function that transforms 3D geographical coordinates (latitude, longitude, height) into 2D image coordinates (locations of each pixel).
-So estimating the parameters of this function (such as the camera location, pose, and the field of view), we can align an image to a DSM.
+So estimating the parameters of this function (such as the camera location, pose, and the field of view), we can map an image onto a DSM.
+We recommend readers to \cite{Portenier2020Cryosphere} for a plain mathmatical explanation of this process.
 Usually, georectification has three steps:
-1. Finding Ground Control Points (GCPs) in the image.
-2. Estimating camera parameters such as camera poses and field of view using GCPs.
+
+1.  Finding Ground Control Points (GCPs) in the image.\
+2.  Estimating camera parameters such as camera poses and field of view using GCPs.\
 3.  Mapping the image onto the DSM using camera parameters.
@@
 ## Local-feature-based matching of images and DSMs
+
 To get matching points between images and DSMs on a broader area, we used an airborne image already georectified.
@@
 ## Modeling and estimating lens distortions
-We modeled the lens distortion based on \cite{Weng1992CameraCalib} and OpenCV's implementation (Eq.
-1).
-Our model includes radial (k1~k6), tangental (p1, p2), thin prism (s1~s4) distortion, and unequal pixel aspect ratio (a1, a2).
+
+We modeled the lens distortion (\ref{camera_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation, where ${x}''$ and ${y}''$ are the coordinates of each pixels after distortion and $x'$ and $y'$ are the coordinates before distortion.
+Our model includes radial ($k1~k6$), tangental ($p1, p2$), thin prism ($s1~s4$) distortion, and unequal pixel aspect ratio ($a1, a2$).
 See Weng et al.
-1992 for lens distortion modeling.
-Also, we recommend readers to \cite{Portenier2020Cryosphere} for camera models without lens distortions.
+1992 for the details of lens distortion modeling.
 Thus, now we can project GCPs' geographical coordinates into image coordinates using lens distortion parameters and other camera parameters (the camera location, pose, and the field of view).
@@
 
-$$
+```{=tex}
+\begin{equation}
+\label{camera_model}
 \begin{bmatrix}
@@
 y’ \frac{1 + a_1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + a_2 + k_4 r^2 + k_5 r^4 + k_6 r^6} + p_1 (r^2 + 2 y’^2) + 2 p_2 x’ y’ + s_3 r^2 + s_4 r^4 \ \end{bmatrix}
-$$
+\end{equation}
+```
+## Implementation and data set
 
-## Implementation and data set  
-We implemented the algorithm with Python3 language and published it as an open-source package via GitHub (https://github.com/0kam/alproj).
+We implemented the algorithm with Python3 language and published it as an open-source package via GitHub (<https://github.com/0kam/alproj>).
 You can try it with your data.
@@
 
-```{r plot_vegetation_acc, echo=FALSE, message=FALSE, fig.width=4, fig.height=3}
+We evaluated the performance of the vegetation classifier using a 5-fold cross-validation design.
+Each fold was stratified with the vegetation categories.
+We used three standard metrics in machine learning evaluation: precision, recall, and F1-score (\ref{metrics}), where $TP, FP, FN$ is true positives, false positives, and false negatives, respectively.
+
+```{=tex}
+\begin{align}
+\label{metrics}
+precision = \frac{TP}{TP + FP} \\
+recall = \frac{TP}{TP + FN} \\
+F_1 = \frac{2 \cdot precision \cdot recall}{precision + recall} \\
+\end{align}
+```
+The vegetation classifier achieved a high recall and precision in all five categories \ref{tab:vegetation_cv}.
+Recall and precision were lowest in dwarf bamboo with the smallest training data.
+Even in dwarf bamboo, false positives occurred at low frequency (about 5%), and only a tiny amount of true positives were missed by the pipeline (about 4%).
+Since the weighted average of each metric was higher (more than 0.99), balancing the training dataset with vegetation categories may improve these results.
+
+\ref{fig:vegetation} shows the products of vegetation classification. We can observe the distribution of dwarf pine and dwarf bamboo at the plant-community scale.
+
+```{r, echo=FALSE, message=FALSE, fig.cap="Cross Validation Results"}
 df <- read_csv("../runs/cnn_lstm9x9_cv_5_ep_200/staritfied_cv.csv",
@@
 theme_gtsummary_mean_sd()
+
 df %>%
@@
   mutate(vegetation = translate_classes(vegetation)) %>%
-  mutate(vegetation = factor(vegetation, levels = vegetation_levels)) %T>%
-  {
+  mutate(vegetation = factor(vegetation, levels = vegetation_levels)) %>%
   group_by(., vegetation, metrics) %>%
   summarise(
-        mean = mean(value),
-        sd = sd(value)
+    mean = sprintf("%1.3f", mean(value)),
+    sd = sprintf("(%1.3f)", sd(value))
   ) %>% 
-      write_csv("table1.csv")
-  } %>%
-  pivot_wider(names_from = metrics, values_from = value) %>%
-  select(-fold) %>%
-  tbl_summary(
-    by = c(vegetation),
-    label = list(
-      precision ~ "Precision",
-      recall ~ "Recall",
-      `f1-score` ~ "F1 Score")
-  ) %>%
-  modify_header(label = "")
+  pivot_longer(cols=c(mean, sd), names_to="var") %>% 
+  pivot_wider(names_from=metrics, values_from=value) %T>%
+  write_csv("table1.csv") %>%
+  select(-var) %>%
+  kable(format="latex", booktabs=TRUE, caption = "Cross validation result \\label{tab:vegetation_cv}") %>% 
+  kable_styling() %>% 
+  collapse_rows(columns=1) %>%
+  footnote(general = "Mean (SD) of 5-Fold Cross-Varidation")
 
+```
+
+```{r, vegetation, echo=FALSE, message=FALSE, fig.cap="Vegetation classification results", out.width="100%", auto_pdf = TRUE}
+knitr::include_graphics("vegetation.jpg")
 ```
@@
 # Discussion
+
 We suggested a fully automated procedure to transform time-lapse imagery into georeferenced vegetation maps at a meager cost.
@@
 ## The benefit of using time-series imagery for vegetation classification
+
 One of the shortcomings of ordinal digital cameras is that they only have three bands (Red, Blue, and Green).
@@
 
-## The performance of our georectification method and its limitation.
+## The performance of the georectification method and its limitation.
 

### 2022-06-15 scripts/run_cnnlstm_5x5.py
modified models

@@ -1,4 +1,5 @@
 from PIL import Image
+from torch import log_
 from scripts.utils import set_patches, find_best_epoch
 from scripts.cnn_lstm import CNNLSTM
 import numpy as np
@@ -6,17 +7,17 @@ import tensorboardX
 hmat = np.loadtxt("data_source/hmat_label.txt")
 mask = np.load("data_source/mask.npy")
 shrink = 3
-log_dir = "cnn_9x9"
+log_dir = "cnn_5x5"
 
-# set_patches("data_source/labels", "data_source/aligned/2012", "data/train/patches9x9/", (9,9), batch_size=50, unlabelled=False, shrink=shrink, hmat=hmat, mask=mask)
-# set_patches("data_source/labels", "data_source/aligned/2021", "data/train/patches9x9/", (9,9), batch_size=50, unlabelled=False, shrink=shrink, hmat=hmat, mask=mask)
+# set_patches("data_source/labels", "data_source/aligned/2012", "data/train/patches5x5/", (5,5), batch_size=50, unlabelled=False, shrink=shrink, hmat=hmat, mask=mask)
+# set_patches("data_source/labels", "data_source/aligned/2021", "data/train/patches5x5/", (5,5), batch_size=50, unlabelled=False, shrink=shrink, hmat=hmat, mask=mask)
 
-lstm = CNNLSTM("data/train/patches9x9", "data_source/labels", (9,9), 200, device="cuda", test_size = 0.2)
+lstm = CNNLSTM("data/train/patches5x5", "data_source/labels", (5,5), 200, device="cuda", test_size = 0.2)
 lstm.draw_legend("results/legend.png")
 lstm.draw_teacher("results/teacher.png", (5616,3744), shrink=shrink, hmat=hmat, mask=mask)
 
 k = 5
-cv_log_dir = "cnn_lstm9x9_cv_5_ep_200"
+cv_log_dir = "cnn_lstm5x5_cv_5_ep_200"
 lstm.kfold(100, cv_log_dir, k)
 
 best_epochs = []
@@ -24,10 +25,10 @@ res2012 = []
 res2021 = []
 for i in range(k):
     path = "runs/" +  cv_log_dir + "/fold_{}".format(i) + "/best.pth"
[…]

### 2022-06-15 paper/paper.Rmd
merged

@@
 
-Since images are slightly misaligned with each other due to wind, we aligned them before processing.
+Since images are slightly misaligned with each other due to the effect of wind and human interactions, we aligned them before processing.
 We implemented the program with Python3 programming language and OpenCV4 (<https://opencv.org/>) image processing library.
-First, we set one image of 2010 as the alignment target.
+First, we set one image of 2012 as the alignment target.
 Next, we automatically found matching keypoints between the target and other images using AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
 Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's "findHomography" function.
+Because not all matched points are correct, we estimated the homography matrix using the RANdom SAmple Consensus (RANSAC) to avoid influences of such outliers.
 
@@
 In plain words, georectification means aligning images into Digital Surface Models (DSMs) so that every pixel of an image gets a geographical coordinate.
-We can consider a camera as a function that transforms 3D geographical coordinates (latitude, longitude, height) into 2D image coordinates (locations of each pixel).
-So estimating the parameters of this function (such as the camera location, pose, and the field of view), we can map an image onto a DSM.
+We can consider a camera as a function that transforms 3D geographical coordinates (e.g., X, Y and height in a Universal Transverse Mercator coordinate system (UTM)) into 2D image coordinates (locations of each pixel in the picture).
+Estimating the parameters of this function (such as the camera location, pose, and the field of view), we can map an image onto a DSM.
 We recommend readers to \cite{Portenier2020Cryosphere} for a plain mathmatical explanation of this process.
@@
 
+## Modeling and estimating camera parameters
+
+As we mentioned before, we considered a camera as a function that transforms geographical coordinates of each location of the target mountain to image coordinates in the acquired photograph.
+We implemented this procedure using the OpenGL framework to accelerate it with graphical processing units (GPUs).
+In OpenGL, we can separate this process into three operations:
+
+1. Transforming the world (geographical) coordinates to the view coordinates using camera's extrinsic parameters (i.e., the location and angles of the camera).
+2. Distorting the view coordinates using the lens distortion parameters.
+3. Transforming the view coordinates to the screen (image) coordinates using camera's intrinsic parameters (i.e., the FoV and aspect ratio of the camera).
+
+First, we transform the absolute geographic coordinates (also known as the world coordinates) to the view coordinates that are relative to the camera's position and direction.
+We apply a $4 \times 4$ view matrix (\ref{view_matrix}) to the geographic coordinates in this step.
+The view matrix represents the position and the direction (pan, tilt, roll) of the camera.
+Note that the geographic coordinate system must be cartesian (such as the UTM).
+
+```{=tex}
+\label{view_matrix}
+\begin{equation}
+  M_{view} = 
+  \begin{bmatrix}
+    \cos roll & -\sin roll & 0 & 0 \\
+    \sin roll & \cos roll & 0 & 0 \\
+    0 & 0 & 1 & 0 \\
+    0 & 0 & 0 & 1 \\
+  \end{bmatrix}
+  \begin{bmatrix}
+    1 & 0 & 0 & 0 \\
+    0 & \cos tilt & -\sin tilt & 0 \\
+    0 & \sin tilt & \cos tilt & 0 \\
+    0 & 0 & 0 & 1 \\
+  \end{bmatrix}
+  \begin{bmatrix}
+    \cos pan & 0 & \sin pan & 0 \\
+    0 & 1 & 0 & 0 \\
+    -\sin pan & 0 & \cos pan & 0 \\
+    0 & 0 & 0 & 1 \\
+  \end{bmatrix}
+  \begin{bmatrix}
+    1 & 0 & 0 & -x \\
+    0 & 1 & 0 & -z \\
+    0 & 0 & 1 & -y \\
+    0& 0 & 0 & 1 \\
+  \end{bmatrix}
+\end{equation}
+```
+
+Where $pan, tilt, roll$ are the Euler angles of the camera and $x, y, z$ are the camera location in the geographic coordinate system.
+Then, we can transform the geographic coordinates of the DSM $\begin{bmatrix} X_{geo} & Z_{geo} & Y_{geo} & 1 \end{bmatrix}$ to the camera coordinates $\begin{bmatrix} X_{camera} & Z_{camera} & Y_{camera} & 1 \end{bmatrix}$ applying the view matrix $M_{view}$ (\ref{view_tf}).
+In the OpenGL's camera coordinate system, $X_{camera}$, $Z_{camera}$ and $Y_{camera}$ represents horizontal, vertical, and depth positions respectively.
+
+```{=tex}
+\label{view_tf}
+\begin{equation}
+  \begin{bmatrix} 
+    X_{camera} \\ Z_{camera} \\ Y_{camera} \\ 1 
+  \end{bmatrix}
+  =
+  M_{view}
+  \begin{bmatrix} 
+    X_{geo} \\ Z_{geo} \\ Y_{geo} \\ 1 
+  \end{bmatrix}
+\end{equation}
+```
+
+Second, we distort the camera coordinates to simulate the lens distortion.
+We modeled the lens distortion (\ref{dist_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation, where $X_{norm}$ and $Z_{norm}$ are the $Y$-normalized coordinates of the camera coordinates.
+This model distorts points' locations according to the distance from the center of the image when projected to the image surface.
+Our model includes radial ($k1~k6$), tangental ($p1, p2$), thin prism ($s1~s4$) distortion, and unequal pixel aspect ratio ($a1, a2$).
+See Weng et al.
+1992 for the details of lens distortion modeling.
+
+```{=tex}
+\label{dist_model}
+\begin{gather}
+  X_{norm} = \frac{X_{camera}}{Y_{camera}} \\
+  Z_{norm} = \frac{Z_{camera}}{Y_{camera}} \\
+  r^2 = {X_{norm}}^2 + {Z_{norm}}^2 \\
+  \begin{bmatrix}
+    X_{dist\_norm} \\ 
+    Z_{dist\_norm} \\
+  \end{bmatrix} 
+  = 
+  \begin{bmatrix} 
+    X_{norm} \frac{1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + k_4 r^2 + k_5 r^4 + k_6 r^6} + 2 p_1 x’ y’ + p_2(r^2 + 2 x’^2) + s_1 r^2 + s_2 r^4 \\ 
+    Z_{norm} \frac{1 + a_1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + a_2 + k_4 r^2 + k_5 r^4 + k_6 r^6} + p_1 (r^2 + 2 y’^2) + 2 p_2 x’ y’ + s_3 r^2 + s_4 r^4 \\    \end{bmatrix} \\
+  X_{dist} = X_{dist\_norm} Y_{camera} \\
+  Z_{dist} = Z_{dist\_norm} Y_{camera} \\
+\end{gather}
+```
+
+Then we transform the distorted camera coordinates to the image coordinates by perspective projection.
+During the perspective projection, a closer object is drawn larger.
+We used a $4 \times 4$ projection matrix $M_{proj}$ (\ref{proj_mat}), that represents the camera's horizontal ($fov_x$) and vertical ($fov_z$) FoV.
+Finally, we can get the image coordinates of each point of the DSM as $X_{image}, Z_{image}$ (\ref{proj_tf}).
+
+```{=tex}
+\label{proj_mat}
+\begin{gather}
+  f_x = \frac{1}{\frac{\tan fov_x}{2}} 
+  f_z = \frac{1}{\frac{\tan fov_z}{2}}
+  M_{proj} = 
+  \begin{bmatrix} 
+    f_x & 0 & 1 & 0\\ 
+    0 & f_z & -1 & 0 \\ 
+    0 & 0 & 0 & 1\\ 
+    0 & 0 & -1 & 0 
+  \end{bmatrix}
+\end{gather}
+```
+
+```{=tex}
+\label{proj_tf}
+\begin{equation}
+  \begin{bmatrix} 
+    X_{image} \\ Z_{image} \\ Y_{image} \\ 1 
+  \end{bmatrix}
+  =
+  M_{proj}
+  \begin{bmatrix} 
+    X_{dist} \\ Z_{dist} \\ Y_{dist} \\ 1 
+  \end{bmatrix}
+\end{equation}
+```
+
+Thus, now we can project GCPs' geographical coordinates into image coordinates using lens distortion parameters and other camera parameters (the camera location, pose, and the field of view).
+We optimized these (except camera location) by minimizing the square projection error of the GCPs using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}).
+We could not estimate the camera location because it makes the problem too complicated (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).
+
 ## Local-feature-based matching of images and DSMs
@@
 
-## Modeling and estimating lens distortions
-
-We modeled the lens distortion (\ref{camera_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation, where ${x}''$ and ${y}''$ are the coordinates of each pixels after distortion and $x'$ and $y'$ are the coordinates before distortion.
-Our model includes radial ($k1~k6$), tangental ($p1, p2$), thin prism ($s1~s4$) distortion, and unequal pixel aspect ratio ($a1, a2$).
-See Weng et al.
-1992 for the details of lens distortion modeling.
-Thus, now we can project GCPs' geographical coordinates into image coordinates using lens distortion parameters and other camera parameters (the camera location, pose, and the field of view).
-We optimized these (except camera location) by minimizing the square projection error of the GCPs using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}).
-We could not estimate the camera location because it makes the problem too complicated (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).
-
-```{=tex}
-\begin{equation}
-\label{camera_model}
-\begin{bmatrix}
-{x}'' \\ 
-{y}'' 
-\end{bmatrix} 
-= 
-\begin{bmatrix} 
-x’ \frac{1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + k_4 r^2 + k_5 r^4 + k_6 r^6} + 2 p_1 x’ y’ + p_2(r^2 + 2 x’^2) + s_1 r^2 + s_2 r^4 \\ 
-y’ \frac{1 + a_1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + a_2 + k_4 r^2 + k_5 r^4 + k_6 r^6} + p_1 (r^2 + 2 y’^2) + 2 p_2 x’ y’ + s_3 r^2 + s_4 r^4 \ \end{bmatrix}
-\end{equation}
-```
 ## Implementation and data set
@@
 ```{=tex}
+\label{metrics}
 \begin{align}
-\label{metrics}
   precision = \frac{TP}{TP + FP} \\

### 2022-06-15 paper/paper.tex
merged

@@
 
-Since images are slightly misaligned with each other due to wind, we aligned them before processing.
+Since images are slightly misaligned with each other due to the effect of wind and human interactions, we aligned them before processing.
 We implemented the program with Python3 programming language and OpenCV4 (\url{https://opencv.org/}) image processing library.
-First, we set one image of 2010 as the alignment target.
+First, we set one image of 2012 as the alignment target.
 Next, we automatically found matching keypoints between the target and other images using AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
 Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's ``findHomography'' function.
+Because not all matched points are correct, we estimated the homography matrix using the RANdom SAmple Consensus (RANSAC) to avoid influences of such outliers.
 
@@
 
-\hypertarget{modeling-and-estimating-lens-distortions}{%
-\subsection{Modeling and estimating lens distortions}\label{modeling-and-estimating-lens-distortions}}
+\hypertarget{modeling-and-estimating-camera-parameters}{%
+\subsection{Modeling and estimating camera parameters}\label{modeling-and-estimating-camera-parameters}}
 
-We modeled the lens distortion (\ref{camera_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation, where \({x}''\) and \({y}''\) are the coordinates of each pixels after distortion and \(x'\) and \(y'\) are the coordinates before distortion.
+As we mentioned before, we considered a camera as a function that transforms geographical coordinates of each location of the target mountain to image coordinates in the acquired photograph.
+We implemented this procedure using the OpenGL framework to accelerate it with graphical processing units (GPUs).
+In OpenGL, we can separate this process into three operations:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Transforming the world (geographical) coordinates to the view coordinates using camera's extrinsic parameters (i.e., the location and angles of the camera).
+\item
+  Distorting the view coordinates using the lens distortion parameters.
+\item
+  Transforming the view coordinates to the screen (image) coordinates using camera's intrinsic parameters (i.e., the FoV and aspect ratio of the camera).
+\end{enumerate}
+
+First, we transform the absolute geographic coordinates (also known as the world coordinates) to the view coordinates that are relative to the camera's position and direction.
+We apply a \(4 \times 4\) view matrix (\ref{view_matrix}) to the geographic coordinates in this step.
+The view matrix represents the position and the direction (pan, tilt, roll) of the camera.
+Note that the geographic coordinate system must be cartesian (such as the UTM).
+
+\label{view_matrix}
+\begin{equation}
+  M_{view} = 
+  \begin{bmatrix}
+    \cos roll & -\sin roll & 0 & 0 \\
+    \sin roll & \cos roll & 0 & 0 \\
+    0 & 0 & 1 & 0 \\
+    0 & 0 & 0 & 1 \\
+  \end{bmatrix}
+  \begin{bmatrix}
+    1 & 0 & 0 & 0 \\
+    0 & \cos tilt & -\sin tilt & 0 \\
+    0 & \sin tilt & \cos tilt & 0 \\
+    0 & 0 & 0 & 1 \\
+  \end{bmatrix}
+  \begin{bmatrix}
+    \cos pan & 0 & \sin pan & 0 \\
+    0 & 1 & 0 & 0 \\
+    -\sin pan & 0 & \cos pan & 0 \\
+    0 & 0 & 0 & 1 \\
+  \end{bmatrix}
+  \begin{bmatrix}
+    1 & 0 & 0 & -x \\
+    0 & 1 & 0 & -z \\
+    0 & 0 & 1 & -y \\
+    0& 0 & 0 & 1 \\
+  \end{bmatrix}
+\end{equation}
+
+Where \(pan, tilt, roll\) are the Euler angles of the camera and \(x, y, z\) are the camera location in the geographic coordinate system.
+Then, we can transform the geographic coordinates of the DSM \(\begin{bmatrix} X_{geo} & Z_{geo} & Y_{geo} & 1 \end{bmatrix}\) to the camera coordinates \(\begin{bmatrix} X_{camera} & Z_{camera} & Y_{camera} & 1 \end{bmatrix}\) applying the view matrix \(M_{view}\) (\ref{view_tf}).
+In the OpenGL's camera coordinate system, \(X_{camera}\), \(Z_{camera}\) and \(Y_{camera}\) represents horizontal, vertical, and depth positions respectively.
+
+\label{view_tf}
+\begin{equation}
+  \begin{bmatrix} 
+    X_{camera} \\ Z_{camera} \\ Y_{camera} \\ 1 
+  \end{bmatrix}
+  =
+  M_{view}
+  \begin{bmatrix} 
+    X_{geo} \\ Z_{geo} \\ Y_{geo} \\ 1 
+  \end{bmatrix}
+\end{equation}
+
+Second, we distort the camera coordinates to simulate the lens distortion.
+We modeled the lens distortion (\ref{dist_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation, where \(X_{norm}\) and \(Z_{norm}\) are the \(Y\)-normalized coordinates of the camera coordinates.
+This model distorts points' locations according to the distance from the center of the image when projected to the image surface.
 Our model includes radial (\(k1~k6\)), tangental (\(p1, p2\)), thin prism (\(s1~s4\)) distortion, and unequal pixel aspect ratio (\(a1, a2\)).
 See Weng et al.~1992 for the details of lens distortion modeling.
+
+\label{dist_model}
+\begin{gather}
+  X_{norm} = \frac{X_{camera}}{Y_{camera}} \\
+  Z_{norm} = \frac{Z_{camera}}{Y_{camera}} \\
+  r^2 = {X_{norm}}^2 + {Z_{norm}}^2 \\
+  \begin{bmatrix}
+    X_{dist\_norm} \\ 
+    Z_{dist\_norm} \\
+  \end{bmatrix} 
+  = 
+  \begin{bmatrix} 
+    X_{norm} \frac{1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + k_4 r^2 + k_5 r^4 + k_6 r^6} + 2 p_1 x’ y’ + p_2(r^2 + 2 x’^2) + s_1 r^2 + s_2 r^4 \\ 
+    Z_{norm} \frac{1 + a_1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + a_2 + k_4 r^2 + k_5 r^4 + k_6 r^6} + p_1 (r^2 + 2 y’^2) + 2 p_2 x’ y’ + s_3 r^2 + s_4 r^4 \\    \end{bmatrix} \\
+  X_{dist} = X_{dist\_norm} Y_{camera} \\
+  Z_{dist} = Z_{dist\_norm} Y_{camera} \\
+\end{gather}
+
+Then we transform the distorted camera coordinates to the image coordinates by perspective projection.
+During the perspective projection, a closer object is drawn larger.
+We used a \(4 \times 4\) projection matrix \(M_{proj}\) (\ref{proj_mat}), that represents the camera's horizontal (\(fov_x\)) and vertical (\(fov_z\)) FoV.
+Finally, we can get the location of each point of the DSM on the image as \(X_{image}, Z_{image}\) (\ref{proj_tf}) i.e., we can generate a virtual image with given set of camera parameters.
+
+\label{proj_mat}
+\begin{gather}
+  f_x = \frac{1}{\frac{\tan fov_x}{2}} 
+  f_z = \frac{1}{\frac{\tan fov_z}{2}}
+  M_{proj} = 
+  \begin{bmatrix} 
+    f_x & 0 & 1 & 0\\ 
+    0 & f_z & -1 & 0 \\ 
+    0 & 0 & 0 & 1\\ 
+    0 & 0 & -1 & 0 
+  \end{bmatrix}
+\end{gather}
+
+\label{proj_tf}
+\begin{equation}
+  \begin{bmatrix} 
+    X_{image} \\ Z_{image} \\ Y_{image} \\ 1 
+  \end{bmatrix}
+  =
+  M_{proj}
+  \begin{bmatrix} 
+    X_{dist} \\ Z_{dist} \\ Y_{dist} \\ 1 
+  \end{bmatrix}
+\end{equation}
+
 Thus, now we can project GCPs' geographical coordinates into image coordinates using lens distortion parameters and other camera parameters (the camera location, pose, and the field of view).
@@
 We could not estimate the camera location because it makes the problem too complicated (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).
-
-\begin{equation}
-\label{camera_model}
-\begin{bmatrix}
-{x}'' \\ 
-{y}'' 
-\end{bmatrix} 
-= 
-\begin{bmatrix} 
-x’ \frac{1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + k_4 r^2 + k_5 r^4 + k_6 r^6} + 2 p_1 x’ y’ + p_2(r^2 + 2 x’^2) + s_1 r^2 + s_2 r^4 \\ 
-y’ \frac{1 + a_1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + a_2 + k_4 r^2 + k_5 r^4 + k_6 r^6} + p_1 (r^2 + 2 y’^2) + 2 p_2 x’ y’ + s_3 r^2 + s_4 r^4 \ \end{bmatrix}
-\end{equation}
 
@@
 
+\label{metrics}
 \begin{align}
-\label{metrics}
   precision = \frac{TP}{TP + FP} \\
@@
 
+\begin{verbatim}
+## Warning: One or more parsing issues, see `problems()` for details
+\end{verbatim}
+
 \begin{table}
@@
 \midrule
- & 0.982 & 0.977 & 0.987\\
+ & 0.986 & 0.984 & 0.988\\
 \cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash Macro Average} & (0.005) & (0.008) & (0.001)\\
+\multirow{-2}{*}{\raggedright\arraybackslash Macro Average} & (0.006) & (0.010) & (0.001)\\
 \cmidrule{1-4}
@@
 \cmidrule{1-4}
- & 0.986 & 0.977 & 0.995\\
+ & 0.987 & 0.980 & 0.994\\
 \cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash Dwarf Pine} & (0.005) & (0.012) & (0.003)\\
+\multirow{-2}{*}{\raggedright\arraybackslash Dwarf Pine} & (0.004) & (0.010) & (0.003)\\
 \cmidrule{1-4}
- & 0.955 & 0.951 & 0.960\\
+ & 0.962 & 0.964 & 0.961\\
 \cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash Dwarf Bamboo} & (0.004) & (0.013) & (0.006)\\
+\multirow{-2}{*}{\raggedright\arraybackslash Dwarf Bamboo} & (0.010) & (0.020) & (0.004)\\
 \cmidrule{1-4}
- & 0.997 & 0.999 & 0.996\\
+ & 0.998 & 0.999 & 0.997\\
 \cmidrule{2-4}
@@
 \cmidrule{1-4}
- & 0.970 & 0.959 & 0.984\\
+ & 0.978 & 0.972 & 0.985\\
 \cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash Non Vegetation} & (0.034) & (0.066) & (0.004)\\
+\multirow{-2}{*}{\raggedright\arraybackslash Non Vegetation} & (0.028) & (0.053) & (0.004)\\
 \cmidrule{1-4}

### 2022-06-15 scripts/analyse.R

@@ -12,9 +12,9 @@ change_names <- function(nums) {
     )
 }
 
-vege2012 <- read_stars("data/res2012_cnn_9x9.tiff")
-vege2020 <- read_stars("data/res2020_cnn_9x9.tiff")
-dem <- read_stars("data/tateyamadem_small.tiff") %>%
+vege2012 <- read_stars("results/cnn_lstm5x5_cv_5_ep_200/res2012_cnn_5x5.tiff")
+vege2021 <- read_stars("results/cnn_lstm5x5_cv_5_ep_200/res2021_cnn_5x5.tiff")
+dem <- read_stars("data/mrd_dem_1m.tiff") %>%
     st_warp(vege2012)
 
 # Get raster resolutions
@@ -24,15 +24,15 @@ res <- st_dimensions(vege2012) %>%
     as.numeric() %>%
     abs()
 
-df <- c(vege2012, vege2020, dem) %>%
+df <- c(vege2012, vege2021, dem) %>%
     as_tibble() %>%
     rename(
-        v2012 = res2012_cnn_9x9.tiff,
-        v2020 = res2020_cnn_9x9.tiff,
-        elevation = tateyamadem_small.tiff
+        v2012 = res2012_cnn_5x5.tiff,
+        v2021 = res2021_cnn_5x5.tiff,
+        elevation = mrd_dem_1m.tiff
         ) %>%
     pivot_longer(
-        cols = c("v2012", "v2020"),
+        cols = c("v2012", "v2021"),
         names_to = "year",
         values_to = "vegetation",
         names_prefix = "v"
@@ -44,19 +44,25 @@ df <- c(vege2012, vege2020, dem) %>%
 # Vegetation histogram along elevation
 breaks <- seq(2350, 3000, 50)
 
-df %>%
+p <- df %>%
     group_by(vegetation, year) %>%
     ggplot(aes(x = elevation, fill = year)) +
     geom_histogram(
         aes(y = after_stat(count * res[1] * res[2])),
         breaks = breaks,
-        alpha = 0.4,
+        alpha = 0.3,
         position = "identity"
         ) +
     facet_wrap(~vegetation) +
     ylab(expression(paste ("Area (", {mm^2}, ")", sep = ""))) +
     xlab("Elevation") +
-    theme_minimal()
+    theme_minimal() +
+    scale_fill_hue(direction = -1)
+
+pg <- ggplot_build(p)
+
+head(pg$data[[1]])
[…]

### 2022-06-15 scripts/georectify.py

@@ -9,12 +9,12 @@ import rasterio
 
 res = 1.0 # Resolution in m
 aerial = rasterio.open("data/tateyama2.tiff")
-dsm = rasterio.open("data/tateyamadem_small.tiff")
+dsm = rasterio.open("data/mrd_dem_1m.tiff")
 out_path = "data/pointcloud.db" # Output database
 
-create_db(aerial, dsm, out_path) # This takes some minutes
+# create_db(aerial, dsm, out_path) # This takes some minutes
 
-params = {"x":732731,"y":4051171, "z":2458, "fov":70, "pan":100, "tilt":0, "roll":0,\
+params = {"x":732731,"y":4051171, "z":2458, "fov":75, "pan":95, "tilt":0, "roll":0,\
           "a1":1, "a2":1, "k1":0, "k2":0, "k3":0, "k4":0, "k5":0, "k6":0, \
           "p1":0, "p2":0, "s1":0, "s2":0, "s3":0, "s4":0, \
           "w":5616, "h":3744, "cx":5616/2, "cy":3744/2}
@@ -35,7 +35,7 @@ df = reverse_proj(sim, vert, ind, params)
 path_org = "data_source/aligned/2012/mrd_085_eos_vis_20121021_1200.png"
 path_sim = "data/initial.png"
 
-match, plot = akaze_match(path_org, path_sim, ransac_th=200, plot_result=True)
+match, plot = akaze_match(path_org, path_sim, ransac_th=100, plot_result=True)
 cv2.imwrite("data/matched.png", plot)
 gcps = set_gcp(match, df)
 gcps.to_csv("data/gcp.csv")
@@ -44,9 +44,11 @@ obj_points = gcps[["x","y","z"]] # Object points in a geographic coordinate syst
 img_points = gcps[["u","v"]] # Image points in an image coordinate system 
 params_init = params # Initial parameters
 target_params = ["fov", "pan", "tilt", "roll", "a1", "a2", "k1", "k2", "k3", "k4", "k5", "k6", "p1", "p2", "s1", "s2", "s3", "s4"] # Parameters to be optimized
+
 cma_optimizer = CMAOptimizer(obj_points, img_points, params_init) # Create an optimizer instance.
 cma_optimizer.set_target(target_params)
-params_optim, error = cma_optimizer.optimize(generation = 300, bounds = None, sigma = 1.0, population_size=50) # Executing optimization
+
[…]

### 2022-06-15 scripts/interpolate.R

@@ -37,12 +37,14 @@ interpolate <- function(in_path, out_path, res, max_dist, fun=terra::modal) {
   print("Finished !")
 }
   
-files <- c("data/res2012_cnn_9x9.csv", "data/res2020_cnn_9x9.csv", 
-           "data/diff_haimatsu.csv", "data/diff_sasa.csv")
+files <- c("results/cnn_lstm5x5_cv_5_ep_200/diff_sasa.csv",
+          "results/cnn_lstm5x5_cv_5_ep_200/diff_haimatsu.csv",
+           "results/cnn_lstm5x5_cv_5_ep_200/res2012_cnn_5x5.csv",
+           "results/cnn_lstm5x5_cv_5_ep_200/res2021_cnn_5x5.csv")
 
 for (file in files) {
   out_path <- stringr::str_replace(file, "csv", "tiff")
-  interpolate(file, out_path, 0.5, 1)
+  interpolate(file, out_path, 0.2, 1)
 }
 
 

### 2022-06-15 scripts/aggregate.py
merged everything

@@ -1,0 +1,97 @@
+import numpy as np
+from matplotlib import pyplot as plt
+import pylab as pl
+from matplotlib.colors import ListedColormap
+from PIL import Image
+import numpy as np
+from scipy.stats import mode
+import torch
+
+mask = np.asarray(Image.open("results/cnn_lstm5x5_cv_5_ep_200/mask.png"))[:,:,0]
+mask[mask>0] = 1
+
+d = "results/cnn_lstm5x5_cv_5_ep_200/"
+res2012 = []
+res2021 = []
+
+for i in range(5):
+    r2012 = np.load(d + "fold_{}/2012.npy".format(i))
+    r2021 = np.load(d + "fold_{}/2021.npy".format(i))
+    res2012.append(r2012)
+    res2021.append(r2021)
+
+res2012 = torch.Tensor(np.stack(res2012))
+res2021 = torch.Tensor(np.stack(res2021))
+
+res2012 = torch.mode(res2012, dim = 0)
+res2021 = torch.mode(res2021, dim = 0)
+
+res2012 = res2012[0].numpy()
+res2021 = res2021[0].numpy()
+
+## Color maps
+cmap_veg = ListedColormap(
+    np.array(
+        [[0,0,0], # 0: No data
+        [154,205,50], # 1: Dwarf bamboo
+        [192,192,192], # 2: No vegetation
+        [139,69,19], # 3: Other vegetation
+        [255,255,255], # 4: Sky
+        [0,100,0]] # 5: Dwarf pine
+    ) / 255
+)
+
+cmap_diff = ListedColormap(
+    np.array(
+        [[0,0,0,0], # 0: No data
+        [192,192,192, 127], # 1: No Difference
+        [255,0,0, 127], # 2: Increase
+        [0,0,255, 127]] # 3: Decrease
+    ) / 255
+)
+
+res2012 = (res2012 +1) * mask
+res2021 = (res2021  +1) * mask
+np.save("results/cnn_lstm5x5_cv_5_ep_200/res2012_cnn_5x5.npy", res2012)
+np.save("results/cnn_lstm5x5_cv_5_ep_200/res2021_cnn_5x5.npy", res2021)
[…]

### 2022-06-27 scripts/models/run_rnn.py
modified run_rnn.py

@@ -23,3 +23,25 @@ np.save("results/rnn1x1.npy", res[0])
 from matplotlib import pyplot as plt
 
 plt.imsave("results/rnn1x1.png", res[0], cmap = cmap)
+
+from glob import glob
+rnn = RNNClassifier("data/multidays_1x1", "data_source/labels", 500, test_size=0.2, cmap=cmap)
+
+for d in glob("runs/cv/rnn1x1/*"):
+    print(d)
+    rnn.load(d + "/best.pth")
+    res = rnn.draw("data_source/aligned/multi_days", "results/rnn1x1.png", (1,1), 5000)
+    np.save(d + "/pred.npy", res[0])
+    plt.imsave(d + "/pred.png", res[0], cmap = cmap)
+
+preds = []
+import os
+import torch
+for d in glob("runs/cv/rnn1x1/*"):
+    if os.path.isdir(d):
+        preds.append(np.load(d + "/pred.npy"))
+
+preds = torch.Tensor(np.stack(preds))
+pred, _ = torch.mode(preds, dim = 0)
+np.save("results/rnn.npy", pred)
+plt.imsave("results/rnn.png", pred, cmap=cmap)

### 2022-06-27 scripts/analyse.R
modified analyse.R

@@ -1,0 +1,65 @@
+library(tidyverse)
+library(stars)
+library(sf)
+
+change_names <- function(nums) {
+    case_when(
+        nums == 1 ~ "Dwarf Bamboo",
+        nums == 2 ~ "Other Vegetation",
+        nums == 3 ~ "No Vegetation",
+        nums == 4 ~ "Rowans",
+        nums == 5 ~ "Golden Birch",
+        nums == 6 ~ "Montane Alder",
+        nums == 7 ~ "Dwarf Pine"
+    )
+}
+
+vege_levels <- c(
+    "Dwarf Pine",
+    "Dwarf Bamboo",
+    "Rowans",
+    "Golden Birch",
+    "Montane Alder",
+    "Other Vegetation",
+    "No Vegetation"
+)
+
+rnn <- read_stars("results/rnn.tiff")
+dem <- read_stars("data/mrd_dem_1m.tiff") %>%
+    st_warp(rnn)
+
+# Get raster resolutions
+res <- st_dimensions(rnn) %>%
+    as_tibble() %>%
+    pull(delta) %>%
+    as.numeric() %>%
+    abs()
+
+df <- c(rnn, dem) %>%
+    as_tibble() %>%
+    rename(
+        vegetation = rnn.tiff,
+        elevation = mrd_dem_1m.tiff
+        ) %>%
+    filter(is.na(vegetation) == FALSE) %>%
+    mutate(vegetation = change_names(vegetation)) %>%
+    mutate(vegetation = factor(vegetation, levels = vege_levels))
+
+# Vegetation histogram along elevation
+breaks <- seq(2350, 3000, 50)
+
+p1 <- df %>%
+    group_by(vegetation) %>%
+    ggplot(aes(x = elevation)) +
+    geom_histogram(
+        aes(y = after_stat(count * res[1] * res[2])),
+        breaks = breaks,
+        position = "identity"
+        ) +
+    facet_wrap(~vegetation, scales = "free") +
+    ylab(expression(paste ("Area (", {mm^2}, ")", sep = ""))) +
+    xlab("Elevation") +
+    theme_bw() +
+    scale_fill_hue(direction = -1)
+
+ggsave("results/vegetation_area_rnn.png", p1, width = 12, height = 8)

### 2022-06-27 scripts/utils/georectify.py

@@ -4,8 +4,10 @@ from alproj.project import sim_image, reverse_proj
 from alproj.gcp import akaze_match, set_gcp
 from alproj.optimize import CMAOptimizer
 import sqlite3
+from matplotlib import pyplot as plt
 import numpy as np
 import rasterio
+import cv2
 
 res = 1.0 # Resolution in m
 aerial = rasterio.open("data/tateyama2.tiff")
@@ -26,7 +28,6 @@ chunksize = 1000000
 
 vert, col, ind = crop(conn, params, distance, chunksize) # This takes some minutes.
 
-import cv2
 sim = sim_image(vert, col, ind, params)
 cv2.imwrite("data/initial.png", sim)
 
@@ -60,16 +61,33 @@ import json
 with open('data/params_optim.json', 'w') as f:
     json.dump(params_optim, f, indent=4)
 
-# Reverse projection
-original = cv2.imread(path_org)
-georectified = reverse_proj(original, vert, ind, params_optim, chnames=["B", "G", "R"])
-georectified = georectified[georectified["R"] > 0]
-georectified = georectified[georectified["G"] > 0]
-georectified = georectified[georectified["B"] > 0]
-georectified.to_csv("data/georectified.csv", index=False)
-
-
 # Apply georectification
+## Mask images
+# m1 = cv2.imread("data_source/sky_mask_2015.png")[:,:,0].astype(float)
+# m2 = cv2.imread("data_source/ground_mask.png")[:,:,0].astype(float)
+# m3 = np.load("data_source/mask.npy")
+
+# mask = m1 * m2 * m3
+# mask[mask > 0] = 1
+# np.save("data_source/mask_all.npy", mask)
+
+# mask = np.load("data_source/mask_all.npy")
+# img = cv2.imread("data_source/aligned/multi_days/mrd_085_eos_vis_20150926_1205.png")
+# img = img * mask[:,:,None].astype(np.uint8)
+# cv2.imwrite("results/image.png", img)
+
+# for f in ["results/rnn.png", "results/svm.png"]:
+#     img = cv2.imread(f)
+#     img = img * mask[:,:,None].astype(np.uint8)
+#     cv2.imwrite(f, img)
+
+# for f in ["results/rnn.npy", "results/svm.npy"]:
+#     img = np.load(f)
+#     # img = img + 1 # only run once
+#     img = img * mask
+#     np.save(f, img.astype(int))
+
+# Reverse projection
[…]

### 2022-06-27 scripts/utils/interpolate.R

@@ -24,7 +24,7 @@ interpolate <- function(in_path, out_path, res, max_dist, fun=terra::modal) {
     as("Raster") %>%
     terra::rast()
   
-  times <- ceiling(max_dist / res)
+  times <- ceiling(max_dist / res) - 1
   for (i in 1:times) {
     print(str_c("Interpolating ......", i, " of ", times, " iterations"))
     ras <- ras %>%
@@ -37,17 +37,14 @@ interpolate <- function(in_path, out_path, res, max_dist, fun=terra::modal) {
   print("Finished !")
 }
   
-files <- c("results/cnn_lstm5x5_cv_5_ep_200/diff_sasa.csv",
-          "results/cnn_lstm5x5_cv_5_ep_200/diff_haimatsu.csv",
-           "results/cnn_lstm5x5_cv_5_ep_200/res2012_cnn_5x5.csv",
-           "results/cnn_lstm5x5_cv_5_ep_200/res2021_cnn_5x5.csv")
+files <- c("results/svm.csv", "results/rnn.csv")
 
 for (file in files) {
   out_path <- stringr::str_replace(file, "csv", "tiff")
-  interpolate(file, out_path, 0.2, 1)
+  interpolate(file, out_path, 0.5, 2.0)
 }
 
 
-file <- "data/georectified.csv"
+file <- "results/georectified.csv"
 out_path <- stringr::str_replace(file, "csv", "tiff")
-interpolate(file, out_path, 0.5, 1.0, fun = mean)
+interpolate(file, out_path, 0.5, 2.0, fun = mean)

### 2022-06-29 scripts/georec_acc.R
georectification accuracy added

@@ -1,0 +1,102 @@
+library(tidyverse)
+library(jsonlite)
+
+as_df <- function(pt) {
+    u <- as.integer(pt$points[[1]][[1]])
+    v <- as.integer(pt$points[[1]][[2]])
+    label <- pt$label %>% as.integer()
+    return(tibble(u = u, v = v, label=label))
+}
+
+projection_error <- function(org_json, sim_json, georec_csv) {
+    org <- read_json(org_json)
+    sim <- read_json(sim_json)
+    org <- org$shapes %>%
+        map_dfr(as_df) %>% 
+        arrange(label)
+    sim <- sim$shapes %>%
+        map_dfr(as_df) %>%
+        arrange(label)
+    all(sim$label == org$label)
+    gr <- read_csv(georec_csv) %>%
+        select(-c(B, G, R))
+    org2 <- org %>%
+        inner_join(gr, by = c("u", "v")) %>%
+        select(-c(u, v)) %>%
+        rename(
+            x_org = x,
+            y_org = y,
+            z_org = z
+        )
+    sim2 <- sim %>%
+        inner_join(gr, by = c("u", "v")) %>%
+        select(-c(u, v)) %>%
+        rename(
+            x_sim = x,
+            y_sim = y,
+            z_sim = z
+        )
+    df <- inner_join(org2, sim2, by = "label") %>%
+        mutate(error = sqrt((x_org - x_sim)^2 + (y_org - y_sim)^2 + (z_org - z_sim)^2)) %>%
+        arrange(desc(error))
+    return(df)
+}
+
+w_dist <- projection_error(
+    "data/hand_picked_gcp/with_distortion/handpicked_original.json",
+    "data/hand_picked_gcp/with_distortion/handpicked_simulated.json",
+    "data/hand_picked_gcp/with_distortion/georectified.csv"
+)
+
+h1 <- w_dist %>%
+    ggplot(aes(x = error)) +
+    geom_histogram()
+
+ggsave("data/hand_picked_gcp/with_distortion/hist_w_dist.png", h1)
+
+w_dist %>%
+    summarise(mean(error))
+
+p <- read_json("data/hand_picked_gcp/with_distortion/params_optim.json")
+
+gcp <- read_csv("data/gcp.csv") %>%
+    mutate(distance = sqrt((p$x - x)^2 + (p$y - y) + (p$z - z))) %>%
+    mutate(type = "GCP")
+
[…]

### 2022-06-29 scripts/utils/georectify_wo_dist.py

@@ -1,0 +1,114 @@
+# Loading requirements
+from alproj.surface import create_db, crop
+from alproj.project import sim_image, reverse_proj
+from alproj.gcp import akaze_match, set_gcp
+from alproj.optimize import CMAOptimizer
+import sqlite3
+from matplotlib import pyplot as plt
+import numpy as np
+import rasterio
+import cv2
+
+res = 1.0 # Resolution in m
+aerial = rasterio.open("data/tateyama2.tiff")
+dsm = rasterio.open("data/mrd_dem_1m.tiff")
+out_path = "data/pointcloud.db" # Output database
+
+# create_db(aerial, dsm, out_path) # This takes some minutes
+
+params = {"x":732731,"y":4051171, "z":2458, "fov":75, "pan":95, "tilt":0, "roll":0,\
+          "a1":1, "a2":1, "k1":0, "k2":0, "k3":0, "k4":0, "k5":0, "k6":0, \
+          "p1":0, "p2":0, "s1":0, "s2":0, "s3":0, "s4":0, \
+          "w":5616, "h":3744, "cx":5616/2, "cy":3744/2}
+
+conn = sqlite3.connect("data/pointcloud.db")
+
+distance = 3000 # The radius of the fan shape
+chunksize = 1000000
+
+vert, col, ind = crop(conn, params, distance, chunksize) # This takes some minutes.
+
+sim = sim_image(vert, col, ind, params)
+cv2.imwrite("data/hand_picked_gcp/wo_distortion/initial.png", sim)
+
+df = reverse_proj(sim, vert, ind, params)
+
+path_org = "data_source/aligned/multi_days/mrd_085_eos_vis_20151010_1205.png"
+path_sim = "data/hand_picked_gcp/wo_distortion/initial.png"
+
+match, plot = akaze_match(path_org, path_sim, ransac_th=100, plot_result=True)
+cv2.imwrite("data/hand_picked_gcp/wo_distortion/matched.png", plot)
+gcps = set_gcp(match, df)
+gcps.to_csv("data/hand_picked_gcp/wo_distortion/gcp.csv")
+
+obj_points = gcps[["x","y","z"]] # Object points in a geographic coordinate system
+img_points = gcps[["u","v"]] # Image points in an image coordinate system 
+params_init = params # Initial parameters
+target_params = ["fov", "pan", "tilt", "roll"] # Parameters to be optimized
+
+cma_optimizer = CMAOptimizer(obj_points, img_points, params_init) # Create an optimizer instance.
[…]

### 2022-06-29 paper/paper.Rmd
georectification accuracy added

@@
 For example, the growth of dwarf pine (*Pinus pumila*), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}).
-Monitoring and predicting such changes are essential for effective conservation planning.
-Since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.
+Effective conservation planning requires early detection and constant monitoring of such vegetation changes.
+Also, since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.
 
@@
 These studies set some regions of interest (ROI) in the images and calculate the phenology index (e.g., excess greenness, \cite{Woebbecke1995ASAE}).
-Also, we can visually interpret the vegetation distribution and its changes from such time-lapse images.
-However, few studies have tackled this.
+However, few studies have utilized such images in monitoring vegetation distributions.
 This lack of studies seems to be because applying such repeat photography in monitoring vegetation distribution has two technical challenges.
@@
 Second, since digital time-lapse cameras are mounted on the ground, transforming these images into geospatial data (e.g., orthoimage) is challenging.
-In other words, even if we find a vegetation change, we cannot quantitatively measure and analyze it as geographic data.
+In other words, even if we classify the vegetation from such images, we cannot quantitatively measure and analyze it as geographic data.
 It is essential to treat ground-based images as geographic data to utilize them in conservation planning.
 
-This study proposes an automated method for drawing vegetation maps and locating and measuring vegetation changes with a digital time-lapse camera by solving these two challenges.
-We solved the first challenge by utilizing temporal changes in leaf colors in vegetation classification.
-We also developed an accurate method for transforming a ground-based photograph into geographic data to tackle the second challenge.
-Finally, we show an example application of our method by detecting and localizing vegetation changes with an 8-years digital time-lapse imagery of the Japanese alps.
-We aim to use cheap but powerful digital time-lapse cameras in alpine ecosystem conservation.
+This study proposes an automated method for drawing vegetation maps with a digital time-lapse camera by solving these two challenges.
+We solved the first challenge by using time-lapse images to classify vegetation.
+Since the autumn leaf phenology varies among species, we utilized that information.
+We show the effectiveness of such phenological information in vegetation classification.
+We also developed a novel method for transforming a ground-based photograph into geographic data to tackle the second challenge.
+Finally, we show an example of a vegetation map drawn by the proposed method.
+We aim to use cheap but powerful digital time-lapse cameras in alpine ecosystem monitoring and conservation.
 
@@
 We used repeat photography data owned by National Institute for Environmental Studies, Japan (NIES).
-All the images are publically available on NIES' webpage (<https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2>).
+All the images are publically available on NIES' webpage (https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2).
 In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt.
 Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps.
-The camera takes one photograph per hour, from 6 a.m.
+The camera takes a photograph per hour, from 6 a.m.
 to 7 p.m.
@@
 The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines.
-From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen, deciduous dwarf trees (e.g., *Pinus pumila*, *Sorbus* sp.), dwarf bamboos (e.g., *Sasa kurilensis*), and alpine herbaceous plants (e.g., *Geum pentapetalum*, *Nephrophyllidium crista-galli*).
-We used the images from late summer to late fall of 2012 and 2020 to observe the distribution changes of the dwarf pine (*Pinus pumila*): the dominant species in Japanese alps, and the invasive dwarf bamboo (*Sasa kurilensis*).
+From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen(e.g., *Pinus pumila*) and deciduous (*Sorbus* sp.,  *Betula ermanii*) dwarf trees, dwarf bamboos (e.g., *Sasa kurilensis*), and alpine shrubs and herbaceous plants (e.g., *Geum pentapetalum*, *Nephrophyllidium crista-galli*).
+This study used images from the summer and fall of 2015 to classify vegetation with the temporal patterns of the leaf color.
 
@@
 First, we selected images that are suitable for vegetation classification.
-We choose four days with good weather from late summer to late fall each year (9/19, 10/1, 10/11, 10/23 in 2010.
-9/19, 10/2, 10/11, 10/23 in 2020).
-We used the images of this season because we can classify vegetation with the patterns of autumn foliage coloration.
-Also, we chose four images from 11 a.m.
-to 2 p.m.
-each day to avoid the effect of temporal noise such as shadows.
-Finally, we got 16 images for each year.
+We choose seven days with good weather from late summer to late fall of 2015 (8/25, 9/5, 9/12, 9/20, 9/26, 10/3, 10/10).
+We used the images of this season because we can separate vegetation from the patterns of autumn foliage coloration.
 
@@
 
-Since images are slightly misaligned with each other due to the effect of wind and human interactions, we aligned them before processing.
-We implemented the program with Python3 programming language and OpenCV4 (<https://opencv.org/>) image processing library.
-First, we set one image of 2012 as the alignment target.
-Next, we automatically found matching keypoints between the target and other images using AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
+Since images are slightly misaligned, we aligned them before processing.
+We implemented the program with the Python3 programming language and OpenCV4 (https://opencv.org/) image processing library.
+First, we set one image of 2015 as the alignment target.
+Next, we automatically found matching keypoints between the target and other images using the AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
 Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's "findHomography" function.
-Because not all matched points are correct, we estimated the homography matrix using the RANdom SAmple Consensus (RANSAC) to avoid influences of such outliers.
+Applying the estimated homography matrix, we could align the images accurately (0.654 pixels in root mean square error of the matching points).
+Finally, we prepared an input mask to define image regions that should be ignored in the following procedure, such as the sky and the regions too close to the camera.
 
@@
 
-Next, we classified the pixel time series of repeat photography imagery into vegetation.
+Since we successfully aligned the images, we can stack the images and extract a time series of pixel values (Red, Green, and Blue, Fig.
+1) for each pixel.
+Such pixel time series reflects the temporal patterns of leaf colors.
 Because deciduous plants have great differences in autumn phenology among species, researchers have used that information for vegetation classification with satellite imagery (e.g., \cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}).
-In our target area, we can recognize the vegetation type with the pixel time series of autumn (Fig.
-2).
 However, no research has applied this technique to ground-based repeat photography imagery.
-We developed a deep-learning method to take advantage of high-resolution and frequent repeat photography data.
-Fig.3 shows the classification process.
+We implemented Support Vector Machine (SVM) and Recurrent Neural Network (RNN) based vegetation classification methods in this study.
+We tested the effects of using pixel time series on the classification performance.
 
@@
 
-Since ground-based photographs can provide high spatial resolution (sub-meter scale in our dataset), we can use leaf texture as additional information for classification.
-For example, we can see a glossy surface on dwarf bamboos and a mat surface on dwarf pines.
-Thus, we used a small patch (9x9 pixels square) rather than a single pixel as an input of the model.
-Therefore, a model input is a time series of image patches.
-
-Our model has two components to deal with this data structure (see Fig.
-3).
-First, we extracted each patch's features (e.g., texture) using Convolutional Neural Network (CNN) layers (Fig.
-4a).
-CNN is a neural network specialized in recognizing spatial structures of data, such as images.
-The CNN part outputs a time series of extracted features.
-Second, we used Recurrent Neural Net (RNN) layers (Fig.
-4b) to classify the temporal patterns of the features extracted by the CNN part.
-RNN is a neural network specialized in recognizing temporal or sequential data dynamics, such as text and speech.
-Amongst many variants of RNN, we used Long Short Time Memory (LSTM, \cite{Hochreiter1997LSTM}).
-Combining CNN and RNN, our model can classify the input image-patch time series considering the colors and textures of each patch and their temporal patterns.
-This CNN-RNN architecture has also been used for audio classification(\cite{Shi2015CRNNtext}) and scene text recognition(\cite{Shi2015CRNNtext}).
-
-Using a Deep Learning method has another positive side effect; mini-batch training.
-Since we used high-resolution images (16 x 21M pix), the training dataset became so immense that we could not feed them to the model at once: that consumes the computer's RAM too much.
-However, using Deep Learning methods enables us to provide them in small portions (called mini-batches) to save RAM consumption.
+We prepared two supervised models, SVM and RNN, to classify the pixel time series into vegetation categories.
+SVM is one of the most popular machine learning models in remote sensing and has many applications (\cite{Mountrakis2011SVMReview}), including vegetation classification with multitemporal satellite imagery (\cite{Tigges2013RemSenEnv}).
+RNN is a neural network that recognizes temporal or sequential data dynamics.
+Researchers have also utilized RNN for remote sensing tasks, such as land cover classification, with multi-temporal satellite imagery (\cite{Ienco2017RemSenLSTM}, \cite{Sharma2018NN}).
+Amongst many variants of RNN, we used Long Short Time Memory (LSTM, \cite{Hochreiter1997LSTM}), one of the most well-known RNN architectures.
+We also classified the pixel of every single image separately using SVM classifiers to test whether using multi-temporal imagery increases the classification performance.
 
@@
 
-We set 5 vegetation classes: dwarf pine, dwarf bamboo, other vegetation, no vegetation, and sky.
-Using a free image annotation software (Semantic Segmentation Editor, Hitachi, <https://github.com/Hitachi-Automotive-And-Industry-Lab/semantic-segmentation-editor>), an expert drew polygons on an image of 2015 for each class.
-Since vegetation might be different in 2012, 2015, and 2020, applying this teacher data to the image of 2012 and 2020 may cause misclassification.
-However, vegetation changes are expected to occur at the edge of the plant community.
-Thus we shrink each polygon with several pixels before applying it to the training.
+We set 7 vegetation classes: Dwarf Pine (*Pinus pumila*), Dwarf Bamboo (*Sasa kurilensis*), Rowans (*Sorbus sambucifolia*, *Sorbus matsumurana*), Birch (*Betula ermanii*), Alder (*Alnus viridis* subsp.
+*maximowiczii*), Other Vegetations (such as alpine shrubs and herbaceous plants), and No Vegetation.
+Using an open-source image annotation software (Semantic Segmentation Editor, Hitachi, https://github.com/Hitachi-Automotive-And-Industry-Lab/semantic-segmentation-editor), an expert prepared a teacher dataset for each class.
+Then we validated the teacher dataset with a set of telephotos taken in the summer and fall of 2016.
 
@@
 
-We implemented the classifier with Python3 language and PyTorch deep neural network library (<https://pytorch.org/>).
+We implemented the classifier with Python3 language, ThunderSVM library (<https://github.com/Xtra-Computing/thundersvm>) for the SVM classifier, and  PyTorch deep neural network library (<https://pytorch.org/>) for the RNN classifier.
 All source codes are publically available via GitHub (<https://github.com/0kam/xxxx>).
@@
 
-```{r, echo=FALSE, message=FALSE, fig.cap="Cross Validation Results"}
+```#{r, echo=FALSE, message=FALSE, fig.cap="Cross Validation Results"}
 df <- read_csv("../runs/cnn_lstm9x9_cv_5_ep_200/staritfied_cv.csv",
@@
 
-```{r, vegetation, echo=FALSE, message=FALSE, fig.cap="Vegetation classification results", out.width="100%", auto_pdf = TRUE}
+```#{r, vegetation, echo=FALSE, message=FALSE, fig.cap="Vegetation classification results", out.width="100%", auto_pdf = TRUE}
 knitr::include_graphics("vegetation.jpg")

### 2022-06-29 paper/paper.tex
georectification accuracy added

@@
 For example, the growth of dwarf pine (\emph{Pinus pumila}), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}).
-Monitoring and predicting such changes are essential for effective conservation planning.
-Since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.
+Effective conservation planning requires early detection and constant monitoring of such vegetation changes.
+Also, since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.
 
@@
 Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps.
-The camera takes one photograph per hour, from 6 a.m.
+The camera takes a photograph per hour, from 6 a.m.
 to 7 p.m.
@@
 The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines.
-From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen, deciduous dwarf trees (e.g., \emph{Pinus pumila}, \emph{Sorbus} sp.), dwarf bamboos (e.g., \emph{Sasa kurilensis}), and alpine herbaceous plants (e.g., \emph{Geum pentapetalum}, \emph{Nephrophyllidium crista-galli}).
-We used the images from late summer to late fall of 2012 and 2020 to observe the distribution changes of the dwarf pine (\emph{Pinus pumila}): the dominant species in Japanese alps, and the invasive dwarf bamboo (\emph{Sasa kurilensis}).
+From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen(e.g., \emph{Pinus pumila}) and deciduous (\emph{Sorbus} sp., \emph{Betula ermanii}) dwarf trees, dwarf bamboos (e.g., \emph{Sasa kurilensis}), and alpine shrubs and herbaceous plants (e.g., \emph{Geum pentapetalum}, \emph{Nephrophyllidium crista-galli}).
+This study used images from the summer and fall of 2015 to classify vegetation with the temporal patterns of the leaf color.
 
@@
 
-Since images are slightly misaligned with each other due to the effect of wind and human interactions, we aligned them before processing.
-We implemented the program with Python3 programming language and OpenCV4 (\url{https://opencv.org/}) image processing library.
-First, we set one image of 2012 as the alignment target.
-Next, we automatically found matching keypoints between the target and other images using AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
+Since images are slightly misaligned, we aligned them before processing.
+We implemented the program with the Python3 programming language and OpenCV4 (\url{https://opencv.org/}) image processing library.
+First, we set one image of 2015 as the alignment target.
+Next, we automatically found matching keypoints between the target and other images using the AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
 Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's ``findHomography'' function.
-Because not all matched points are correct, we estimated the homography matrix using the RANdom SAmple Consensus (RANSAC) to avoid influences of such outliers.
+Applying the estimated homography matrix, we could align the images accurately (0.654 pixels in root mean square error of the matching points).
+Finally, we prepared an input mask to define image regions that should be ignored in the following procedure, such as the sky and the regions too close to the camera.
 
@@
 Because our target site has a complex vegetation distribution and our camera has considerable lens distortion, we needed a more accurate method.
-
-\hypertarget{local-feature-based-matching-of-images-and-dsms}{%
-\subsection{Local-feature-based matching of images and DSMs}\label{local-feature-based-matching-of-images-and-dsms}}
-
-To get matching points between images and DSMs on a broader area, we used an airborne image already georectified.
-Combining an airborne image and a DSM, we rendered simulated landscape images (Fig.
-x).
-Then we got matching points (GCPs) by applying AKAZE local feature matcher to a target image and this simulated image (Fig.
-x).
-GCPs have geographical coordinates (from the DSM) and image coordinates (from the image).
-Our procedure requires the camera's exact location and initial camera parameters to render the simulated image.
 
@@
 We used a \(4 \times 4\) projection matrix \(M_{proj}\) (\ref{proj_mat}), that represents the camera's horizontal (\(fov_x\)) and vertical (\(fov_z\)) FoV.
-Finally, we can get the location of each point of the DSM on the image as \(X_{image}, Z_{image}\) (\ref{proj_tf}) i.e., we can generate a virtual image with given set of camera parameters.
+Finally, we can get the image coordinates of each point of the DSM as \(X_{image}, Z_{image}\) (\ref{proj_tf}).
 
@@
 We could not estimate the camera location because it makes the problem too complicated (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).
+
+\hypertarget{local-feature-based-matching-of-images-and-dsms}{%
+\subsection{Local-feature-based matching of images and DSMs}\label{local-feature-based-matching-of-images-and-dsms}}
+
+To get matching points between images and DSMs on a broader area, we used an airborne image already georectified.
+Combining an airborne image and a DSM, we rendered simulated landscape images (Fig.
+x).
+Then we got matching points (GCPs) by applying AKAZE local feature matcher to a target image and this simulated image (Fig.
+x).
+GCPs have geographical coordinates (from the DSM) and image coordinates (from the image).
+Our procedure requires the camera's exact location and initial camera parameters to render the simulated image.
 
@@
 
+```\#\{r, echo=FALSE, message=FALSE, fig.cap=``Cross Validation Results''\}
+df \textless- read\_csv(``../runs/cnn\_lstm9x9\_cv\_5\_ep\_200/staritfied\_cv.csv'',
+col\_select = c(metrics, vegetation, value, fold))
+theme\_gtsummary\_mean\_sd()
+
+df \%\textgreater\%
+filter(metrics != ``support'') \%\textgreater\%
+mutate(vegetation = translate\_classes(vegetation)) \%\textgreater\%
+mutate(vegetation = factor(vegetation, levels = vegetation\_levels)) \%\textgreater\%
+group\_by(., vegetation, metrics) \%\textgreater\%
+summarise(
+mean = sprintf(``\%1.3f'', mean(value)),
+sd = sprintf(``(\%1.3f)'', sd(value))
+) \%\textgreater\%
+pivot\_longer(cols=c(mean, sd), names\_to=``var'') \%\textgreater\%
+pivot\_wider(names\_from=metrics, values\_from=value) \%T\textgreater\%
+write\_csv(``table1.csv'') \%\textgreater\%
+select(-var) \%\textgreater\%
+kable(format=``latex'', booktabs=TRUE, caption = ``Cross validation result \textbackslash label\{tab:vegetation\_cv\}'') \%\textgreater\%
+kable\_styling() \%\textgreater\%
+collapse\_rows(columns=1) \%\textgreater\%
+footnote(general = ``Mean (SD) of 5-Fold Cross-Varidation'')
+
 \begin{verbatim}
-## Warning: One or more parsing issues, see `problems()` for details
+```#{r, vegetation, echo=FALSE, message=FALSE, fig.cap="Vegetation classification results", out.width="100%", auto_pdf = TRUE}
+knitr::include_graphics("vegetation.jpg")
 \end{verbatim}
-
-\begin{table}
-
-\caption{\label{tab:unnamed-chunk-1}Cross validation result \label{tab:vegetation_cv}}
-\centering
-\begin{tabular}[t]{llll}
-\toprule
-vegetation & f1-score & precision & recall\\
-\midrule
- & 0.986 & 0.984 & 0.988\\
-\cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash Macro Average} & (0.006) & (0.010) & (0.001)\\
-\cmidrule{1-4}
- & 0.997 & 0.997 & 0.997\\
-\cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash Weighted Average} & (0.001) & (0.001) & (0.001)\\
-\cmidrule{1-4}
- & 0.987 & 0.980 & 0.994\\
-\cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash Dwarf Pine} & (0.004) & (0.010) & (0.003)\\
-\cmidrule{1-4}
- & 0.962 & 0.964 & 0.961\\
-\cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash Dwarf Bamboo} & (0.010) & (0.020) & (0.004)\\
-\cmidrule{1-4}
- & 0.998 & 0.999 & 0.997\\
-\cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash Other vegetation} & (0.001) & (0.000) & (0.002)\\
-\cmidrule{1-4}
- & 0.978 & 0.972 & 0.985\\
-\cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash Non Vegetation} & (0.028) & (0.053) & (0.004)\\
-\cmidrule{1-4}
- & 1.000 & 1.000 & 1.000\\
-\cmidrule{2-4}
-\multirow{-2}{*}{\raggedright\arraybackslash Sky} & (0.000) & (0.000) & (0.000)\\
-\bottomrule
-\multicolumn{4}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{4}{l}{\rule{0pt}{1em}Mean (SD) of 5-Fold Cross-Varidation}\\
-\end{tabular}
-\end{table}
-
-\begin{figure}
-\includegraphics[width=1\linewidth]{vegetation} \caption{Vegetation classification results}\label{fig:vegetation}
-\end{figure}
 

### 2022-06-29 scripts/utils/georectify_silhouette.py

@@ -1,6 +1,7 @@
 # Loading requirements
 from alproj.surface import create_db, crop
 from alproj.project import sim_image, reverse_proj
+from scripts.utils.optimize_silhouette import CMAOptimizer
 from alproj.gcp import akaze_match, set_gcp
 from alproj.optimize import CMAOptimizer
 import sqlite3
@@ -29,41 +30,45 @@ chunksize = 1000000
 vert, col, ind = crop(conn, params, distance, chunksize) # This takes some minutes.
 
 sim = sim_image(vert, col, ind, params)
-cv2.imwrite("data/hand_picked_gcp/wo_distortion/initial.png", sim)
+sim[sim > 0] = 255
+cv2.imwrite("data/hand_picked_gcp/silhouette/initial.png", sim)
 
 df = reverse_proj(sim, vert, ind, params)
 
-path_org = "data_source/aligned/multi_days/mrd_085_eos_vis_20151010_1205.png"
-path_sim = "data/hand_picked_gcp/wo_distortion/initial.png"
+org = cv2.imread("data_source/sky_mask_2015.png")
+org[org > 0] = 255
+cv2.imwrite("data/hand_picked_gcp/silhouette/original.png", org)
+
+path_org = "data/hand_picked_gcp/silhouette/original.png"
+path_sim = "data/hand_picked_gcp/silhouette/initial.png"
 
 match, plot = akaze_match(path_org, path_sim, ransac_th=100, plot_result=True)
-cv2.imwrite("data/hand_picked_gcp/wo_distortion/matched.png", plot)
+cv2.imwrite("data/hand_picked_gcp/silhouette/matched.png", plot)
 gcps = set_gcp(match, df)
-gcps.to_csv("data/hand_picked_gcp/wo_distortion/gcp.csv")
+gcps.to_csv("data/hand_picked_gcp/silhouette/gcp.csv")
 
 obj_points = gcps[["x","y","z"]] # Object points in a geographic coordinate system
 img_points = gcps[["u","v"]] # Image points in an image coordinate system 
 params_init = params # Initial parameters
-target_params = ["fov", "pan", "tilt", "roll"] # Parameters to be optimized
+target_params = ["fov", "pan", "tilt", "roll", "a1", "a2", "k1", "k2", "k3", "k4", "k5", "k6", "p1", "p2", "s1", "s2", "s3", "s4"] # Parameters to be optimized
 
 cma_optimizer = CMAOptimizer(obj_points, img_points, params_init) # Create an optimizer instance.
[…]

### 2022-06-29 scripts/utils/optimize_silhouette.py

@@ -1,0 +1,264 @@
+import numpy as np
+from math import pi, sin, cos, tan
+import pandas as pd
+from cmaes import CMA
+from tqdm import tqdm
+from scipy.signal import correlate
+
+def intrinsic_mat(fov_x_deg, w, h, cx=None, cy=None):
+    """ 
+    Makes an intrinsic camera matrix (in OpenCV style) from given parameters.
+    See https://learnopencv.com/geometry-of-image-formation/ .
+
+    Parameters
+    ----------
+    fov_x_deg : float
+        Field of View in degree.
+    w : int
+        Width of the image
+    h : int
+        Height of the image
+    cx : float default None
+        X-coordinate of the principal point. If None, cx = w/2.
+    cy : float default None
+        Y-coordinate of the principal point. If None, y = h/2.
+    
+    Returns
+    -------
+    mat : numpy.ndarray
+        Intrinsic matrix.
+    """
+    if cx == None:
+        cx = w/2
+    if cy == None:
+        cy = h/2
+    fov_x = fov_x_deg * pi / 180
+    fov_y = fov_x * h / w
+    fx = w / (2 * tan(fov_x/2))
+    fy = h / (2 * tan(fov_y/2))
+    mat = np.array([
+        [fx, 0, cx],
+        [0, fy, cy],
+        [0, 0, 1]
+    ])
+    return mat
+
+
+def extrinsic_mat(pan_deg, tilt_deg, roll_deg, t_x, t_y, t_z):
+    """
+    Makes an extrinsic camera matrix from given parameters.
+    See https://learnopencv.com/geometry-of-image-formation/ .
+
+    Parameters
+    ----------
+    pan_deg : float
+        Pan angle in degree.
+    tilt_deg : float
+        Tilt angle in degree.
+    roll_deg : float
+        Roll angle in degree.
+    t_x : float
+        X-axis coordinate of the camera location.
+    t_y : float
+        Y-axis coordinate of the camera location.
+    t_z : float
+        Z-axis coordinate of the camera location.
+    
+    Returns
+    -------
+    mat : numpy.ndarray
+        Extrinsic camera matrix.
+    """
+    pan = pan_deg * pi / 180
+    tilt = -(tilt_deg + 90) * pi / 180
+    roll = -roll_deg * pi / 180
+    rmat_z = np.array([
+        [cos(pan), -sin(pan), 0],
[…]

### 2022-07-19 paper/paper.Rmd
methods done

@@
 library(kableExtra)
+library(maps)
+library(mapdata)
 translate_classes <- function(names) {
@@
 In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt.
-Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps.
+Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps \ref{fig:map}.
 The camera takes a photograph per hour, from 6 a.m.
@@
 This study used images from the summer and fall of 2015 to classify vegetation with the temporal patterns of the leaf color.
+
+(ref:map) The study site. (a) The location of Mt. Tateyama. (b) The installation point of the camera in Murodo-sanso lodge. (c) The camera (EOS 5D MK2, Canon Inc.)
+
+```{r, map, echo=FALSE, message=FALSE, fig.cap="(ref:map)", out.width="100%", auto_pdf = TRUE}
+# map('japan', xlim = c(127,148), ylim = c(30,47))
+# map.axes()
+# points(137.618973, 36.574844, col="red",pch=20)
+# text(133.5, 38,"Mt. Tateyama",col="red")
+knitr::include_graphics("paper_files/figures/Slide3.jpg")
+```
 
@@
 
-Since we successfully aligned the images, we can stack the images and extract a time series of pixel values (Red, Green, and Blue, Fig.
-1) for each pixel.
+Because we successfully aligned the images, we can stack the images and extract a time series of pixel values (Red, Green, and Blue, \ref{fig:pixtimeseries}) for each pixel.
 Such pixel time series reflects the temporal patterns of leaf colors.
@@
 We tested the effects of using pixel time series on the classification performance.
+
+(ref:pixtimeseries) Pixel time series acquired from the time lapse camera.
+You can obtain a time series of pixel values (i.e., Red, Green, and Blue) for each pixel on the photographs.
+Such pixel time series reflects the autumn phenology of the vegetation.
+
+```{r, pixtimeseries, echo=FALSE, message=FALSE, fig.cap="(ref:pixtimeseries)", out.width="100%", auto_pdf = TRUE}
+knitr::include_graphics("paper_files/figures/Slide1.jpg")
+```
 
@@
 
-# Automatic georectification
+## Automatic georectification
 
@@
 Estimating the parameters of this function (such as the camera location, pose, and the field of view), we can map an image onto a DSM.
-We recommend readers to \cite{Portenier2020Cryosphere} for a plain mathmatical explanation of this process.
 Usually, georectification has three steps:
@@
 1.  Finding Ground Control Points (GCPs) in the image.\
-2.  Estimating camera parameters such as camera poses and field of view using GCPs.\
-3.  Mapping the image onto the DSM using camera parameters.
+2.  Estimating the camera parameters such as camera poses and field of view using GCPs.\
+3.  Mapping the image onto the DSM using the camera parameters.
 
@@
 
-As we mentioned before, we considered a camera as a function that transforms geographical coordinates of each location of the target mountain to image coordinates in the acquired photograph.
+As we mentioned before, we considered a camera as a function that transforms geographical coordinates of the target mountain to the image coordinates in the acquired photograph.
 We implemented this procedure using the OpenGL framework to accelerate it with graphical processing units (GPUs).
@@
 
-1. Transforming the world (geographical) coordinates to the view coordinates using camera's extrinsic parameters (i.e., the location and angles of the camera).
-2. Distorting the view coordinates using the lens distortion parameters.
+1.
+Transforming the world (geographical) coordinates to the view coordinates (coordinates seen from the camera's point of view) using camera's extrinsic parameters (i.e., the location and angles of the camera).
+\
+2. Distorting the view coordinates using the lens distortion parameters. \
 3. Transforming the view coordinates to the screen (image) coordinates using camera's intrinsic parameters (i.e., the FoV and aspect ratio of the camera).
 
-First, we transform the absolute geographic coordinates (also known as the world coordinates) to the view coordinates that are relative to the camera's position and direction.
-We apply a $4 \times 4$ view matrix (\ref{view_matrix}) to the geographic coordinates in this step.
+First, we transformed the absolute geographic coordinates (also known as the world coordinates) to the view coordinates that are relative to the camera's position and direction.
+We applied a $4 \times 4$ view matrix $M_{view}$ (\ref{view_matrix}) to the geographic coordinates in this step.
 The view matrix represents the position and the direction (pan, tilt, roll) of the camera.
@@
 
-Where $pan, tilt, roll$ are the Euler angles of the camera and $x, y, z$ are the camera location in the geographic coordinate system.
-Then, we can transform the geographic coordinates of the DSM $\begin{bmatrix} X_{geo} & Z_{geo} & Y_{geo} & 1 \end{bmatrix}$ to the camera coordinates $\begin{bmatrix} X_{camera} & Z_{camera} & Y_{camera} & 1 \end{bmatrix}$ applying the view matrix $M_{view}$ (\ref{view_tf}).
-In the OpenGL's camera coordinate system, $X_{camera}$, $Z_{camera}$ and $Y_{camera}$ represents horizontal, vertical, and depth positions respectively.
+Where $pan, tilt, roll$ are the Euler angles of the camera pose and $x, y, z$ are the camera location in the geographic coordinate system.
+Then, we can transform the geographic coordinates of the DSM $\begin{bmatrix} X_{geo} & Z_{geo} & Y_{geo} & 1 \end{bmatrix}$ to the view coordinates $\begin{bmatrix} X_{view} & Z_{view} & Y_{view} & 1 \end{bmatrix}$ applying the view matrix $M_{view}$ (\ref{view_tf}).
+In the OpenGL's view coordinate system, $X_{view}$, $Z_{view}$ and $Y_{view}$ represents horizontal, vertical, and depth positions respectively.
 
@@
   \begin{bmatrix} 
-    X_{camera} \\ Z_{camera} \\ Y_{camera} \\ 1 
+    X_{view} \\ Z_{view} \\ Y_{view} \\ 1 
   \end{bmatrix}
@@
 
-Second, we distort the camera coordinates to simulate the lens distortion.
-We modeled the lens distortion (\ref{dist_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation, where $X_{norm}$ and $Z_{norm}$ are the $Y$-normalized coordinates of the camera coordinates.
+Second, we distorted the camera coordinates to simulate the lens distortion.
+We modeled the lens distortion (\ref{dist_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation (<https://docs.opencv.org/4.x/d9/d0c/group__calib3d.html>), where $X_{norm}$ and $Z_{norm}$ are the $Y$-normalized coordinates of the camera coordinates.
 This model distorts points' locations according to the distance from the center of the image when projected to the image surface.
-Our model includes radial ($k1~k6$), tangental ($p1, p2$), thin prism ($s1~s4$) distortion, and unequal pixel aspect ratio ($a1, a2$).
-See Weng et al.
-1992 for the details of lens distortion modeling.
+Our model includes radial ($k1$~$k6$), tangental ($p1$, $p2$), thin prism ($s1$~$s4$) distortion, and unequal pixel aspect ratio ($a1$, $a2$).
+See \cite{Weng1992CameraCalib} for the details of lens distortion modeling.
 
@@
 
-Then we transform the distorted camera coordinates to the image coordinates by perspective projection.
+Next, we transformed the distorted view coordinates to the image coordinates by perspective projection.
 During the perspective projection, a closer object is drawn larger.
 We used a $4 \times 4$ projection matrix $M_{proj}$ (\ref{proj_mat}), that represents the camera's horizontal ($fov_x$) and vertical ($fov_z$) FoV.
-Finally, we can get the image coordinates of each point of the DSM as $X_{image}, Z_{image}$ (\ref{proj_tf}).
+Finally, we can get the image coordinates of the points as $X_{image}, Z_{image}$ (\ref{proj_tf}).
 
@@
 \begin{gather}
-  f_x = \frac{1}{\frac{\tan fov_x}{2}} 
-  f_z = \frac{1}{\frac{\tan fov_z}{2}}
+  f_x = \frac{1}{\frac{\tan fov_x}{2}} \\
+  f_z = \frac{1}{\frac{\tan fov_z}{2}} \\
   M_{proj} = 
@@
 
-Thus, now we can project GCPs' geographical coordinates into image coordinates using lens distortion parameters and other camera parameters (the camera location, pose, and the field of view).
-We optimized these (except camera location) by minimizing the square projection error of the GCPs using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}).
+Now you can project GCPs' geographical coordinates into image coordinates using lens distortion parameters and other camera parameters (the camera location, pose, and the field of view).
+We optimized these parameters (except camera location) by minimizing the square projection error of the GCPs using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}, \ref{fig:optim}).
 We could not estimate the camera location because it makes the problem too complicated (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).
+
+(ref:optim) Work flow of the camera parameter optimization. We estimated the camera parameters by minimizing the GCP's reprojection error.
+
+```{r, optim, echo=FALSE, message=FALSE, fig.cap="(ref:optim)", out.width="100%", auto_pdf = TRUE}
+knitr::include_graphics("paper_files/figures/Slide5.jpg")
+```
 
@@
 
-To get matching points between images and DSMs on a broader area, we used an airborne image already georectified.
-Combining an airborne image and a DSM, we rendered simulated landscape images (Fig.
-x).
-Then we got matching points (GCPs) by applying AKAZE local feature matcher to a target image and this simulated image (Fig.
-x).
+To get matching points between images and DSMs on a broader area, we additionally used an orthorectified airborne image.
+Combining an airborne image, a DSM, and a set of initial camera parameters, we rendered simulated landscape images \ref{fig:matched} applying the camera model.
+Then we got matching points (GCPs) by applying AKAZE local feature matcher to a target image and this simulated image \ref{fig:matched}.
 GCPs have geographical coordinates (from the DSM) and image coordinates (from the image).
 Our procedure requires the camera's exact location and initial camera parameters to render the simulated image.
+Note that the orthorectification accuracy of the airborne photograph may affect the georectification accuracy.
+
+(ref:matched) The original image (left) and the simulated image (right).
+The simulated image was rendered with an orthophoto, DSM, and initial camera parameters.
+Red points shows the matching points found by the AKAZE local feature matcher.
+We used these points as GCPs.
+
+```{r, matched, echo=FALSE, message=FALSE, fig.cap="(ref:matched)", out.width="100%", auto_pdf = TRUE}
+knitr::include_graphics("paper_files/figures/Slide4.jpg")
+```
+
+## Georectification
+(ref:georec) Georectification procedure. We applied the optimized camera parameters to the DSM and the vegetation classification result to get a vegetation map.
+
+```{r, georec, echo=FALSE, message=FALSE, fig.cap="(ref:georec)", out.width="100%", auto_pdf = TRUE}
+knitr::include_graphics("paper_files/figures/Slide6.jpg")
+```
+
+Finally, we applied the optimized camera parameters to the DSM and the vegetation classification result \ref{fig:georec}.
 
@@
 We used an airborne photograph taken in the November of 201X with a spatial resolution of 1.0 m.
-Also, we used the 5m resolution Digital Elevation Model provided by the Geospatial Information Authority of Japan (GSI) as a DSM.
+Also, we used the 1m resolution Digital Surface Model that were also used in the orthorectification process of the airborne photograph.
 
@@
 
-```#{r, echo=FALSE, message=FALSE, fig.cap="Cross Validation Results"}
-df <- read_csv("../runs/cnn_lstm9x9_cv_5_ep_200/staritfied_cv.csv",
-               col_select = c(metrics, vegetation, value, fold))
-theme_gtsummary_mean_sd()
-
-df %>%
-  filter(metrics != "support") %>%
-  mutate(vegetation = translate_classes(vegetation)) %>%
-  mutate(vegetation = factor(vegetation, levels = vegetation_levels)) %>%
-  group_by(., vegetation, metrics) %>%
-  summarise(
-    mean = sprintf("%1.3f", mean(value)),
-    sd = sprintf("(%1.3f)", sd(value))
-  ) %>% 
-  pivot_longer(cols=c(mean, sd), names_to="var") %>% 
-  pivot_wider(names_from=metrics, values_from=value) %T>%
-  write_csv("table1.csv") %>%
-  select(-var) %>%
-  kable(format="latex", booktabs=TRUE, caption = "Cross validation result \\label{tab:vegetation_cv}") %>% 
-  kable_styling() %>% 
-  collapse_rows(columns=1) %>%
-  footnote(general = "Mean (SD) of 5-Fold Cross-Varidation")
-
-```
-
-```#{r, vegetation, echo=FALSE, message=FALSE, fig.cap="Vegetation classification results", out.width="100%", auto_pdf = TRUE}
-knitr::include_graphics("vegetation.jpg")
+(ref:vegetation) Vegetation classification results of the RNN model. The masked area, i.e., the sky and the regions too close to the camera, is shown in black.
+```{r, vegetation, echo=FALSE, message=FALSE, fig.cap="(ref:vegetation)", out.width="100%", auto_pdf = TRUE}
+knitr::include_graphics("paper_files/figures/Slide2.jpg")
 ```
@@
 ## Georectification accuracy
+ We tested the accuracy of our georectification method and compared the effect of its features, i.e., using image matching in the image-to-DSM alignment, and modeling the lens distortion.
 

### 2022-07-19 paper/paper.tex
methods done

@@
 This study used images from the summer and fall of 2015 to classify vegetation with the temporal patterns of the leaf color.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{paper_files/figures/Slide3} \caption{The study site.
+(a) The location of Mt.
+Tateyama.
+(b) The installation point of the camera in Murodo-sanso lodge.
+(c) The camera (EOS 5D MK2, Canon Inc.)}\label{fig:map}
+\end{figure}
 
@@
 We tested the effects of using pixel time series on the classification performance.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{paper_files/figures/Slide1} \caption{Pixel time series acquired from the time lapse camera.
+You can obtain a time series of pixel values (i.e., Red, Green, and Blue) for each pixel on the photographs.
+Such pixel time series reflects the autumn phenology of the vegetation.}\label{fig:pixtimeseries}
+\end{figure}
 
@@
 
-We set 5 vegetation classes: dwarf pine, dwarf bamboo, other vegetation, no vegetation, and sky.
-Using a free image annotation software (Semantic Segmentation Editor, Hitachi, \url{https://github.com/Hitachi-Automotive-And-Industry-Lab/semantic-segmentation-editor}), an expert drew polygons on an image of 2015 for each class.
-Since vegetation might be different in 2012, 2015, and 2020, applying this teacher data to the image of 2012 and 2020 may cause misclassification.
-However, vegetation changes are expected to occur at the edge of the plant community.
-Thus we shrink each polygon with several pixels before applying it to the training.
+We set 7 vegetation classes: Dwarf Pine (\emph{Pinus pumila}), Dwarf Bamboo (\emph{Sasa kurilensis}), Rowans (\emph{Sorbus sambucifolia}, \emph{Sorbus matsumurana}), Birch (\emph{Betula ermanii}), Alder (\emph{Alnus viridis} subsp.
+\emph{maximowiczii}), Other Vegetations (such as alpine shrubs and herbaceous plants), and No Vegetation.
+Using an open-source image annotation software (Semantic Segmentation Editor, Hitachi, \url{https://github.com/Hitachi-Automotive-And-Industry-Lab/semantic-segmentation-editor}), an expert prepared a teacher dataset for each class.
+Then we validated the teacher dataset with a set of telephotos taken in the summer and fall of 2016.
 
@@
 
-We implemented the classifier with Python3 language and PyTorch deep neural network library (\url{https://pytorch.org/}).
+We implemented the classifier with Python3 language, ThunderSVM library (\url{https://github.com/Xtra-Computing/thundersvm}) for the SVM classifier, and PyTorch deep neural network library (\url{https://pytorch.org/}) for the RNN classifier.
 All source codes are publically available via GitHub (\url{https://github.com/0kam/xxxx}).
@@
 \hypertarget{automatic-georectification}{%
-\section{Automatic georectification}\label{automatic-georectification}}
+\subsection{Automatic georectification}\label{automatic-georectification}}
 
@@
 \item
-  Estimating camera parameters such as camera poses and field of view using GCPs.\\
+  Estimating the camera parameters such as camera poses and field of view using GCPs.\\
 \item
-  Mapping the image onto the DSM using camera parameters.
+  Mapping the image onto the DSM using the camera parameters.
 \end{enumerate}
@@
 \item
-  Transforming the world (geographical) coordinates to the view coordinates using camera's extrinsic parameters (i.e., the location and angles of the camera).
+  Transforming the world (geographical) coordinates to the view coordinates (coordinates seen from the camera's point of view) using camera's extrinsic parameters (i.e., the location and angles of the camera).\\
 \item
-  Distorting the view coordinates using the lens distortion parameters.
+  Distorting the view coordinates using the lens distortion parameters.\\
 \item
@@
 
-First, we transform the absolute geographic coordinates (also known as the world coordinates) to the view coordinates that are relative to the camera's position and direction.
-We apply a \(4 \times 4\) view matrix (\ref{view_matrix}) to the geographic coordinates in this step.
+First, we transformed the absolute geographic coordinates (also known as the world coordinates) to the view coordinates that are relative to the camera's position and direction.
+We applied a \(4 \times 4\) view matrix \(M_{view}\) (\ref{view_matrix}) to the geographic coordinates in this step.
 The view matrix represents the position and the direction (pan, tilt, roll) of the camera.
@@
 
-Where \(pan, tilt, roll\) are the Euler angles of the camera and \(x, y, z\) are the camera location in the geographic coordinate system.
-Then, we can transform the geographic coordinates of the DSM \(\begin{bmatrix} X_{geo} & Z_{geo} & Y_{geo} & 1 \end{bmatrix}\) to the camera coordinates \(\begin{bmatrix} X_{camera} & Z_{camera} & Y_{camera} & 1 \end{bmatrix}\) applying the view matrix \(M_{view}\) (\ref{view_tf}).
-In the OpenGL's camera coordinate system, \(X_{camera}\), \(Z_{camera}\) and \(Y_{camera}\) represents horizontal, vertical, and depth positions respectively.
+Where \(pan, tilt, roll\) are the Euler angles of the camera pose and \(x, y, z\) are the camera location in the geographic coordinate system.
+Then, we can transform the geographic coordinates of the DSM \(\begin{bmatrix} X_{geo} & Z_{geo} & Y_{geo} & 1 \end{bmatrix}\) to the view coordinates \(\begin{bmatrix} X_{view} & Z_{view} & Y_{view} & 1 \end{bmatrix}\) applying the view matrix \(M_{view}\) (\ref{view_tf}).
+In the OpenGL's view coordinate system, \(X_{view}\), \(Z_{view}\) and \(Y_{view}\) represents horizontal, vertical, and depth positions respectively.
 
@@
 
-Second, we distort the camera coordinates to simulate the lens distortion.
-We modeled the lens distortion (\ref{dist_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation, where \(X_{norm}\) and \(Z_{norm}\) are the \(Y\)-normalized coordinates of the camera coordinates.
+Second, we distorted the camera coordinates to simulate the lens distortion.
+We modeled the lens distortion (\ref{dist_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation (\url{https://docs.opencv.org/4.x/d9/d0c/group__calib3d.html}), where \(X_{norm}\) and \(Z_{norm}\) are the \(Y\)-normalized coordinates of the camera coordinates.
 This model distorts points' locations according to the distance from the center of the image when projected to the image surface.
-Our model includes radial (\(k1~k6\)), tangental (\(p1, p2\)), thin prism (\(s1~s4\)) distortion, and unequal pixel aspect ratio (\(a1, a2\)).
-See Weng et al.~1992 for the details of lens distortion modeling.
+Our model includes radial (\(k1\)\textasciitilde{}\(k6\)), tangental (\(p1\), \(p2\)), thin prism (\(s1\)\textasciitilde{}\(s4\)) distortion, and unequal pixel aspect ratio (\(a1\), \(a2\)).
+See \cite{Weng1992CameraCalib} for the details of lens distortion modeling.
 
@@
 
-Then we transform the distorted camera coordinates to the image coordinates by perspective projection.
+Next, we transformed the distorted camera coordinates to the image coordinates by perspective projection.
 During the perspective projection, a closer object is drawn larger.
 We used a \(4 \times 4\) projection matrix \(M_{proj}\) (\ref{proj_mat}), that represents the camera's horizontal (\(fov_x\)) and vertical (\(fov_z\)) FoV.
-Finally, we can get the image coordinates of each point of the DSM as \(X_{image}, Z_{image}\) (\ref{proj_tf}).
+Finally, we can get the image coordinates of the points as \(X_{image}, Z_{image}\) (\ref{proj_tf}).
 
@@
 
-Thus, now we can project GCPs' geographical coordinates into image coordinates using lens distortion parameters and other camera parameters (the camera location, pose, and the field of view).
-We optimized these (except camera location) by minimizing the square projection error of the GCPs using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}).
+Now you can project GCPs' geographical coordinates into image coordinates using lens distortion parameters and other camera parameters (the camera location, pose, and the field of view).
+We optimized these (except camera location) by minimizing the square projection error of the GCPs using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}, \ref{fig:optim}).
 We could not estimate the camera location because it makes the problem too complicated (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{paper_files/figures/Slide5} \caption{Work flow of the camera parameter optimization.
+We estimated the camera parameters by minimizing the GCP's reprojection error.}\label{fig:optim}
+\end{figure}
 
@@
 
-To get matching points between images and DSMs on a broader area, we used an airborne image already georectified.
-Combining an airborne image and a DSM, we rendered simulated landscape images (Fig.
-x).
-Then we got matching points (GCPs) by applying AKAZE local feature matcher to a target image and this simulated image (Fig.
-x).
+To get matching points between images and DSMs on a broader area, we additionally used an orthorectified airborne image.
+Combining an airborne image, a DSM, and a set of initial camera parameters, we rendered simulated landscape images \ref{fig:matched} applying the camera model.
+Then we got matching points (GCPs) by applying AKAZE local feature matcher to a target image and this simulated image \ref{fig:matched}.
 GCPs have geographical coordinates (from the DSM) and image coordinates (from the image).
 Our procedure requires the camera's exact location and initial camera parameters to render the simulated image.
+Note that the orthorectification accuracy of the airborne photograph may affect the georectification accuracy.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{paper_files/figures/Slide4} \caption{The original image (left) and the simulated image (right).
+The simulated image was rendered with an orthophoto, DSM, and initial camera parameters.
+Red points shows the matching points found by the AKAZE local feature matcher.
+We used these points as GCPs.}\label{fig:matched}
+\end{figure}
+
+\hypertarget{georectification}{%
+\subsection{Georectification}\label{georectification}}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{paper_files/figures/Slide6} \caption{Georectification procedure.
+We applied the optimized camera parameters to the DSM and the vegetation classification result to get a vegetation map.}\label{fig:georec}
+\end{figure}
+
+Finally, we applied the optimized camera parameters to the DSM and the vegetation classification result \ref{fig:georec}.
 
@@
 
-```\#\{r, echo=FALSE, message=FALSE, fig.cap=``Cross Validation Results''\}
-df \textless- read\_csv(``../runs/cnn\_lstm9x9\_cv\_5\_ep\_200/staritfied\_cv.csv'',
-col\_select = c(metrics, vegetation, value, fold))
-theme\_gtsummary\_mean\_sd()
-
-df \%\textgreater\%
-filter(metrics != ``support'') \%\textgreater\%
-mutate(vegetation = translate\_classes(vegetation)) \%\textgreater\%
-mutate(vegetation = factor(vegetation, levels = vegetation\_levels)) \%\textgreater\%
-group\_by(., vegetation, metrics) \%\textgreater\%
-summarise(
-mean = sprintf(``\%1.3f'', mean(value)),
-sd = sprintf(``(\%1.3f)'', sd(value))
-) \%\textgreater\%
-pivot\_longer(cols=c(mean, sd), names\_to=``var'') \%\textgreater\%
-pivot\_wider(names\_from=metrics, values\_from=value) \%T\textgreater\%
-write\_csv(``table1.csv'') \%\textgreater\%
-select(-var) \%\textgreater\%
-kable(format=``latex'', booktabs=TRUE, caption = ``Cross validation result \textbackslash label\{tab:vegetation\_cv\}'') \%\textgreater\%
-kable\_styling() \%\textgreater\%
-collapse\_rows(columns=1) \%\textgreater\%
-footnote(general = ``Mean (SD) of 5-Fold Cross-Varidation'')
-
-\begin{verbatim}
-```#{r, vegetation, echo=FALSE, message=FALSE, fig.cap="Vegetation classification results", out.width="100%", auto_pdf = TRUE}
-knitr::include_graphics("vegetation.jpg")
-\end{verbatim}
+\begin{figure}
+\includegraphics[width=1\linewidth]{paper_files/figures/Slide2} \caption{Vegetation classification results of the RNN model.
+The masked area, i.e., the sky and the regions too close to the camera, is shown in black.}\label{fig:vegetation}
+\end{figure}
 
@@
 \subsection{Georectification accuracy}\label{georectification-accuracy}}
+
+We tested the accuracy of our georectification method and compared the effect of its features, i.e., using image matching in the image-to-DSM alignment, and modeling the lens distortion.
 

### 2022-07-19 scripts/georec_acc.R

@@ -100,3 +100,39 @@ p2 <- wo_dist %>%
     geom_point()
 
 ggsave("data/hand_picked_gcp/wo_distortion/scatter.png", p2)
+
+#-----------------------------------------------------------------------------
+
+silh <- projection_error(
+    "data/hand_picked_gcp/silhouette/handpicked_original.json",
+    "data/hand_picked_gcp/silhouette/handpicked_simulated.json",
+    "data/hand_picked_gcp/silhouette/georectified.csv"
+)
+
+h3 <- silh %>%
+    ggplot(aes(x = error)) +
+    geom_histogram()
+
+ggsave("data/hand_picked_gcp/silhouette/hist_silh.png", h3)
+
+silh %>%
+    summarise(mean(error))
+
+p <- read_json("data/hand_picked_gcp/silhouette/params_optim.json")
+
+gcp <- read_csv("data/hand_picked_gcp/silhouette/gcp.csv") %>%
+    mutate(distance = sqrt((p$x - x)^2 + (p$y - y) + (p$z - z))) %>%
+    mutate(type = "GCP")
+
+gcp %>% 
+    ggplot(aes(x = distance)) +
+    geom_boxplot()
+
+silh <- silh %>%
+    mutate(distance = sqrt((p$x - x_org)^2 + (p$y - y_org) + (p$z - z_org))) 
+    
+p3 <- ggplot() +
+    geom_point(data = silh, mapping = aes(x = distance, y = error)) +
+    geom_violin(data = gcp, mapping = aes(x = distance, y = 0))
+
+ggsave("data/hand_picked_gcp/silhouette/scatter.png", p3)

### 2022-07-19 scripts/models/run_rnn.py

@@ -5,13 +5,13 @@ import numpy as np
 
 cmap = ListedColormap(
     np.array(
-        [[154,205,50], # 1: Dwarf bamboo
-        [70, 130, 180], # 2: Other vegetation
+        [[133,153,0], # 1: Dwarf bamboo
+        [238, 232, 213], # 2: Other vegetation
         [192,192,192], # 3: No vegetation
-        [220,20,60], # 4: ナナカマド
-        [255,215,0], # 5: ダケカンバ
-        [139,69,19],
-        [0,100,0]] # 4: Dwarf pine
+        [220,50,47], # 4: ナナカマド
+        [181,137,0], # 5: ダケカンバ
+        [108,113,196], # 6 ミヤマハンノキ
+        [42,161,152]] # 7: ハイマツ 
     ) / 255
 )
 
@@ -44,4 +44,20 @@ for d in glob("runs/cv/rnn1x1/*"):
 preds = torch.Tensor(np.stack(preds))
 pred, _ = torch.mode(preds, dim = 0)
 np.save("results/rnn.npy", pred)
+plt.imsave("results/rnn.png", pred, cmap=cmap)
+
+pred = np.load("results/rnn.npy")
+cmap = ListedColormap(
+    np.array(
+        [[0,0,0], # 0 No data
+        [133,153,0], # 1: Dwarf bamboo
+        [238, 232, 213], # 2: Other vegetation
+        [192,192,192], # 3: No vegetation
+        [220,50,47], # 4: ナナカマド
+        [181,137,0], # 5: ダケカンバ
+        [108,113,196], # 6 ミヤマハンノキ
+        [42,161,152]] # 7: ハイマツ 
+    ) / 255
+)
+
 plt.imsave("results/rnn.png", pred, cmap=cmap)

### 2022-07-19 scripts/utils/georectify.py

@@ -33,11 +33,25 @@ cv2.imwrite("data/initial.png", sim)
 
 df = reverse_proj(sim, vert, ind, params)
 
-path_org = "data_source/aligned/2012/mrd_085_eos_vis_20121021_1200.png"
+path_org = "data_source/aligned/multi_days/mrd_085_eos_vis_20151010_1205.png"
 path_sim = "data/initial.png"
 
 match, plot = akaze_match(path_org, path_sim, ransac_th=100, plot_result=True)
-cv2.imwrite("data/matched.png", plot)
+
+org = cv2.cvtColor(cv2.imread(path_org), cv2.COLOR_BGR2RGB)
+sim = cv2.cvtColor(cv2.imread(path_sim), cv2.COLOR_BGR2RGB)
+
+fig, ax = plt.subplots(1, 2, figsize=(16,6))
+ax[0].axis("off")
+ax[0].imshow(org)
+ax[0].scatter(match["u_org"], match["v_org"], s=32, c="#dc322f")
+ax[1].axis("off")
+ax[1].imshow(sim)
+ax[1].scatter(match["u_sim"], match["v_sim"], s=32, c="#dc322f")
+plt.subplots_adjust(left=0, right=1, bottom=0, top=1, wspace=0.05, hspace=0.1)
+# plt.show()
+plt.savefig("data/matched.png")
+
 gcps = set_gcp(match, df)
 gcps.to_csv("data/gcp.csv")
 

### 2022-07-19 scripts/utils/georectify_silhouette.py

@@ -66,6 +66,7 @@ import json
 with open('data/hand_picked_gcp/silhouette/params_optim.json', 'w') as f:
     json.dump(params_optim, f, indent=4)
 
+
 # Reverse projection
 import json
 with open('data/hand_picked_gcp/silhouette/params_optim.json', 'r') as f:
@@ -80,14 +81,3 @@ georectified = georectified[georectified["R"] > 0]
 georectified = georectified[georectified["G"] > 0]
 georectified = georectified[georectified["B"] > 0]
 georectified.to_csv("data/hand_picked_gcp/silhouette/georectified.csv", index=False)
-
-targets = ["results/rnn.npy", "results/svm.png"]
-
-for target in targets:
-    t = np.load(target)
-    t = t[:, :, np.newaxis]
-    georectified = reverse_proj(t, vert, ind, params_optim, chnames=["vegetation"])
-    georectified["vegetation"] = georectified["vegetation"].astype(int)
-    georectified = georectified[georectified["vegetation"]!=0]
-    out = target.replace("npy", "csv")
-    georectified.to_csv(out, index=False)

### 2022-07-19 scripts/utils/georectify_wo_dist.py

@@ -75,14 +75,3 @@ georectified = georectified[georectified["R"] > 0]
 georectified = georectified[georectified["G"] > 0]
 georectified = georectified[georectified["B"] > 0]
 georectified.to_csv("data/hand_picked_gcp/wo_distortion/georectified.csv", index=False)
-
-targets = ["results/rnn.npy", "results/svm.png"]
-
-for target in targets:
-    t = np.load(target)
-    t = t[:, :, np.newaxis]
-    georectified = reverse_proj(t, vert, ind, params_optim, chnames=["vegetation"])
-    georectified["vegetation"] = georectified["vegetation"].astype(int)
-    georectified = georectified[georectified["vegetation"]!=0]
-    out = target.replace("npy", "csv")
-    georectified.to_csv(out, index=False)

### 2022-07-26 paper/paper.Rmd
Result finished

@@
 library(magrittr)
-library(gtsummary)
 library(kableExtra)
-library(maps)
-library(mapdata)
-translate_classes <- function(names) {
-  res = c()
-  for (i in 1:length(names)) {
-    res[i] <- 
-      switch (names[i],
-              "コケモモ-ハイマツ群集" = "Dwarf Pine",
-              "ササ群落" = "Dwarf Bamboo",
-              "その他植生" = "Other vegetation",
-              "裸地等" = "Non Vegetation",
-              "空" = "Sky",
-              "macro avg" = "Macro Average",
-              "weighted avg" = "Weighted Average"
-      )
-  }
-  return(res)
-}
-
-vegetation_levels = c(
-  "Macro Average",
-  "Weighted Average",
-  "Dwarf Pine",
-  "Dwarf Bamboo",
-  "Other vegetation",
-  "Non Vegetation",
-  "Sky"
-)
+library(tidyverse)
+library(magrittr)
+library(fs)
+library(lubridate)
 ```
@@
 Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's "findHomography" function.
-Applying the estimated homography matrix, we could align the images accurately (0.654 pixels in root mean square error of the matching points).
+Applying the estimated homography matrix, we could align the images accurately (0.654 pixels in root mean square error (rmse) of the matching points).
 Finally, we prepared an input mask to define image regions that should be ignored in the following procedure, such as the sky and the regions too close to the camera.
@@
 Georectification of ground-based images has been a difficult task, and this causes the underuse of potentially rich information in ground-based imagery.
-In plain words, georectification means aligning images into Digital Surface Models (DSMs) so that every pixel of an image gets a geographical coordinate.
-We can consider a camera as a function that transforms 3D geographical coordinates (e.g., X, Y and height in a Universal Transverse Mercator coordinate system (UTM)) into 2D image coordinates (locations of each pixel in the picture).
-Estimating the parameters of this function (such as the camera location, pose, and the field of view), we can map an image onto a DSM.
+In plain words, georectification means aligning images onto Digital Surface Models (DSMs) so that every pixel of a image gets a geographical coordinate.
+You can do this by modeling the camera.
+A camera is considered as a function that transforms 3D geographical coordinates (e.g., X, Y and height in a Universal Transverse Mercator coordinate system (UTM)) into 2D image coordinates (locations of each pixel in the image).
+Estimating the parameters of this function (such as the camera location, pose, and the FoV), you can simulate how each point of the DSM appears in the image.
 Usually, georectification has three steps:
@@
 2.  Estimating the camera parameters such as camera poses and field of view using GCPs.\
-3.  Mapping the image onto the DSM using the camera parameters.
+3.  Projecting the DSM into the image using the camera parameters.
 
@@
 
-As we mentioned before, we considered a camera as a function that transforms geographical coordinates of the target mountain to the image coordinates in the acquired photograph.
+As we mentioned before, we considered a camera as a function that transforms geographical coordinates of the target mountain to the image coordinates in the acquired image.
 We implemented this procedure using the OpenGL framework to accelerate it with graphical processing units (GPUs).
@@
 The view matrix represents the position and the direction (pan, tilt, roll) of the camera.
-Note that the geographic coordinate system must be cartesian (such as the UTM).
+Note that the geographic coordinate system must be cartesian (such as the UTMs).
 
@@
 Second, we distorted the camera coordinates to simulate the lens distortion.
-We modeled the lens distortion (\ref{dist_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation (<https://docs.opencv.org/4.x/d9/d0c/group__calib3d.html>), where $X_{norm}$ and $Z_{norm}$ are the $Y$-normalized coordinates of the camera coordinates.
+We modeled the lens distortion (\ref{dist_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation (<https://docs.opencv.org/4.x/d9/d0c/group__calib3d.html>), where $X_{norm}$ and $Z_{norm}$ are the $Y$-normalized view coordinates.
 This model distorts points' locations according to the distance from the center of the image when projected to the image surface.
@@
 
-Now you can project GCPs' geographical coordinates into image coordinates using lens distortion parameters and other camera parameters (the camera location, pose, and the field of view).
-We optimized these parameters (except camera location) by minimizing the square projection error of the GCPs using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}, \ref{fig:optim}).
+Applying these procedures to the GCPs' geographical coordinates, we can calculate the reprojected image coordinates with a set of camera parameters (the camera location, pose, FoV, and the lens distortions).
+Then, we can major the distance from the actual image coordinates of GCPs ($U, V$ of \ref{fig:optim}) to the reprojected image coordinates ($U', V'$ of \ref{fig:optim}).
+We optimized the camera parameters (except camera location) by minimizing this distance using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}, \ref{fig:optim}).
 We could not estimate the camera location because it makes the problem too complicated (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).
@@
 
-## Local-feature-based matching of images and DSMs
+## Image-matching-based aqcuisition of GCPs
 
 To get matching points between images and DSMs on a broader area, we additionally used an orthorectified airborne image.
-Combining an airborne image, a DSM, and a set of initial camera parameters, we rendered simulated landscape images \ref{fig:matched} applying the camera model.
-Then we got matching points (GCPs) by applying AKAZE local feature matcher to a target image and this simulated image \ref{fig:matched}.
-GCPs have geographical coordinates (from the DSM) and image coordinates (from the image).
+Applying the camera model to an airborne image, a DSM, and a set of initial camera parameters, we rendered a simulated landscape image \ref{fig:matched}.
+Then we got matching points of an original image and the simulated image using AKAZE local feature matcher  \ref{fig:matched}.
+Since these matching points have both geographical coordinates (from the DSM) and image coordinates (from the original image), we used these points as GCPs.
 Our procedure requires the camera's exact location and initial camera parameters to render the simulated image.
@@
 
-## Georectification
-(ref:georec) Georectification procedure. We applied the optimized camera parameters to the DSM and the vegetation classification result to get a vegetation map.
+## Georectification of the vegetation map
+(ref:georec) Our georectification procedure. We applied the optimized camera parameters to the DSM and the vegetation classification result to get a vegetation map.
 
@@
 
-Finally, we applied the optimized camera parameters to the DSM and the vegetation classification result \ref{fig:georec}.
+Finally, we georectified the vegetation classification result using the optimized camera parameters \ref{fig:georec}.
+At this point, we got point data of vegetation (as shown in the table on the right of \ref{fig:georec}) that every row represents a pixel of the original image.
+To measure the area of each vegetation class, we converted the point data to a raster data.
+We rasterized the point data in 1 m resolution, then interpolated holes up to 2 m since the maximum pixel foot print was about 2 m on the ridge of the mountain.
+We implemented these procedure using R language \cite{RCore}, `stars` package \cite{Rstars} and `terra` \cite{Rterra} package.
+See <https://github.com/0kam/xxx/xxx> for the source code.
 
@@
 Each fold was stratified with the vegetation categories.
-We used three standard metrics in machine learning evaluation: precision, recall, and F1-score (\ref{metrics}), where $TP, FP, FN$ is true positives, false positives, and false negatives, respectively.
+We used F1-score, a standard metrics in machine learning evaluation (\ref{metrics}), where $TP, FP, FN$ is true positives, false positives, and false negatives, respectively.
 
@@
 ```
-The vegetation classifier achieved a high recall and precision in all five categories \ref{tab:vegetation_cv}.
-Recall and precision were lowest in dwarf bamboo with the smallest training data.
-Even in dwarf bamboo, false positives occurred at low frequency (about 5%), and only a tiny amount of true positives were missed by the pipeline (about 4%).
-Since the weighted average of each metric was higher (more than 0.99), balancing the training dataset with vegetation categories may improve these results.
 
-\ref{fig:vegetation} shows the products of vegetation classification. We can observe the distribution of dwarf pine and dwarf bamboo at the plant-community scale.
+(ref:vegeacc) F1-scores of vegetation classification.
+F1-score was calculated for each vegetation class.
+Each box shows the results of 5-fold cross validation.
+We classified vegetation using single image (shown as the shooting date) with SVM classifiers, and all images with SVM (shown as "Multidays") and RNN (shown as "Multidays RNN") classifiers.
+
+```{r, vegeacc, echo=FALSE, message=FALSE, fig.cap="(ref:vegeacc)", out.width="100%", auto_pdf = TRUE}
+knitr::include_graphics("../results/cv.png")
+```
 
 (ref:vegetation) Vegetation classification results of the RNN model. The masked area, i.e., the sky and the regions too close to the camera, is shown in black.
+
 ```{r, vegetation, echo=FALSE, message=FALSE, fig.cap="(ref:vegetation)", out.width="100%", auto_pdf = TRUE}
-knitr::include_graphics("paper_files/figures/Slide2.jpg")
+knitr::include_graphics("paper_files/figures/vege.png")
 ```
 
+\ref{fig:vegeacc} shows the results of the 5-fold cross validation.
+Focusing on the single image classification (shown as the shooting date), the best date for classification was different among classes.
+For example, 26th Sep was the best for identifying rowans, but 10th Oct was for dwarf pines and dwarf bamboos.
+Note that the autumn colorization of rowan leaves was at the best on 26th Sep, and the most vegetation except dwarf bamboo and dwarf pine were blasted at 10th Oct.
+No single image can classify birch and montane alder accurately.
+In contrast, using all images (shown as "Multidays", "Multidays RNN", representing the SVM and RNN classifiers respectively) resulted high F1 score in every classes.
+Also, the RNN classifier outperforms the SVM classifier (0.937 and 0.918 in macro average F1 score).
+\ref{fig:vegetation} shows the products of the RNN classifier.
+We can observe the distribution of dwarf pine and dwarf bamboo at the plant-community scale.
+
 ## Georectification accuracy
- We tested the accuracy of our georectification method and compared the effect of its features, i.e., using image matching in the image-to-DSM alignment, and modeling the lens distortion.
+We tested the accuracy of our georectification method and evaluated the effect of its two features: using image matching to acquire GCPs, and modeling the lens distortion.
+We manually searched 83 matching points between the simulated photograph and the original photograph and treated them as the test GCPs: GCPs that are not used in the georectification process.
+We additionally prepared two comparison methods to test the performance of our proposed method.
+The first one is the silhouette based matching method (hereinafter called silhouette) used in previous studies (\cite{Portenier2020Cryosphere}).
+The second one is the proposed method without the lens distortion model (hereinafter called no distortion).
+We evaluated the projection error of the test GCPs using these three methods.
+The proposed method achieves accurate projection (3.45 m as the root mean square error) while the other two did not (16.1 m with silhouette, 23.6 m with no distortion).
+Note that we estimated the lens distortion parameters in the silhouette method.
+\ref{fig:geoacc} shows the relationship between the projection error of the proposed method and the test GCPs' distance from the shooting point.
+The projection error was especially large in the GCPs near to the shooting point.
+
+(ref:geoacc) Vegetation classification results of the RNN model. The masked area, i.e., the sky and the regions too close to the camera, is shown in black.
+
+```{r, geoacc, echo=FALSE, message=FALSE, fig.cap="(ref:geoacc)", out.width="100%", auto_pdf = TRUE}
+knitr::include_graphics("../results/georec_acc.png")
+```
 
@@
 
-## Detection and localization of vegetation changes
-
 # Discussion
 
-We suggested a fully automated procedure to transform time-lapse imagery into georeferenced vegetation maps at a meager cost.
+We suggested a fully automated procedure to transform time-lapse imagery into a georeferenced vegetation map at a meager cost.
 This task is challenging because of 1.
 the difficulty of classifying vegetation with ordinal digital camera imagery and 2.
-the difficulty of georectification.
+the difficulty of georectification of such ground-based imagery.
 We solved these issues by 1.
@@
 developing a novel method for accurate image georectification.
-Our vegetation classification performance (with an accuracy of 0.87) and georectification methods (with an RMSE of $rmse$ m) are practical.
+The proposed methods reached a practical performance (0.937 in a mean F1 Score of vegetation classification, 3.4 m in a mean projection error of georectification).
 
@@
 We made up for this lack of information by using the rich temporal information that time-lapse cameras can obtain.
-Many plant species have characteristic phenologies, such as flowering and autumn foliages.
-Observing this requires long-term (such as year-round) monitoring with a high frequency, and digital time-lapse cameras are suitable.
-This study only focused on the two species (dwarf bamboo and stone pine) that are easy to classify, even with a single image.
-However, like the previous studies (\cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}), we expect our method to classify more vegetation (e.g., dwarf deciduous trees and alpine herbaceous plants) using the temporal information of leaf colors.
-We also used hourly images for each day.
-Fig.
-x shows that this additional information made our model robust against transient noises, such as shadows.
-Since alpine ecosystems have rough topologies, shadows are a considerable problem.
-Time-lapse cameras are also beneficial for this reason.
+Many plant species have characteristic phenologies, such as autumn foliages, and the suitable season to observe them are different among species.
+The result (\ref{fig:vegeacc}) shows that each vegetation class has its suitable timing to identify it in photographs.
+Classifying multiple vegetation classes hence requires long-term (such as several months long) and frequent (such as daily) monitoring, and digital time-lapse cameras are suitable.
 

### 2022-07-26 paper/paper.tex
Result finished

@@
 \item
-  Mapping the image onto the DSM using the camera parameters.
+  Projecting the DSM into the image using the camera parameters.
 \end{enumerate}
@@
 Second, we distorted the camera coordinates to simulate the lens distortion.
-We modeled the lens distortion (\ref{dist_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation (\url{https://docs.opencv.org/4.x/d9/d0c/group__calib3d.html}), where \(X_{norm}\) and \(Z_{norm}\) are the \(Y\)-normalized coordinates of the camera coordinates.
+We modeled the lens distortion (\ref{dist_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation (\url{https://docs.opencv.org/4.x/d9/d0c/group__calib3d.html}), where \(X_{norm}\) and \(Z_{norm}\) are the \(Y\)-normalized view coordinates.
 This model distorts points' locations according to the distance from the center of the image when projected to the image surface.
@@
 
-Next, we transformed the distorted camera coordinates to the image coordinates by perspective projection.
+Next, we transformed the distorted view coordinates to the image coordinates by perspective projection.
 During the perspective projection, a closer object is drawn larger.
@@
 
-Now you can project GCPs' geographical coordinates into image coordinates using lens distortion parameters and other camera parameters (the camera location, pose, and the field of view).
-We optimized these (except camera location) by minimizing the square projection error of the GCPs using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}, \ref{fig:optim}).
+Applying these procedures to the GCPs' geographical coordinates, we can calculate the reprojected image coordinates with a set of camera parameters (the camera location, pose, FoV, and the lens distortions).
+Then, we can major the distance from the actual image coordinates of GCPs (\(U, V\) of \ref{fig:optim}) to the reprojected image coordinates (\(U', V'\) of \ref{fig:optim}).
+We optimized the camera parameters (except camera location) by minimizing this distance using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}, \ref{fig:optim}).
 We could not estimate the camera location because it makes the problem too complicated (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).
@@
 
-\hypertarget{local-feature-based-matching-of-images-and-dsms}{%
-\subsection{Local-feature-based matching of images and DSMs}\label{local-feature-based-matching-of-images-and-dsms}}
+\hypertarget{image-matching-based-aqcuisition-of-gcps}{%
+\subsection{Image-matching-based aqcuisition of GCPs}\label{image-matching-based-aqcuisition-of-gcps}}
 
 To get matching points between images and DSMs on a broader area, we additionally used an orthorectified airborne image.
-Combining an airborne image, a DSM, and a set of initial camera parameters, we rendered simulated landscape images \ref{fig:matched} applying the camera model.
-Then we got matching points (GCPs) by applying AKAZE local feature matcher to a target image and this simulated image \ref{fig:matched}.
-GCPs have geographical coordinates (from the DSM) and image coordinates (from the image).
+Applying the camera model to an airborne image, a DSM, and a set of initial camera parameters, we rendered a simulated landscape image \ref{fig:matched}.
+Then we got matching points of an original image and the simulated image using AKAZE local feature matcher \ref{fig:matched}.
+Since these matching points have both geographical coordinates (from the DSM) and image coordinates (from the original image), we used these points as GCPs.
 Our procedure requires the camera's exact location and initial camera parameters to render the simulated image.
@@
 
-\hypertarget{georectification}{%
-\subsection{Georectification}\label{georectification}}
+\hypertarget{georectification-of-the-vegetation-map}{%
+\subsection{Georectification of the vegetation map}\label{georectification-of-the-vegetation-map}}
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figures/Slide6} \caption{Georectification procedure.
+\includegraphics[width=1\linewidth]{paper_files/figures/Slide6} \caption{Our georectification procedure.
 We applied the optimized camera parameters to the DSM and the vegetation classification result to get a vegetation map.}\label{fig:georec}
@@
 
-Finally, we applied the optimized camera parameters to the DSM and the vegetation classification result \ref{fig:georec}.
+Finally, we georectified the vegetation classification result using the optimized camera parameters \ref{fig:georec}.
+At this point, we got point data of vegetation (as shown in the table on the right of \ref{fig:georec}) that every row represents a pixel of the original image.
+To measure the area of each vegetation class, we converted the point data to a raster data.
+We rasterized the point data in 1 m resolution, then interpolated holes up to 2 m since the maximum pixel foot print was about 2 m on the ridge of the mountain.
+We implemented these procedure using R language \cite{RCore}, \texttt{stars} package \cite{Rstars} and \texttt{terra} \cite{Rterra} package.
+See \url{https://github.com/0kam/xxx/xxx} for the source code.
 
@@
 Each fold was stratified with the vegetation categories.
-We used three standard metrics in machine learning evaluation: precision, recall, and F1-score (\ref{metrics}), where \(TP, FP, FN\) is true positives, false positives, and false negatives, respectively.
+We used F1-score, a standard metrics in machine learning evaluation (\ref{metrics}), where \(TP, FP, FN\) is true positives, false positives, and false negatives, respectively.
 
@@
 
-The vegetation classifier achieved a high recall and precision in all five categories \ref{tab:vegetation_cv}.
-Recall and precision were lowest in dwarf bamboo with the smallest training data.
-Even in dwarf bamboo, false positives occurred at low frequency (about 5\%), and only a tiny amount of true positives were missed by the pipeline (about 4\%).
-Since the weighted average of each metric was higher (more than 0.99), balancing the training dataset with vegetation categories may improve these results.
-
-\ref{fig:vegetation} shows the products of vegetation classification. We can observe the distribution of dwarf pine and dwarf bamboo at the plant-community scale.
+\begin{figure}
+\includegraphics[width=1\linewidth]{../results/cv} \caption{F1-scores of vegetation classification.
+F1-score was calculated for each vegetation class.
+Each box shows the results of 5-fold cross validation.
+We classified vegetation using single image (shown as the shooting date) with SVM classifiers, and all images with SVM (shown as ``Multidays'') and RNN (shown as ``Multidays RNN'') classifiers.}\label{fig:vegeacc}
+\end{figure}
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figures/Slide2} \caption{Vegetation classification results of the RNN model.
+\includegraphics[width=1\linewidth]{paper_files/figures/vege} \caption{Vegetation classification results of the RNN model.
 The masked area, i.e., the sky and the regions too close to the camera, is shown in black.}\label{fig:vegetation}
 \end{figure}
+
+\ref{fig:vegeacc} shows the results of the 5-fold cross validation.
+Focusing on the single image classification (shown as the shooting date), the best date for classification was different among classes.
+For example, 26th Sep was the best for identifying rowans, but 10th Oct was for dwarf pines and dwarf bamboos.
+Note that the autumn colorization of rowan leaves was at the best on 26th Sep, and the most vegetation except dwarf bamboo and dwarf pine were blasted at 10th Oct.~No single image can classify birch and montane alder accurately.
+In contrast, using all images (shown as ``Multidays'', ``Multidays RNN'', representing the SVM and RNN classifiers respectively) resulted high F1 score in every classes.
+Also, the RNN classifier outperforms the SVM classifier (0.937 and 0.918 in mean macro average F1 score).
+\ref{fig:vegetation} shows the products of the RNN classifier.
+We can observe the distribution of dwarf pine and dwarf bamboo at the plant-community scale.
 
@@
 
-We tested the accuracy of our georectification method and compared the effect of its features, i.e., using image matching in the image-to-DSM alignment, and modeling the lens distortion.
+We tested the accuracy of our georectification method and evaluated the effect of its two features: using image matching to acquire GCPs, and modeling the lens distortion.
+We manually searched 83 matching points between the simulated photograph and the original photograph and treated them as the test GCPs: GCPs that are not used in the georectification process.
+We additionally prepared two comparison methods to test the performance of our proposed method.
+The first one is the silhouette based matching method (hereinafter called silhouette) used in previous studies (\cite{Portenier2020Cryosphere}).
+The second one is the proposed method without the lens distortion model (hereinafter called no distortion).
+We evaluated the projection error of the test GCPs using these three methods.
+The proposed method achieves accurate projection (3.45 m as the root mean square error) while the other two did not (16.1 m with silhouette, 23.6 m with no distortion).
+Note that we estimated the lens distortion parameters in the silhouette method.
+\ref{fig:geoacc} shows the relationship between the projection error of the proposed method and the test GCPs' distance from the shooting point.
+The projection error was especially large in the GCPs near to the shooting point.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{../results/georec_acc} \caption{Vegetation classification results of the RNN model.
+The masked area, i.e., the sky and the regions too close to the camera, is shown in black.}\label{fig:geoacc}
+\end{figure}
 
@@
 \subsection{Vegetation maps}\label{vegetation-maps}}
-
-\hypertarget{detection-and-localization-of-vegetation-changes}{%
-\subsection{Detection and localization of vegetation changes}\label{detection-and-localization-of-vegetation-changes}}
 

### 2022-07-26 scripts/draw_product.R

@@ -1,0 +1,76 @@
+library(stars)
+library(tidyverse)
+library(ggspatial)
+
+setwd("~/VegetationMapPaper/")
+
+cmap = c(
+  "#2aa198", # Dwarf pine
+  "#859900", # Dwarf bamboo
+  "#dc322f", # Rowans
+  "#b58900", # Birch
+  "#6c71c4", # Montane Alder
+  "#eee8d5", # Other vegetation
+  "#c0c0c0" # No vegetation
+)
+
+vegetation_levels <- c(
+  "Dwarf Pine",
+  "Dwarf Bamboo",
+  "Rowans",
+  "Birch",
+  "Montane Alder",
+  "Other Vegetation",
+  "No Vegetation"
+)
+
+
+ras <- read_stars("results/rnn.tiff") %>%
+  rename(vegetation = rnn.tiff) %>%
+  mutate(vegetation = as.integer(vegetation)) %>%
+  mutate(
+    vegetation = case_when(
+      vegetation == 1 ~ "Dwarf Bamboo",
+      vegetation == 2 ~ "Other Vegetation",
+      vegetation == 3 ~ "No Vegetation",
+      vegetation == 4 ~ "Rowans",
+      vegetation == 5 ~ "Birch",
+      vegetation == 6 ~ "Montane Alder",
+      vegetation == 7 ~ "Dwarf Pine"
+    )
+  ) %>%
+  mutate(vegetation = factor(vegetation, levels = vegetation_levels))
+
+dem <- read_stars("data/mrd_dem_1m.tiff") %>%
+  st_crop(ras) %>%
+  rename(Elevation = mrd_dem_1m.tiff)
+
+write_stars(dem, "data/dem_small.tiff")
+dem <- read_stars("data/dem_small.tiff")
+
+cont <- st_contour(dem, contour_lines = T)
+
+p1 <- ggplot() +
+  geom_sf(data = cont, size = 0.1) +
+  geom_stars(
+    mapping = aes(x = x, y = y, fill = vegetation), 
+    data = ras
+  ) +
+  scale_fill_manual(values = cmap, na.value = "transparent") +
+  labs(x = "Longitude", y = "Latitude", fill = "Vegetation") +
+  theme_minimal() +
+  theme(
+    axis.text = element_text(size = 18),
+    text = element_text(size = 20),
+    plot.background = element_rect(fill = "white")
+  )
+
+ggsave("results/vegemap.png", p1, width = 10, height = 10)
+
[…]

### 2022-07-26 scripts/georec_acc2.R

@@ -1,0 +1,122 @@
+library(tidyverse)
+library(jsonlite)
+
+setwd("~/VegetationMapPaper/")
+
+as_df <- function(pt) {
+  u <- as.integer(pt$points[[1]][[1]])
+  v <- as.integer(pt$points[[1]][[2]])
+  label <- pt$label %>% as.integer()
+  return(tibble(u = u, v = v, label=label))
+}
+
+projection_error <- function(org_json, sim_json, georec_csv) {
+  org <- read_json(org_json)
+  sim <- read_json(sim_json)
+  org <- org$shapes %>%
+    map_dfr(as_df) %>% 
+    arrange(label)
+  sim <- sim$shapes %>%
+    map_dfr(as_df) %>%
+    arrange(label)
+  all(sim$label == org$label)
+  gr <- read_csv(georec_csv) %>%
+    select(-c(B, G, R))
+  org2 <- org %>%
+    inner_join(gr, by = c("u", "v")) %>%
+    select(-c(u, v)) %>%
+    rename(
+      x_org = x,
+      y_org = y,
+      z_org = z
+    )
+  sim2 <- sim %>%
+    inner_join(gr, by = c("u", "v")) %>%
+    select(-c(u, v)) %>%
+    rename(
+      x_sim = x,
+      y_sim = y,
+      z_sim = z
+    )
+  df <- inner_join(org2, sim2, by = "label") %>%
+    mutate(error = sqrt((x_org - x_sim)^2 + (y_org - y_sim)^2 + (z_org - z_sim)^2)) %>%
+    arrange(desc(error))
+  return(df)
+}
+
+p <- read_json("data/hand_picked_gcp/with_distortion/params_optim.json")
+
+w_dist <- projection_error(
+  "data/hand_picked_gcp/with_distortion/handpicked_original.json",
+  "data/hand_picked_gcp/with_distortion/handpicked_simulated.json",
+  "data/hand_picked_gcp/with_distortion/georectified.csv"
+) %>%
+  mutate(distance = sqrt((p$x - x_org)^2 + (p$y - y_org) + (p$z - z_org))) %>%
+  mutate(method = "Proposed Method")
+
+wo_dist <- projection_error(
+  "data/hand_picked_gcp/wo_distortion/handpicked_original.json",
+  "data/hand_picked_gcp/wo_distortion/handpicked_simulated.json",
+  "data/hand_picked_gcp/wo_distortion/georectified.csv"
+) %>% 
[…]

### 2022-07-26 scripts/models/model_comparison.R

@@ -14,7 +14,7 @@ translate_classes <- function(names) {
               "ハイマツ" = "Dwarf Pine",
               "ササ" = "Dwarf Bamboo",
               "ナナカマド" = "Rowans",
-              "ダケカンバ" = "Golden Birch",
+              "ダケカンバ" = "Birch",
               "ミヤマハンノキ" = "Montane Alder",
               "その他植生" = "Other vegetation",
               "無植生" = "Non Vegetation",
@@ -31,7 +31,7 @@ vegetation_levels <- c(
   "Dwarf Pine",
   "Dwarf Bamboo",
   "Rowans",
-  "Golden Birch",
+  "Birch",
   "Montane Alder",
   "Other vegetation",
   "Non Vegetation"
@@ -53,13 +53,7 @@ summarise_cv <- function(path) {
         pivot_longer(cols = c(mean, sd), names_to = "var") %>%
         pivot_wider(names_from = metrics, values_from = value) %>%
         mutate(path = path) %T>%
-        write_csv(out) #%>%
-        # select(-var) %>%
-        # kable(booktabs = TRUE,
-        #     caption = "Cross validation result \\label{tab:vegetation_cv}") %>%
-        # kable_styling() %>%
-        # collapse_rows(columns = 1) %>%
-        # footnote(general = "Mean (SD) of 5-Fold Cross-Varidation")
+        write_csv(out)
 }
 
 read_cv <- function(path) {
@@ -89,105 +83,29 @@ p1 <- df %>%
     filter(vegetation != "Macro Average") %>%
     filter(vegetation != "Weighted Average") %>%
     mutate(date = as.character(date)) %>%
-    mutate(date = ifelse(is.na(date), str_c("Multidays", kernel_size), date)) %>%
-    mutate(date = ifelse(str_detect(path, "rnn"), "Multidays RNN 1x1", date)) %>%
+    mutate(date = ifelse(is.na(date), "Multidays", date)) %>%
+    mutate(date = ifelse(str_detect(path, "rnn"), "Multidays RNN", date)) %>%
     ggplot(aes(x = date, y = value)) +
     geom_boxplot() +
     ylab("F1 score") +
-    facet_wrap(~ vegetation) +
-    theme_minimal() +
-    theme(
-        axis.text = element_text(size = 18),
-        text = element_text(size = 20),
-        axis.text.x = element_text(angle = 45, hjust = 1),
-        plot.background = element_rect(fill = "white")
-    )
-
[…]

### 2022-09-13 paper/paper.Rmd
added phenology graph

@@
     affiliation: National Institute for Environmental Studies
-    location: 16-2 Onogawa, Tsukuba, Ibaraki 305-8506 JAPAN
+    location: 16-2 Onogawa, Tsukuba, Ibaraki 305-8506 Japan
     email: oguma@nies.go.jp
@@
     affiliation: National Institute for Environmental Studies
-    location: 16-2 Onogawa, Tsukuba, Ibaraki 305-8506 JAPAN
+    location: 16-2 Onogawa, Tsukuba, Ibaraki 305-8506 Japan
     email: ide.reiko@nies.go.jp
 abstract: |
-  Enter the text of your abstract here.
+  Alpine ecosystems are particularly vulnerable to the effect of climate change.
+Monitoring the distribution of alpine vegetation is required to plan practical conservation activities.
+However, conventional field observation and satellite remote sensing have difficulties in the coverage and frequency in alpine areas.
+Researchers have also utilized ground-based time-lapse cameras to observe alpine regions' snowmelt and vegetation phenology.
+Such time-lapse cameras have significant advantages in cost, resolution, and frequency.
+However, no research has used these to monitor the vegetation distribution.
+This study proposes a novel method to draw georeferenced vegetation maps from ground-based imagery of the Japanese alps.
+Our approach has two components: the classification and georectification method.
+The proposed classification method uses pixel time series acquired from autumn images to utilize the patterns of autumn foliage.
+We show that using time-lapse imagery and a Recurrent Neural Network improves the performance of the vegetation classification.
+We also developed a novel method to accurately transform a ground-based image into georeferenced data.
+We propose 1.
+an automated procedure to acquire Ground Control Points (GCPs) and 2.
+a camera model that considers the lens distortion for accurate georectification.
+We show that our approach outperforms the conventional method.
+The proposed method achieved sufficient accuracy to observe the vegetation distribution on a plant-community scale.
+The evaluation reveals an F1 score of 0.937 in the vegetation classification and a root mean square error (RMSE) of 3.4 m in the georectification.
+Our results highlight the potential of cheap time-lapse cameras to monitor the distribution of alpine vegetation.
+The proposed method should significantly contribute to effective conservation planning of the alpine ecosystems.
 keywords:
@@
 For example, the growth of dwarf pine (*Pinus pumila*), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}).
-Effective conservation planning requires early detection and constant monitoring of such vegetation changes.
+Effective conservation planning requires constant monitoring of vegetation distribution to detect such changes.
 Also, since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.
@@
 Previous studies have mainly depended on field observations, yet it is hard to cover broad areas in alpine regions due to the poor accessibility and severe weather.
-Satellite, airborne, and Unmanned Aerial Vehicle (UAV) remote sensing methods seem to be alternatives.
+Satellite, airborne, and Unmanned Aerial Vehicle (UAV) remote sensing methods are alternatives.
 However, satellite imagery of alpine areas is rarely available due to cloud cover, and the spatial resolution is not enough to observe vegetation changes at the plant community scale.
@@
 On the other hand, researchers have also utilized automated digital time-lapse cameras mounted on the ground for monitoring green-leaf phenologies in forests (\cite{Richardson2009EcolAppl}), grasslands (\cite{Browning2017RemSen}), and alpine meadows (\cite{IdeOguma2013EcolInfom}).
-Unlike satellite imagery, such cameras provide images free of clouds and atmospheric effects.
+Unlike satellite imagery, ground-based cameras provide images free of clouds and atmospheric effects.
 Also, they can obtain high-resolution (i.e., sub-meter scale) and frequent (i.e., daily or hourly) images at a meager cost.
@@
 However, few studies have utilized such images in monitoring vegetation distributions.
-This lack of studies seems to be because applying such repeat photography in monitoring vegetation distribution has two technical challenges.
+This lack of studies seems to be because applying such time-lapse imagery in monitoring vegetation distribution has two technical challenges.
 
@@
 
-We used repeat photography data owned by National Institute for Environmental Studies, Japan (NIES).
+We used time-lapse images of a Japanese alpine region owned by the National Institute for Environmental Studies, Japan (NIES).
 All the images are publically available on NIES' webpage (https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2).
 In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt.
-Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps \ref{fig:map}.
+Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps (Fig.
+\ref{fig:map}).
 The camera takes a photograph per hour, from 6 a.m.
@@
 The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines.
-From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen(e.g., *Pinus pumila*) and deciduous (*Sorbus* sp.,  *Betula ermanii*) dwarf trees, dwarf bamboos (e.g., *Sasa kurilensis*), and alpine shrubs and herbaceous plants (e.g., *Geum pentapetalum*, *Nephrophyllidium crista-galli*).
+From April to November, the camera observed the snowmelt and seasonal phenology of evergreen(e.g., *Pinus pumila*) and deciduous (*Sorbus* sp.,  *Betula ermanii*) dwarf trees, dwarf bamboos (e.g., *Sasa kurilensis*), and alpine shrubs and herbaceous plants (e.g., *Geum pentapetalum*, *Nephrophyllidium crista-galli*).
 This study used images from the summer and fall of 2015 to classify vegetation with the temporal patterns of the leaf color.
@@
 
-First, we selected images that are suitable for vegetation classification.
+First, we selected images.
 We choose seven days with good weather from late summer to late fall of 2015 (8/25, 9/5, 9/12, 9/20, 9/26, 10/3, 10/10).
-We used the images of this season because we can separate vegetation from the patterns of autumn foliage coloration.
+The temporal patterns of autumn foliage coloration are largely different among species (see Fig.
+\ref{fig:pixtimeseries}).
+Our method utilizes this information in the vegetation classification.
+Time-lapse cameras are particularly good at observing such temporal changes of the vegetation, while UAVs and airborne imagery cost much.
 
@@
 
-Since images are slightly misaligned, we aligned them before processing.
-We implemented the program with the Python3 programming language and OpenCV4 (https://opencv.org/) image processing library.
-First, we set one image of 2015 as the alignment target.
-Next, we automatically found matching keypoints between the target and other images using the AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
+Although the camera is fixed on the mountain lodge, the images are slightly misalighned do to the wind.
+To handle this issue, we aligned the images before processing using Python3 programming language and OpenCV4 (https://opencv.org/) image processing library.
+First, one image of 2015 were set as the alignment target.
+Next, we automatically matched key points between the target and other images using the AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
 Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's "findHomography" function.
-Applying the estimated homography matrix, we could align the images accurately (0.654 pixels in root mean square error (rmse) of the matching points).
-Finally, we prepared an input mask to define image regions that should be ignored in the following procedure, such as the sky and the regions too close to the camera.
+Applying the estimated homography matrix, we could align the images accurately (0.654 pixels in root mean square error (RMSE) of the matching points).
+Finally, an input mask were applied to define image regions that should be ignored in the following procedure, such as the sky and the regions too close to the camera.
+This process ensures that a set of pixel time-series reflects a phenological information of a same location, which is essential in the vegetation classification process.
 
@@
 
-Because we successfully aligned the images, we can stack the images and extract a time series of pixel values (Red, Green, and Blue, \ref{fig:pixtimeseries}) for each pixel.
+Because the images were aligned succesfuly, we can stack the images and extract a time series of pixel values (Red, Green, and Blue, Fig.
+\ref{fig:pixtimeseries}) for each pixel.
 Such pixel time series reflects the temporal patterns of leaf colors.
-Because deciduous plants have great differences in autumn phenology among species, researchers have used that information for vegetation classification with satellite imagery (e.g., \cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}).
-However, no research has applied this technique to ground-based repeat photography imagery.
-We implemented Support Vector Machine (SVM) and Recurrent Neural Network (RNN) based vegetation classification methods in this study.
-We tested the effects of using pixel time series on the classification performance.
+Because deciduous plants have great differences in autumn leaf phenology among species, researchers have used that information for vegetation classification with satellite imagery (\cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}).
+However, no research has applied this technique to ground-based time-lapse imagery.
+We implemented Support Vector Machine (SVM) and Recurrent Neural Network (RNN) based vegetation classifiers, and tested the effects of using pixel time series of the ground-based imagery on the classification performance.
 
-(ref:pixtimeseries) Pixel time series acquired from the time lapse camera.
+(ref:pixtimeseries) Pixel time series acquired from the time-lapse camera.
 You can obtain a time series of pixel values (i.e., Red, Green, and Blue) for each pixel on the photographs.
@@
 Researchers have also utilized RNN for remote sensing tasks, such as land cover classification, with multi-temporal satellite imagery (\cite{Ienco2017RemSenLSTM}, \cite{Sharma2018NN}).
+\cite{Ienco2017RemSenLSTM} reported that an RNN classifier outperforms an SVM classifier.
 Amongst many variants of RNN, we used Long Short Time Memory (LSTM, \cite{Hochreiter1997LSTM}), one of the most well-known RNN architectures.
-We also classified the pixel of every single image separately using SVM classifiers to test whether using multi-temporal imagery increases the classification performance.
+Batch-normalization technique (\cite{IoffeSzegedy2015BatchNorm}) was employed to speed up and stabilize the model training.
+We also classified the pixel of every single image separately using SVM classifiers to test whether using multi-temporal imagery improves the classification performance.
 
@@
 We implemented the classifier with Python3 language, ThunderSVM library (<https://github.com/Xtra-Computing/thundersvm>) for the SVM classifier, and  PyTorch deep neural network library (<https://pytorch.org/>) for the RNN classifier.
-All source codes are publically available via GitHub (<https://github.com/0kam/xxxx>).
+All source codes are publically available via GitHub (<https://github.com/0kam/VegetationMapPaper>).
 
@@
 
-Then, we developed a novel method to convert ground-based landscape imagery into GIS-ready geographical data.
+Then, we developed a novel method to convert ground-based landscape imagery into geographical data.
 This process is called georectification.
 Georectification of ground-based images has been a difficult task, and this causes the underuse of potentially rich information in ground-based imagery.
-In plain words, georectification means aligning images onto Digital Surface Models (DSMs) so that every pixel of a image gets a geographical coordinate.
+In plain words, georectification means aligning images onto Digital Surface Models (DSMs) so that every pixel of an image gets a geographical coordinate.
 You can do this by modeling the camera.
-A camera is considered as a function that transforms 3D geographical coordinates (e.g., X, Y and height in a Universal Transverse Mercator coordinate system (UTM)) into 2D image coordinates (locations of each pixel in the image).
+A camera is considered a function that transforms 3D geographical coordinates (e.g., X, Y, and height in a Universal Transverse Mercator coordinate system (UTM)) into 2D image coordinates (locations of each pixel in the image).
 Estimating the parameters of this function (such as the camera location, pose, and the FoV), you can simulate how each point of the DSM appears in the image.
@@
 1.  Finding Ground Control Points (GCPs) in the image.\
-2.  Estimating the camera parameters such as camera poses and field of view using GCPs.\
+2.  Estimating the camera parameters such as camera poses and FoV using GCPs.\
 3.  Projecting the DSM into the image using the camera parameters.
@@
 Recently, researchers have developed some georectification methods to use ground-based photographs in glaciology (\cite{Messerli2015GeoInst}) and snow cover studies (\cite{Portenier2020Cryosphere}).
-Especially, \cite{Portenier2020Cryosphere} is worth mentioning for its semi-automatic method using mountain silhouettes as GCPs.
+Especially, \cite{Portenier2020Cryosphere} is worth mentioning for its semi-automatic method using mountain silhouettes as GCPs since setting GCPs in alpine region is not easy.
 However, this silhouette-based method has a drawback in the projection accuracy.
-It only uses limited areas (silhouettes) of images in the image-to-DSM alignment, and also it ignores lens distortion.
+It only uses limited areas (silhouettes) of images in the GCP acquisition, and also it ignores lens distortion.
 Because our target site has a complex vegetation distribution and our camera has considerable lens distortion, we needed a more accurate method.
@@
 
-As we mentioned before, we considered a camera as a function that transforms geographical coordinates of the target mountain to the image coordinates in the acquired image.
-We implemented this procedure using the OpenGL framework to accelerate it with graphical processing units (GPUs).
-In OpenGL, we can separate this process into three operations:
+As we mentioned before, we modeled a camera as a function that transforms the geographical coordinates of the target mountain into the image coordinates in the acquired image.
+We implemented this procedure using the OpenGL framework (<https://www.opengl.org/>) to accelerate it with graphical processing units (GPUs).
+In OpenGL, we can divide this process into three operations:
 
 1.
-Transforming the world (geographical) coordinates to the view coordinates (coordinates seen from the camera's point of view) using camera's extrinsic parameters (i.e., the location and angles of the camera).
+Transforming the world (geographical) coordinates to the view coordinates (coordinates seen from the camera's point of view) using the camera's extrinsic parameters (i.e., the location and angles of the camera).
 \
 2. Distorting the view coordinates using the lens distortion parameters. \
-3. Transforming the view coordinates to the screen (image) coordinates using camera's intrinsic parameters (i.e., the FoV and aspect ratio of the camera).
+3. Transforming the view coordinates to the screen (image) coordinates using the camera's intrinsic parameters (i.e., the FoV of the camera).
 
-First, we transformed the absolute geographic coordinates (also known as the world coordinates) to the view coordinates that are relative to the camera's position and direction.
+First, we transformed the absolute geographic coordinates (also known as the world coordinates) into the view coordinates relative to the camera's position and direction.
 We applied a $4 \times 4$ view matrix $M_{view}$ (\ref{view_matrix}) to the geographic coordinates in this step.
-The view matrix represents the position and the direction (pan, tilt, roll) of the camera.
-Note that the geographic coordinate system must be cartesian (such as the UTMs).
+The view matrix represents the camera's position and direction (pan, tilt, roll).
+The geographic coordinate system must be cartesian (such as the UTM coordinate systems).
 
 ```{=tex}
+\begin{equation}
 \label{view_matrix}
-\begin{equation}
   M_{view} = 
@@
 ```{=tex}
+\begin{equation}
 \label{view_tf}
-\begin{equation}
   \begin{bmatrix} 
@@
 ```{=tex}
+\begin{gather}
 \label{dist_model}
-\begin{gather}
+  \begin{gathered}
   X_{norm} = \frac{X_{camera}}{Y_{camera}} \\
@@
   Z_{dist} = Z_{dist\_norm} Y_{camera} \\
+  \end{gathered}
 \end{gather}
@@
 ```{=tex}
+\begin{gather}
 \label{proj_mat}
-\begin{gather}
+  \begin{gathered}
   f_x = \frac{1}{\frac{\tan fov_x}{2}} \\
@@
   \end{bmatrix}
+  \end{gathered}
 \end{gather}
@@
 ```{=tex}
+\begin{equation}
 \label{proj_tf}
-\begin{equation}
   \begin{bmatrix} 
@@
 
-Applying these procedures to the GCPs' geographical coordinates, we can calculate the reprojected image coordinates with a set of camera parameters (the camera location, pose, FoV, and the lens distortions).
-Then, we can major the distance from the actual image coordinates of GCPs ($U, V$ of \ref{fig:optim}) to the reprojected image coordinates ($U', V'$ of \ref{fig:optim}).
-We optimized the camera parameters (except camera location) by minimizing this distance using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}, \ref{fig:optim}).
+Applying these procedures to the GCPs' geographical coordinates, we can calculate the reprojected image coordinates with a set of camera parameters (the camera location, pose, FoV, and lens distortion parameters).
+Then, we can measure the distance from the actual image coordinates of GCPs ($U, V$ of Fig.
+\ref{fig:optim}) to the reprojected image coordinates ($U', V'$ of Fig.
+\ref{fig:optim}).
+We estimated the camera parameters (except camera location) by minimizing this distance using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}, Fig.
+\ref{fig:optim}).
 We could not estimate the camera location because it makes the problem too complicated (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).
 
-(ref:optim) Work flow of the camera parameter optimization. We estimated the camera parameters by minimizing the GCP's reprojection error.
+(ref:optim) Workflow of the camera parameter optimization. We estimated the camera parameters by minimizing the GCP's reprojection error.
 
@@
 
-To get matching points between images and DSMs on a broader area, we additionally used an orthorectified airborne image.
-Applying the camera model to an airborne image, a DSM, and a set of initial camera parameters, we rendered a simulated landscape image \ref{fig:matched}.
-Then we got matching points of an original image and the simulated image using AKAZE local feature matcher  \ref{fig:matched}.
+Usually, GNSS-positioned GCPs (such as GCP markers) are set before photo acquisition to get a georeferenced image, however, setting such markers in alpine areas are often tough due to the harsh topology.
+\cite{Portenier2020Cryosphere} solved this problem by developing a method that uses mountain silhouettes to match images and DEMs.
+Its weak point is that the georectification accuracy is sometimes low in the mountainside, where no GCPs are set.
+We developed an novel method that uses  an orthorectified airborne image to get matching points between images and DSMs in a broader area.
+
+First, an airborne image and a DSM that covers the camera's field of view, and a set of initial camera parameters (roughly estimated camera parameters) were prepared.
+We rendered a simulated landscape image by applying the camera model to these.
+Since the simulated image is consists of georeferenced DEM and airborne image, every pixel has a geographic coordinate.
+Then we searched matching points between the original image and the simulated image using AKAZE local feature matcher  (Fig.
+\ref{fig:matched}).
 Since these matching points have both geographical coordinates (from the DSM) and image coordinates (from the original image), we used these points as GCPs.
+This method enables us to acquire GCPs in much broader area than the previous method.
 Our procedure requires the camera's exact location and initial camera parameters to render the simulated image.
-Note that the orthorectification accuracy of the airborne photograph may affect the georectification accuracy.
+Note that the orthorectification accuracy of the airborne image may affect the georectification accuracy.
 
@@
 The simulated image was rendered with an orthophoto, DSM, and initial camera parameters.
-Red points shows the matching points found by the AKAZE local feature matcher.
+Red points show the matching points found by the AKAZE local feature matcher.
 We used these points as GCPs.
@@
 
-Finally, we georectified the vegetation classification result using the optimized camera parameters \ref{fig:georec}.
-At this point, we got point data of vegetation (as shown in the table on the right of \ref{fig:georec}) that every row represents a pixel of the original image.
-To measure the area of each vegetation class, we converted the point data to a raster data.
-We rasterized the point data in 1 m resolution, then interpolated holes up to 2 m since the maximum pixel foot print was about 2 m on the ridge of the mountain.
+Finally, we georectified the vegetation classification result using the optimized camera parameters (Fig.
+\ref{fig:georec}).
+At this point, we got the point data of vegetation (as shown in the table on the right of Fig.
+\ref{fig:georec}) that every row represents a pixel of the original image.
+To measure the area of each vegetation class, we converted the point data to raster data.
+We rasterized the point data in 1 m resolution, then interpolated holes up to 2 m since the maximum pixel footprint was about 2 m on the ridge of the mountain.
 We implemented these procedure using R language \cite{RCore}, `stars` package \cite{Rstars} and `terra` \cite{Rterra} package.
-See <https://github.com/0kam/xxx/xxx> for the source code.
+See <https://github.com/0kam/VegetationMapPaper/blob/master/scripts/utils/interpolate.R> for the source code.
 
@@
 We implemented the algorithm with Python3 language and published it as an open-source package via GitHub (<https://github.com/0kam/alproj>).
-You can try it with your data.
-We used an airborne photograph taken in the November of 201X with a spatial resolution of 1.0 m.
-Also, we used the 1m resolution Digital Surface Model that were also used in the orthorectification process of the airborne photograph.
+We used an airborne photograph taken in the October of 2014 with a spatial resolution of 1.0 m.
+Also, we used the 1m resolution Digital Surface Model that was also used in the orthorectification process of the airborne photograph.
 
@@
 Each fold was stratified with the vegetation categories.
-We used F1-score, a standard metrics in machine learning evaluation (\ref{metrics}), where $TP, FP, FN$ is true positives, false positives, and false negatives, respectively.
+We used F1-score, a standard metric in machine learning evaluation (\ref{metrics}), where $TP, FP, FN$ is true positives, false positives, and false negatives, respectively.
 
 ```{=tex}
+\begin{align}
 \label{metrics}
-\begin{align}
+  \begin{gathered}
   precision = \frac{TP}{TP + FP} \\
@@
   F_1 = \frac{2 \cdot precision \cdot recall}{precision + recall} \\
+  \end{gathered}
 \end{align}
@@
 F1-score was calculated for each vegetation class.
-Each box shows the results of 5-fold cross validation.
-We classified vegetation using single image (shown as the shooting date) with SVM classifiers, and all images with SVM (shown as "Multidays") and RNN (shown as "Multidays RNN") classifiers.
+Each box shows the results of a 5-fold cross-validation.
+We classified vegetation using a single image (shown as the shooting date) with SVM classifiers and all images with SVM (shown as "Multidays") and RNN (shown as "Multidays RNN") classifiers.
 
@@
 
-(ref:vegetation) Vegetation classification results of the RNN model. The masked area, i.e., the sky and the regions too close to the camera, is shown in black.
+(ref:vegetation) Left: Vegetation classification results of the RNN model.
+The masked area, i.e., the sky and the regions too close to the camera, is shown in black.
+Right: The generated vegetation map.
+The background shows contour lines.
 
@@
 
-\ref{fig:vegeacc} shows the results of the 5-fold cross validation.
+Fig.
+\ref{fig:vegeacc} shows the results of the 5-fold cross-validation.
 Focusing on the single image classification (shown as the shooting date), the best date for classification was different among classes.
 For example, 26th Sep was the best for identifying rowans, but 10th Oct was for dwarf pines and dwarf bamboos.
-Note that the autumn colorization of rowan leaves was at the best on 26th Sep, and the most vegetation except dwarf bamboo and dwarf pine were blasted at 10th Oct.
+Note that the autumn colorization of rowan leaves was at best on 26th Sep, and the most vegetation except dwarf bamboo and dwarf pine were blasted on 10th Oct.
 No single image can classify birch and montane alder accurately.
-In contrast, using all images (shown as "Multidays", "Multidays RNN", representing the SVM and RNN classifiers respectively) resulted high F1 score in every classes.
+In contrast, using all images (shown as "Multidays" and "Multidays RNN" representing the SVM and RNN classifiers, respectively) resulted in a high F1 score in every class.
 Also, the RNN classifier outperforms the SVM classifier (0.937 and 0.918 in macro average F1 score).
-\ref{fig:vegetation} shows the products of the RNN classifier.
-We can observe the distribution of dwarf pine and dwarf bamboo at the plant-community scale.
+Fig.
+\ref{fig:vegetation} (left) shows the products of the RNN classifier.
+We can observe the distribution of each vegetation classes at the plant-community scale.
 
 ## Georectification accuracy
-We tested the accuracy of our georectification method and evaluated the effect of its two features: using image matching to acquire GCPs, and modeling the lens distortion.
-We manually searched 83 matching points between the simulated photograph and the original photograph and treated them as the test GCPs: GCPs that are not used in the georectification process.
-We additionally prepared two comparison methods to test the performance of our proposed method.
-The first one is the silhouette based matching method (hereinafter called silhouette) used in previous studies (\cite{Portenier2020Cryosphere}).
-The second one is the proposed method without the lens distortion model (hereinafter called no distortion).
+We tested our georectification method's accuracy and evaluated its two features' effects: using the simulated image and image matching to acquire GCPs, and modeling the lens distortion.
+We manually searched 83 matching points between the simulated and original images and treated them as the test GCPs: GCPs that are not used in the georectification process.
+We additionally prepared two comparison methods to test the performance of the proposed method.
+The first one is the silhouette-based matching method (after this called silhouette) used in previous studies (\cite{Portenier2020Cryosphere}).
+The second is the proposed method without the lens distortion model (after this called no distortion).
 We evaluated the projection error of the test GCPs using these three methods.
 The proposed method achieves accurate projection (3.45 m as the root mean square error) while the other two did not (16.1 m with silhouette, 23.6 m with no distortion).
-Note that we estimated the lens distortion parameters in the silhouette method.
+We estimated the lens distortion parameters in the silhouette method.
+Fig.
 \ref{fig:geoacc} shows the relationship between the projection error of the proposed method and the test GCPs' distance from the shooting point.
-The projection error was especially large in the GCPs near to the shooting point.
+The projection error was especially large in the GCPs near the shooting point.
+Note that the projection errors were measured ignoring the georectification error of the orthophoto and the DSM.
+Fig.
+\ref{fig:vegetation} (right) shows the produced vegetation map.
+The vegetation map has missing areas because ridges blocked the camera's view.
 
-(ref:geoacc) Vegetation classification results of the RNN model. The masked area, i.e., the sky and the regions too close to the camera, is shown in black.
+(ref:geoacc) The projection error of the proposed method. The projection error was particularly large in the area near the camera.
 
@@
 
-## Vegetation maps
-
 # Discussion
 
-We suggested a fully automated procedure to transform time-lapse imagery into a georeferenced vegetation map at a meager cost.
+We suggested a fully automated procedure to transform time-lapse images of an alpine region into a georeferenced vegetation map at a meager cost.
 This task is challenging because of 1.
@@
 developing a novel method for accurate image georectification.
-The proposed methods reached a practical performance (0.937 in a mean F1 Score of vegetation classification, 3.4 m in a mean projection error of georectification).
+The proposed methods reached a functional performance (0.937 in a mean F1 Score of vegetation classification, 3.4 m in a mean projection error of georectification) to use the vegetation map in monitoring the vegetation distributions on a plant-community scale.
 
@@
 One of the shortcomings of ordinal digital cameras is that they only have three bands (Red, Blue, and Green).
-We made up for this lack of information by using the rich temporal information that time-lapse cameras can obtain.
-Many plant species have characteristic phenologies, such as autumn foliages, and the suitable season to observe them are different among species.
-The result (\ref{fig:vegeacc}) shows that each vegetation class has its suitable timing to identify it in photographs.
-Classifying multiple vegetation classes hence requires long-term (such as several months long) and frequent (such as daily) monitoring, and digital time-lapse cameras are suitable.
+We made up for this lack of information using the rich temporal information that time-lapse cameras can obtain.
+Many plant species have characteristic phenologies, such as autumn foliage, and the suitable season to observe them differs among species.
+The result (Fig.
+\ref{fig:vegeacc}) shows that each vegetation class has its suitable timing to identify it in photographs.
+Classifying multiple vegetation classes requires long-term (such as several months long) and frequent (such as daily) monitoring, and digital time-lapse cameras are suitable.
+In addition, combining multi-temporal images improved the classification accuracy, especially with Birch and Montane Alder (Fig.
+\ref{fig:vegeacc}).
+The best F1 score was low with single image classification (0.750 for Montane Alder, 0.345 for Birch), and using multi-temporal images improves them much (0.951 and 0.781 with the SVM classifier).
+This result shows that identifying these vegetation requires multi-temporal information.
+The inter-community heterogeneity of autumn foliage timing in these species may cause this result.
+As the previous study pointed out (\cite{Ienco2017RemSenLSTM}), the RNN model outperformed the SVM model, particularly in identifying Birch (0.781 with SVM and 0.831 with RNN).
+Our model can still be further improved.
+As \cite{Sharma2018NN} claimed, the patch-based classification method may improve the performance.
+Such patch-based models take a time series of small patches as an input to utilize the spatial information, such as textures, in the classification process.
 
@@
 
+The most significant barrier to using ground-based imagery in ecological monitoring is its difficulty in treating it as geospatial data.
+An automated and accurate georectification method was required to overcome this challenge.
+Without georectification, we cannot quantitatively analyze (e.g., measuring the area, locating the place, and analyzing with topographic data) the acquired information, such as the vegetation distribution.
+We suggested a novel method to georectify such imagery.
+With minimal manual user inputs (i.e., the location of the camera and the initial camera parameters), our method achieved a state-of-the-art accuracy (3.45 m).
+We tested the effectiveness of the two features of our method: the lens distortion model and the image-matching-based method to acquire GCPs automatically.
+The results show that the lens distortion model greatly improved the georectification accuracy.
+Without the lens distortion model, our model resulted in a projection accuracy of 23.6 m.
+However, since the effect of lens distortion on the georectification accuracy is different among cameras and lenses (\cite{Portenier2020Cryosphere}), further testing will be required to ensure the advantage of our lens distortion model.
+Note that the proposed lens distortion model does not support a fisheye lens and omnidirectional camera.
+Another feature of our method is the automatic acquisition of GCPs using simulated images and image matching techniques.
+This method requires a high-resolution orthophoto that covers the camera's field of view.
+This costs a bit; however, the reward is considerable.
+Using simulated images in GCP acquisition also improved the georectification accuracy; the conventional silhouette-based method resulted in an RMSE of 16.1 m.
+This result suggests that acquiring matching points between the image and the DSM in a broader area benefits the camera parameter estimation process.
+However, the proposed method (AKAZE image matcher) could not acquire matching points in the area near the camera, and the projection error was relatively large (Fig.
+\ref{fig:geoacc}).
+While the spatial resolution of the simulated image depends on orthophoto (in this study, 1 m), that of the original image changes depending on the distance from the camera.
+In such near areas, the spatial resolution of the original image is much higher than that of the simulated image, and the image matcher cannot handle the difference.
+Recently, researchers have developed some deep-learning-based image-matching methods (e.g., \cite{Yang2018ImageMatching}, \cite{Wu2013AEImageMatching}) that are more robust to the differences in image sources and viewpoints.
+Applying these methods to the GCP acquiring process may improve the performance of our method, especially in near areas.
+Theoretically, our approach can handle the images of other ecosystems, such as forests.
+However, because the georectification accuracy strongly depends on the accuracy of the DSM, this may be difficult.
+Since alpine plants tend to be very short, readily available Digital Elevation Models (DEMs) can be used as the DSMs.
+In forestry areas, vegetation height is considerable, and the gap between the DEMs and the actual surface (top of the forest) will cause significant errors in the georectification process.
+
 ## Future application and conclusion
+Here, we proposed an automated method to draw a vegetation map from a series of images acquired by a digital time-lapse camera.
+The produced vegetation map has sufficient accuracy for monitoring endemic and vulnerable alpine vegetation.
+One of the benefits of digital time-lapse cameras is their long-term operability.
+Applying the proposed method to the existing long-term time-lapse imagery will enable the researchers to quantitatively understand the vegetation changes and their trends.
+That information will help plan the field observations and conservation activities more effectively.
+Our methods facilitate cost-efficient monitoring of alpine vegetation and understanding of the progressing impacts of climate changes on alpine ecosystems.

### 2022-09-13 paper/paper.tex
added phenology graph

@@
     National Institute for Environmental Studies \\
-  16-2 Onogawa, Tsukuba, Ibaraki 305-8506 JAPAN \\
+  16-2 Onogawa, Tsukuba, Ibaraki 305-8506 Japan \\
   \texttt{\href{mailto:oguma@nies.go.jp}{\nolinkurl{oguma@nies.go.jp}}} \\
@@
     National Institute for Environmental Studies \\
-  16-2 Onogawa, Tsukuba, Ibaraki 305-8506 JAPAN \\
+  16-2 Onogawa, Tsukuba, Ibaraki 305-8506 Japan \\
   \texttt{\href{mailto:ide.reiko@nies.go.jp}{\nolinkurl{ide.reiko@nies.go.jp}}} \\
@@
 \begin{abstract}
-Enter the text of your abstract here.
+Alpine ecosystems are particularly vulnerable to the effect of climate change.
+Monitoring the distribution of alpine vegetation is required to plan practical conservation activities.
+However, conventional field observation and satellite remote sensing have difficulties in the coverage and frequency in alpine areas.
+Researchers have also utilized ground-based time-lapse cameras to observe alpine regions' snowmelt and vegetation phenology.
+Such time-lapse cameras have significant advantages in cost, resolution, and frequency.
+However, no research has used these to monitor the vegetation distribution.
+This study proposes a novel method to draw georeferenced vegetation maps from ground-based imagery of the Japanese alps.
+Our approach has two components: the classification and georectification method.
+The proposed classification method uses pixel time series acquired from autumn images to utilize the patterns of autumn foliage.
+We show that using time-lapse imagery and a Recurrent Neural Network improves the performance of the vegetation classification.
+We also developed a novel method to accurately transform a ground-based image into georeferenced data.
+We propose 1.
+an automated procedure to acquire Ground Control Points (GCPs) and 2.
+a camera model that considers the lens distortion for accurate georectification.
+We show that our approach outperforms the conventional method.
+The proposed method achieved sufficient accuracy to observe the vegetation distribution on a plant-community scale.
+The evaluation reveals an F1 score of 0.937 in the vegetation classification and a root mean square error (RMSE) of 3.4 m in the georectification.
+Our results highlight the potential of cheap time-lapse cameras to monitor the distribution of alpine vegetation.
+The proposed method should significantly contribute to effective conservation planning of the alpine ecosystems.
 \end{abstract}
@@
 For example, the growth of dwarf pine (\emph{Pinus pumila}), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}).
-Effective conservation planning requires early detection and constant monitoring of such vegetation changes.
+Effective conservation planning requires constant monitoring of vegetation distribution to detect such changes.
 Also, since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.
@@
 
-We used repeat photography data owned by National Institute for Environmental Studies, Japan (NIES).
+We used time-lapse images of a Japanese alpine region owned by the National Institute for Environmental Studies, Japan (NIES).
 All the images are publically available on NIES' webpage (\url{https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2}).
 In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt.
-Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps \ref{fig:map}.
+Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps (Fig.
+\ref{fig:map}).
 The camera takes a photograph per hour, from 6 a.m.
@@
 The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines.
-From April to November, the camera has observed the snowmelt and seasonal phenology of evergreen(e.g., \emph{Pinus pumila}) and deciduous (\emph{Sorbus} sp., \emph{Betula ermanii}) dwarf trees, dwarf bamboos (e.g., \emph{Sasa kurilensis}), and alpine shrubs and herbaceous plants (e.g., \emph{Geum pentapetalum}, \emph{Nephrophyllidium crista-galli}).
+From April to November, the camera observed the snowmelt and seasonal phenology of evergreen(e.g., \emph{Pinus pumila}) and deciduous (\emph{Sorbus} sp., \emph{Betula ermanii}) dwarf trees, dwarf bamboos (e.g., \emph{Sasa kurilensis}), and alpine shrubs and herbaceous plants (e.g., \emph{Geum pentapetalum}, \emph{Nephrophyllidium crista-galli}).
 This study used images from the summer and fall of 2015 to classify vegetation with the temporal patterns of the leaf color.
@@
 
-Since images are slightly misaligned, we aligned them before processing.
-We implemented the program with the Python3 programming language and OpenCV4 (\url{https://opencv.org/}) image processing library.
-First, we set one image of 2015 as the alignment target.
-Next, we automatically found matching keypoints between the target and other images using the AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
+Although the camera is fixed on the mountain lodge, the images are slightly misalighned do to the wind.
+To handle this issue, we aligned the images before processing using Python3 programming language and OpenCV4 (\url{https://opencv.org/}) image processing library.
+First, one image of 2015 were set as the alignment target.
+Next, we automatically matched key points between the target and other images using the AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
 Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's ``findHomography'' function.
-Applying the estimated homography matrix, we could align the images accurately (0.654 pixels in root mean square error of the matching points).
-Finally, we prepared an input mask to define image regions that should be ignored in the following procedure, such as the sky and the regions too close to the camera.
+Applying the estimated homography matrix, we could align the images accurately (0.654 pixels in root mean square error (RMSE) of the matching points).
+Finally, an input mask were applied to define image regions that should be ignored in the following procedure, such as the sky and the regions too close to the camera.
+This process ensures that a set of pixel time-series reflects a phenological information of a same location, which is essential in the vegetation classification process.
 
@@
 
-Because we successfully aligned the images, we can stack the images and extract a time series of pixel values (Red, Green, and Blue, \ref{fig:pixtimeseries}) for each pixel.
+Because the images were aligned succesfuly, we can stack the images and extract a time series of pixel values (Red, Green, and Blue, Fig.
+\ref{fig:pixtimeseries}) for each pixel.
 Such pixel time series reflects the temporal patterns of leaf colors.
-Because deciduous plants have great differences in autumn phenology among species, researchers have used that information for vegetation classification with satellite imagery (e.g., \cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}).
-However, no research has applied this technique to ground-based repeat photography imagery.
-We implemented Support Vector Machine (SVM) and Recurrent Neural Network (RNN) based vegetation classification methods in this study.
-We tested the effects of using pixel time series on the classification performance.
+Because deciduous plants have great differences in autumn leaf phenology among species, researchers have used that information for vegetation classification with satellite imagery (\cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}).
+However, no research has applied this technique to ground-based time-lapse imagery.
+We implemented Support Vector Machine (SVM) and Recurrent Neural Network (RNN) based vegetation classifiers, and tested the effects of using pixel time series of the ground-based imagery on the classification performance.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figures/Slide1} \caption{Pixel time series acquired from the time lapse camera.
+\includegraphics[width=1\linewidth]{paper_files/figures/Slide1} \caption{Pixel time series acquired from the time-lapse camera.
 You can obtain a time series of pixel values (i.e., Red, Green, and Blue) for each pixel on the photographs.
@@
 We implemented the classifier with Python3 language, ThunderSVM library (\url{https://github.com/Xtra-Computing/thundersvm}) for the SVM classifier, and PyTorch deep neural network library (\url{https://pytorch.org/}) for the RNN classifier.
-All source codes are publically available via GitHub (\url{https://github.com/0kam/xxxx}).
+All source codes are publically available via GitHub (\url{https://github.com/0kam/VegetationMapPaper}).
 
@@
 \item
-  Estimating the camera parameters such as camera poses and field of view using GCPs.\\
+  Estimating the camera parameters such as camera poses and FoV using GCPs.\\
 \item
@@
 
-As we mentioned before, we considered a camera as a function that transforms geographical coordinates of the target mountain to the image coordinates in the acquired image.
-We implemented this procedure using the OpenGL framework to accelerate it with graphical processing units (GPUs).
-In OpenGL, we can separate this process into three operations:
+As we mentioned before, we modeled a camera as a function that transforms the geographical coordinates of the target mountain into the image coordinates in the acquired image.
+We implemented this procedure using the OpenGL framework (\url{https://www.opengl.org/}) to accelerate it with graphical processing units (GPUs).
+In OpenGL, we can divide this process into three operations:
 
@@
 \item
-  Transforming the world (geographical) coordinates to the view coordinates (coordinates seen from the camera's point of view) using camera's extrinsic parameters (i.e., the location and angles of the camera).\\
+  Transforming the world (geographical) coordinates to the view coordinates (coordinates seen from the camera's point of view) using the camera's extrinsic parameters (i.e., the location and angles of the camera).\\
 \item
@@
 \item
-  Transforming the view coordinates to the screen (image) coordinates using camera's intrinsic parameters (i.e., the FoV and aspect ratio of the camera).
+  Transforming the view coordinates to the screen (image) coordinates using the camera's intrinsic parameters (i.e., the FoV of the camera).
 \end{enumerate}
 
-First, we transformed the absolute geographic coordinates (also known as the world coordinates) to the view coordinates that are relative to the camera's position and direction.
+First, we transformed the absolute geographic coordinates (also known as the world coordinates) into the view coordinates relative to the camera's position and direction.
 We applied a \(4 \times 4\) view matrix \(M_{view}\) (\ref{view_matrix}) to the geographic coordinates in this step.
-The view matrix represents the position and the direction (pan, tilt, roll) of the camera.
-Note that the geographic coordinate system must be cartesian (such as the UTMs).
+The view matrix represents the camera's position and direction (pan, tilt, roll).
+The geographic coordinate system must be cartesian (such as the UTM coordinate systems).
 
+\begin{equation}
 \label{view_matrix}
-\begin{equation}
   M_{view} = 
@@
 
+\begin{equation}
 \label{view_tf}
-\begin{equation}
   \begin{bmatrix} 
@@
 
+\begin{gather}
 \label{dist_model}
-\begin{gather}
+  \begin{gathered}
   X_{norm} = \frac{X_{camera}}{Y_{camera}} \\
@@
 
+\begin{gather}
 \label{proj_mat}
-\begin{gather}
+  \begin{gathered}
   f_x = \frac{1}{\frac{\tan fov_x}{2}} \\
@@
   \end{bmatrix}
+  \end{gathered}
 \end{gather}
 
+\begin{equation}
 \label{proj_tf}
-\begin{equation}
   \begin{bmatrix} 
@@
 
-Applying these procedures to the GCPs' geographical coordinates, we can calculate the reprojected image coordinates with a set of camera parameters (the camera location, pose, FoV, and the lens distortions).
-Then, we can major the distance from the actual image coordinates of GCPs (\(U, V\) of \ref{fig:optim}) to the reprojected image coordinates (\(U', V'\) of \ref{fig:optim}).
-We optimized the camera parameters (except camera location) by minimizing this distance using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}, \ref{fig:optim}).
+Applying these procedures to the GCPs' geographical coordinates, we can calculate the reprojected image coordinates with a set of camera parameters (the camera location, pose, FoV, and lens distortion parameters).
+Then, we can measure the distance from the actual image coordinates of GCPs (\(U, V\) of Fig.
+\ref{fig:optim}) to the reprojected image coordinates (\(U', V'\) of Fig.
+\ref{fig:optim}).
+We estimated the camera parameters (except camera location) by minimizing this distance using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}, Fig.
+\ref{fig:optim}).
 We could not estimate the camera location because it makes the problem too complicated (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figures/Slide5} \caption{Work flow of the camera parameter optimization.
+\includegraphics[width=1\linewidth]{paper_files/figures/Slide5} \caption{Workflow of the camera parameter optimization.
 We estimated the camera parameters by minimizing the GCP's reprojection error.}\label{fig:optim}
@@
 
-To get matching points between images and DSMs on a broader area, we additionally used an orthorectified airborne image.
-Applying the camera model to an airborne image, a DSM, and a set of initial camera parameters, we rendered a simulated landscape image \ref{fig:matched}.
-Then we got matching points of an original image and the simulated image using AKAZE local feature matcher \ref{fig:matched}.
+Usually, GNSS-positioned GCPs (such as GCP markers) are set before photo acquisition to get a georeferenced image, however, setting such markers in alpine areas are often tough due to the harsh topology.
+\cite{Portenier2020Cryosphere} solved this problem by developing a method that uses mountain silhouettes to match images and DEMs.
+Its weak point is that the georectification accuracy is sometimes low in the mountainside, where no GCPs are set.
+We developed an novel method that uses an orthorectified airborne image to get matching points between images and DSMs in a broader area.
+
+First, an airborne image and a DSM that covers the camera's field of view, and a set of initial camera parameters (roughly estimated camera parameters) were prepared.
+We rendered a simulated landscape image by applying the camera model to these.
+Since the simulated image is consists of georeferenced DEM and airborne image, every pixel has a geographic coordinate.
+Then we searched matching points between the original image and the simulated image using AKAZE local feature matcher (Fig.
+\ref{fig:matched}).
 Since these matching points have both geographical coordinates (from the DSM) and image coordinates (from the original image), we used these points as GCPs.
+This method enables us to acquire GCPs in much broader area than the previous method.
 Our procedure requires the camera's exact location and initial camera parameters to render the simulated image.
-Note that the orthorectification accuracy of the airborne photograph may affect the georectification accuracy.
+Note that the orthorectification accuracy of the airborne image may affect the georectification accuracy.
 
@@
 The simulated image was rendered with an orthophoto, DSM, and initial camera parameters.
-Red points shows the matching points found by the AKAZE local feature matcher.
+Red points show the matching points found by the AKAZE local feature matcher.
 We used these points as GCPs.}\label{fig:matched}
@@
 
-Finally, we georectified the vegetation classification result using the optimized camera parameters \ref{fig:georec}.
-At this point, we got point data of vegetation (as shown in the table on the right of \ref{fig:georec}) that every row represents a pixel of the original image.
-To measure the area of each vegetation class, we converted the point data to a raster data.
-We rasterized the point data in 1 m resolution, then interpolated holes up to 2 m since the maximum pixel foot print was about 2 m on the ridge of the mountain.
+Finally, we georectified the vegetation classification result using the optimized camera parameters (Fig.
+\ref{fig:georec}).
+At this point, we got the point data of vegetation (as shown in the table on the right of Fig.
+\ref{fig:georec}) that every row represents a pixel of the original image.
+To measure the area of each vegetation class, we converted the point data to raster data.
+We rasterized the point data in 1 m resolution, then interpolated holes up to 2 m since the maximum pixel footprint was about 2 m on the ridge of the mountain.
 We implemented these procedure using R language \cite{RCore}, \texttt{stars} package \cite{Rstars} and \texttt{terra} \cite{Rterra} package.
-See \url{https://github.com/0kam/xxx/xxx} for the source code.
+See \url{https://github.com/0kam/VegetationMapPaper/blob/master/scripts/utils/interpolate.R} for the source code.
 
@@
 We implemented the algorithm with Python3 language and published it as an open-source package via GitHub (\url{https://github.com/0kam/alproj}).
-You can try it with your data.
-We used an airborne photograph taken in the November of 201X with a spatial resolution of 1.0 m.
-Also, we used the 1m resolution Digital Surface Model that were also used in the orthorectification process of the airborne photograph.
+We used an airborne photograph taken in the October of 2014 with a spatial resolution of 1.0 m.
+Also, we used the 1m resolution Digital Surface Model that was also used in the orthorectification process of the airborne photograph.
 
@@
 Each fold was stratified with the vegetation categories.
-We used F1-score, a standard metrics in machine learning evaluation (\ref{metrics}), where \(TP, FP, FN\) is true positives, false positives, and false negatives, respectively.
+We used F1-score, a standard metric in machine learning evaluation (\ref{metrics}), where \(TP, FP, FN\) is true positives, false positives, and false negatives, respectively.
 
+\begin{align}
 \label{metrics}
-\begin{align}
+  \begin{gathered}
   precision = \frac{TP}{TP + FP} \\
@@
 F1-score was calculated for each vegetation class.
-Each box shows the results of 5-fold cross validation.
-We classified vegetation using single image (shown as the shooting date) with SVM classifiers, and all images with SVM (shown as ``Multidays'') and RNN (shown as ``Multidays RNN'') classifiers.}\label{fig:vegeacc}
+Each box shows the results of a 5-fold cross-validation.
+We classified vegetation using a single image (shown as the shooting date) with SVM classifiers and all images with SVM (shown as ``Multidays'') and RNN (shown as ``Multidays RNN'') classifiers.}\label{fig:vegeacc}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figures/vege} \caption{Vegetation classification results of the RNN model.
-The masked area, i.e., the sky and the regions too close to the camera, is shown in black.}\label{fig:vegetation}
+\includegraphics[width=1\linewidth]{paper_files/figures/vege} \caption{Left: Vegetation classification results of the RNN model.
+The masked area, i.e., the sky and the regions too close to the camera, is shown in black.
+Right: The generated vegetation map.
+The background shows contour lines.}\label{fig:vegetation}
 \end{figure}
 
-\ref{fig:vegeacc} shows the results of the 5-fold cross validation.
+Fig.
+\ref{fig:vegeacc} shows the results of the 5-fold cross-validation.
 Focusing on the single image classification (shown as the shooting date), the best date for classification was different among classes.
 For example, 26th Sep was the best for identifying rowans, but 10th Oct was for dwarf pines and dwarf bamboos.
-Note that the autumn colorization of rowan leaves was at the best on 26th Sep, and the most vegetation except dwarf bamboo and dwarf pine were blasted at 10th Oct.~No single image can classify birch and montane alder accurately.
-In contrast, using all images (shown as ``Multidays'', ``Multidays RNN'', representing the SVM and RNN classifiers respectively) resulted high F1 score in every classes.
-Also, the RNN classifier outperforms the SVM classifier (0.937 and 0.918 in mean macro average F1 score).
-\ref{fig:vegetation} shows the products of the RNN classifier.
-We can observe the distribution of dwarf pine and dwarf bamboo at the plant-community scale.
+Note that the autumn colorization of rowan leaves was at best on 26th Sep, and the most vegetation except dwarf bamboo and dwarf pine were blasted on 10th Oct.~No single image can classify birch and montane alder accurately.
+In contrast, using all images (shown as ``Multidays'' and ``Multidays RNN'' representing the SVM and RNN classifiers, respectively) resulted in a high F1 score in every class.
+Also, the RNN classifier outperforms the SVM classifier (0.937 and 0.918 in macro average F1 score).
+Fig.
+\ref{fig:vegetation} (left) shows the products of the RNN classifier.
+We can observe the distribution of each vegetation classes at the plant-community scale.
 
@@
 
-We tested the accuracy of our georectification method and evaluated the effect of its two features: using image matching to acquire GCPs, and modeling the lens distortion.
-We manually searched 83 matching points between the simulated photograph and the original photograph and treated them as the test GCPs: GCPs that are not used in the georectification process.
-We additionally prepared two comparison methods to test the performance of our proposed method.
-The first one is the silhouette based matching method (hereinafter called silhouette) used in previous studies (\cite{Portenier2020Cryosphere}).
-The second one is the proposed method without the lens distortion model (hereinafter called no distortion).
+We tested our georectification method's accuracy and evaluated its two features' effects: using the simulated image and image matching to acquire GCPs, and modeling the lens distortion.
+We manually searched 83 matching points between the simulated and original images and treated them as the test GCPs: GCPs that are not used in the georectification process.
+We additionally prepared two comparison methods to test the performance of the proposed method.
+The first one is the silhouette-based matching method (after this called silhouette) used in previous studies (\cite{Portenier2020Cryosphere}).
+The second is the proposed method without the lens distortion model (after this called no distortion).
 We evaluated the projection error of the test GCPs using these three methods.
 The proposed method achieves accurate projection (3.45 m as the root mean square error) while the other two did not (16.1 m with silhouette, 23.6 m with no distortion).
-Note that we estimated the lens distortion parameters in the silhouette method.
+We estimated the lens distortion parameters in the silhouette method.
+Fig.
 \ref{fig:geoacc} shows the relationship between the projection error of the proposed method and the test GCPs' distance from the shooting point.
-The projection error was especially large in the GCPs near to the shooting point.
+The projection error was especially large in the GCPs near the shooting point.
+Note that the projection errors were measured ignoring the georectification error of the orthophoto and the DSM.
+Fig.
+\ref{fig:vegetation} (right) shows the produced vegetation map.
+The vegetation map has missing areas because ridges blocked the camera's view.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{../results/georec_acc} \caption{Vegetation classification results of the RNN model.
-The masked area, i.e., the sky and the regions too close to the camera, is shown in black.}\label{fig:geoacc}
+\includegraphics[width=1\linewidth]{../results/georec_acc} \caption{The projection error of the proposed method.
+The projection error was particularly large in the area near the camera.}\label{fig:geoacc}
 \end{figure}
-
-\hypertarget{vegetation-maps}{%
-\subsection{Vegetation maps}\label{vegetation-maps}}
 
@@
 
-We suggested a fully automated procedure to transform time-lapse imagery into georeferenced vegetation maps at a meager cost.
+We suggested a fully automated procedure to transform time-lapse images of an alpine region into a georeferenced vegetation map at a meager cost.
 This task is challenging because of 1.
 the difficulty of classifying vegetation with ordinal digital camera imagery and 2.
-the difficulty of georectification.
+the difficulty of georectification of such ground-based imagery.
 We solved these issues by 1.
@@
 developing a novel method for accurate image georectification.
-Our vegetation classification performance (with an accuracy of 0.87) and georectification methods (with an RMSE of \(rmse\) m) are practical.
+The proposed methods reached a functional performance (0.937 in a mean F1 Score of vegetation classification, 3.4 m in a mean projection error of georectification) to use the vegetation map in monitoring the vegetation distributions on a plant-community scale.
 
@@
 One of the shortcomings of ordinal digital cameras is that they only have three bands (Red, Blue, and Green).
-We made up for this lack of information by using the rich temporal information that time-lapse cameras can obtain.
-Many plant species have characteristic phenologies, such as flowering and autumn foliages.
-Observing this requires long-term (such as year-round) monitoring with a high frequency, and digital time-lapse cameras are suitable.
-This study only focused on the two species (dwarf bamboo and stone pine) that are easy to classify, even with a single image.
-However, like the previous studies (\cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}), we expect our method to classify more vegetation (e.g., dwarf deciduous trees and alpine herbaceous plants) using the temporal information of leaf colors.
-We also used hourly images for each day.
-Fig.
-x shows that this additional information made our model robust against transient noises, such as shadows.
-Since alpine ecosystems have rough topologies, shadows are a considerable problem.
-Time-lapse cameras are also beneficial for this reason.
+We made up for this lack of information using the rich temporal information that time-lapse cameras can obtain.
+Many plant species have characteristic phenologies, such as autumn foliage, and the suitable season to observe them differs among species.
+The result (Fig.
+\ref{fig:vegeacc}) shows that each vegetation class has its suitable timing to identify it in photographs.
+Classifying multiple vegetation classes requires long-term (such as several months long) and frequent (such as daily) monitoring, and digital time-lapse cameras are suitable.
+In addition, combining multi-temporal images improved the classification accuracy, especially with Birch and Montane Alder (Fig.
+\ref{fig:vegeacc}).
+The best F1 score was low with single image classification (0.750 for Montane Alder, 0.345 for Birch), and using multi-temporal images improves them much (0.951 and 0.781 with the SVM classifier).
+This result shows that identifying these vegetation requires multi-temporal information.
+The inter-community heterogeneity of autumn foliage timing in these species may cause this result.
+As the previous study pointed out (\cite{Ienco2017RemSenLSTM}), the RNN model outperformed the SVM model, particularly in identifying Birch (0.781 with SVM and 0.831 with RNN).
+Our model can still be further improved.
+As \cite{Sharma2018NN} claimed, the patch-based classification method may improve the performance.
+Such patch-based models take a time series of small patches as an input to utilize the spatial information, such as textures, in the classification process.
 
@@
 
+The most significant barrier to using ground-based imagery in ecological monitoring is its difficulty in treating it as geospatial data.
+An automated and accurate georectification method was required to overcome this challenge.
+Without georectification, we cannot quantitatively analyze (e.g., measuring the area, locating the place, and analyzing with topographic data) the acquired information, such as the vegetation distribution.
+We suggested a novel method to georectify such imagery.
+With minimal manual user inputs (i.e., the location of the camera and the initial camera parameters), our method achieved a state-of-the-art accuracy (3.45 m).
+We tested the effectiveness of the two features of our method: the lens distortion model and the image-matching-based method to acquire GCPs automatically.
+The results show that the lens distortion model greatly improved the georectification accuracy.
+Without the lens distortion model, our model resulted in a projection accuracy of 23.6 m.
+However, since the effect of lens distortion on the georectification accuracy is different among cameras and lenses (\cite{Portenier2020Cryosphere}), further testing will be required to ensure the advantage of our lens distortion model.
+Note that the proposed lens distortion model does not support a fisheye lens and omnidirectional camera.
+Another feature of our method is the automatic acquisition of GCPs using simulated images and image matching techniques.
+This method requires a high-resolution orthophoto that covers the camera's field of view.
+This costs a bit; however, the reward is considerable.
+Using simulated images in GCP acquisition also improved the georectification accuracy; the conventional silhouette-based method resulted in an RMSE of 16.1 m.
+This result suggests that acquiring matching points between the image and the DSM in a broader area benefits the camera parameter estimation process.
+However, the proposed method (AKAZE image matcher) could not acquire matching points in the area near the camera, and the projection error was relatively large (Fig.
+\ref{fig:geoacc}).
+While the spatial resolution of the simulated image depends on orthophoto (in this study, 1 m), that of the original image changes depending on the distance from the camera.
+In such near areas, the spatial resolution of the original image is much higher than that of the simulated image, and the image matcher cannot handle the difference.
+Recently, researchers have developed some deep-learning-based image-matching methods (e.g., \cite{Yang2018ImageMatching}, \cite{Wu2013AEImageMatching}) that are more robust to the differences in image sources and viewpoints.
+Applying these methods to the GCP acquiring process may improve the performance of our method, especially in near areas.
+Theoretically, our approach can handle the images of other ecosystems, such as forests.
+However, because the georectification accuracy strongly depends on the accuracy of the DSM, this may be difficult.
+Since alpine plants tend to be very short, readily available Digital Elevation Models (DEMs) can be used as the DSMs.
+In forestry areas, vegetation height is considerable, and the gap between the DEMs and the actual surface (top of the forest) will cause significant errors in the georectification process.
+
 \hypertarget{future-application-and-conclusion}{%
 \subsection{Future application and conclusion}\label{future-application-and-conclusion}}
+
+Here, we proposed an automated method to draw a vegetation map from a series of images acquired by a digital time-lapse camera.
+The produced vegetation map has sufficient accuracy for monitoring endemic and vulnerable alpine vegetation.
+One of the benefits of digital time-lapse cameras is their long-term operability.
+Applying the proposed method to the existing long-term time-lapse imagery will enable the researchers to quantitatively understand the vegetation changes and their trends.
+That information will help plan the field observations and conservation activities more effectively.
+Our methods facilitate cost-efficient monitoring of alpine vegetation and understanding of the progressing impacts of climate changes on alpine ecosystems.
 

### 2022-09-13 scripts/models/model_comparison.R

@@ -38,66 +38,66 @@ vegetation_levels <- c(
 )
 
 summarise_cv <- function(path) {
-    out <- str_replace(path, ".csv", "_sum.csv")
-    df <- read_csv(path,
-               col_select = c(metrics, vegetation, value, fold))
-    df %>%
-        filter(metrics != "support") %>%
-        mutate(vegetation = translate_classes(vegetation)) %>%
-        mutate(vegetation = factor(vegetation, levels = vegetation_levels)) %>%
-        group_by(., vegetation, metrics) %>%
-        summarise(
-          mean = sprintf("%1.3f", mean(value)),
-          sd = sprintf("(%1.3f)", sd(value))
-        ) %>%
-        pivot_longer(cols = c(mean, sd), names_to = "var") %>%
-        pivot_wider(names_from = metrics, values_from = value) %>%
-        mutate(path = path) %T>%
-        write_csv(out)
+  out <- str_replace(path, ".csv", "_sum.csv")
+  df <- read_csv(path,
+                 col_select = c(metrics, vegetation, value, fold))
+  df %>%
+    filter(metrics != "support") %>%
+    mutate(vegetation = translate_classes(vegetation)) %>%
+    mutate(vegetation = factor(vegetation, levels = vegetation_levels)) %>%
+    group_by(., vegetation, metrics) %>%
+    summarise(
+      mean = sprintf("%1.3f", mean(value)),
+      sd = sprintf("(%1.3f)", sd(value))
+    ) %>%
+    pivot_longer(cols = c(mean, sd), names_to = "var") %>%
+    pivot_wider(names_from = metrics, values_from = value) %>%
+    mutate(path = path) %T>%
+    write_csv(out)
 }
 
 read_cv <- function(path) {
-    read_csv(path, col_select = c(metrics, vegetation, value, fold)) %>%
-        filter(metrics != "support") %>%
-        mutate(vegetation = translate_classes(vegetation)) %>%
-        mutate(vegetation = factor(vegetation, levels = vegetation_levels)) %>%
-        mutate(path = path)
+  read_csv(path, col_select = c(metrics, vegetation, value, fold)) %>%
+    filter(metrics != "support") %>%
+    mutate(vegetation = translate_classes(vegetation)) %>%
[…]

### 2022-09-13 scripts/plot_phenology.R

@@ -1,0 +1,57 @@
+library(tidyverse)
+library(reticulate)
+library(lubridate)
+setwd("~/VegetationMapPaper/")
+
+reticulate::source_python("scripts/plot_phenology.py")
+
+df <- sample_timeseries(n = 10L)
+
+change_names <- function(nums) {
+  case_when(
+    nums == 0 ~ "Dwarf Bamboo",
+    nums == 1 ~ "Other Vegetation",
+    nums == 2 ~ "No Vegetation",
+    nums == 3 ~ "Rowans",
+    nums == 4 ~ "Golden Birch",
+    nums == 5 ~ "Montane Alder",
+    nums == 6 ~ "Dwarf Pine"
+  )
+}
+
+df %>%
+  as_tibble() %>%
+  mutate(
+    vegetation = change_names(vegetation),
+    date = ymd(str_extract(path, "\\d{8}"))
+  ) %>%
+  select(-path) %>%
+  pivot_longer(cols = c("R", "G", "B"), names_to = "band", values_to = "value") %>% 
+  write_csv("results/phenology.csv")
+
+df <- read_csv("results/phenology.csv")
+
+p <- df %>%
+  mutate(band = factor(band, levels = c("R", "G", "B"))) %>%
+  mutate(id = str_c(index, band)) %>%
+  mutate(date = as.character(date)) %>%
+  ggplot() +
+  geom_line(aes(x = date, y = value, colour = band, group = id)) +
+  facet_wrap(~ vegetation, nrow = 3) +
+  labs(
+    x = "Date",
+    y = "Pixel Value",
+    colour = "Band"
+  ) +
+  theme_minimal() +
+  theme(
+    axis.text = element_text(size = 18),
+    text = element_text(size = 20),
+    axis.text.x = element_text(angle = 60, hjust = 1),
+    plot.background = element_rect(fill = "white"),
+    panel.spacing = grid::unit(2, "lines")
+  )
+
+p
+
+ggsave("results/phenology.png", plot = p, width = 10, height = 8)

### 2022-09-13 scripts/plot_phenology.py

@@ -1,0 +1,50 @@
+import numpy as np
+from PIL import Image
+from glob import glob
+import random
+from pathlib import Path
+import pandas as pd
+
+def sample_timeseries(n = 10):
+  n = int(n)
+  files = sorted(glob("data_source/aligned/multi_days/*"))
+  
+  t = np.load("results/teacher.npy")
+  t2 = np.asarray(Image.open("results/teacher.png"))
+  t2 = np.max(t2, 2)
+  t[t2 == 0] = 99
+  imgs = np.stack([Image.open(f) for f in files])
+  
+  vege = []
+  path = []
+  num = []
+  R = []
+  G = []
+  B = []
+  
+  paths = [Path(f).stem for f in files]
+  
+  for c in range(7):
+    pixes = imgs[:, t == c, :]
+    random.seed(12)
+    idx = random.sample(range(pixes.shape[1]), n)
+    pix = pixes[:, idx, :]
+    for i in range(pix.shape[1]):
+      p = pix[:, i, :]
+      for j in range(pix.shape[0]):
+        vege.append(c)
+        path.append(paths[j])
+        num.append(i)
+        R.append(int(p[j, 0]))
+        G.append(int(p[j, 1]))
+        B.append(int(p[j, 2]))
+  df = pd.DataFrame({
+    "vegetation": vege,
+    "index": num,
+    "path": path,
+    "R": R,
+    "G": G,
+    "B": B
+  })
+  
+  return df

### 2022-10-30 paper/paper.Rmd
modified paper

@@
 ---
-title: Automatically drawing vegetation maps using digital time-lapse cameras in alpine ecosystems
+title: Automatically drawing vegetation classification maps using digital time-lapse cameras in alpine ecosystems
 authors:
@@
   - \usepackage{amsmath}
+  - \usepackage{nicefrac}
   - \setlength{\parindent}{10.5pt}
@@
 library(lubridate)
+setwd("~/projects/VegetationMapPaper/paper/")
 ```
@@
 Alpine vegetation depends on severe conditions such as low temperatures and long snow-covered periods.
-Thus alpine areas have rare and unique species adapted to the extreme environments.
+Thus alpine areas have unique species adapted to such extreme environments.
 Several studies have reported that recent global climatic changes, e.g., increasing temperatures and reducing snow-covered periods, have accelerated the invasion of non-native species into alpine areas (see \cite{Alexander2016AlpBotany}).
 In Japan, dwarf bamboo (*Sasa kurilensis*) has invaded alpine snow meadows, probably driven by the extension of the snow-free period (\cite{Kudo2011EcoEvo}).
-Also, climate change has affected the growth and phenologies of native species.
+Climate change has also affected the growth and phenologies of native species.
 For example, the growth of dwarf pine (*Pinus pumila*), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}).
-Effective conservation planning requires constant monitoring of vegetation distribution to detect such changes.
-Also, since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.
+In addition, researchers have reported that such changes vary depending on species and microhabitats (\cite{Kudo2010AAA}, \cite{XXXXXX}).
+Understanding and predicting the undergoing changes of alpine vegetation requires a monitoring method scalable to a wide range with a spatially and temporally high resolution.
 
@@
 Airborne imagery can obtain high-resolution data, but its cost becomes a bottleneck for frequent monitoring.
-Although UAV methods have become a cost-effective tool for ecological monitoring (\cite{Baena2017PLOSONE}), operating UAVs in alpine regions is challenging due to the strong wind and harsh topology.
+Although UAV methods have become a cost-effective tool for ecological monitoring (\cite{Baena2017PLOSONE}), operating UAVs in alpine regions is sometimes challenging due to the strong wind and harsh topology.
 
@@
 Also, they can obtain high-resolution (i.e., sub-meter scale) and frequent (i.e., daily or hourly) images at a meager cost.
-These studies set some regions of interest (ROI) in the images and calculate the phenology index (e.g., excess greenness, \cite{Woebbecke1995ASAE}).
-However, few studies have utilized such images in monitoring vegetation distributions.
+Most previous studies with such cameras were about calculating the phenology index (e.g., excess greenness, \cite{Woebbecke1995ASAE}) by setting some regions of interest (ROI) in the images.
+Few studies have utilized such images in monitoring vegetation distributions.
 This lack of studies seems to be because applying such time-lapse imagery in monitoring vegetation distribution has two technical challenges.
@@
 First, unlike satellites' multispectral sensors, ordinal digital cameras can only obtain three bands (Red, Green, and Blue), making it harder to classify the vegetation.
-Second, since digital time-lapse cameras are mounted on the ground, transforming these images into geospatial data (e.g., orthoimage) is challenging.
-In other words, even if we classify the vegetation from such images, we cannot quantitatively measure and analyze it as geographic data.
-It is essential to treat ground-based images as geographic data to utilize them in conservation planning.
+Second, since digital time-lapse cameras are mounted on the ground, transforming these images into geospatial data (e.g., orthoimage, this process is called georectification) is challenging.
+In other words, even if we classify the vegetation from such images, we cannot quantitatively measure and analyze it using Geographic Information Systems (GIS) tools.
+Georectification is essential for utilizing time-lapse cameras in scientific conservation planning.
 
-This study proposes an automated method for drawing vegetation maps with a digital time-lapse camera by solving these two challenges.
+This study proposes an automated method for drawing vegetation classification maps with a digital time-lapse camera by solving these two challenges.
 We solved the first challenge by using time-lapse images to classify vegetation.
-Since the autumn leaf phenology varies among species, we utilized that information.
+The autumn leaf phenology, which varies among species, was utilized in the classification process.
 We show the effectiveness of such phenological information in vegetation classification.
-We also developed a novel method for transforming a ground-based photograph into geographic data to tackle the second challenge.
-Finally, we show an example of a vegetation map drawn by the proposed method.
-We aim to use cheap but powerful digital time-lapse cameras in alpine ecosystem monitoring and conservation.
+A novel georectification method for ground-based photographs was also developed to tackle the second challenge.
+Finally, the proposed method generated a vegetation classification map from time-lapse images taken in the Japanese alps.
+Our method enables us to continuously monitor vegetation distribution and its changes at a plant-community scale, covering broad areas at a meager cost.
 
@@
 
-## Digital time-lapse camera imagery
+Our approach has three steps:
+Image-to-image alignment for correcting the movements of the camera
+Vegetation classification for classifying each pixel into vegetation categories
+Georectification for transforming vegetation classification results into geospatial data
+Fig.
+\ref{fig:diagram} shows the overview of the entire process.
+The proposed method requires training data for the vegetation classification model, a Digital Elevation Model (DEM), and a georectified airborne/satellite image that covers the camera's field of view.
 
-We used time-lapse images of a Japanese alpine region owned by the National Institute for Environmental Studies, Japan (NIES).
+(ref:diagram) An overview of the proposed procedure
+
+```{r, diagram, echo=FALSE, message=FALSE, fig.cap="(ref:diagram)", out.width="50%", auto_pdf = TRUE}
+knitr::include_graphics("paper_files/figures/diagram.png")
+```
+
+## Time-lapse image acquisition
+
+Our method is intended for digital time-lapse images of alpine landscapes.
+In this study, we used time-lapse photos of a Japanese alpine region owned by the National Institute for Environmental Studies, Japan (NIES).
 All the images are publically available on NIES' webpage (https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2).
@@
 \ref{fig:map}).
-The camera takes a photograph per hour, from 6 a.m.
+The photographs were taken hourly, from 6 a.m.
 to 7 p.m.
-.
 The camera's field of view (FOV) includes Mt.
@@
 in elevation.
+The pixel size on the ground was about 0.5 m at the ridge, about 1 km from the cameras.
 The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines.
 From April to November, the camera observed the snowmelt and seasonal phenology of evergreen(e.g., *Pinus pumila*) and deciduous (*Sorbus* sp.,  *Betula ermanii*) dwarf trees, dwarf bamboos (e.g., *Sasa kurilensis*), and alpine shrubs and herbaceous plants (e.g., *Geum pentapetalum*, *Nephrophyllidium crista-galli*).
-This study used images from the summer and fall of 2015 to classify vegetation with the temporal patterns of the leaf color.
 
@@
 
-### Selecting images
-
-First, we selected images.
-We choose seven days with good weather from late summer to late fall of 2015 (8/25, 9/5, 9/12, 9/20, 9/26, 10/3, 10/10).
-The temporal patterns of autumn foliage coloration are largely different among species (see Fig.
-\ref{fig:pixtimeseries}).
-Our method utilizes this information in the vegetation classification.
-Time-lapse cameras are particularly good at observing such temporal changes of the vegetation, while UAVs and airborne imagery cost much.
+### Image selection
+We selected seven images from late summer to late fall (8/25, 9/5, 9/12, 9/20, 9/26, 10/3, and 10/10) in 2015.
+Since the temporal patterns of autumn foliage coloration vary among species (see Fig.
+\ref{fig:pixtimeseries}), this season is suitable for classifying vegetation.
+While acquiring a series of images costs a lot with UAVs and airborne imagery, time-lapse cameras are particularly good at observing such temporal patterns of leaf color.
 

### 2022-10-30 paper/paper.tex
modified paper

@@
 
-\title{Automatically drawing vegetation maps using digital time-lapse cameras in alpine ecosystems}
+\title{Automatically drawing vegetation classification maps using digital time-lapse cameras in alpine ecosystems}
 
@@
 \usepackage{amsmath}
+\usepackage{nicefrac}
 \setlength{\parindent}{10.5pt}
@@
 
+\hypertarget{introduction-1}{%
+\section{Introduction}\label{introduction-1}}
+
 The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (\cite{IPCC2007}).
 Alpine vegetation depends on severe conditions such as low temperatures and long snow-covered periods.
-Thus alpine areas have rare and unique species adapted to the extreme environments.
+Thus alpine areas have unique species adapted to such extreme environments.
 Several studies have reported that recent global climatic changes, e.g., increasing temperatures and reducing snow-covered periods, have accelerated the invasion of non-native species into alpine areas (see \cite{Alexander2016AlpBotany}).
 In Japan, dwarf bamboo (\emph{Sasa kurilensis}) has invaded alpine snow meadows, probably driven by the extension of the snow-free period (\cite{Kudo2011EcoEvo}).
-Also, climate change has affected the growth and phenologies of native species.
+Climate change has also affected the growth and phenologies of native species.
 For example, the growth of dwarf pine (\emph{Pinus pumila}), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}).
-Effective conservation planning requires constant monitoring of vegetation distribution to detect such changes.
-Also, since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.
+In addition, researchers have reported that such changes vary depending on species and microhabitats (\cite{Kudo2010AAA}, \cite{XXXXXX}).
+Understanding and predicting the undergoing changes of alpine vegetation requires a monitoring method scalable to a wide range with a spatially and temporally high resolution.
 
@@
 
-\hypertarget{digital-time-lapse-camera-imagery}{%
-\subsection{Digital time-lapse camera imagery}\label{digital-time-lapse-camera-imagery}}
+Our approach has three steps:
+Image-to-image alignment for correcting the movements of the camera
+Vegetation classification for classifying each pixel into vegetation categories
+Georectification for transforming vegetation classification results into geospatial data
+Fig.
+\ref{fig:diagram} shows the overview of the entire process.
+The proposed method requires training data for the vegetation classification model, a Digital Elevation Model (DEM), and a georectified airborne/satellite image that covers the camera's field of view.
 
-We used time-lapse images of a Japanese alpine region owned by the National Institute for Environmental Studies, Japan (NIES).
+\begin{figure}
+\includegraphics[width=0.5\linewidth]{paper_files/figures/diagram} \caption{An overview of the proposed procedure}\label{fig:diagram}
+\end{figure}
+
+\hypertarget{time-lapse-image-acquisition}{%
+\subsection{Time-lapse image acquisition}\label{time-lapse-image-acquisition}}
+
+Our method is intended for digital time-lapse images of alpine landscapes.
+In this study, we used time-lapse photos of a Japanese alpine region owned by the National Institute for Environmental Studies, Japan (NIES).
 All the images are publically available on NIES' webpage (\url{https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2}).
@@
 in elevation.
+The pixel size on the ground was about 0.5 m at the ridge, about 1 km from the cameras.
 The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines.
 From April to November, the camera observed the snowmelt and seasonal phenology of evergreen(e.g., \emph{Pinus pumila}) and deciduous (\emph{Sorbus} sp., \emph{Betula ermanii}) dwarf trees, dwarf bamboos (e.g., \emph{Sasa kurilensis}), and alpine shrubs and herbaceous plants (e.g., \emph{Geum pentapetalum}, \emph{Nephrophyllidium crista-galli}).
-This study used images from the summer and fall of 2015 to classify vegetation with the temporal patterns of the leaf color.
 
@@
 
-\hypertarget{selecting-images}{%
-\subsubsection{Selecting images}\label{selecting-images}}
+\hypertarget{image-selection}{%
+\subsubsection{Image selection}\label{image-selection}}
 
-First, we selected images.
-We choose seven days with good weather from late summer to late fall of 2015 (8/25, 9/5, 9/12, 9/20, 9/26, 10/3, 10/10).
-The temporal patterns of autumn foliage coloration are largely different among species (see Fig.
-\ref{fig:pixtimeseries}).
-Our method utilizes this information in the vegetation classification.
-Time-lapse cameras are particularly good at observing such temporal changes of the vegetation, while UAVs and airborne imagery cost much.
+We selected seven images from late summer to late fall (8/25, 9/5, 9/12, 9/20, 9/26, 10/3, and 10/10) in 2015.
+Since the temporal patterns of autumn foliage coloration vary among species (see Fig.
+\ref{fig:pixtimeseries}), this season is suitable for classifying vegetation.
+While acquiring a series of images costs a lot with UAVs and airborne imagery, time-lapse cameras are particularly good at observing such temporal patterns of leaf color.
 

### 2022-10-30 scripts/diagraph.R

@@ -1,0 +1,51 @@
+library(DiagrammeR)
+
+grViz("
+  digraph procedure {
+    image[
+      label = 'Time-Lapse Images'  ,
+      shape = cylinder
+    ];
+    teacher[
+      label = 'Teacher Dataset',
+      shape = tab
+    ];
+    selection[
+      label = 'Image Selection',
+      shape = box
+    ];
+    alignment[
+      label = 'Image-to-Image Alignment',
+      shape = box
+    ];
+    classification[
+      label = 'Vegetation Classification',
+      shape = box
+    ];
+    dem[
+      label = 'DEM',
+      shape = cylinder
+    ];
+    airborne[
+      label = 'Airborne/Satellite Image',
+      shape = cylinder
+    ];
+    georec[
+      label = 'Georectification',
+      shape = box
+    ];
+    vegemap[
+      label = 'Vegetation Classification Map',
+      shape = tab
+    ];
+    
+    {rank = same; alignment; teacher;}
+    {rank = same; georec, dem, airborne;}
+    
+    image -> selection -> alignment -> classification -> georec -> vegemap
+    alignment -> teacher [dir = none];
+    teacher -> classification
+    dem -> georec
+    airborne -> georec
+  }
+")

### 2022-11-24 paper/paper.Rmd
modified paper

@@
 Such time-lapse cameras have significant advantages in cost, resolution, and frequency.
-However, no research has used these to monitor the vegetation distribution.
+However, no research has used these to monitor vegetation distribution.
 This study proposes a novel method to draw georeferenced vegetation maps from ground-based imagery of the Japanese alps.
-Our approach has two components: the classification and georectification method.
+Our approach has two components:classification and georectification methods.
 The proposed classification method uses pixel time series acquired from autumn images to utilize the patterns of autumn foliage.
 We show that using time-lapse imagery and a Recurrent Neural Network improves the performance of the vegetation classification.
-We also developed a novel method to accurately transform a ground-based image into georeferenced data.
+We also developed a novel method to transform a ground-based image into georeferenced data accurately.
 We propose 1.
@@
 The proposed method achieved sufficient accuracy to observe the vegetation distribution on a plant-community scale.
-The evaluation reveals an F1 score of 0.937 in the vegetation classification and a root mean square error (RMSE) of 3.4 m in the georectification.
+The evaluation reveals an F1 score of 0.937 in the vegetation classification and a root-mean-square error (RMSE) of 3.4 m in the georectification.
 Our results highlight the potential of cheap time-lapse cameras to monitor the distribution of alpine vegetation.
@@
 library(lubridate)
-setwd("~/projects/VegetationMapPaper/paper/")
+setwd("~/Projects/VegetationMapPaper/paper/")
 ```
@@
 Climate change has also affected the growth and phenologies of native species.
-For example, the growth of dwarf pine (*Pinus pumila*), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}).
-In addition, researchers have reported that such changes vary depending on species and microhabitats (\cite{Kudo2010AAA}, \cite{XXXXXX}).
+For example, the growth of dwarf pine (*Pinus pumila*), a dominant species in Japanese alpine regions, have been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}).
+In addition, researchers have reported that such changes vary depending on species and microhabitats (\cite{Kudo2010AAA}).
 Understanding and predicting the undergoing changes of alpine vegetation requires a monitoring method scalable to a wide range with a spatially and temporally high resolution.
@@
 This lack of studies seems to be because applying such time-lapse imagery in monitoring vegetation distribution has two technical challenges.
-
 First, unlike satellites' multispectral sensors, ordinal digital cameras can only obtain three bands (Red, Green, and Blue), making it harder to classify the vegetation.
@@
 A novel georectification method for ground-based photographs was also developed to tackle the second challenge.
-Finally, the proposed method generated a vegetation classification map from time-lapse images taken in the Japanese alps.
-Our method enables us to continuously monitor vegetation distribution and its changes at a plant-community scale, covering broad areas at a meager cost.
+Using the proposed method, we generated a vegetation classification map from time-lapse images taken in the Japanese alps.
+Our approach enables us to continuously monitor vegetation distribution and its changes at a plant-community scale, covering broad areas at a meager cost.
 
@@
 
-Our approach has three steps:
-Image-to-image alignment for correcting the movements of the camera
-Vegetation classification for classifying each pixel into vegetation categories
-Georectification for transforming vegetation classification results into geospatial data
+The proposed method has three steps:
+1. Image-to-image alignment for correcting the movements of the camera.
+2. Vegetation classification for classifying each pixel into vegetation categories.
+3. Georectification for transforming vegetation classification results into geospatial data.
 Fig.
@@
 The proposed method requires training data for the vegetation classification model, a Digital Elevation Model (DEM), and a georectified airborne/satellite image that covers the camera's field of view.
+
+Fig.
+\ref{fig:diagram} shows the overview of the entire process.
+The proposed method requires a teacher dataset for training the vegetation classification model, a Digital Elevation Model (DEM), and a georectified airborne/satellite image that covers the camera's field of view for the georectification process.
 
@@
 
-Our method is intended for digital time-lapse images of alpine landscapes.
-In this study, we used time-lapse photos of a Japanese alpine region owned by the National Institute for Environmental Studies, Japan (NIES).
+Our approach is intended for digital time-lapse images of alpine landscapes.
+In this study, we demonstrated it with time-lapse photos of a Japanese alpine region owned by the National Institute for Environmental Studies, Japan (NIES).
 All the images are publically available on NIES' webpage (https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2).
@@
 to 7 p.m.
-The camera's field of view (FOV) includes Mt.
+The camera's field of view (FoV) includes Mt.
 Tateyama, which ranges from about 2350 m a.s.l.
@@
 ### Image selection
-We selected seven images from late summer to late fall (8/25, 9/5, 9/12, 9/20, 9/26, 10/3, and 10/10) in 2015.
-Since the temporal patterns of autumn foliage coloration vary among species (see Fig.
+
+In the beginning, we selected seven images with good weather from late summer to late fall (25th Aug, 5th, 12th, 20th, 26th Sep, 3rd, and 10th Oct) in 2015.
+Since the temporal patterns of autumn foliage coloration vary among species (Fig.
 \ref{fig:pixtimeseries}), this season is suitable for classifying vegetation.
@@
 
-### Automatic image-to-image alignment
-
-Although the camera is fixed on the mountain lodge, the images are slightly misalighned do to the wind.
-To handle this issue, we aligned the images before processing using Python3 programming language and OpenCV4 (https://opencv.org/) image processing library.
-First, one image of 2015 were set as the alignment target.
-Next, we automatically matched key points between the target and other images using the AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
-Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's "findHomography" function.
-Applying the estimated homography matrix, we could align the images accurately (0.654 pixels in root mean square error (RMSE) of the matching points).
-Finally, an input mask were applied to define image regions that should be ignored in the following procedure, such as the sky and the regions too close to the camera.
-This process ensures that a set of pixel time-series reflects a phenological information of a same location, which is essential in the vegetation classification process.
-
-## Automatic vegetation classification
-
-Because the images were aligned succesfuly, we can stack the images and extract a time series of pixel values (Red, Green, and Blue, Fig.
-\ref{fig:pixtimeseries}) for each pixel.
-Such pixel time series reflects the temporal patterns of leaf colors.
-Because deciduous plants have great differences in autumn leaf phenology among species, researchers have used that information for vegetation classification with satellite imagery (\cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}).
-However, no research has applied this technique to ground-based time-lapse imagery.
-We implemented Support Vector Machine (SVM) and Recurrent Neural Network (RNN) based vegetation classifiers, and tested the effects of using pixel time series of the ground-based imagery on the classification performance.
-
 (ref:pixtimeseries) Pixel time series acquired from the time-lapse camera.
-You can obtain a time series of pixel values (i.e., Red, Green, and Blue) for each pixel on the photographs.
-Such pixel time series reflects the autumn phenology of the vegetation.
-
+You can obtain a time series of pixel values (i.e., Red, Green, and Blue) for each pixel on the photographs (left).
+Such pixel time series reflects the autumn phenology of the vegetation and varies among vegetation classes (right).
 ```{r, pixtimeseries, echo=FALSE, message=FALSE, fig.cap="(ref:pixtimeseries)", out.width="100%", auto_pdf = TRUE}
@@
 
+### Automatic image-to-image alignment
+
+Time-lapse images often suffer from the camera's movement caused by strong wind, human interference, and thermal expansion of the camera platform.
+Since such movement can cause errors in vegetation classification and georectification, we implemented an alignment method that aligns each image to one image called the master image.
+The software was developed using Python3 programming language and OpenCV4 (https://opencv.org/) image processing library.
+We employed a feature-based alignment method used by previous studies (\cite{Hulton2020PyTrx}, \cite{Portenier2020Cryosphere}).
+First, we searched and matched key points between an image and the master image using the AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
+Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's "findHomography" function (\ref{homography}).
+Applying the estimated homography matrix, we could align the images accurately (0.654 pixels in root mean square error (RMSE) of the matching points).
+Finally, an input mask was applied to define image regions that should be ignored in the following procedure, such as the sky and the regions too close to the camera.
+This process ensures that a set of pixel time series reflects phenological information of the same location, which is essential in the vegetation classification process.
+
+(ref:homography) A homography matrix.
+$u$ and $v$ indicates the x and y-axis coordinates of a point on an image.
+We optimized $H$ by minimizing the Euclid distance between the transformed coordinate of a key point $\begin{bmatrix}{u', v'}\end{bmatrix}$ and the corresponding key point on the master image.
+
+```{=tex}
+\label{homography}
+\begin{equation}
+  \begin{bmatrix} 
+    u' \\ v' \\ w'
+  \end{bmatrix}
+  =
+  H
+  \begin{bmatrix} 
+    u \\ v \\ w 
+  \end{bmatrix}
+\end{equation}
+```
+
+## Vegetation classification
+
+After the image-to-image alignment, we stuck the images and extract a time series of pixel values (Red, Green, and Blue, see Fig.
+\ref{fig:pixtimeseries}) for each pixel.
+Such pixel time series reflects the temporal patterns of leaf colors.
+Because deciduous plants have great differences in autumn leaf phenology among species, researchers have used that information for vegetation classification with satellite imagery (\cite{Son2013RemSen}, \cite{Tigges2013RemSenEnv}, \cite{Heupel2018PFG}).
+However, no research has applied this technique to ground-based time-lapse imagery.
+We implemented Support Vector Machine (SVM) and Recurrent Neural Network (RNN) based vegetation classifiers and tested the effects of using pixel time series of the ground-based imagery on the classification performance.
+
 ### Model Architecture
@@
 We prepared two supervised models, SVM and RNN, to classify the pixel time series into vegetation categories.
-SVM is one of the most popular machine learning models in remote sensing and has many applications (\cite{Mountrakis2011SVMReview}), including vegetation classification with multitemporal satellite imagery (\cite{Tigges2013RemSenEnv}).
-RNN is a neural network that recognizes temporal or sequential data dynamics.
+SVM is one of the most popular machine-learning models in remote sensing and has many applications (\cite{Mountrakis2011SVMReview}), including vegetation classification with multitemporal satellite imagery (\cite{Tigges2013RemSenEnv}).
+RNN is a neural network that recurrently processes sequential or temporal steps of data to recognize their dynamics.
+RNN has been used in many tasks such as speech recognition (\cite{Graves2013SpeechRNN}, \cite{Graves2014SpeechRNN}, \cite{Sak2014acousticLSTM}), and machine translation (\cite{Auli2013translationRNN}, \cite{Cho2014RNN}).
 Researchers have also utilized RNN for remote sensing tasks, such as land cover classification, with multi-temporal satellite imagery (\cite{Ienco2017RemSenLSTM}, \cite{Sharma2018NN}).
-\cite{Ienco2017RemSenLSTM} reported that an RNN classifier outperforms an SVM classifier.
-Amongst many variants of RNN, we used Long Short Time Memory (LSTM, \cite{Hochreiter1997LSTM}), one of the most well-known RNN architectures.
-Batch-normalization technique (\cite{IoffeSzegedy2015BatchNorm}) was employed to speed up and stabilize the model training.
-We also classified the pixel of every single image separately using SVM classifiers to test whether using multi-temporal imagery improves the classification performance.
+(\cite{Ienco2017RemSenLSTM}) reported that an RNN classifier outperforms an SVM classifier on the land cover classification accuracy.
+Amongst many variants of RNN, we used Long Short-Time Memory (LSTM, \cite{Hochreiter1997LSTM}, one of the most well-known RNN architectures.
+Batch-normalization technique (\cite{IoffeSzegedy2015BatchNorm}) and the GELU activation function (\cite{HendrycksGimpel2016GELU}) were employed to speed up and stabilize the model training.
+As a comparison, we also classified the pixel of every single image separately using SVM classifiers to test whether using multi-temporal imagery improves the classification performance.
 
@@
 
-We set 7 vegetation classes: Dwarf Pine (*Pinus pumila*), Dwarf Bamboo (*Sasa kurilensis*), Rowans (*Sorbus sambucifolia*, *Sorbus matsumurana*), Birch (*Betula ermanii*), Alder (*Alnus viridis* subsp.
+Each pixel time series was classified into 7 vegetation classes: Dwarf Pine (*Pinus pumila*), Dwarf Bamboo (*Sasa kurilensis*), Rowans (*Sorbus sambucifolia*, *Sorbus matsumurana*), Maple (*Acer tschonoskii*), Montane Alder (*Alnus viridis* subsp.
 *maximowiczii*), Other Vegetations (such as alpine shrubs and herbaceous plants), and No Vegetation.
-Using an open-source image annotation software (Semantic Segmentation Editor, Hitachi, https://github.com/Hitachi-Automotive-And-Industry-Lab/semantic-segmentation-editor), an expert prepared a teacher dataset for each class.
-Then we validated the teacher dataset with a set of telephotos taken in the summer and fall of 2016.
+Experts prepared a teacher dataset for each class using an open-source image annotation software (Semantic Segmentation Editor, Hitachi, https://github.com/Hitachi-Automotive-And-Industry-Lab/semantic-segmentation-editor).
+The prepared teacher dataset contains XX pixels in XX polygons, which covers about X% of the image.
+Each polygon was validated with telephotos taken at the same place in 2016.
+For some polygons that were not seen clearly even in the telephoto, we conducted a field survey in the November of 2022.
 
-### Implementation and model training
+### Experimental Settings
+We implemented the classifiers with Python3 language.
+For the SVM classifier, we used the ThunderSVM library (<https://github.com/Xtra-Computing/thundersvm>) and an RBF kernel with a regularization parameter equal to 1.0.
+The gamma value was set automatically by the “scaled“ setting of the ThunderSVM library as $\gamma = \frac{1}{n_{features} \times V(X)}$, where and stand for the dimensions and variance of the input data respectively.
+The RNN classifier was developed using the PyTorch deep neural network library (<https://pytorch.org/>).
+We set the number of hidden dimensions equal to 5.
+We trained the model 200 epochs with the RAdam optimizer (\cite{Liu2020RAdam}) with a learning rate of 0.001 and a batch size of 500.
+To validate the performance of the different classifiers, we performed a 5-fold cross-validation.
+Each fold was stratified with the vegetation categories.
+As a model evaluation metric, we used the per-class F1-score, a standard metric in machine learning (\ref{f1score}).
+$TP, FP, FN$ stand for the numbers of true positives, false positives, and false negatives, respectively.
+All source codes are available via GitHub (https://github.com/0kam/VegetationMapPaper).
 
-We implemented the classifier with Python3 language, ThunderSVM library (<https://github.com/Xtra-Computing/thundersvm>) for the SVM classifier, and  PyTorch deep neural network library (<https://pytorch.org/>) for the RNN classifier.
-All source codes are publically available via GitHub (<https://github.com/0kam/VegetationMapPaper>).
+```{=tex}
+\label{f1score}
+\begin{align}
+\label{metrics}
+  \begin{gathered}
+  precision = \frac{TP}{TP + FP} \\
+  recall = \frac{TP}{TP + FN} \\
+  F_1 = \frac{2 \cdot precision \cdot recall}{precision + recall} \\
+  \end{gathered}
+\end{align}
+```
 
@@
 
-Then, we developed a novel method to convert ground-based landscape imagery into geographical data.
-This process is called georectification.
+The second challenge of utilizing time-lapse cameras in vegetation monitoring is the difficulty of georectification, i.e., georeferencing and transforming the images into geographic data.
+We developed a novel method to perform this process automatically and accurately.
 Georectification of ground-based images has been a difficult task, and this causes the underuse of potentially rich information in ground-based imagery.
 In plain words, georectification means aligning images onto Digital Surface Models (DSMs) so that every pixel of an image gets a geographical coordinate.
-You can do this by modeling the camera.
+It usually requires a camera model.
 A camera is considered a function that transforms 3D geographical coordinates (e.g., X, Y, and height in a Universal Transverse Mercator coordinate system (UTM)) into 2D image coordinates (locations of each pixel in the image).
@@
 
-1.  Finding Ground Control Points (GCPs) in the image.\
-2.  Estimating the camera parameters such as camera poses and FoV using GCPs.\
-3.  Projecting the DSM into the image using the camera parameters.
+1. Finding Ground Control Points (GCPs) in the image.
+2. Estimating the camera parameters such as the camera pose and FoV using GCPs.
+3. Projecting the image onto the DSM using the camera parameters.
 
-Recently, researchers have developed some georectification methods to use ground-based photographs in glaciology (\cite{Messerli2015GeoInst}) and snow cover studies (\cite{Portenier2020Cryosphere}).
-Especially, \cite{Portenier2020Cryosphere} is worth mentioning for its semi-automatic method using mountain silhouettes as GCPs since setting GCPs in alpine region is not easy.
-However, this silhouette-based method has a drawback in the projection accuracy.
-It only uses limited areas (silhouettes) of images in the GCP acquisition, and also it ignores lens distortion.
-Because our target site has a complex vegetation distribution and our camera has considerable lens distortion, we needed a more accurate method.
+Recently, researchers have developed some georectification methods to use ground-based photographs in glaciology (\cite{Messerli2015GeoInst}, \cite{Hulton2020PyTrx}) and snow cover studies (\cite{Portenier2020Cryosphere}).
+Usually, GNSS-positioned GCPs (such as GCP markers) are set before photo acquisition to acquire GCPs.
+However, setting such markers in alpine areas is often difficult due to their rugged topology.
+(\cite{Portenier2020Cryosphere}) tackled this problem by developing a method that uses mountain silhouettes to match images and DSMs directly.
+However, this silhouette-based method has a drawback in projection accuracy.
+It ignores lens distortion and only uses limited areas (silhouettes) of images in the GCP acquisition.
+To overcome these challenges, This study proposes 1.
+a camera model which includes lens distortion and 2.
+a novel method to acquire GCPs in a broader area than the silhouette-based method.
 
@@
 
-As we mentioned before, we modeled a camera as a function that transforms the geographical coordinates of the target mountain into the image coordinates in the acquired image.
-We implemented this procedure using the OpenGL framework (<https://www.opengl.org/>) to accelerate it with graphical processing units (GPUs).
+In this section, we explain our camera model with lens distortion modeling.
+As mentioned, we modeled a camera as a function that transforms geographical coordinates into image coordinates.
+We implemented this procedure using the OpenGL framework (https://www.opengl.org) and the ModernGL Python library (\cite{moderngl}) to accelerate it with graphical processing units (GPUs).
 In OpenGL, we can divide this process into three operations:
@@
 1.
-Transforming the world (geographical) coordinates to the view coordinates (coordinates seen from the camera's point of view) using the camera's extrinsic parameters (i.e., the location and angles of the camera).
-\
-2. Distorting the view coordinates using the lens distortion parameters. \
-3. Transforming the view coordinates to the screen (image) coordinates using the camera's intrinsic parameters (i.e., the FoV of the camera).
+Transforming the geographical coordinates (also called the world coordinates) to the view coordinates (coordinates seen from the camera's point of view) using the camera's extrinsic parameters (i.e., the location and angles of the camera).
+2. Distorting the view coordinates using the lens distortion parameters.
+3. Transforming the view coordinates to the image coordinates (also called the screen coordinates) using the camera's intrinsic parameters (i.e., the camera's FoV).
 
-First, we transformed the absolute geographic coordinates (also known as the world coordinates) into the view coordinates relative to the camera's position and direction.
-We applied a $4 \times 4$ view matrix $M_{view}$ (\ref{view_matrix}) to the geographic coordinates in this step.
+First, we transformed the geographic coordinates into the view coordinates, which are relative to the camera's position and direction.
+We used a $4 \times 4$ view matrix (\ref{view_matrix}) $M_{view}$ in this step.
 The view matrix represents the camera's position and direction (pan, tilt, roll).
-The geographic coordinate system must be cartesian (such as the UTM coordinate systems).
 
@@
 Where $pan, tilt, roll$ are the Euler angles of the camera pose and $x, y, z$ are the camera location in the geographic coordinate system.
-Then, we can transform the geographic coordinates of the DSM $\begin{bmatrix} X_{geo} & Z_{geo} & Y_{geo} & 1 \end{bmatrix}$ to the view coordinates $\begin{bmatrix} X_{view} & Z_{view} & Y_{view} & 1 \end{bmatrix}$ applying the view matrix $M_{view}$ (\ref{view_tf}).
+Applying the view matrix $M_{view}$ transforms the geographic coordinates  $\begin{bmatrix} X_{geo} & Z_{geo} & Y_{geo} & 1 \end{bmatrix}$ (the horizontal, vertical, and depth coordinates, respectively) into the view coordinates $\begin{bmatrix} X_{view} & Z_{view} & Y_{view} & 1 \end{bmatrix}$ (\ref{view_tf}).
 In the OpenGL's view coordinate system, $X_{view}$, $Z_{view}$ and $Y_{view}$ represents horizontal, vertical, and depth positions respectively.
+Note that the geographic coordinate system must be cartesian (such as the UTM coordinate systems, not the lat/long coordinate system).
 
@@
 
-Second, we distorted the camera coordinates to simulate the lens distortion.
+Second, we distorted the view coordinates to simulate the lens distortion.
 We modeled the lens distortion (\ref{dist_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation (<https://docs.opencv.org/4.x/d9/d0c/group__calib3d.html>), where $X_{norm}$ and $Z_{norm}$ are the $Y$-normalized view coordinates.
@@
   \begin{gathered}
-  X_{norm} = \frac{X_{camera}}{Y_{camera}} \\
-  Z_{norm} = \frac{Z_{camera}}{Y_{camera}} \\
+  X_{norm} = \frac{X_{view}}{Y_{view}} \\
+  Z_{norm} = \frac{Z_{view}}{Y_{view}} \\
   r^2 = {X_{norm}}^2 + {Z_{norm}}^2 \\
@@
     Z_{norm} \frac{1 + a_1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + a_2 + k_4 r^2 + k_5 r^4 + k_6 r^6} + p_1 (r^2 + 2 y’^2) + 2 p_2 x’ y’ + s_3 r^2 + s_4 r^4 \\    \end{bmatrix} \\
-  X_{dist} = X_{dist\_norm} Y_{camera} \\
-  Z_{dist} = Z_{dist\_norm} Y_{camera} \\
+  X_{dist} = X_{dist\_norm} Y_{view} \\
+  Z_{dist} = Z_{dist\_norm} Y_{view} \\
   \end{gathered}
@@
 
-Next, we transformed the distorted view coordinates to the image coordinates by perspective projection.
+Lastly, we transformed the distorted view coordinates into the image coordinates by perspective projection.
 During the perspective projection, a closer object is drawn larger.
 We used a $4 \times 4$ projection matrix $M_{proj}$ (\ref{proj_mat}), that represents the camera's horizontal ($fov_x$) and vertical ($fov_z$) FoV.
-Finally, we can get the image coordinates of the points as $X_{image}, Z_{image}$ (\ref{proj_tf}).
+Finally, we got the image coordinates as $X_{image}, Z_{image}$ (\ref{proj_tf}).
 
@@
 
-Applying these procedures to the GCPs' geographical coordinates, we can calculate the reprojected image coordinates with a set of camera parameters (the camera location, pose, FoV, and lens distortion parameters).
+## Image-matching-based aqcuisition of GCPs
+
+The second weak point of the previous silhouette-based method is a low georectification accuracy on the mountainside.
+We developed a novel image-matching-based method to acquire GCPs in a broader area.
+Before processing, an orthorectified airborne/satellite image (orthophoto) and a DSM that covers the camera's field of view, and a set of initial camera parameters (roughly estimated camera parameters) should be prepared.
+Our method consists of two parts: 1.
+rendering a simulated landscape image and 2.
+matching the simulated and original image.
+In the first step, we rendered a simulated landscape image by applying the camera model to the DSM and orthophoto.
+Every pixel of this simulated image has a geographic coordinate.
+In the second step, we searched for matching key points between the original image and the simulated image (\ref{fig:matched}) by the same AKAZE feature-based method used in the image-to-image-alignment process.
+Since these matching points have both geographical coordinates (from the DSM) and image coordinates (from the original image), we used them as GCPs.
+This method enables us to acquire GCPs in a much broader area than the silhouette-based method.
+Note that the quality of the DSM and the orthorectification accuracy of the orthophoto may affect the accuracy of GCPs.
+
+(ref:matched) Automatic acquisition of GCPs.
+The original image (left) and the simulated image (right).
+The simulated image was rendered with an orthophoto, DSM, and initial camera parameters.
+Red points show the matching points.
+We used these points as GCPs.
+
+```{r, matched, echo=FALSE, message=FALSE, fig.cap="(ref:matched)", out.width="100%", auto_pdf = TRUE}
+knitr::include_graphics("paper_files/figures/Slide4.jpg")
+```
+
+## Camera parameter estimation
+The acquired GCPs were used to estimate the camera parameters of the image.
+Applying the camera model to the GCPs' geographical coordinates, we can calculate the reprojected image coordinates with a set of camera parameters (the camera location, pose, FoV, and lens distortion parameters).
 Then, we can measure the distance from the actual image coordinates of GCPs ($U, V$ of Fig.
@@
 \ref{fig:optim}).
-We estimated the camera parameters (except camera location) by minimizing this distance using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}, Fig.
-\ref{fig:optim}).
+We estimated the camera parameters (except camera location) by minimizing this distance using the Covariance Matrix Adaptation Evolution Strategy (CMA-ES, (\cite{Hansen2003CMAES}), Fig.
+\ref{fig:optim}), which performs well in optimizing a multimodal, complex function with less parameters to be set.
 We could not estimate the camera location because it makes the problem too complicated (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).
@@
 
-## Image-matching-based aqcuisition of GCPs
-
-Usually, GNSS-positioned GCPs (such as GCP markers) are set before photo acquisition to get a georeferenced image, however, setting such markers in alpine areas are often tough due to the harsh topology.
-\cite{Portenier2020Cryosphere} solved this problem by developing a method that uses mountain silhouettes to match images and DEMs.
-Its weak point is that the georectification accuracy is sometimes low in the mountainside, where no GCPs are set.
-We developed an novel method that uses  an orthorectified airborne image to get matching points between images and DSMs in a broader area.
-
-First, an airborne image and a DSM that covers the camera's field of view, and a set of initial camera parameters (roughly estimated camera parameters) were prepared.
-We rendered a simulated landscape image by applying the camera model to these.
-Since the simulated image is consists of georeferenced DEM and airborne image, every pixel has a geographic coordinate.
-Then we searched matching points between the original image and the simulated image using AKAZE local feature matcher  (Fig.
-\ref{fig:matched}).
-Since these matching points have both geographical coordinates (from the DSM) and image coordinates (from the original image), we used these points as GCPs.
-This method enables us to acquire GCPs in much broader area than the previous method.
-Our procedure requires the camera's exact location and initial camera parameters to render the simulated image.
-Note that the orthorectification accuracy of the airborne image may affect the georectification accuracy.
-
-(ref:matched) The original image (left) and the simulated image (right).
-The simulated image was rendered with an orthophoto, DSM, and initial camera parameters.
-Red points show the matching points found by the AKAZE local feature matcher.
-We used these points as GCPs.
-
-```{r, matched, echo=FALSE, message=FALSE, fig.cap="(ref:matched)", out.width="100%", auto_pdf = TRUE}
-knitr::include_graphics("paper_files/figures/Slide4.jpg")
-```
-
 ## Georectification of the vegetation map
-(ref:georec) Our georectification procedure. We applied the optimized camera parameters to the DSM and the vegetation classification result to get a vegetation map.
+(ref:georec) Our georectification procedure. We applied the optimized camera parameters to the DSM and the vegetation classification result to get a vegetation classification map.
 
@@
 
-Finally, we georectified the vegetation classification result using the optimized camera parameters (Fig.
+At last, we georectified the vegetation classification result using the optimized camera parameters (Fig.
 \ref{fig:georec}).
 At this point, we got the point data of vegetation (as shown in the table on the right of Fig.
-\ref{fig:georec}) that every row represents a pixel of the original image.
+\ref{fig:georec}) which every row represents a pixel of the original image.
 To measure the area of each vegetation class, we converted the point data to raster data.
 We rasterized the point data in 1 m resolution, then interpolated holes up to 2 m since the maximum pixel footprint was about 2 m on the ridge of the mountain.
-We implemented these procedure using R language \cite{RCore}, `stars` package \cite{Rstars} and `terra` \cite{Rterra} package.
-See <https://github.com/0kam/VegetationMapPaper/blob/master/scripts/utils/interpolate.R> for the source code.
+This rasterization procedure was implemented using the R language (R Core Team, 2022), the “stars” package (Pebesma, 2022), and the “terra” (J Hijmans, 2022) package.
+See https://github.com/0kam/VegetationMapPaper/blob/master/scripts/utils/interpolate.R for the source code.
 
@@
 
-We implemented the algorithm with Python3 language and published it as an open-source package via GitHub (<https://github.com/0kam/alproj>).
-We used an airborne photograph taken in the October of 2014 with a spatial resolution of 1.0 m.
-Also, we used the 1m resolution Digital Surface Model that was also used in the orthorectification process of the airborne photograph.
+We implemented the procedure with Python3 language and published it as an open-source package via GitHub (<https://github.com/0kam/alproj>).
+We used an airborne image taken in October 2014 with a spatial resolution of 1.0 m.
+Also, we used the 1m resolution Digital Surface Model that was also used in the orthorectification process of the airborne image.
 
 # Results
-
 ## Vegetation classification accuracy
 
-We evaluated the performance of the vegetation classifier using a 5-fold cross-validation design.
-Each fold was stratified with the vegetation categories.
-We used F1-score, a standard metric in machine learning evaluation (\ref{metrics}), where $TP, FP, FN$ is true positives, false positives, and false negatives, respectively.
-
-```{=tex}
-\begin{align}
-\label{metrics}
-  \begin{gathered}
-  precision = \frac{TP}{TP + FP} \\
-  recall = \frac{TP}{TP + FN} \\
-  F_1 = \frac{2 \cdot precision \cdot recall}{precision + recall} \\
-  \end{gathered}
-\end{align}
-```
-
-(ref:vegeacc) F1-scores of vegetation classification.
+(ref:vegeacc) F1-scores of the vegetation classification.
 F1-score was calculated for each vegetation class.
-Each box shows the results of a 5-fold cross-validation.
-We classified vegetation using a single image (shown as the shooting date) with SVM classifiers and all images with SVM (shown as "Multidays") and RNN (shown as "Multidays RNN") classifiers.
+Each box plot shows the results of a 5-fold cross-validation.
+We classified each pixel of single image (shown as the shooting date) with SVM classifiers and pixel time-seriese with SVM (shown as "Multidays") and RNN (shown as "Multidays RNN") classifiers.
 
 ```{r, vegeacc, echo=FALSE, message=FALSE, fig.cap="(ref:vegeacc)", out.width="100%", auto_pdf = TRUE}
-knitr::include_graphics("../results/cv.png")
+knitr::include_graphics("paper_files/figures/cv.png")
 ```
@@
 \ref{fig:vegeacc} shows the results of the 5-fold cross-validation.
-Focusing on the single image classification (shown as the shooting date), the best date for classification was different among classes.
-For example, 26th Sep was the best for identifying rowans, but 10th Oct was for dwarf pines and dwarf bamboos.
-Note that the autumn colorization of rowan leaves was at best on 26th Sep, and the most vegetation except dwarf bamboo and dwarf pine were blasted on 10th Oct.
-No single image can classify birch and montane alder accurately.
+Focusing on the single pixel classification (shown as the shooting date), the best date for classification was different among classes.
+For example, 26th Sep was the best for identifying Rowans, but 10th Oct was for Dwarf Pine and Dwarf Bamboo.
+The autumn colorization of Rowans was at best on 26th Sep, and most vegetation except Dwarf Bamboo and Dwarf Pine were blasted on 10th Oct.
+No single image can classify Maple and Montane Alder accurately.
 In contrast, using all images (shown as "Multidays" and "Multidays RNN" representing the SVM and RNN classifiers, respectively) resulted in a high F1 score in every class.
@@
 \ref{fig:vegetation} (left) shows the products of the RNN classifier.
-We can observe the distribution of each vegetation classes at the plant-community scale.
+We can observe the distribution of each vegetation class at the plant-community scale.
 
 ## Georectification accuracy
-We tested our georectification method's accuracy and evaluated its two features' effects: using the simulated image and image matching to acquire GCPs, and modeling the lens distortion.
+We tested the accuracy of our georectification method and evaluated the effect of its two features: using the simulated image and image matching to acquire GCPs and modeling the lens distortion.
 We manually searched 83 matching points between the simulated and original images and treated them as the test GCPs: GCPs that are not used in the georectification process.
 We additionally prepared two comparison methods to test the performance of the proposed method.
-The first one is the silhouette-based matching method (after this called silhouette) used in previous studies (\cite{Portenier2020Cryosphere}).
+The first one is the silhouette-based matching method (after called the silhouette method) used in previous studies (\cite{Portenier2020Cryosphere}).
 The second is the proposed method without the lens distortion model (after this called no distortion).
@@
 The proposed method achieves accurate projection (3.45 m as the root mean square error) while the other two did not (16.1 m with silhouette, 23.6 m with no distortion).
-We estimated the lens distortion parameters in the silhouette method.
-Fig.
-\ref{fig:geoacc} shows the relationship between the projection error of the proposed method and the test GCPs' distance from the shooting point.
+Note that while (Portenier et al., 2020) does not consider lens distortion, we did in the silhouette method.
+To investigate the tendency of our method’s georectification error, we also checked the relationship between the projection error and the distance from the shooting point for each test GCP (Fig.
+\ref{fig:geoacc}).
 The projection error was especially large in the GCPs near the shooting point.
-Note that the projection errors were measured ignoring the georectification error of the orthophoto and the DSM.
 Fig.
@@
 ```{r, geoacc, echo=FALSE, message=FALSE, fig.cap="(ref:geoacc)", out.width="100%", auto_pdf = TRUE}
-knitr::include_graphics("../results/georec_acc.png")
+knitr::include_graphics("paper_files/figures/georec_acc.png")
 ```
@@
 
-We suggested a fully automated procedure to transform time-lapse images of an alpine region into a georeferenced vegetation map at a meager cost.
+We suggested an automated procedure to transform time-lapse images of an alpine region into a georeferenced vegetation map at a meager cost.
 This task is challenging because of 1.
@@
 Many plant species have characteristic phenologies, such as autumn foliage, and the suitable season to observe them differs among species.
-The result (Fig.
-\ref{fig:vegeacc}) shows that each vegetation class has its suitable timing to identify it in photographs.
-Classifying multiple vegetation classes requires long-term (such as several months long) and frequent (such as daily) monitoring, and digital time-lapse cameras are suitable.
-In addition, combining multi-temporal images improved the classification accuracy, especially with Birch and Montane Alder (Fig.
-\ref{fig:vegeacc}).
-The best F1 score was low with single image classification (0.750 for Montane Alder, 0.345 for Birch), and using multi-temporal images improves them much (0.951 and 0.781 with the SVM classifier).
-This result shows that identifying these vegetation requires multi-temporal information.
+The accuracy of the single-pixel classification (shown in the shooting date in Fig.
+\ref{fig:vegeacc}) shows that each vegetation class has suitable timing to identify it in photographs.
+Classifying multiple vegetation classes requires a long-term (such as several months long) and frequent (such as daily) monitoring, and digital time-lapse cameras are suitable.
+In addition, combining multi-temporal images improved the classification accuracy, especially with Maple and Montane Alder.
+The best F1 score was low with single pixel classification (0.750 for Montane Alder, 0.345 for Maple), and using multi-temporal images improves them much (0.951 and 0.781 with the SVM classifier).
+This result shows that identifying these classes requires multi-temporal information.
 The inter-community heterogeneity of autumn foliage timing in these species may cause this result.
-As the previous study pointed out (\cite{Ienco2017RemSenLSTM}), the RNN model outperformed the SVM model, particularly in identifying Birch (0.781 with SVM and 0.831 with RNN).
+As the previous study pointed out (\cite{Ienco2017RemSenLSTM}), the RNN model outperformed the SVM model, particularly in identifying Maple (0.781 with SVM and 0.831 with RNN).
 Our model can still be further improved.
-As \cite{Sharma2018NN} claimed, the patch-based classification method may improve the performance.
+As (\cite{Sharma2018NN}) claimed, the patch-based classification method may improve the performance.
 Such patch-based models take a time series of small patches as an input to utilize the spatial information, such as textures, in the classification process.
@@
 Note that the proposed lens distortion model does not support a fisheye lens and omnidirectional camera.
-Another feature of our method is the automatic acquisition of GCPs using simulated images and image matching techniques.
+Another feature of our method is the automatic acquisition of GCPs using simulated images and image-matching techniques.
 This method requires a high-resolution orthophoto that covers the camera's field of view.
-This costs a bit; however, the reward is considerable.
+This costs a bit but the reward is considerable.
 Using simulated images in GCP acquisition also improved the georectification accuracy; the conventional silhouette-based method resulted in an RMSE of 16.1 m.
 This result suggests that acquiring matching points between the image and the DSM in a broader area benefits the camera parameter estimation process.
-However, the proposed method (AKAZE image matcher) could not acquire matching points in the area near the camera, and the projection error was relatively large (Fig.
+Our method assumes that the landscape (e.g., topography and vegetation cover) looks the same between the original image and the simulated image.
+While we employed a robust matching method, large changes in mountain terrain (such as landslides) may cause a matching error.
+Slight changes in vegetation cover will also affect the quality of GCPs.
+However, the negative effect of it (a few meters) should be much smaller than the positive effect (about 13 m) of using these points as GCPs.
+The proposed method (AKAZE image matcher) could not acquire matching points in the area near the camera, and the projection error was relatively large (Fig.
 \ref{fig:geoacc}).

### 2022-11-24 paper/paper.tex
modified paper

@@
 
-\hypertarget{introduction-1}{%
-\section{Introduction}\label{introduction-1}}
-
 The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (\cite{IPCC2007}).
@@
 Climate change has also affected the growth and phenologies of native species.
-For example, the growth of dwarf pine (\emph{Pinus pumila}), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}).
-In addition, researchers have reported that such changes vary depending on species and microhabitats (\cite{Kudo2010AAA}, \cite{XXXXXX}).
+For example, the growth of dwarf pine (\emph{Pinus pumila}), a dominant species in Japanese alpine regions, have been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}).
+In addition, researchers have reported that such changes vary depending on species and microhabitats (\cite{Kudo2010AAA}).
 Understanding and predicting the undergoing changes of alpine vegetation requires a monitoring method scalable to a wide range with a spatially and temporally high resolution.
@@
 
-Our method is intended for digital time-lapse images of alpine landscapes.
-In this study, we used time-lapse photos of a Japanese alpine region owned by the National Institute for Environmental Studies, Japan (NIES).
+Our approach is intended for digital time-lapse images of alpine landscapes.
+In this study, we demonstrated it with time-lapse photos of a Japanese alpine region owned by the National Institute for Environmental Studies, Japan (NIES).
 All the images are publically available on NIES' webpage (\url{https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2}).
@@
 
-We selected seven images from late summer to late fall (8/25, 9/5, 9/12, 9/20, 9/26, 10/3, and 10/10) in 2015.
-Since the temporal patterns of autumn foliage coloration vary among species (see Fig.
+In the beginning, we selected seven images with good weather from late summer to late fall (25th Aug, 5th, 12th, 20th, 26th Sep, 3rd, and 10th Oct) in 2015.
+Since the temporal patterns of autumn foliage coloration vary among species (Fig.
 \ref{fig:pixtimeseries}), this season is suitable for classifying vegetation.
 While acquiring a series of images costs a lot with UAVs and airborne imagery, time-lapse cameras are particularly good at observing such temporal patterns of leaf color.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{paper_files/figures/Slide1} \caption{Pixel time series acquired from the time-lapse camera.
+You can obtain a time series of pixel values (i.e., Red, Green, and Blue) for each pixel on the photographs (left).
+Such pixel time series reflects the autumn phenology of the vegetation and varies among vegetation classes (right).}\label{fig:pixtimeseries}
+\end{figure}
 
@@
 
-Although the camera is fixed on the mountain lodge, the images are slightly misalighned do to the wind.
-To handle this issue, we aligned the images before processing using Python3 programming language and OpenCV4 (\url{https://opencv.org/}) image processing library.
-First, one image of 2015 were set as the alignment target.
-Next, we automatically matched key points between the target and other images using the AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
-Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's ``findHomography'' function.
+Time-lapse images often suffer from the camera's movement caused by strong wind, human interference, and thermal expansion of the camera platform.
+Since such movement can cause errors in vegetation classification and georectification, we implemented an alignment method that aligns each image to one image called the master image.
+The software was developed using Python3 programming language and OpenCV4 (\url{https://opencv.org/}) image processing library.
+We employed a feature-based alignment method used by previous studies (\cite{Hulton2020PyTrx}, \cite{Portenier2020Cryosphere}).
+First, we searched and matched key points between an image and the master image using the AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and K-nearest neighbor matcher.
+Then, we searched and applied the homography matrix that minimizes the distance between each pair of the matching points, using OpenCV's ``findHomography'' function (\ref{homography}).
 Applying the estimated homography matrix, we could align the images accurately (0.654 pixels in root mean square error (RMSE) of the matching points).
-Finally, an input mask were applied to define image regions that should be ignored in the following procedure, such as the sky and the regions too close to the camera.
-This process ensures that a set of pixel time-series reflects a phenological information of a same location, which is essential in the vegetation classification process.
+Finally, an input mask was applied to define image regions that should be ignored in the following procedure, such as the sky and the regions too close to the camera.
+This process ensures that a set of pixel time series reflects phenological information of the same location, which is essential in the vegetation classification process.
 
-\hypertarget{automatic-vegetation-classification}{%
-\subsection{Automatic vegetation classification}\label{automatic-vegetation-classification}}
+\label{homography}
+\begin{equation}
+  \begin{bmatrix} 
+    u' \\ v' \\ w'
+  \end{bmatrix}
+  =
+  H
+  \begin{bmatrix} 
+    u \\ v \\ w 
+  \end{bmatrix}
+\end{equation}
 
-Because the images were aligned succesfuly, we can stack the images and extract a time series of pixel values (Red, Green, and Blue, Fig.
+\hypertarget{vegetation-classification}{%
+\subsection{Vegetation classification}\label{vegetation-classification}}
+
+After the image-to-image alignment, we stuck the images and extract a time series of pixel values (Red, Green, and Blue, see Fig.
 \ref{fig:pixtimeseries}) for each pixel.
 Such pixel time series reflects the temporal patterns of leaf colors.
-Because deciduous plants have great differences in autumn leaf phenology among species, researchers have used that information for vegetation classification with satellite imagery (\cite{Tigges2013RemSenEnv}, \cite{Son2013RemSen}, \cite{Heupel2018PFG}).
+Because deciduous plants have great differences in autumn leaf phenology among species, researchers have used that information for vegetation classification with satellite imagery (\cite{Son2013RemSen}, \cite{Tigges2013RemSenEnv}, \cite{Heupel2018PFG}).
 However, no research has applied this technique to ground-based time-lapse imagery.
-We implemented Support Vector Machine (SVM) and Recurrent Neural Network (RNN) based vegetation classifiers, and tested the effects of using pixel time series of the ground-based imagery on the classification performance.
-
-\begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figures/Slide1} \caption{Pixel time series acquired from the time-lapse camera.
-You can obtain a time series of pixel values (i.e., Red, Green, and Blue) for each pixel on the photographs.
-Such pixel time series reflects the autumn phenology of the vegetation.}\label{fig:pixtimeseries}
-\end{figure}
+We implemented Support Vector Machine (SVM) and Recurrent Neural Network (RNN) based vegetation classifiers and tested the effects of using pixel time series of the ground-based imagery on the classification performance.
 
@@
 
-We set 7 vegetation classes: Dwarf Pine (\emph{Pinus pumila}), Dwarf Bamboo (\emph{Sasa kurilensis}), Rowans (\emph{Sorbus sambucifolia}, \emph{Sorbus matsumurana}), Birch (\emph{Betula ermanii}), Alder (\emph{Alnus viridis} subsp.
+Each pixel time series was classified into 7 vegetation classes: Dwarf Pine (\emph{Pinus pumila}), Dwarf Bamboo (\emph{Sasa kurilensis}), Rowans (\emph{Sorbus sambucifolia}, \emph{Sorbus matsumurana}), Maple (\emph{Acer tschonoskii}), Montane Alder (\emph{Alnus viridis} subsp.
 \emph{maximowiczii}), Other Vegetations (such as alpine shrubs and herbaceous plants), and No Vegetation.
-Using an open-source image annotation software (Semantic Segmentation Editor, Hitachi, \url{https://github.com/Hitachi-Automotive-And-Industry-Lab/semantic-segmentation-editor}), an expert prepared a teacher dataset for each class.
-Then we validated the teacher dataset with a set of telephotos taken in the summer and fall of 2016.
+Experts prepared a teacher dataset for each class using an open-source image annotation software (Semantic Segmentation Editor, Hitachi, \url{https://github.com/Hitachi-Automotive-And-Industry-Lab/semantic-segmentation-editor}).
+The prepared teacher dataset contains XX pixels in XX polygons, which covers about X\% of the image.
+Each polygon was validated with telephotos taken at the same place in 2016.
+For some polygons that were not seen clearly even in the telephoto, we conducted a field survey in the November of 2022.
 
-\hypertarget{implementation-and-model-training}{%
-\subsubsection{Implementation and model training}\label{implementation-and-model-training}}
+\hypertarget{experimental-settings}{%
+\subsubsection{Experimental Settings}\label{experimental-settings}}
 
-We implemented the classifier with Python3 language, ThunderSVM library (\url{https://github.com/Xtra-Computing/thundersvm}) for the SVM classifier, and PyTorch deep neural network library (\url{https://pytorch.org/}) for the RNN classifier.
-All source codes are publically available via GitHub (\url{https://github.com/0kam/VegetationMapPaper}).
+We implemented the classifiers with Python3 language.
+For the SVM classifier, we used the ThunderSVM library (\url{https://github.com/Xtra-Computing/thundersvm}) and an RBF kernel with a regularization parameter equal to 1.0.
+The gamma value was set automatically by the ``scaled`` setting of the ThunderSVM library as \(\gamma = \frac{1}{n_{features} \times V(X)}\), where and stand for the dimensions and variance of the input data respectively.
+The RNN classifier was developed using the PyTorch deep neural network library (\url{https://pytorch.org/}).
+We set the number of hidden dimensions equal to 5.
+We trained the model 200 epochs with the RAdam optimizer (\cite{Liu2020RAdam}) with a learning rate of 0.001 and a batch size of 500.
+To validate the performance of the different classifiers, we performed a 5-fold cross-validation.
+Each fold was stratified with the vegetation categories.
+As a model evaluation metric, we used the per-class F1-score, a standard metric in machine learning (\ref{f1score}).
+\(TP, FP, FN\) stand for the numbers of true positives, false positives, and false negatives, respectively.
+All source codes are available via GitHub (\url{https://github.com/0kam/VegetationMapPaper}).
+
+\label{f1score}
+\begin{align}
+\label{metrics}
+  \begin{gathered}
+  precision = \frac{TP}{TP + FP} \\
+  recall = \frac{TP}{TP + FN} \\
+  F_1 = \frac{2 \cdot precision \cdot recall}{precision + recall} \\
+  \end{gathered}
+\end{align}
 
@@
 \item
-  Finding Ground Control Points (GCPs) in the image.\\
+  Finding Ground Control Points (GCPs) in the image.
 \item
-  Estimating the camera parameters such as camera poses and FoV using GCPs.\\
+  Estimating the camera parameters such as the camera pose and FoV using GCPs.
 \item
-  Projecting the DSM into the image using the camera parameters.
+  Projecting the image onto the DSM using the camera parameters.
 \end{enumerate}
 
-Recently, researchers have developed some georectification methods to use ground-based photographs in glaciology (\cite{Messerli2015GeoInst}) and snow cover studies (\cite{Portenier2020Cryosphere}).
-Especially, \cite{Portenier2020Cryosphere} is worth mentioning for its semi-automatic method using mountain silhouettes as GCPs since setting GCPs in alpine region is not easy.
-However, this silhouette-based method has a drawback in the projection accuracy.
-It only uses limited areas (silhouettes) of images in the GCP acquisition, and also it ignores lens distortion.
-Because our target site has a complex vegetation distribution and our camera has considerable lens distortion, we needed a more accurate method.
+Recently, researchers have developed some georectification methods to use ground-based photographs in glaciology (\cite{Messerli2015GeoInst}, \cite{Hulton2020PyTrx}) and snow cover studies (\cite{Portenier2020Cryosphere}).
+Usually, GNSS-positioned GCPs (such as GCP markers) are set before photo acquisition to acquire GCPs.
+However, setting such markers in alpine areas is often difficult due to their rugged topology.
+(\cite{Portenier2020Cryosphere}) tackled this problem by developing a method that uses mountain silhouettes to match images and DSMs directly.
+However, this silhouette-based method has a drawback in projection accuracy.
+It ignores lens distortion and only uses limited areas (silhouettes) of images in the GCP acquisition.
+To overcome these challenges, This study proposes 1.
+a camera model which includes lens distortion and 2.
+a novel method to acquire GCPs in a broader area than the silhouette-based method.
 
@@
 
-As we mentioned before, we modeled a camera as a function that transforms the geographical coordinates of the target mountain into the image coordinates in the acquired image.
-We implemented this procedure using the OpenGL framework (\url{https://www.opengl.org/}) to accelerate it with graphical processing units (GPUs).
+In this section, we explain our camera model with lens distortion modeling.
+As mentioned, we modeled a camera as a function that transforms geographical coordinates into image coordinates.
+We implemented this procedure using the OpenGL framework (\url{https://www.opengl.org}) and the ModernGL Python library (\cite{moderngl}) to accelerate it with graphical processing units (GPUs).
 In OpenGL, we can divide this process into three operations:
@@
 \item
-  Transforming the world (geographical) coordinates to the view coordinates (coordinates seen from the camera's point of view) using the camera's extrinsic parameters (i.e., the location and angles of the camera).\\
+  Transforming the geographical coordinates (also called the world coordinates) to the view coordinates (coordinates seen from the camera's point of view) using the camera's extrinsic parameters (i.e., the location and angles of the camera).
 \item
-  Distorting the view coordinates using the lens distortion parameters.\\
+  Distorting the view coordinates using the lens distortion parameters.
 \item
-  Transforming the view coordinates to the screen (image) coordinates using the camera's intrinsic parameters (i.e., the FoV of the camera).
+  Transforming the view coordinates to the image coordinates (also called the screen coordinates) using the camera's intrinsic parameters (i.e., the camera's FoV).
 \end{enumerate}
 
-First, we transformed the absolute geographic coordinates (also known as the world coordinates) into the view coordinates relative to the camera's position and direction.
-We applied a \(4 \times 4\) view matrix \(M_{view}\) (\ref{view_matrix}) to the geographic coordinates in this step.
+First, we transformed the geographic coordinates into the view coordinates, which are relative to the camera's position and direction.
+We used a \(4 \times 4\) view matrix (\ref{view_matrix}) \(M_{view}\) in this step.
 The view matrix represents the camera's position and direction (pan, tilt, roll).
-The geographic coordinate system must be cartesian (such as the UTM coordinate systems).
 
@@
 Where \(pan, tilt, roll\) are the Euler angles of the camera pose and \(x, y, z\) are the camera location in the geographic coordinate system.
-Then, we can transform the geographic coordinates of the DSM \(\begin{bmatrix} X_{geo} & Z_{geo} & Y_{geo} & 1 \end{bmatrix}\) to the view coordinates \(\begin{bmatrix} X_{view} & Z_{view} & Y_{view} & 1 \end{bmatrix}\) applying the view matrix \(M_{view}\) (\ref{view_tf}).
+Applying the view matrix \(M_{view}\) transforms the geographic coordinates \(\begin{bmatrix} X_{geo} & Z_{geo} & Y_{geo} & 1 \end{bmatrix}\) (the horizontal, vertical, and depth coordinates, respectively) into the view coordinates \(\begin{bmatrix} X_{view} & Z_{view} & Y_{view} & 1 \end{bmatrix}\) (\ref{view_tf}).
 In the OpenGL's view coordinate system, \(X_{view}\), \(Z_{view}\) and \(Y_{view}\) represents horizontal, vertical, and depth positions respectively.
+Note that the geographic coordinate system must be cartesian (such as the UTM coordinate systems, not the lat/long coordinate system).
 
@@
 
-Second, we distorted the camera coordinates to simulate the lens distortion.
+Second, we distorted the view coordinates to simulate the lens distortion.
 We modeled the lens distortion (\ref{dist_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation (\url{https://docs.opencv.org/4.x/d9/d0c/group__calib3d.html}), where \(X_{norm}\) and \(Z_{norm}\) are the \(Y\)-normalized view coordinates.
@@
 
-Next, we transformed the distorted view coordinates to the image coordinates by perspective projection.
+Lastly, we transformed the distorted view coordinates into the image coordinates by perspective projection.
 During the perspective projection, a closer object is drawn larger.
 We used a \(4 \times 4\) projection matrix \(M_{proj}\) (\ref{proj_mat}), that represents the camera's horizontal (\(fov_x\)) and vertical (\(fov_z\)) FoV.
-Finally, we can get the image coordinates of the points as \(X_{image}, Z_{image}\) (\ref{proj_tf}).
+Finally, we got the image coordinates as \(X_{image}, Z_{image}\) (\ref{proj_tf}).
 
@@
 
-Applying these procedures to the GCPs' geographical coordinates, we can calculate the reprojected image coordinates with a set of camera parameters (the camera location, pose, FoV, and lens distortion parameters).
+\hypertarget{image-matching-based-aqcuisition-of-gcps}{%
+\subsection{Image-matching-based aqcuisition of GCPs}\label{image-matching-based-aqcuisition-of-gcps}}
+
+The second weak point of the previous silhouette-based method is a low georectification accuracy on the mountainside.
+We developed a novel image-matching-based method to acquire GCPs in a broader area.
+Before processing, an orthorectified airborne/satellite image (orthophoto) and a DSM that covers the camera's field of view, and a set of initial camera parameters (roughly estimated camera parameters) should be prepared.
+Our method consists of two parts: 1.
+rendering a simulated landscape image and 2.
+matching the simulated and original image.
+In the first step, we rendered a simulated landscape image by applying the camera model to the DSM and orthophoto.
+Every pixel of this simulated image has a geographic coordinate.
+In the second step, we searched for matching key points between the original image and the simulated image (\ref{fig:matched}) by the same AKAZE feature-based method used in the image-to-image-alignment process.
+Since these matching points have both geographical coordinates (from the DSM) and image coordinates (from the original image), we used them as GCPs.
+This method enables us to acquire GCPs in a much broader area than the silhouette-based method.
+Note that the quality of the DSM and the orthorectification accuracy of the orthophoto may affect the accuracy of GCPs.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{paper_files/figures/Slide4} \caption{Automatic acquisition of GCPs.
+The original image (left) and the simulated image (right).
+The simulated image was rendered with an orthophoto, DSM, and initial camera parameters.
+Red points show the matching points.
+We used these points as GCPs.}\label{fig:matched}
+\end{figure}
+
+\hypertarget{camera-parameter-estimation}{%
+\subsection{Camera parameter estimation}\label{camera-parameter-estimation}}
+
+The acquired GCPs were used to estimate the camera parameters of the image.
+Applying the camera model to the GCPs' geographical coordinates, we can calculate the reprojected image coordinates with a set of camera parameters (the camera location, pose, FoV, and lens distortion parameters).
 Then, we can measure the distance from the actual image coordinates of GCPs (\(U, V\) of Fig.
@@
 
-\hypertarget{image-matching-based-aqcuisition-of-gcps}{%
-\subsection{Image-matching-based aqcuisition of GCPs}\label{image-matching-based-aqcuisition-of-gcps}}
-
-Usually, GNSS-positioned GCPs (such as GCP markers) are set before photo acquisition to get a georeferenced image, however, setting such markers in alpine areas are often tough due to the harsh topology.
-\cite{Portenier2020Cryosphere} solved this problem by developing a method that uses mountain silhouettes to match images and DEMs.
-Its weak point is that the georectification accuracy is sometimes low in the mountainside, where no GCPs are set.
-We developed an novel method that uses an orthorectified airborne image to get matching points between images and DSMs in a broader area.
-
-First, an airborne image and a DSM that covers the camera's field of view, and a set of initial camera parameters (roughly estimated camera parameters) were prepared.
-We rendered a simulated landscape image by applying the camera model to these.
-Since the simulated image is consists of georeferenced DEM and airborne image, every pixel has a geographic coordinate.
-Then we searched matching points between the original image and the simulated image using AKAZE local feature matcher (Fig.
-\ref{fig:matched}).
-Since these matching points have both geographical coordinates (from the DSM) and image coordinates (from the original image), we used these points as GCPs.
-This method enables us to acquire GCPs in much broader area than the previous method.
-Our procedure requires the camera's exact location and initial camera parameters to render the simulated image.
-Note that the orthorectification accuracy of the airborne image may affect the georectification accuracy.
-
-\begin{figure}
-\includegraphics[width=1\linewidth]{paper_files/figures/Slide4} \caption{The original image (left) and the simulated image (right).
-The simulated image was rendered with an orthophoto, DSM, and initial camera parameters.
-Red points show the matching points found by the AKAZE local feature matcher.
-We used these points as GCPs.}\label{fig:matched}
-\end{figure}
-
 \hypertarget{georectification-of-the-vegetation-map}{%
@@
 \includegraphics[width=1\linewidth]{paper_files/figures/Slide6} \caption{Our georectification procedure.
-We applied the optimized camera parameters to the DSM and the vegetation classification result to get a vegetation map.}\label{fig:georec}
+We applied the optimized camera parameters to the DSM and the vegetation classification result to get a vegetation classification map.}\label{fig:georec}
 \end{figure}
 
-Finally, we georectified the vegetation classification result using the optimized camera parameters (Fig.
+At last, we georectified the vegetation classification result using the optimized camera parameters (Fig.
 \ref{fig:georec}).
 At this point, we got the point data of vegetation (as shown in the table on the right of Fig.
-\ref{fig:georec}) that every row represents a pixel of the original image.
+\ref{fig:georec}) which every row represents a pixel of the original image.
 To measure the area of each vegetation class, we converted the point data to raster data.
 We rasterized the point data in 1 m resolution, then interpolated holes up to 2 m since the maximum pixel footprint was about 2 m on the ridge of the mountain.
-We implemented these procedure using R language \cite{RCore}, \texttt{stars} package \cite{Rstars} and \texttt{terra} \cite{Rterra} package.
+This rasterization procedure was implemented using the R language (R Core Team, 2022), the ``stars'' package (Pebesma, 2022), and the ``terra'' (J Hijmans, 2022) package.
 See \url{https://github.com/0kam/VegetationMapPaper/blob/master/scripts/utils/interpolate.R} for the source code.
@@
 
-We implemented the algorithm with Python3 language and published it as an open-source package via GitHub (\url{https://github.com/0kam/alproj}).
-We used an airborne photograph taken in the October of 2014 with a spatial resolution of 1.0 m.
-Also, we used the 1m resolution Digital Surface Model that was also used in the orthorectification process of the airborne photograph.
+We implemented the procedure with Python3 language and published it as an open-source package via GitHub (\url{https://github.com/0kam/alproj}).
+We used an airborne image taken in October 2014 with a spatial resolution of 1.0 m.
+Also, we used the 1m resolution Digital Surface Model that was also used in the orthorectification process of the airborne image.
 
@@
 
-We evaluated the performance of the vegetation classifier using a 5-fold cross-validation design.
-Each fold was stratified with the vegetation categories.
-We used F1-score, a standard metric in machine learning evaluation (\ref{metrics}), where \(TP, FP, FN\) is true positives, false positives, and false negatives, respectively.
-
-\begin{align}
-\label{metrics}
-  \begin{gathered}
-  precision = \frac{TP}{TP + FP} \\
-  recall = \frac{TP}{TP + FN} \\
-  F_1 = \frac{2 \cdot precision \cdot recall}{precision + recall} \\
-  \end{gathered}
-\end{align}
-
 \begin{figure}
-\includegraphics[width=1\linewidth]{../results/cv} \caption{F1-scores of vegetation classification.
+\includegraphics[width=1\linewidth]{paper_files/figures/cv} \caption{F1-scores of the vegetation classification.
 F1-score was calculated for each vegetation class.
-Each box shows the results of a 5-fold cross-validation.
-We classified vegetation using a single image (shown as the shooting date) with SVM classifiers and all images with SVM (shown as ``Multidays'') and RNN (shown as ``Multidays RNN'') classifiers.}\label{fig:vegeacc}
+Each box plot shows the results of a 5-fold cross-validation.
+We classified each pixel of single image (shown as the shooting date) with SVM classifiers and pixel time-seriese with SVM (shown as ``Multidays'') and RNN (shown as ``Multidays RNN'') classifiers.}\label{fig:vegeacc}
 \end{figure}
@@
 \ref{fig:vegeacc} shows the results of the 5-fold cross-validation.
-Focusing on the single image classification (shown as the shooting date), the best date for classification was different among classes.
-For example, 26th Sep was the best for identifying rowans, but 10th Oct was for dwarf pines and dwarf bamboos.
-Note that the autumn colorization of rowan leaves was at best on 26th Sep, and the most vegetation except dwarf bamboo and dwarf pine were blasted on 10th Oct.~No single image can classify birch and montane alder accurately.
+Focusing on the single pixel classification (shown as the shooting date), the best date for classification was different among classes.
+For example, 26th Sep was the best for identifying Rowans, but 10th Oct was for Dwarf Pine and Dwarf Bamboo.
+The autumn colorization of Rowans was at best on 26th Sep, and most vegetation except Dwarf Bamboo and Dwarf Pine were blasted on 10th Oct.~No single image can classify Maple and Montane Alder accurately.
 In contrast, using all images (shown as ``Multidays'' and ``Multidays RNN'' representing the SVM and RNN classifiers, respectively) resulted in a high F1 score in every class.
@@
 \ref{fig:vegetation} (left) shows the products of the RNN classifier.
-We can observe the distribution of each vegetation classes at the plant-community scale.
+We can observe the distribution of each vegetation class at the plant-community scale.
 
@@
 
-We tested our georectification method's accuracy and evaluated its two features' effects: using the simulated image and image matching to acquire GCPs, and modeling the lens distortion.
+We tested the accuracy of our georectification method and evaluated the effect of its two features: using the simulated image and image matching to acquire GCPs and modeling the lens distortion.
 We manually searched 83 matching points between the simulated and original images and treated them as the test GCPs: GCPs that are not used in the georectification process.
 We additionally prepared two comparison methods to test the performance of the proposed method.
-The first one is the silhouette-based matching method (after this called silhouette) used in previous studies (\cite{Portenier2020Cryosphere}).
+The first one is the silhouette-based matching method (after called the silhouette method) used in previous studies (\cite{Portenier2020Cryosphere}).
 The second is the proposed method without the lens distortion model (after this called no distortion).
@@
 The proposed method achieves accurate projection (3.45 m as the root mean square error) while the other two did not (16.1 m with silhouette, 23.6 m with no distortion).
-We estimated the lens distortion parameters in the silhouette method.
-Fig.
-\ref{fig:geoacc} shows the relationship between the projection error of the proposed method and the test GCPs' distance from the shooting point.
+Note that while (Portenier et al., 2020) does not consider lens distortion, we did in the silhouette method.
+To investigate the tendency of our method's georectification error, we also checked the relationship between the projection error and the distance from the shooting point for each test GCP (Fig.
+\ref{fig:geoacc}).
 The projection error was especially large in the GCPs near the shooting point.
-Note that the projection errors were measured ignoring the georectification error of the orthophoto and the DSM.
 Fig.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{../results/georec_acc} \caption{The projection error of the proposed method.
+\includegraphics[width=1\linewidth]{paper_files/figures/georec_acc} \caption{The projection error of the proposed method.
 The projection error was particularly large in the area near the camera.}\label{fig:geoacc}

### 2022-11-24 scripts/analyse.R

@@ -8,7 +8,7 @@ change_names <- function(nums) {
         nums == 2 ~ "Other Vegetation",
         nums == 3 ~ "No Vegetation",
         nums == 4 ~ "Rowans",
-        nums == 5 ~ "Golden Birch",
+        nums == 5 ~ "Maple",
         nums == 6 ~ "Montane Alder",
         nums == 7 ~ "Dwarf Pine"
     )

### 2022-11-24 scripts/draw_product.R

@@ -2,13 +2,13 @@ library(stars)
 library(tidyverse)
 library(ggspatial)
 
-setwd("~/VegetationMapPaper/")
+setwd("~/Projects/VegetationMapPaper/")
 
 cmap = c(
   "#2aa198", # Dwarf pine
   "#859900", # Dwarf bamboo
   "#dc322f", # Rowans
-  "#b58900", # Birch
+  "#b58900", # Maple
   "#6c71c4", # Montane Alder
   "#eee8d5", # Other vegetation
   "#c0c0c0" # No vegetation
@@ -18,7 +18,7 @@ vegetation_levels <- c(
   "Dwarf Pine",
   "Dwarf Bamboo",
   "Rowans",
-  "Birch",
+  "Maple",
   "Montane Alder",
   "Other Vegetation",
   "No Vegetation"
@@ -34,7 +34,7 @@ ras <- read_stars("results/rnn.tiff") %>%
       vegetation == 2 ~ "Other Vegetation",
       vegetation == 3 ~ "No Vegetation",
       vegetation == 4 ~ "Rowans",
-      vegetation == 5 ~ "Birch",
+      vegetation == 5 ~ "Maple",
       vegetation == 6 ~ "Montane Alder",
       vegetation == 7 ~ "Dwarf Pine"
     )
@@ -65,7 +65,7 @@ p1 <- ggplot() +
     plot.background = element_rect(fill = "white")
   )
 
-ggsave("results/vegemap.png", p1, width = 10, height = 10)
+ggsave("results/vegemap.png", p1, width = 12, height = 8)
 
 library(magick)
 rnn <- magick::image_read("results/rnn.png")

### 2022-11-24 scripts/models/model_comparison.R

@@ -4,7 +4,7 @@ library(kableExtra)
 library(fs)
 library(lubridate)
 
-setwd("~/VegetationMapPaper")
+setwd("~/Projects/VegetationMapPaper")
 
 translate_classes <- function(names) {
   res <- c()
@@ -14,7 +14,7 @@ translate_classes <- function(names) {
               "ハイマツ" = "Dwarf Pine",
               "ササ" = "Dwarf Bamboo",
               "ナナカマド" = "Rowans",
-              "ダケカンバ" = "Birch",
+              "ダケカンバ" = "Maple",
               "ミヤマハンノキ" = "Montane Alder",
               "その他植生" = "Other vegetation",
               "無植生" = "Non Vegetation",
@@ -31,7 +31,7 @@ vegetation_levels <- c(
   "Dwarf Pine",
   "Dwarf Bamboo",
   "Rowans",
-  "Birch",
+  "Maple",
   "Montane Alder",
   "Other vegetation",
   "Non Vegetation"

### 2022-11-24 scripts/plot_phenology.R

@@ -1,7 +1,7 @@
 library(tidyverse)
 library(reticulate)
 library(lubridate)
-setwd("~/VegetationMapPaper/")
+setwd("~/Projects/VegetationMapPaper/")
 
 reticulate::source_python("scripts/plot_phenology.py")
 
@@ -13,8 +13,8 @@ change_names <- function(nums) {
     nums == 1 ~ "Other Vegetation",
     nums == 2 ~ "No Vegetation",
     nums == 3 ~ "Rowans",
-    nums == 4 ~ "Golden Birch",
-    nums == 5 ~ "Montane Alder",
+    nums == 4 ~ "Maple",
+    nums == 5 ~ "Alder",
     nums == 6 ~ "Dwarf Pine"
   )
 }
@@ -29,7 +29,8 @@ df %>%
   pivot_longer(cols = c("R", "G", "B"), names_to = "band", values_to = "value") %>% 
   write_csv("results/phenology.csv")
 
-df <- read_csv("results/phenology.csv")
+df <- read_csv("results/phenology.csv") %>%
+  mutate(vegetation = ifelse(vegetation == "Golden Birch", "Maple", vegetation))
 
 p <- df %>%
   mutate(band = factor(band, levels = c("R", "G", "B"))) %>%

### 2022-11-24 scripts/utils/georectify.py

@@ -21,7 +21,7 @@ params = {"x":732731,"y":4051171, "z":2458, "fov":75, "pan":95, "tilt":0, "roll"
           "p1":0, "p2":0, "s1":0, "s2":0, "s3":0, "s4":0, \
           "w":5616, "h":3744, "cx":5616/2, "cy":3744/2}
 
-conn = sqlite3.connect("data/pointcloud.db")
+conn = sqlite3.connect(out_path)
 
 distance = 3000 # The radius of the fan shape
 chunksize = 1000000

### 2023-02-06 paper/UHETQ_1_24012023-0736624/Automatically_drawing_vegetation_classification_maps_using_digital_time_lapse_cameras_in_alpine_ecosystems/UHETQ_1_Automatically_drawing_vegetation_classification_maps_using_digital_time_lapse_cameras_in_alpine_ecosystems/paper.tex
updated

\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}

\title{Automatically drawing vegetation classification maps using digital time-lapse cameras in alpine ecosystems}

\author{
    Ryotaro Okamoto
    \thanks{\url{https://github.com/0kam}}
   \\
    Doctoral Program in Biology \\
    University of Tsukuba \\
  1-1-1 Tennodai, Tsukuba, Ibaraki 305-8577 Japan. \\
  \texttt{\href{mailto:okamoto.ryotaro.su@alumni.tsukuba.ac.jp}{\nolinkurl{okamoto.ryotaro.su@alumni.tsukuba.ac.jp}}} \\
   \And
    Reiko Ide
   \\
    Earth System Division \\
    National Institute for Environmental Studies, \\
  16-2 Onogawa, Tsukuba, Ibaraki 305-8506 Japan \\
  \texttt{\href{mailto:ide.reiko@nies.go.jp}{\nolinkurl{ide.reiko@nies.go.jp}}} \\
   \And
    Hiroyuki Oguma
   \\
    Biodiversity Division \\
    National Institute for Environmental Studies, \\
  16-2 Onogawa, Tsukuba, Ibaraki 305-8506 Japan \\
  \texttt{\href{mailto:oguma@nies.go.jp}{\nolinkurl{oguma@nies.go.jp}}} \\  
  }

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% From pandoc table feature
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

\usepackage{amsmath}
\usepackage{nicefrac}
\setlength{\parindent}{10.5pt}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\begin{document}
\maketitle

%TC:ignore
\begin{abstract}
Alpine ecosystems are particularly vulnerable to climate change. Monitoring the distribution of alpine vegetation is required to plan practical conservation activities. However, conventional field observations and satellite remote sensing are difficult in terms of coverage and frequency in alpine areas. Ground-based time-lapse cameras have been used to observe the regions' snowmelt and vegetation phenology and have significant advantages in terms of cost, resolution, and frequency. However, they have not been used in research monitoring the distribution patterns of vegetation. This study proposes a novel method for drawing georeferenced vegetation classification maps from ground-based imagery of alpine regions. Our approach had two components: vegetation classification and georectification. The proposed vegetation classification method uses a pixel time series acquired from fall images to utilize the fall leaf color patterns. We demonstrated that the performance of the vegetation classification can be improved by using time-lapse imagery and a Recurrent Neural Network. We also developed a novel method to accurately transform ground-based images into georeferenced data. We propose the following approaches: 1) an automated procedure to acquire Ground Control Points; and 2) a camera model that considers lens distortions for accurate georectification. We demonstrated that the proposed approach outperforms conventional methods, in addition to achieving sufficient accuracy to observe the vegetation distribution on a plant-community scale. The evaluation revealed an F1 score and root-mean-square error of 0.937 and 3.4 m in the vegetation classification and georectification, respectively. Our results highlight the potential of inexpensive time-lapse cameras to monitor the distribution of alpine vegetation. The proposed method can significantly contribute to the effective conservation planning of alpine ecosystems.
\end{abstract}
%TC:endignore

\keywords{
    alpine ecosystem
   \and
    deep learning
   \and
    ecosystem monitoring
   \and
    time-lapse camera
  }

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The effects of climate change on terrestrial ecosystems are particularly severe in alpine regions, and the consequences have already been documented globally. (\cite{IPCC2007}, \cite{Gottfried2012NatClimChange}, \cite{IPCCSR2019HM}). Alpine vegetation depends on severe conditions such as low temperatures and long snow-covered periods. Alpine areas have unique species that are adapted to such extreme environments. Several studies have reported that recent global climatic changes, such as increasing temperatures and reduced periods of snow cover, have accelerated the invasion of non-native species into alpine areas (see \cite{Alexander2016AlpBotany}). In the Taisetsu Mountains, northern Japan, dwarf bamboo (\emph{Sasa kurilensis}) has invaded alpine snow meadows, possibly driven by an extension of the snow-free period (\cite{Kudo2011EcoEvo}). Researchers have also predicted a decrease in suitable habitats for alpine snow meadows in this area (\cite{Amagai2022AVS}). Climate change has also affected the growth and phenology of native species. For example, the growth of dwarf pine (\emph{Pinus pumila}), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt timing (\cite{Amagai2015EcoRes}). In addition, such changes vary depending on the species and microhabitats (\cite{Kudo2010AAA}). Understanding and predicting changes in alpine vegetation requires a monitoring method scalable to a wide range with high spatiotemporal resolution.

Previous studies on alpine ecosystems have relied heavily on field observations; however, it is difficult to cover large areas in alpine regions due to poor accessibility and severe weather. Additionally, variance in alpine plant phenology complicates this problem. Strictly limited by snow cover, the growing season of alpine plants is typically very short, and their phenology varies greatly across years and microtopography (\cite{Kudo1991AAR}). Thus, it is difficult to plan observations by predicting plant phenology, rendering continuous observations over several months necessary. Satellite, airborne, and Unmanned Aerial Vehicle (UAV) remote-sensing methods appear to be alternatives. However, satellite imagery of alpine areas is rarely available because of cloud cover, and the spatial resolution is insufficient to observe vegetation changes at the plant community scale. Airborne imagery can be used to obtain high-resolution data, but frequent monitoring is restricted by its cost. Although UAV methods have become cost-effective tools for ecological monitoring (\cite{Baena2017PLOSONE}), continuous monitoring with UAVs in alpine regions is difficult because of severe weather.

Researchers have utilized automated digital time-lapse cameras mounted on the ground to monitor green-leaf phenology in forests (\cite{Richardson2009EcolAppl}), grasslands (\cite{Browning2017RemSen}), and alpine meadows (\cite{IdeOguma2013EcolInfom}). Unlike satellite imagery, ground-based cameras provide images free of cloud and atmospheric effects. In addition, they can obtain high-resolution (i.e., sub-meter scale) and frequent (i.e., daily or hourly) images at a low cost. Most previous studies using such cameras have calculated the phenology index (e.g., excess greenness, \cite{Woebbecke1995ASAE}) by setting some regions of interest (ROI) in the images. Few studies have utilized such images to monitor vegetation distributions. This is possibly because applying such time-lapse imagery to monitor vegetation distribution has two technical challenges. The first limitation is the spectral sensitivity of the camera. Ordinary digital cameras can only obtain three bands in the visible range (Red, Green, and Blue), rendering the accurate classification of vegetation difficult. However, researchers have reported that using multi/hyperspectral data, particularly in infrared regions, improves the accuracy of vegetation classification (\cite{Thenkabail2004RemSenEnv}, \cite{Schmidt2003RemSenEnv}). The second limitation is the availability of images in geospatial analyses. As digital time-lapse cameras are mounted on the ground, transforming the images into geospatial data (e.g., orthoimages; this process is called georectification) is challenging. That is, even if we classify vegetation from such images, we cannot quantitatively measure and analyze it using Geographic Information System (GIS) tools. Georectification is essential for utilizing time-lapse cameras in conservation planning.

This study proposes an automated method for drawing vegetation classification maps using a digital time-lapse camera by solving the two above-mentioned challenges. We solved the first challenge by using time-lapse images to classify vegetation. Fall leaf phenology, which varies among species, was used for classification. We demonstrated the effectiveness of such phenological information for vegetation classification. A novel georectification method for ground-based images was developed to address the second challenge. Using the proposed procedure, we generated a vegetation classification map from the time-lapse images of the Japanese Alps. Our approach enabled us to continuously monitor vegetation distribution and its changes at a plant-community scale, covering broad areas at a low cost.

\hypertarget{materials-and-methods}{%
\section{Materials and methods}\label{materials-and-methods}}

The proposed method comprises three steps:
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
Image-to-image alignment for correcting the movements of the camera.
\item
Vegetation classification for classifying each pixel into vegetation categories.
\item
Georectification for transforming vegetation classification results into geospatial data.
\end{enumerate}

Fig. \ref{fig:diagram} shows the overview of the entire process. The proposed method requires a training dataset to train the vegetation classification model, and, for the georectification process, a Digital Elevation Model (DEM), and a georectified airborne/satellite image that covers the camera's field of view.

\begin{figure}
\includegraphics[width=0.8\linewidth]{paper_files/figures/diagram} 
\caption{An overview of the proposed procedure. The cylinders, boxes, and hexagons represent the source data to prepare, procedures, and deliverables, respectively.}
\label{fig:diagram}
\end{figure}

\hypertarget{time-lapse-image-acquisition}{%
\subsection{Time-lapse image acquisition}\label{time-lapse-image-acquisition}}

Our approach is intended for digital time-lapse images of alpine landscapes. In this study, we demonstrated the approach using time-lapse images of a Japanese alpine region owned by the National Institute for Environmental Studies, Japan (NIES). All images are publicly available on the NIES webpage (\url{https://db.cger.nies.go.jp/gem/ja/mountain/statWeusedtml?id=2}). In 2010, NIES installed a digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) at a mountain lodge (Murodo-sanso; approximately 2450 m a.s.l. and above the forest limit), located at the foot of Mt. Tateyama (3015 m a.s.l.), in the northern Japanese Alps (Fig. \ref{fig:map}). The area is designated as a restricted zone within the Chubusangaku National Park. The images were taken hourly, from 6 a.m. to 7 p.m., in JPEG format. The camera's field of view (FoV) includes Mt. Tateyama, which ranges from approximately 2350–3015 m a.s.l. in elevation. The pixel size on the ground was approximately 0.5 m at the ridge, approximately 1 km from the camera. The area has a complex mosaic-like vegetation structure because of its topography and climate, including rocks, cliffs, curls, moraines, and heavy winter snow. From April–November, the camera recorded the snowmelt and seasonal phenology of evergreen (e.g., \emph{Pinus pumila}) and deciduous (\emph{Sorbus} sp., \emph{Acer tschonoskii}) dwarf trees, dwarf bamboos (e.g., \emph{Sasa kurilensis}), alpine shrubs, and herbaceous plants (e.g., \emph{Vaccinium ovalifolium}, \emph{Geum pentapetalum}, and \emph{Nephrophyllidium crista-galli}).

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/figures/Slide3} \caption{The location of the camera. (a) The location of Mt. Tateyama. (b) The installation point of the camera in Murodo-sanso lodge. (c) The camera (EOS 5D MK2, Canon Inc.)}\label{fig:map}
\end{figure}

\hypertarget{preprocessing}{%
\subsection{Preprocessing}\label{preprocessing}}

\hypertarget{image-selection}{%
\subsubsection{Image selection}\label{image-selection}}

Initially, we selected seven images with good weather from late summer to late fall (25 Aug; 5, 12, 20, and 26 September; 3 and 10 October) in 2015. To avoid the effects of shadows, we selected images from 11:00 a.m. to 2:00 p.m. As the temporal patterns of fall foliage coloration vary among species, this season is suitable for classifying vegetation. While acquiring a series of images is expensive with UAVs and airborne imagery, time-lapse cameras are particularly good at observing temporal patterns of leaf color at low cost.

\hypertarget{automatic-image-to-image-alignment}{%
\subsubsection{Automatic image-to-image alignment}\label{automatic-image-to-image-alignment}}

Time-lapse images often suffer from camera movement caused by strong winds, human interference, and thermal expansion of the camera platform. As such movements can result in errors in vegetation classification and georectification, we implemented an image alignment method that aligns one (source) image to another (target) image. The software was developed using Python3 and the OpenCV4 image processing library (\url{https://opencv.org/}). We employed the feature-based alignment method used in previous studies (\cite{Hulton2020PyTrx}, \cite{Portenier2020Cryosphere}). First, we searched and matched key points between the source and the target image using the AKAZE local feature extractor (\cite{Alcantarilla2013AKAZE}) and the K-nearest neighbor matcher. Then, we searched and applied the \(3 \times 3\) homography matrix \(H\) that minimizes the distance between each pair of the matching points, using OpenCV's ``findHomography'' function:
\begin{equation}
\label{homography}
  \begin{bmatrix} 
    U' \\ V' \\ 1
  \end{bmatrix}
  =
  H
  \begin{bmatrix}
    U \\ V \\ 1
  \end{bmatrix},
\end{equation}
where \([U', V', 1]\) and \([U, V, 1]\) represent the coordinates of the matching points on the target and source images, respectively. By setting one image as the target and the others as the source, the entire time-series imagery was aligned accurately (0.654 pixels in root mean square error (RMSE) of the matching points). Finally, an input mask was applied to define the image regions that should be ignored in the following procedure, such as the sky and regions too close to the camera. This process ensures that a pixel time series reflects phenological information about the exact location, which is essential in the vegetation classification process.

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/figures/Slide1} \caption{Pixel time series acquired from the time-lapse camera. A time series of pixel values (i.e., Red, Green, and Blue) for each pixel on the images (left) can be obtained. Since the images were taken in 8-bit JPEG format, the pixel values range from 0 to 255. The plots on the right show the pixel time series of 10 pixels randomly sampled for each class. Each line represents a pixel's value (Red, Green, or Blue, shown as the line color) sampled from manually annotated vegetation polygons that were used to train the vegetation classifier (see \ref{dataset-preparation} for more detail).  Such pixel time series reflect the fall phenology of the vegetation and vary among vegetation classes. For example, the high Red values on Maple and Rowans show the fall foliage. On the other hand, evergreen vegetation, such as Dwarf bamboo and Dwarf pine, show flat patterns in pixel values.}\label{fig:pixtimeseries}
\end{figure}

\hypertarget{vegetation-classification}{%
\subsection{Vegetation classification}\label{vegetation-classification}}

After image-to-image alignment, we stuck the images and extracted a time series of pixel values (Red, Green, and Blue, see Fig. \ref{fig:pixtimeseries}) for each pixel. Such pixel time series reflect the temporal patterns of leaf colors that vary among species. For example, Rowans (\emph{Sorbus sambucifolia, Sorbus matsumurana}), which turn red in the fall, exhibited high Red values at the end of September. Maple (\emph{Acer tschonoskii}), which turns yellow to orange and red in the fall, also has high Red values in September but with two peaks. This implies that Maple has intra-species variation in the timing of fall foliage. As deciduous plants show great interspecific variation in fall leaf phenology, researchers have used this information together with satellite imagery for vegetation classification (\cite{Son2013RemSen}, \cite{Tigges2013RemSenEnv}, \cite{Heupel2018PFG}). However, no study has applied this technique to ground-based time-lapse imagery. We implemented a Support Vector Machine- (SVM) and Recurrent Neural Network- (RNN) based vegetation classifiers and tested the effects of using the pixel time series from the ground-based imagery on the classification performance.

\hypertarget{model-architecture}{%
\subsubsection{Model Architecture}\label{model-architecture}}

We prepared two supervised models, SVM and RNN, to classify pixel time series into vegetation categories. The SVM is one of the most popular machine-learning models in remote sensing and has many applications (\cite{Mountrakis2011SVMReview}), including vegetation classification with multitemporal satellite imagery (\cite{Tigges2013RemSenEnv}). An RNN is a neural network that recurrently processes sequential or temporal steps of data to recognize their dynamics. Recurrent Neural Networks have been used in many tasks, such as speech recognition (\cite{Graves2013SpeechRNN}, \cite{Graves2014SpeechRNN}, \cite{Sak2014acousticLSTM}) and machine translation (\cite{Auli2013translationRNN}, \cite{Cho2014RNN}). Researchers have also utilized RNN for remote sensing tasks, such as land cover classification, with multitemporal satellite imagery (\cite{Ienco2017RemSenLSTM}, \cite{Sharma2018NN}). A previous study (\cite{Ienco2017RemSenLSTM}) reported that an RNN classifier outperformed an SVM classifier in terms of land cover classification accuracy. Among the many variants of RNN, we used Long Short-Time Memory (LSTM) \cite{Hochreiter1997LSTM}), which was also used in a previous study (\cite{Ienco2017RemSenLSTM}). The batch-normalization technique (\cite{IoffeSzegedy2015BatchNorm}) and GELU activation function (\cite{HendrycksGimpel2016GELU}) were employed to speed up and stabilize the model training. As a comparison, we also classified the pixels of every single image separately using SVM classifiers to test whether using multitemporal imagery improves the classification performance.

\hypertarget{dataset-preparation}{%
\subsubsection{Dataset preparation}\label{dataset-preparation}}

Each pixel time series was classified into seven vegetation classes: Dwarf Pine (\emph{Pinus pumila}), Dwarf Bamboo (\emph{Sasa kurilensis}), Rowans (\emph{Sorbus sambucifolia}, \emph{Sorbus matsumurana}), Maple (\emph{Acer tschonoskii}), Montane Alder (\emph{Alnus viridis} subsp. \emph{maximowiczii}), Other Vegetations (such as alpine shrubs and herbaceous plants), and No Vegetation. Experts prepared a training dataset for each class using open-source image annotation software (Semantic Segmentation Editor, Hitachi, \url{https://github.com/Hitachi-Automotive-And-Industry-Lab/semantic-segmentation-editor}). The prepared training dataset contained approximately 1.5 M pixels in 137 polygons, which covered approximately 7\% of the image. Each polygon was validated using a set of telephotos that overlapped with the camera's FoV. The telephotos were taken in the fall of 2014 using a Nikon D7100 camera (Nikon Corp.) with a 200 mm lens. Although we were able to observe the shape and texture of the plant community from the telephotos, some vegetation could not be identified without more detailed observation (such as of leaf shapes). We conducted a field survey in September 2022 to identify the vegetation types in these locations.

\hypertarget{experimental-settings}{%
\subsubsection{Experimental Settings}\label{experimental-settings}}

We implemented the classifiers using Python3 language. For the SVM classifier, we used the ThunderSVM library (\\ url{https://github.com/Xtra-Computing/thundersvm}) and a Radial Basis Function (RBF) kernel with a regularization parameter equal to 1.0. The gamma value of the RBF kernel was set automatically by the ``scaled`` setting of the ThunderSVM library as \(\gamma = \frac{1}{n_{features} \times V(X)}\), where \(n_{features}\) and \(V(X)\) represent the input data's dimensions and variance, respectively. The RNN classifier was developed using the PyTorch deep neural network library (\url{https://pytorch.org/}). The number of hidden dimensions was set to five. We trained the model for 200 epochs using the Rectified Adam optimizer (\cite{Liu2020RAdam}) with a learning rate of 0.001 and batch size of 500. To validate the performance of the different classifiers, we performed a 5-fold cross-validation. Each fold was stratified according to the vegetation category. As a model evaluation metric, we used the per-class F1-score, a standard metric in machine learning (\ref{f1score}). \(TP, FP, FN\) stand for the numbers of true positives, false positives, and false negatives, respectively. All the source codes are available via GitHub (\url{https://github.com/0kam/VegetationMapPaper}).

\label{f1score}
\begin{align}
\label{metrics}
  \begin{gathered}
  precision = \frac{TP}{TP + FP} \\
  recall = \frac{TP}{TP + FN} \\
  F_1 = \frac{2 \cdot precision \cdot recall}{precision + recall} \\
  \end{gathered}
\end{align}

\hypertarget{automatic-georectification}{%
\subsection{Automatic georectification}\label{automatic-georectification}}

The second challenge of utilizing time-lapse cameras in vegetation monitoring is the difficulty of georectification, that is, georeferencing and transforming images into geographic data. That is, georectification refers to aligning images onto Digital Surface Models (DSMs) so that every pixel of an image gets a geographical coordinate. This typically requires a camera model. Georectification of ground-based images has been a difficult task, which has led to the underutilization of the potentially rich information in ground-based imagery. We developed a novel method for performing this process automatically and accurately. We considered a camera as a function that transforms 3D geographical coordinates (e.g., X, Y, and Z (height) in a Universal Transverse Mercator coordinate system (UTM)) into 2D image coordinates (locations of each pixel in the image). By estimating the parameters of this function (such as camera location, pose, and FoV, one can simulate how each point of the DSM appears in the image. Georectification usually has three steps:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Finding Ground Control Points (GCPs) in the image.
\item
  Estimating the camera parameters, such as the camera pose and FoV, using GCPs.
\item
  Projecting the image onto the DSM using the camera parameters.
\end{enumerate}

Researchers have recently developed georectification methods to use ground-based images in glaciology (\cite{Messerli2015GeoInst}, \cite{Hulton2020PyTrx}) and snow cover studies (\cite{Portenier2020Cryosphere}). Typically, Global Navigation Satellite System- (GNSS)positioned GCPs (such as GCP markers) are set before image acquisition. However, setting such markers in alpine areas is often difficult owing to their rugged topography. \cite{Portenier2020Cryosphere} tackled this problem by developing a method that uses mountain silhouettes to match an image and a DSM directly. However, this silhouette-based method has a drawback in terms of projection accuracy; it ignores lens distortion and uses only limited areas (silhouettes) of images in the GCP acquisition. To overcome this drawback, this study proposes a camera model that includes lens distortion and a novel method to acquire GCPs in a broader area than that of the silhouette-based method.

\hypertarget{modeling-and-estimating-camera-parameters}{%
\subsection{The camera model}\label{modeling-and-estimating-camera-parameters}}

In this section, we explain our camera model, which considers lens distortion. As mentioned previously, we modeled a camera as a function that transforms geographical coordinates into image coordinates. This procedure was implemented using the OpenGL framework (\url{https://www.opengl.org}) and the ModernGL Python library (\cite{moderngl}) to accelerate it using graphical processing units (GPUs). In OpenGL, this process can be separated into three steps.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Transforming the geographical coordinates (also called the world coordinates) to the view coordinates (coordinates seen from the camera's point of view) using the camera's extrinsic parameters (i.e., the location and angles of the camera).
\item
  Distorting the view coordinates using the lens distortion parameters.
\item
  Transforming the view coordinates into the image coordinates (also called the screen coordinates) using the camera's intrinsic parameters (i.e., the camera's FoV).
\end{enumerate}

First, we transformed the geographic coordinates into view coordinates relative to the camera's position and direction. We used a \(4 \times 4\) view matrix (Eq. \ref{view_matrix}) \(M_{view}\) in this step. The view matrix represents the camera position and direction (pan, tilt, and roll):

\begin{equation}
\label{view_matrix}
  M_{view} = 
  \begin{bmatrix}
    \cos roll & -\sin roll & 0 & 0 \\
    \sin roll & \cos roll & 0 & 0 \\
    0 & 0 & 1 & 0 \\
    0 & 0 & 0 & 1 \\
  \end{bmatrix}
  \begin{bmatrix}
    1 & 0 & 0 & 0 \\
    0 & \cos tilt & -\sin tilt & 0 \\
    0 & \sin tilt & \cos tilt & 0 \\
    0 & 0 & 0 & 1 \\
  \end{bmatrix}
  \begin{bmatrix}
    \cos pan & 0 & \sin pan & 0 \\
    0 & 1 & 0 & 0 \\
    -\sin pan & 0 & \cos pan & 0 \\
    0 & 0 & 0 & 1 \\
  \end{bmatrix}
  \begin{bmatrix}
    1 & 0 & 0 & -x \\
    0 & 1 & 0 & -z \\
    0 & 0 & 1 & -y \\
    0& 0 & 0 & 1 \\
  \end{bmatrix},
\end{equation}
where \(pan, tilt, roll\) are the Euler angles of the camera pose and \(x, y, z\) are the camera location in the geographic coordinate system. Applying the view matrix \(M_{view}\) transforms the geographic coordinates \(\begin{bmatrix} X_{geo} & Z_{geo} & Y_{geo} & 1 \end{bmatrix}\) (the horizontal, vertical, and depth coordinates, respectively) into the view coordinates \(\begin{bmatrix} X_{view} & Z_{view} & Y_{view} & 1 \end{bmatrix}\) (Eq. \ref{view_tf}). In the OpenGL's view coordinate system, \(X_{view}\), \(Z_{view}\) and \(Y_{view}\) represent the horizontal, vertical, and depth positions, respectively. Note that the geographic coordinate system must be cartesian (such as the UTM coordinate systems) and not the lat/long coordinate system.

\begin{equation}
\label{view_tf}
  \begin{bmatrix} 
    X_{view} \\ Z_{view} \\ Y_{view} \\ 1 
  \end{bmatrix}
  =
  M_{view}
  \begin{bmatrix} 
    X_{geo} \\ Z_{geo} \\ Y_{geo} \\ 1 
  \end{bmatrix}
\end{equation}

Second, we distorted the view coordinates to simulate lens distortion. We modeled the lens distortion (Eq. \ref{dist_model}) based on \cite{Weng1992CameraCalib} and OpenCV's implementation (\url{https://docs.opencv.org/4.x/d9/d0c/group__calib3d.html}), where \(X_{norm}\) and \(Z_{norm}\) are the \(Y\)-normalized view coordinates. This model distorts the point locations according to the distance from the center of the image. Our model includes radial (\(k1\)\textasciitilde{}\(k6\)), tangential (\(p1\), \(p2\)), thin prism (\(s1\)\textasciitilde{}\(s4\)) distortion, and unequal pixel aspect ratios (\(a1\), \(a2\)). See \cite{Weng1992CameraCalib} for details on lens distortion modeling.

\begin{gather}
\label{dist_model}
  \begin{gathered}
  X_{norm} = \frac{X_{view}}{Y_{view}} \\
  Z_{norm} = \frac{Z_{view}}{Y_{view}} \\
  r^2 = {X_{norm}}^2 + {Z_{norm}}^2 \\
  \begin{bmatrix}
    X_{dist\_norm} \\ 
    Z_{dist\_norm} \\
  \end{bmatrix} 
  = 
  \begin{bmatrix} 
    X_{norm} \frac{1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + k_4 r^2 + k_5 r^4 + k_6 r^6} + 2 p_1 x’ y’ + p_2(r^2 + 2 x’^2) + s_1 r^2 + s_2 r^4 \\ 
    Z_{norm} \frac{1 + a_1 + k_1 r^2 + k_2 r^4 + k_3 r^6}{1 + a_2 + k_4 r^2 + k_5 r^4 + k_6 r^6} + p_1 (r^2 + 2 y’^2) + 2 p_2 x’ y’ + s_3 r^2 + s_4 r^4 \\    \end{bmatrix} \\
  X_{dist} = X_{dist\_norm} Y_{view} \\
  Z_{dist} = Z_{dist\_norm} Y_{view} \\
  \end{gathered}
\end{gather}

Finally, we transformed the distorted view coordinates into image coordinates using perspective projection. During the perspective projection, a closer object is drawn larger. We used a \(4 \times 4\) projection matrix \(M_{proj}\) (Eq. \ref{proj_mat}), that represents the camera's horizontal (\(fov_x\)) and vertical (\(fov_z\)) FoV. Finally, we obtained the image coordinates as [\(X_{image}, Z_{image}\)] in Eq. \ref{proj_tf}.

\begin{gather}
\label{proj_mat}
  \begin{gathered}
  f_x = \frac{1}{\frac{\tan fov_x}{2}} \\
  f_z = \frac{1}{\frac{\tan fov_z}{2}} \\
  M_{proj} = 
  \begin{bmatrix} 
    f_x & 0 & 1 & 0\\ 
    0 & f_z & -1 & 0 \\ 
    0 & 0 & 0 & 1\\ 
    0 & 0 & -1 & 0 
  \end{bmatrix}
  \end{gathered}
\end{gather}

\vskip\baselineskip

\begin{equation}
\label{proj_tf}
  \begin{bmatrix} 
    X_{image} \\ Z_{image} \\ Y_{image} \\ 1 
  \end{bmatrix}
  =
  M_{proj}
  \begin{bmatrix} 
    X_{dist} \\ Z_{dist} \\ Y_{view} \\ 1 
  \end{bmatrix}
\end{equation}

\hypertarget{image-matching-based-aqcuisition-of-gcps}{%
\subsection{Image-matching-based aqcuisition of GCPs}\label{image-matching-based-aqcuisition-of-gcps}}

One of the weaknesses of the silhouette-based method is its low levels of accuracy on mountainsides. We developed a novel image-matching-based method for acquiring GCPs in a broader area. Prior to processing, an orthorectified airborne/satellite image (orthophoto), a DSM that covers the camera's field of view, and a set of initial camera parameters (roughly estimated camera parameters) must be prepared. The proposed method comprises two parts: 1) Rendering a simulated landscape image, and 2) matching the simulated and original images. In the first step, we rendered a simulated landscape image by applying the camera model to the DSM and orthophoto (Fig. \ref{fig:matched}, right). Every pixel in the simulated image had a geographic coordinate. In the second step, an image taken simultaneously with the orthophoto (original image) was selected from the aligned images. We then searched for matching key points between the original image and the simulated image (Fig. \ref{fig:matched}) by the same feature-based method used in the image-to-image-alignment process. Because these matching points have both geographical coordinates (from the DSM) and image coordinates (from the original image), we used them as GCPs. This method enabled us to automatically acquire GCPs in a much broader area than the silhouette-based method. Importantly, the original image should be captured in the same season as the orthophoto to maximize the number of matching points obtained,. Furthermore, the accuracy of GCPs may be affected by the quality of the DSM and the orthorectification accuracy of the orthophoto.

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/figures/Slide4} \caption{Automatic acquisition of GCPs. The original image (left) and the simulated image (right). The simulated image was rendered with an orthophoto, DSM, and initial camera parameters. Red points show the matching points. We used these points as GCPs.}\label{fig:matched}
\end{figure}

\hypertarget{camera-parameter-estimation}{%
\subsection{Camera parameter estimation}\label{camera-parameter-estimation}}

The acquired GCPs were used to estimate the camera parameters of the images. By applying the camera model to the geographical coordinates of the GCPs (\(X, Y, Z\) in Fig. \ref{fig:optim}), the reprojected image coordinates can be calculated with a set of camera parameters. The distance from the actual image coordinates of the GCPs (\(U, V\) in Fig. \ref{fig:optim}) to the reprojected image coordinates (\(U', V'\) of Fig. \ref{fig:optim}) can then be measured. We estimated the camera parameters by minimizing this distance using a Covariance Matrix Adaptation Evolution Strategy (CMA-ES, \cite{Hansen2003CMAES}, Fig. \ref{fig:optim}). A CMA-ES performs well in optimizing a complex multimodal function with fewer parameters to be set. We were unable to estimate the camera location as it increased the complication of the problem (e.g., a telephoto taken from a distance and a wide-angle taken from a close look similar).

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/figures/Slide5} \caption{Workflow of the camera parameter optimization. We estimated the camera parameters by minimizing the GCP's reprojection error.}\label{fig:optim}
\end{figure}

\hypertarget{georectification-of-the-vegetation-map}{%
\subsection{Georectification of the vegetation classification map}\label{georectification-of-the-vegetation-map}}

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/figures/Slide6} \caption{Our georectification procedure. We applied the optimized camera parameters to the DSM and the vegetation classification result to get a vegetation classification map.}\label{fig:georec}
\end{figure}

Finally, we georectified the vegetation classification results using the optimized camera parameters (Fig. \ref{fig:georec}). At this point, we obtained the point data for the vegetation types(as shown in the table on the right of Fig. \ref{fig:georec}, where every row represents a pixel of the original image). We converted the point data into raster data to measure the area of each vegetation class. We rasterized the point data at a resolution of 1 m and then interpolated holes up to 2 m because the maximum pixel footprint was approximately 2 m on the ridge of the mountain. This rasterization procedure was implemented using the R  (\cite{Rcore}) ``stars''  (\cite{Rstars}) and ``terra'' (\cite{Rterra}) packages. See \url{https://github.com/0kam/VegetationMapPaper/blob/master/scripts/utils/interpolate.R} for the source code.

\hypertarget{implementation-and-evaluation}{%
\subsection{Implementation and evaluation}\label{implementation-and-evaluation}}

We implemented the proposed procedure using Python3 and published it as an open-source package via GitHub (\url{https://github.com/0kam/alproj}). We used an airborne image and DSM in the GCP acquisition process. The Japanese Forestry Agency captured airborne images in the fall of 2010 and orthorectified them using a digital elevation model (DEM) produced by airborne laser scanning. This DEM was also used as the DSM in the GCP acquisition and georectification processes. The airborne image and DSM had spatial resolutions of 0.2 m and 2 m, respectively, and were both resampled to a resolution of 1 m.

The accuracy of the georectification method was tested. We manually searched 83 matching points between the simulated and original images and treated them as test GCPs (i.e., GCPs that were not used in the georectification process). First, we used the silhouette-based matching method (hereafter referred to as the silhouette method) used in the previous study (\cite{Portenier2020Cryosphere})to demonstrate the benefits of the image-matching-based GCP acquisition method. That is, we considered lens distortion in the silhouette, whereas \cite{Portenier2020Cryosphere} did not. Second, our method without the lens distortion model (hereafter referred to as no distortion) was used to evaluate the advantages of the lens distortion model. We evaluated the projection errors of the test GCPs using these three methods.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{vegetation-classification-accuracy}{%
\subsection{Vegetation classification accuracy}\label{vegetation-classification-accuracy}}

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/figures/cv} \caption{The per-class F1-scores of the vegetation classification. Each box plot shows the results of a 5-fold cross-validation. We classified each pixel of a single image (shown as the shooting date) with SVM classifiers, and pixel time series with SVM (shown as ``Multidays'') and RNN (shown as ``Multidays RNN'') classifiers.}\label{fig:vegeacc}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/figures/vege} \caption{Left: Vegetation classification results of the RNN model. The masked area, i.e., the sky and the regions too close to the camera, is shown in black. Right: The generated vegetation classification map. The background shows contour lines.}\label{fig:vegetation}
\end{figure}

Fig. \ref{fig:vegeacc} shows the results of the 5-fold cross-validation. When focusing on a single-day classification (shown as the shooting date), the best classification date differed between classes. For example, September 26 was the best for identifying Rowans, but October 10 was the best for identifying Dwarf Pine and Dwarf Bamboo. The fall colorization of Rowans was best on September 26, and most vegetation (except Dwarf Bamboo and Dwarf Pine) was blasted on October 10. No single image could accurately classify Maple or Montane Alder. In contrast, using all images (shown as ``Multidays'' and ``Multidays RNN'' representing the SVM and RNN classifiers, respectively) resulted in a high F1 score in every class. In addition, the RNN classifier outperformed the SVM classifier ( macro average F1 scores of 0.937 and 0.918, respectively). Fig. \ref{fig:vegetation} (left) shows the products of the RNN classifier. We observed the distribution of each vegetation class at the plant-community scale.

\hypertarget{georectification-accuracy}{%
\subsection{Georectification accuracy}\label{georectification-accuracy}}

The proposed method achieved accurate projection (RMSE = 3.45 m), whereas the other methods did not (RMSE = 16.1 m and 23.6 m using the silhouette and no distortion methods, respectively). We also checked the relationship between the projection error and the distance from the shooting point for each test GCP (Fig. \ref{fig:geoacc})to examine our method's georectification error. The projection error was particularly large in the GCPs near the shooting point. Fig. \ref{fig:vegetation} (right) shows the produced vegetation classification map. The vegetation classification map has missing areas because ridges blocked the view of the camera.

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/figures/georec_acc} \caption{The projection error of the proposed method. The projection error was particularly large in the area near the camera.}\label{fig:geoacc}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

We proposed a low-cost automated procedure to transform time-lapse images of alpine regions into georeferenced vegetation classification maps. Two aspects made this a challenging task: 1) the difficulty of classifying vegetation using ordinal digital camera imagery, and 2) the difficulty of georectifying such ground-based imagery. We solved these issues by: 1) using the temporal information of fall leaf colors for vegetation classification, and 2) developing a novel method for accurate image georectification. The proposed methods performed functionally (0.937 mean F1 Score of vegetation classification and 3.4 m mean projection error of georectification,) and the vegetation classification map could be used in monitoring the vegetation distributions at a plant-community scale.

\hypertarget{the-benefit-of-using-time-series-imagery-for-vegetation-classification}{%
\subsection{The benefit of using time-series imagery for vegetation classification}\label{the-benefit-of-using-time-series-imagery-for-vegetation-classification}}

One of the shortcomings of ordinary digital cameras is that they have only three bands (Red, Blue, and Green). We compensated for this lack of information by using the rich temporal information that time-lapse data collection offers. Many plant species have characteristic phenologies, such as fall foliage, and the suitable season to observe them differs among species. The accuracy of the single-day classification (see shooting dates in Fig. \ref{fig:vegeacc}) shows that the best time for identification from the images varied with vegetation class. Classifying multiple vegetation classes requires long-term (e.g., several months) and frequent (such as daily) monitoring, and digital time-lapse cameras are suitable for this purpose. In addition, combining multitemporal images improved the classification accuracy, especially for Maple and Montane Alder. The best F1 score achieved using the single-day classification was low (0.750 for Montane Alder, 0.345 for Maple), whereas it was improved significantly (0.951 and 0.781 with the SVM classifier) by using multitemporal images. This shows that identifying these classes requires multitemporal information. As indicated in a previous study (\cite{Ienco2017RemSenLSTMn the RNN model outperformed the SVM model. This result was particularly noticeable for Maple (0.781 with SVM and 0.831 with RNN), which exhibited intraspecies variation in fall foliage timings. We found a weak correlation between two Maple pixel time series with different fall foliage timings but a strong temporal correlation. This may explain why the SVM model could not correctly detect Maple: it ignores the temporal correlation of the data, while the RNN model does not. However, our model can still be improved further. As (\cite{Sharma2018NN}) claimed, patch-based classification methods may improve performance. Such patch-based models use a time series of small patches as input to utilize the spatial information, such as textures, in the classification process.

\hypertarget{the-performance-of-the-georectification-method-and-its-limitation.}{%
\subsection{The performance of the georectification method and its limitation.}\label{the-performance-of-the-georectification-method-and-its-limitation.}}

The most significant barrier to using ground-based imagery in ecological monitoring is the difficulty of treating it as geospatial data. Therefore, an automated and accurate georectification method is required to overcome this challenge. Without georectification, we cannot quantitatively analyze (e.g., measure the area, locate the place, or analyze the topographic data) the acquired information, such as vegetation distribution. We propose a novel method to georectify such imagery. With minimal manual user inputs (i.e., the camera location and initial camera parameters), our approach achieved a very high level of accuracy (3.45 m). We tested the effectiveness of two features of our method: the lens distortion model and the image-matching-based method for acquiring GCPs.

The results demonstrate that the lens distortion model significantly improved the georectification accuracy. Without the lens distortion model, our model resulted in a projection accuracy of 23.6 m. However, as the effect of lens distortion on the georectification accuracy is different among cameras and lenses (\cite{Portenier2020Cryosphere}), further testing will be required. Another feature of our method is the automatic acquisition of GCPs using simulated images and image-matching techniques. A high-resolution orthophoto that covers the field of view of the camera is required. This is quite expensive, but the reward is considerable. The conventional silhouette-based method resulted in an RMSE of 16.1 m. This suggests that acquiring matching points between the image and DSM in a broader area benefits the camera parameter estimation process.

However, our method has some limitations. The proposed lens distortion model does not support a fisheye lens or omnidirectional camera. Focusing on the GCP acquisition method, we assumed that the landscape (e.g., topography and vegetation cover) would appear the same between the original and simulated images. While we employed a robust matching method, significant changes in the mountain terrain (such as those caused by landslides) may cause a matching error. Slight changes in vegetation cover may also affect the quality of the GCPs. However, the negative effect (a few meters) of using these points as GCPs should be much smaller than the positive effect (approximately 12.6 m). In addition, the AKAZE image matcher could not acquire matching points in the area near the camera, and here the projection error was relatively large (Fig. \ref{fig:geoacc}). While the spatial resolution of the simulated image depends on the orthophoto and is constant (in this study, 1 m), that of the original image changes depending on the distance from the camera. In areas near the camera, the spatial resolution of the original image is much higher than that of the simulated image, and the image matcher cannot handle this difference. Recently, researchers developed deep-learning-based image-matching methods (e.g., \cite{Yang2018ImageMatching}, \cite{Wu2013AEImageMatching}) that are more robust in terms of differences in image sources and viewpoints. Applying these methods to the GCP acquisition process may improve the performance of our method, especially in nearby areas.

Theoretically, our approach can handle images of other ecosystems, such as forests. However, this may be difficult because georectification accuracy strongly depends on the accuracy of the DSM. Because alpine plants tend to be very short, readily available Digital Elevation Models (DEMs) can be used as DSMs. In forestry areas, vegetation height is considerable, and the gap between the DEMs and the actual surface (top of the forest) may cause significant errors in the georectification process.

\hypertarget{future-application-and-conclusion}{%
\subsection{Future application and conclusion}\label{future-application-and-conclusion}}

In this study, we propose an automated method to draw a vegetation classification map from a series of images acquired using a digital time-lapse camera. The vegetation classification map had sufficient accuracy for monitoring endemic and vulnerable alpine vegetation. One benefit of digital time-lapse cameras is their long-term operability. Applying the proposed method to existing long-term time-lapse imagery will enable researchers to quantitatively understand vegetation changes and their trends. This information will help researchers and stakeholders plan field observations and conservation activities more effectively. Our methods facilitate cost-efficient monitoring of alpine vegetation and understanding the impacts of climate change on alpine ecosystems.

%TC:ignore
\hypertarget{acknowledgement}{%
\section*{Acknowledgement}\label{acknowledgement}}
The authors would like to thank Tohru Ohmiya and Hisashi Sugita for their help with field observations and validation of the training dataset.
%TC:endignore

\bibliographystyle{unsrt}
\bibliography{export.bib}

\end{document}

### 2023-02-06 data_source/align_photographs.py

@@ -1,0 +1,114 @@
+import cv2
+import numpy as np
+from glob import glob
+import os
+import pandas as pd
+from tqdm import tqdm
+
+def homography(src_img, dst_img, flann = True, ransac_th=5):
+    im1 = src_img
+    im2 = dst_img
+    # Akaze descripter
+    akaze = cv2.AKAZE_create()
+    kp1, des1 = akaze.detectAndCompute(im1, None)
+    kp2, des2 = akaze.detectAndCompute(im2, None)
+    if flann:
+        # Flann matcher
+        FLANN_INDEX_LSH = 6
+        index_params= dict(algorithm = FLANN_INDEX_LSH,
+                          table_number = 6,  
+                          key_size = 12,     
+                          multi_probe_level = 1) 
+        search_params = dict(checks = 50)
+        matcher = cv2.FlannBasedMatcher(index_params, search_params)
+    else: 
+        # Brute Force matcher
+        matcher = cv2.BFMatcher()
+    matches = matcher.knnMatch(des1, des2, k = 2)
+    ratio = 0.75
+    good = []
+    # Filter matching points
+    for m, n in matches:
+        if m.distance < ratio * n.distance:
+            good.append(m)
+
+    pts1 = np.float32([ kp1[match.queryIdx].pt for match in good ])
+    pts2 = np.float32([ kp2[match.trainIdx].pt for match in good ])
+    pts1 = pts1.reshape(-1,1,2)
+    pts2 = pts2.reshape(-1,1,2)
+
+    # Find homography matrix
+    hmat, mask = cv2.findHomography(pts1, pts2, cv2.RANSAC, ransac_th)
+    pts1 = pts1[mask.astype('bool')]
+    pts2 = pts2[mask.astype('bool')]
+    
+    # Culculate Root Mean Square Error
+    pts1 = pts1.reshape(-1,2)
+    pts2 = pts2.reshape(-1,2)
+    pts1 = np.insert(pts1, 2, 1, axis = 1)
+    pts1 = np.dot(hmat, pts1.T).T
+    pts1[:,0] = pts1[:,0] / pts1[:,2]
+    pts1[:,1] = pts1[:,1] / pts1[:,2]
+    pts1 = pts1[:,0:2]
+    rmse = np.mean(((pts1[:,0] - pts2[:,0])**2 + (pts1[:,1] - pts2[:,1])**2)**0.5) 
+    
+    # Homography Transformation 
[…]

### 2023-02-06 data_source/as_animation.py

@@ -1,0 +1,6 @@
+from PIL import Image
+from glob import glob
+
+images = [Image.open(i).convert("P", palette=Image.ADAPTIVE, colors=256) for i in sorted(glob("data_source/source/2020/*"))]
+images = [i.resize((800,600), Image.BICUBIC) for i in images]
+images[0].save("data_source/2020.gif", save_all=True, append_images=images[1:],  duration=300, loop=0)

### 2023-02-06 data_source/mask_sky.py

@@ -1,0 +1,15 @@
+import cv2
+
+path = "data_source/source/2015/mrd_085_eos_vis_20150905_1405.JPG"
+
+img = cv2.imread(path)
+gray = cv2.cvtColor(img, cv2.COLOR_BGR2GRAY)
+for i in range(gray.shape[1]):
+    for j in range(gray.shape[0]):
+        if gray[j, i] >= 250:
+            gray[j, i] = 0
+        else:
+            break
+
+img[gray==0,:] = 0
+cv2.imwrite("data_source/sky_mask_2015.png", img)

### 2023-02-06 scripts/diagraph.R

@@ -3,12 +3,20 @@ library(DiagrammeR)
 grViz("
   digraph procedure {
     image[
-      label = 'Time-Lapse Images'  ,
+      label = 'Time-Lapse Images',
       shape = cylinder
     ];
     teacher[
-      label = 'Teacher Dataset',
-      shape = tab
+      label = 'Training Dataset',
+      shape = hexagon
+    ];
+    cv[
+      label = 'Cross-Validation',
+      shape = box
+    ];
+    classifier[
+      label = 'Classifier',
+      shape = hexagon
     ];
     selection[
       label = 'Image Selection',
@@ -22,9 +30,17 @@ grViz("
       label = 'Vegetation Classification',
       shape = box
     ];
-    dem[
-      label = 'DEM',
+    dsm[
+      label = 'DSM',
       shape = cylinder
+    ];
+    sim[
+      label = 'Simulated Image',
+      shape = hexagon
+    ];
+    gcp[
+      label = 'GCP acquisition',
+      shape = box
     ];
     airborne[
       label = 'Airborne/Satellite Image',
@@ -36,16 +52,26 @@ grViz("
     ];
     vegemap[
       label = 'Vegetation Classification Map',
-      shape = tab
+      shape = hexagon
     ];
     
-    {rank = same; alignment; teacher;}
-    {rank = same; georec, dem, airborne;}
-    
-    image -> selection -> alignment -> classification -> georec -> vegemap
-    alignment -> teacher [dir = none];
-    teacher -> classification
-    dem -> georec
-    airborne -> georec
+    {rank = same; teacher; alignment; dsm; airborne;}
+    {rank = same; cv; sim;}
+    {rank = same; classifier; classification; gcp;}
+    subgraph c {
+        teacher -> cv -> classifier
+    }
+    subgraph g {
+        dsm -> sim -> gcp
+        airborne -> sim
+    }
+    subgraph main {
+      image -> selection -> alignment -> classification -> georec -> vegemap
+    }
+    alignment -> teacher
+    dsm -> georec
+    gcp -> georec
+    alignment -> gcp
+    classifier -> classification
   }
 ")

### 2023-02-06 scripts/models/model_comparison.R

@@ -82,7 +82,7 @@ df <- df %>%
 p1 <- df %>%
   filter(vegetation != "Macro Average") %>%
   filter(vegetation != "Weighted Average") %>%
-  mutate(date = as.character(date)) %>%
+  mutate(date = str_c(str_pad(month(date), 2, pad="0"), "/", day(date))) %>%
   mutate(date = ifelse(is.na(date), "Multidays", date)) %>%
   mutate(date = ifelse(str_detect(path, "rnn"), "Multidays RNN", date)) %>%
   ggplot(aes(x = date, y = value)) +
@@ -99,7 +99,9 @@ p1 <- df %>%
     panel.spacing = grid::unit(2, "lines")
   )
 
-ggsave(file = "results/cv.png", plot = p1, width = 12, height = 6)
+p1
+
+ggsave(file = "results/cv.png", plot = p1, width = 14, height = 8)
 
 df %>% 
   filter(metrics == "f1-score") %>%

### 2023-02-06 scripts/plot_phenology.R

@@ -30,12 +30,12 @@ df %>%
   write_csv("results/phenology.csv")
 
 df <- read_csv("results/phenology.csv") %>%
-  mutate(vegetation = ifelse(vegetation == "Golden Birch", "Maple", vegetation))
+  mutate(vegetation = ifelse(vegetation == "Golden Birch", "Maple", vegetation)) %>%
+  mutate(date = str_c(str_pad(month(date), 2, pad="0"), "/", day(date)))
 
 p <- df %>%
   mutate(band = factor(band, levels = c("R", "G", "B"))) %>%
   mutate(id = str_c(index, band)) %>%
-  mutate(date = as.character(date)) %>%
   ggplot() +
   geom_line(aes(x = date, y = value, colour = band, group = id)) +
   facet_wrap(~ vegetation, nrow = 3) +

### 2023-02-06 scripts/utils/georectify.py

@@ -126,3 +126,7 @@ for target in targets:
     georectified = georectified[georectified["vegetation"]!=0]
     out = target.replace("npy", "csv")
     georectified.to_csv(out, index=False)
+
+
+
+# draw mask

### 2023-02-06 scripts/utils/utils.py

@@ -34,12 +34,6 @@ def read_sses(label_dir, image_size, label="all"):
         (width, height) of the specified image
     label : str or list of str
         list of labels to use. If "all" (default), use all labels
-    shrink : int
-        shrink size in pixels  
-    hmat : np.array
-        homography matrix to apply
-    mask : np.array
-        mask to apply
     Returns
     -------
     image : np.array
